---
title: "Attention pilots"
author: "Marjan Biria"
date: "2023-12-09"
output: 
    pdf_document:
    toc: true
    toc_depth: 2
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(root.dir = "aim_lab_1", echo = TRUE)
```


```{r echo=FALSE, warning=FALSE, message=FALSE}
library(dplyr)
library(ggplot2)
library(tidyr)
library(lme4)
library(parameters)
library(broom.mixed)
library(lmerTest)
```

\newpage
# Attention pilot 1: study description
In this pilot we tested people on the attention pilot, where no feedback was provided and no prediction was collected. We have m_hist, anxiety, mood and certainty ratings for this pilot. This is the experiment on Gorilla: https://app.gorilla.sc/admin/project/115369
This is the task version used: https://app.gorilla.sc/admin/task/712861/editor?version=3  
The Externally focused attention condition was presented first, followed by the internally focused attention. Each condition had 24 trials. I will keep the mood and anxiety ratings before they start the task to look at baseline anxiety and mood in the following analysis.

```{r echo=FALSE, warning=FALSE, message=FALSE}
df_att <- read.csv("/Users/marjan/Desktop/aim_lab_1/SUP_PRF_pilot_no_fdbk_attention_vid/SUP_PRF_pilot_no_fdbk_attention_vid_v3/SUP_PRF_pilot_no_fdbk_attention_vid_v3_task_main.csv")
df_att_spin <- read.csv("/Users/marjan/Desktop/aim_lab_1/SUP_PRF_pilot_no_fdbk_attention_vid/SUP_PRF_pilot_no_fdbk_attention_vid_v3/SUP_PRF_pilot_no_fdbk_attention_vid_v3_mini_spin.csv")

df_att <- df_att[, c("Event.Index", "Trial.Number", "Random_ID", "Spreadsheet..Histogram", "Screen", "Display", "Response", "Response.Type", "Object.ID" )]
df_att <- df_att %>% dplyr::filter(Random_ID != "SUPPRF17915")
df_att_spin <- df_att_spin %>% dplyr::filter(Random_ID != "SUPPRF17915")

# let's also exclude the mood and anxiety ratings during practice
df_att <- df_att %>% dplyr::filter(!Event.Index %in% c(15, 17))
```

```{r echo=FALSE, warning=FALSE, message=FALSE}

df_att$m_hist <- case_when(
  df_att$Spreadsheet..Histogram == "h1.png" ~ 20,
  df_att$Spreadsheet..Histogram == "h2.png" ~ 29,
  df_att$Spreadsheet..Histogram == "h3.png" ~ 37,
  df_att$Spreadsheet..Histogram == "h4.png" ~ 46,
  df_att$Spreadsheet..Histogram == "h5.png" ~ 54,
  df_att$Spreadsheet..Histogram == "h6.png" ~ 63,
  df_att$Spreadsheet..Histogram == "h7.png" ~ 71,
  df_att$Spreadsheet..Histogram == "h8.png" ~ 80,
  TRUE ~ NA_real_
)

df_att <- df_att %>%
  dplyr::filter(
    (Display == "Trials - Externally Focused Attention") |
    (Display == "Trials - Self Focused Attention") |
    (Display == "Anxiety ") |
    (Display == "Mood ") 
  )

df_hist <- df_att %>%
  filter(Screen == "Introducing judge") %>%
  select(Event.Index, Response.Type, Object.ID, Random_ID, Trial.Number, Screen, Display, m_hist, Spreadsheet..Histogram)

df_hist <- df_hist %>%
  mutate(Screen = ifelse(Screen == "Introducing judge", "m_hist", Screen))

df_hist_modified <- df_hist %>%
  select(Event.Index, Random_ID, Spreadsheet..Histogram, Trial.Number, m_hist, Screen, Display, Response.Type, Object.ID) %>%
  dplyr::rename(Response = m_hist)

df_hist_modified <- df_hist_modified %>%
  mutate(Response = as.character(Response))

df_attention <- bind_rows(df_att, df_hist_modified)


# setting Mood and Anxiety trial numbers to start from 0 for baseline, and 1 for task, also making sure we match the anxiety and mood trials with the experiment trials
# experiment trials run from 1-24 per condition whereas for mood and anxiety rating this goes continuously from 1-50; we will change this in the next version of the task
df_attention$Trial.Number <- ifelse(df_attention$Display == 'Mood ' | df_attention$Display == 'Anxiety ', df_attention$Trial.Number - 2, df_attention$Trial.Number)

df_attention <- df_attention %>%
  mutate(Display = case_when(
    Screen == "m_hist" ~ "m_hist",
    Display == 'Mood ' & Trial.Number <= 26 ~ 'Mood_OUT',
    Display == 'Anxiety ' & Trial.Number <= 26 ~ 'Anxiety_OUT',
    Display == 'Mood ' & Trial.Number > 26 ~ 'Mood_IN',
    Display == 'Anxiety ' & Trial.Number > 26 ~ 'Anxiety_IN',
    TRUE ~ Display  
  ))

df_attention <- df_attention %>%
  mutate(Response = as.numeric(as.character(Response))) %>%
  dplyr::filter(!is.na(Response))

df_attention <- df_attention %>% filter(Trial.Number != -1)

df_attention <- df_attention %>%
  select(-Event.Index, -Object.ID, -m_hist, -Response.Type, -Spreadsheet..Histogram)

# Let's score mini-spin and add its total score to df_attention per subject
df_att_spin <- df_att_spin %>%
  rename(
   "Q1" =  "Rating.Scale.object.2.Fear.of.embarrassment.causes.me.to.avoid.doing.things.or.speaking.to.people.",
   "Q2" =  "Rating.Scale.object.2.I.avoid.activities.in.which.I.am.the.center.of.attention.",
   "Q3" = "Rating.Scale.object.2.Being.embarrassed.or.looking.stupid.are.among.my.worst.fears."
  )

df_att_spin_test <- df_att_spin %>%
  mutate(mini_SPIN_total = sum(c(Q1, Q2, Q3), na.rm = TRUE))

df_att_spin <- df_att_spin %>%
  rowwise() %>%
  mutate(mini_SPIN_total = sum(c(Q1, Q2, Q3), na.rm = TRUE)) %>%
  ungroup()


df_attention_spin <- merge(df_attention, df_att_spin[, c("Random_ID", "mini_SPIN_total")], by = "Random_ID", all.x = TRUE)

df_attention_spin$Social_Anxiety <- ifelse(df_attention_spin$mini_SPIN_total >= 6, "high", "low")

# write.csv(df_attention_spin, file = "df_attention_pilots_with_spin", row.names = FALSE)
```


\newpage 
# Anxiety and Mood ratings within subjects
There were 3 people that had given the same rating across all trials. Some people show the pattern we expect (lower anxiety, higher mood from IN to OUT conditions) but not everyone.

**QUESTION**: How can we best plot the group plot? We cannot plot the individual points anymore, as they would become hard to read; we could average within subjects but again not sure if this is the best approach? I also wonder maybe the fact that there was no feedback (per trial, only at the end) was not stressful enough. It would be interesting to pilot it with the feedback and prediction.  
**Let's also think how to have the feedback across both conditions: we do want to keep feedback constant to be comparable between conditions, right? If so, we would need to have 2 x 48 trials?**

```{r echo=FALSE, warning=FALSE, message=FALSE}
# df_attention_spin <- read.csv("df_attention_pilots_with_spin.csv")

df_attention_spin_f1 <- df_attention_spin %>% filter(Display != "m_hist")
random_ids <- unique(df_attention$Random_ID)

unique_high_anxiety_ids <- df_attention_spin_f1 %>%
  filter(Social_Anxiety == "high") %>%
  distinct(Random_ID) %>%
  nrow()

total_n <- length(unique(df_attention_spin_f1$Random_ID))
message_to_print <- paste(unique_high_anxiety_ids, "subjects out of", total_n,"had high social anxiety")
print(message_to_print)


list_of_dfs <- list()

for (i in seq_along(random_ids)) {
  x <- random_ids[i]  # Get the current value from random_ids
  df_si <- subset(df_attention_spin_f1, Random_ID == x)  # Create the subset
  list_of_dfs[[paste0("df_s", i)]] <- df_si  # Add the subset to list_of_df10s
}

plot_function <- function(df_attention_spin_f1, title) {
  p <- ggplot(df_attention_spin_f1, aes(x = Display, y = Response, fill = Social_Anxiety, color = Screen)) +
    geom_boxplot(outlier.colour = "black", outlier.shape = 16, 
                 outlier.size = 2, notch = TRUE) +
    geom_point(position = position_jitter(width = 0.2), alpha = 0.5) +
    theme_minimal() +
    labs(x = "Display", y = "Response", fill = "Social Anxiety") +
    scale_fill_manual(values = c("low" = "blue", "high" = "red")) +
    scale_y_continuous(breaks = seq(0, 100, by = 10), limits = c(0, 100)) +
    ggtitle(paste("Anxiety and Mood ratings for subject:", title)) +
    xlab("") + 
    ylab("Mood/Anxiety ratings") +
    facet_wrap(~Display, scales = "free")

  return(p)
}

list_of_plots <- Map(plot_function, list_of_dfs, random_ids)

for (i in seq_along(list_of_plots)) {
  print(list_of_plots[[i]])
}

```



\newpage
# Relationship between mini_SPIN and momentary anxiety ratings 

The plot below show the relationship between the (average) anxiety ratings on the task and total mini_SPIN scores.  

```{r echo=FALSE, warning=FALSE, message=FALSE}
avg_response <- df_attention_spin_f1 %>%
  group_by(Random_ID, Display) %>%
  summarise(avg_Response = mean(Response, na.rm = TRUE)) %>%
  ungroup()

wide_avg_response <- avg_response %>%
  pivot_wider(names_from = Display, values_from = avg_Response)

final_df_p1 <- df_attention_spin_f1 %>%
  select(Random_ID, mini_SPIN_total, Social_Anxiety) %>%
  distinct(Random_ID, .keep_all = TRUE) %>%
  left_join(wide_avg_response, by = "Random_ID") %>%
  pivot_longer(
    cols = c(Anxiety_IN, Anxiety_OUT, Mood_IN, Mood_OUT),
    names_to = "Screens",
    values_to = "Response"
  )

final_df_p1 <- final_df_p1 %>%
  mutate(Display = sapply(strsplit(Screens, "_"), `[`, 1))


df_ax_p1 <- final_df_p1 %>% dplyr::filter(Screens == "Anxiety_IN" | Screens == "Anxiety_OUT")
df_M_p1 <-  final_df_p1 %>% dplyr::filter(Screens == "Mood_IN" | Screens == "Mood_OUT")


correlations_ax <- df_ax_p1 %>%
  group_by(Screens) %>%
  summarise(correlation = cor(mini_SPIN_total, Response, use = "complete.obs")) %>%
  mutate(label = paste("R = ", round(correlation, digits = 2)))  

average_correlation_ax <- mean(correlations_ax$correlation, na.rm = TRUE)
message_to_print <- paste("correlation between mini_SPIN_total and average anxiety ratings:", average_correlation_ax)
print(message_to_print)


ggplot(df_ax_p1, aes(x=mini_SPIN_total, y=Response)) +
  geom_point(aes(color="Data Points", alpha = 0.5)) +
  geom_smooth(method = "lm", color="blue") +     
  labs(color="Legend") +
  facet_wrap(~ Screens, scales = "free") +
  theme_minimal() +
  xlab("mini_SPIN_total") + 
  ylab("Average Momentary Anxiety Ratings") +
  geom_text(data=correlations_ax, aes(x=Inf, y=Inf, label=label, group=Screens), hjust=1.5, vjust=4.1, size=2.7, fontface = "bold", inherit.aes=FALSE) 

```



\newpage
# Relationship between mini_SPIN and momentary mood ratings 

The plot below show the relationship between (average) mood ratings on the task and the total mini_SPIN scores.  

```{r echo=FALSE, warning=FALSE, message=FALSE}
correlations_M <- df_M_p1 %>%
  group_by(Screens) %>%
  summarise(correlation = cor(mini_SPIN_total, Response, use = "complete.obs")) %>%
  mutate(label = paste("R = ", round(correlation, digits = 2)))  

average_correlation_M <- mean(correlations_M$correlation, na.rm = TRUE)
message_to_print <- paste("correlation between mini_SPIN_total and average anxiety ratings:", average_correlation_M)
print(message_to_print)


ggplot(df_M_p1, aes(x=mini_SPIN_total, y=Response)) +
  geom_point(aes(color="Data Points", alpha = 0.5)) +
  geom_smooth(method = "lm", color="blue") +     
  labs(color="Legend") +
  facet_wrap(~ Screens, scales = "free") +
  theme_minimal() +
  xlab("mini_SPIN_total") + 
  ylab("Average Momentary Mood Ratings") +
  geom_text(data=correlations_M, aes(x=Inf, y=Inf, label=label, group=Screens), hjust=1.5, vjust=4.1, size=2.7, fontface = "bold", inherit.aes=FALSE) 
```


\newpage
# Average Anxiety in IN and OUT attention conditions
The plot below show the average anxiety ratings in IN and OUT attention conditions where people paid internal and external attention respectively. I think without the outlier (black dot), the difference becomes bigger, will test it later.


```{r echo=FALSE, warning=FALSE, message=FALSE}
ggplot(df_ax_p1, aes(x = Display, y = Response, color = Screens)) +
    geom_boxplot(outlier.colour = "black", outlier.shape = 16, 
                 outlier.size = 2, notch = TRUE) +
    geom_point(position = position_jitter(width = 0.2), alpha = 0.5) +
    theme_minimal() +
    labs(x = "Display", y = "Response", fill = "Social Anxiety") +
    # scale_fill_manual(values = c("low" = "blue", "high" = "red")) +
    scale_y_continuous(breaks = seq(0, 100, by = 10), limits = c(0, 100)) +
    ggtitle(paste("Average anxiety ratings in IN and OUT attention conditions")) +
    xlab("") + 
    ylab("Average Anxiety Ratings") +
    facet_wrap(~Screens, scales = "free")

```

\newpage
# Average Mood in IN and OUT attention conditions

The plot below show the average mood ratings in IN and OUT attention conditions where people paid internal and external attention respectively.


```{r echo=FALSE, warning=FALSE, message=FALSE}
ggplot(df_M_p1, aes(x = Display, y = Response, color = Screens)) +
    geom_boxplot(outlier.colour = "black", outlier.shape = 16, 
                 outlier.size = 2, notch = TRUE) +
    geom_point(position = position_jitter(width = 0.2), alpha = 0.5) +
    theme_minimal() +
    labs(x = "Display", y = "Response", fill = "Social Anxiety") +
    # scale_fill_manual(values = c("low" = "blue", "high" = "red")) +
    scale_y_continuous(breaks = seq(0, 100, by = 10), limits = c(0, 100)) +
    ggtitle(paste("Average mood ratings in IN and OUT attention conditions")) +
    xlab("") + 
    ylab("Average Mood Ratings") +
    facet_wrap(~Screens, scales = "free")

```

\newpage 
# Repeating the group plots after excluding outliers

I have excluded the following subjects to see how the group plots change:"SUPPRF09833", "SUPPRF54499", "SUPPRF50800". They all had rated the same scores for anxiety and mood throughout the task (their histograms above are flat).

```{r echo=FALSE, warning=FALSE, message=FALSE}
ids_to_exclude <- c("SUPPRF09833", "SUPPRF54499", "SUPPRF50800" )
df_ax_p1_ex <- df_ax_p1[!df_ax_p1$Random_ID %in% ids_to_exclude, ]
df_M_p1_ex <- df_M_p1[!df_M_p1$Random_ID %in% ids_to_exclude, ]

ggplot(df_ax_p1_ex, aes(x = Display, y = Response, color = Screens)) +
    geom_boxplot(outlier.colour = "black", outlier.shape = 16, 
                 outlier.size = 2, notch = TRUE) +
    geom_point(position = position_jitter(width = 0.2), alpha = 0.5) +
    theme_minimal() +
    labs(x = "Display", y = "Response", fill = "Social Anxiety") +
    # scale_fill_manual(values = c("low" = "blue", "high" = "red")) +
    scale_y_continuous(breaks = seq(0, 100, by = 10), limits = c(0, 100)) +
    ggtitle(paste("Average anxiety ratings in IN and OUT attention conditions")) +
    xlab("") + 
    ylab("Average Anxiety Ratings") +
    facet_wrap(~Screens, scales = "free")

ggplot(df_M_p1_ex, aes(x = Display, y = Response, color = Screens)) +
    geom_boxplot(outlier.colour = "black", outlier.shape = 16, 
                 outlier.size = 2, notch = TRUE) +
    geom_point(position = position_jitter(width = 0.2), alpha = 0.5) +
    theme_minimal() +
    labs(x = "Display", y = "Response", fill = "Social Anxiety") +
    # scale_fill_manual(values = c("low" = "blue", "high" = "red")) +
    scale_y_continuous(breaks = seq(0, 100, by = 10), limits = c(0, 100)) +
    ggtitle(paste("Average mood ratings in IN and OUT attention conditions")) +
    xlab("") + 
    ylab("Average Mood Ratings") +
    facet_wrap(~Screens, scales = "free")
```


\newpage 
# Between condition tests

Since in this version we only had the mood and anxiety ratings without feedback and prediction, let's have a look at between condition differences per emotion rating (Mood and Anxiety) using two paired t-tests. We could look at the slopes for both attention conditions using a model with only the intercept? 

```{r echo=FALSE, warning=FALSE, message=FALSE}
library(tidyverse)

final_df_p1$condition <- final_df_p1$Screens %>% 
                      str_extract(pattern = "IN|OUT")


Mood <- subset(final_df_p1, Display == "Mood")
Anxiety <- subset(final_df_p1, Display == "Anxiety")

# Paired t-test for Mood
Mood_IN <- Mood$Response[Mood$condition == "IN"]
Mood_OUT <- Mood$Response[Mood$condition == "OUT"]
t_test_Mood <- t.test(Mood_IN, Mood_OUT, paired = TRUE)
print(t_test_Mood)

# Paired t-test for Anxiety
Anxiety_IN <- Anxiety$Response[Anxiety$condition == "IN"]
Anxiety_OUT <- Anxiety$Response[Anxiety$condition == "OUT"]
t_test_Anxiety <- t.test(Anxiety_IN, Anxiety_OUT, paired = TRUE)
print(t_test_Anxiety)

```



```{r echo=FALSE, warning=FALSE, message=FALSE}
# df_attentions <- cbind(df_M, df_ax)
# dim(final_df)
# 
# 
# pe_mood_plots <- list()
# 
# my_splits <- (split(df_surprises, df_surprises$pilot_nr))
# my_splits <- my_splits[pilots] # make sure to re-arrange the order to be from 6-10 
# 
# for(i in 1:length(my_splits)){
#   
#   plot <- my_splits[[i]] %>% 
#     ggplot(aes(x = SubjPE, y = Mood)) +
#     geom_smooth(method = "lm", colour = "red") +
#     geom_point(alpha = 0.2) +
#     facet_wrap(~Random_ID)+
#     ggtitle(paste(pilots[i], "overall r = ", round(correlations_df[i,2], 2)))
#   
#   # Store the plot in the list
#   pe_mood_plots[[i]] <- plot
# }
# 
# # Print  plots
# for (i in 1: length(my_splits)) {
#   print(pe_mood_plots[[i]])
# }
# dev.off()
# 
# 
# 
# # now run lme models for random interecept only and rint + random slope and choose between them
# 
# # first lmes with random intercept models
# rint_models <- list()
# for(i in 1:length(my_splits)){
#   rint_models[[i]] <- lmer(Mood ~ SubjPE + (1| Random_ID), data = 
#                              df_surprises[df_surprises$pilot_nr==pilots[i],], 
#                            REML = FALSE, 
#                            control = lmerControl(optimizer = "bobyqa"))
# }
# rint_models
# 
# # now  lmes with random slopes
# rslope_models <- list()
# for(i in 1:length(my_splits)){
#   rslope_models[[i]] <- lmer(Mood ~ SubjPE + (SubjPE| Random_ID), data = 
#                                df_surprises[df_surprises$pilot_nr==pilots[i],], 
#                              REML = FALSE, 
#                              control = lmerControl(optimizer = "bobyqa"))
# }
# rslope_models
# 
# # now compare between them
# p_vals <- 0
# for(i in 1: length(my_splits)){
#   p_vals[i] <-  (anova(rint_models[[i]], rslope_models[[i]]))$`Pr(>Chisq)`[2]
# }
# 
# format(p_vals, scientific = F) # the p-values show that there is always a significant difference
# 
# 
# 
# mix_models_per_pilot <- list() # the lme objects for each pilot
# mix_models_coefficients <- list() # the coefficients for each pilot
# std_param_mix_models_per_pilot <- list() # the standardised coefficients for each lme object
# dfs_RE_raw_pe_mood <- list() # the dataframes that contain raw values and coefficeints (may not need this)
# for(i in 1: length(my_splits)){
#   
#   mix_models_per_pilot[[i]] <-  lmer(Mood ~ SubjPE + (SubjPE| Random_ID), data = 
#                                        df_surprises[df_surprises$pilot_nr==pilots[i],], 
#                                      REML = FALSE, 
#                                      control = lmerControl(optimizer = "bobyqa"))
#   std_param_mix_models_per_pilot[[i]] <- parameters:: standardise_parameters( mix_models_per_pilot[[i]])
#   
#   mix_models_coefficients[[i]] <-  coef(mix_models_per_pilot[[i]])
#   mix_models_coefficients[[i]] <- data.frame(mix_models_coefficients[[i]]$Random_ID)
#   mix_models_coefficients[[i]]$Random_ID <- rownames(mix_models_coefficients[[i]])
#   colnames(mix_models_coefficients[[i]]) <-c( "intercept", "slope", "Random_ID")
#   
#   #now merge these datasets with the raw values 
#   dfs_RE_raw_pe_mood[[i]] <- left_join(my_splits[[i]], mix_models_coefficients[[i]], by = "Random_ID" )
#   
# }
# names(std_param_mix_models_per_pilot) <- pilots
# std_param_mix_models_per_pilot$`Pilot 7`$Std_Coefficient[1] # to get intercept for example
# 
# # display coefficients
# df_std_coefficients <- data.frame(do.call(rbind,std_param_mix_models_per_pilot))
# df_std_coefficients <- df_std_coefficients %>% 
#    filter(Parameter != "(Intercept)") %>% 
#  # mutate(experiment = names(std_param_mix_models_per_pilot))
#    mutate(experiment = paste0("experiment ", 1:6)) %>% 
#    relocate(experiment, .before = Std_Coefficient) %>% 
#   dplyr::select(!c(Parameter, CI)) %>% 
#   remove_rownames()
#   
# knitr:: kable(df_std_coefficients)
# 
# # Put all datasets together now 
# df_all_surprise_experiments <- do.call(rbind,dfs_RE_raw_pe_mood)
# 
# 
# # test the ICC, i.e. variance explained by random effects.
# # first for IDs
# 
# test_icc_id <- lmer(Mood ~  (1| Random_ID), data = 
#                       df_all_surprise_experiments, 
#                     REML = FALSE, 
#                     control = lmerControl(optimizer = "bobyqa")) 
# icc_results_id <- performance::icc(test_icc_id)
# 
# icc_results_id
# 
# 
# #  nesting by pilot (i.e. number of experiment)
# 
# 
# test_icc_pilot <- lmer(Mood ~  (1| pilot_nr) , data = 
#                          df_all_surprise_experiments, 
#                        REML = FALSE, 
#                        control = lmerControl(optimizer = "bobyqa")) 
# icc_results_pilot <- performance::icc(test_icc_pilot)
# icc_results_pilot
# 
# # it seems that pilot number explains very little of the variance
# 
# 
# # now test whether adding slope improves fit
# 
# big_model_1 <- lmer (Mood ~ SubjPE + (1| Random_ID) ,
#                      data = df_all_surprise_experiments, 
#                      REML = FALSE, 
#                      control = lmerControl(optimizer = "bobyqa"))
# 
# 
# big_model_2 <- lmer (Mood ~ SubjPE + (SubjPE| Random_ID) ,
#                      data = df_all_surprise_experiments, 
#                      REML = FALSE, 
#                      control = lmerControl(optimizer = "bobyqa"))
# summary(big_model_2)
# standard_beta <- parameters:: standardise_parameters (big_model_2)
# AIC(big_model_1, big_model_2)
# 
# big_model_3 <- lmer (Mood ~ SubjPE*Social_Anxiety + (SubjPE| Random_ID) ,
#                      data = df_all_surprise_experiments, 
#                      REML = FALSE, 
#                      control = lmerControl(optimizer = "bobyqa"))
# summary(big_model_3)
# anova(big_model_2, big_model_3)
# 
# 
# # example of how to get positive slopes per dataframe here. Will g --------
# 
# 
# df_all_surprise_experiments_with_anxiety_status <-df_all_surprise_experiments %>% 
#   group_by(Random_ID) %>% 
#   filter(row_number()==1) %>% 
#   mutate(positve_mood_slopes = case_when(slope>0~1, slope <=0 ~0)) %>% 
#   mutate(high_social_anxiety = case_when(Social_Anxiety=="high"~1, Social_Anxiety=="low"~0))
# 
# glimpse(df_all_surprise_experiments_with_anxiety_status)
# 
# only_first_row_df_all_surprise_experiments_with_anxiety_status <- df_all_surprise_experiments_with_anxiety_status %>% 
#   distinct(Random_ID, .keep_all = TRUE)
# 
# only_first_row_df_all_surprise_experiments_with_anxiety_status %>% 
#   count(high_social_anxiety, positve_mood_slopes)
# 
# table(only_first_row_df_all_surprise_experiments_with_anxiety_status$Social_Anxiety)
# table(table(only_first_row_df_all_surprise_experiments_with_anxiety_status$positve_mood_slopes, 
#             only_first_row_df_all_surprise_experiments_with_anxiety_status$high_social_anxiety))
# perc_pos_slop <- prop.table(table( 
#   only_first_row_df_all_surprise_experiments_with_anxiety_status$high_social_anxiety,
#   only_first_row_df_all_surprise_experiments_with_anxiety_status$positve_mood_slopes))
# 
# chisq.test(table(only_first_row_df_all_surprise_experiments_with_anxiety_status$positve_mood_slopes, 
#                  only_first_row_df_all_surprise_experiments_with_anxiety_status$high_social_anxiety))
# 
# # creating a new dataframe with people with high social anxiety from pilot 11, and pilot 10
# df_SA <- subset(df_all_surprise_experiments, (pilot_nr == "Pilot 11") | ((pilot_nr == "Pilot 10") & (Social_Anxiety == "high")))
# 
# # intercept <- mean(df_all_surprise_experiments$intercept)
# # slope <- mean(df_all_surprise_experiments$slope)
# 
# intercept <- mean(df_SA$intercept)
# slope <- mean(df_SA$slope)
```

\newpage
# Attention pilot 2: study description

This pilot was the same as before but we had 59 people counterbalancing the order of conditions between them. Another difference with previous attention pilot is that around 51% of people had high social anxiety scores, and this was 72% in attention pilot 1. In pilot 1, the picture was presented for 4 seconds before they have to describe it and then would disappear. In pilot 2, we re-introduced the picture to have the same design as the surprise task if ultimately we wanted to combine both. However, we need to keep in mind for the next attention pilots, to present the picture separately for 4s, and remove it from the performance trial to see whether it improves the results.  

This was the Gorilla experiment:https://app.gorilla.sc/admin/experiment/157047/design
This was the task used: https://app.gorilla.sc/admin/task/725729/editor?version=10

```{r echo=FALSE, warning=FALSE, message=FALSE}

df_att_p2 <- read.csv("/Users/marjan/Desktop/aim_lab_1/SUP_PRF_pilot_no_fdbk_attention_vid_cbal/SUP_PRF_pilot_no_fdbk_attention_vid_cbal_v5/SUP_PRF_pilot_no_fdbk_attention_vid_cbal_v5_task_main.csv")
df_att_spin_p2 <- read.csv("/Users/marjan/Desktop/aim_lab_1/SUP_PRF_pilot_no_fdbk_attention_vid_cbal/SUP_PRF_pilot_no_fdbk_attention_vid_cbal_v5/SUP_PRF_pilot_no_fdbk_attention_vid_cbal_v5_mini_spin.csv")

df_att_p2 <- df_att_p2[, c("Event.Index", "Trial.Number", "Random_ID", "Spreadsheet..Histogram", "Screen", "Display", "Response", "Response.Type", "Object.ID", "counterbalance.af8t" )]
```

```{r echo=FALSE, warning=FALSE, message=FALSE}

df_att_p2$m_hist <- case_when(
  df_att_p2$Spreadsheet..Histogram == "h1.png" ~ 20,
  df_att_p2$Spreadsheet..Histogram == "h2.png" ~ 29,
  df_att_p2$Spreadsheet..Histogram == "h3.png" ~ 37,
  df_att_p2$Spreadsheet..Histogram == "h4.png" ~ 46,
  df_att_p2$Spreadsheet..Histogram == "h5.png" ~ 54,
  df_att_p2$Spreadsheet..Histogram == "h6.png" ~ 63,
  df_att_p2$Spreadsheet..Histogram == "h7.png" ~ 71,
  df_att_p2$Spreadsheet..Histogram == "h8.png" ~ 80,
  TRUE ~ NA_real_
)

df_att_p2<- df_att_p2%>%
  dplyr::filter(
    (Display == "Trials - Externally Focused Attention") |
    (Display == "Trials - Self Focused Attention") |
    (Display == "Anxiety (Self-focused attention) ") |
    (Display == "Mood (Self-focused attention)") |
    (Display == "Anxiety (External attention) ") |
    (Display == "Mood (External attention)"
     ) 
  )

df_hist_p2 <- df_att_p2%>%
  dplyr::filter(Screen == "Introducing judge") %>%
  select(Event.Index, Response.Type, Object.ID, Random_ID, Trial.Number, Screen, Display, m_hist, Spreadsheet..Histogram, counterbalance.af8t)

df_hist_p2 <- df_hist_p2 %>%
  mutate(Screen = ifelse(Screen == "Introducing judge", "m_hist", Screen))

df_hist_modified_p2 <- df_hist_p2 %>%
  select(Event.Index, Random_ID, Spreadsheet..Histogram, Trial.Number, m_hist, Screen, Display, Response.Type, Object.ID, counterbalance.af8t) %>% dplyr::rename(Response = m_hist)

df_hist_modified_p2 <- df_hist_modified_p2 %>%
  mutate(Response = as.character(Response))

df_attention_p2 <- bind_rows(df_att_p2, df_hist_modified_p2)


df_attention_p2 <- df_attention_p2 %>%
  mutate(Response = as.numeric(as.character(Response))) %>%
  dplyr::filter(!is.na(Response))

df_attention_p2 <- df_attention_p2 %>%
  select(-Event.Index, -Object.ID, -m_hist, -Response.Type, -Spreadsheet..Histogram)


# Let's score mini-spin and add its total score to df_attention per subject
df_att_spin_p2 <- df_att_spin_p2 %>%
  rename(
   "Q1" =  "Rating.Scale.object.2.Fear.of.embarrassment.causes.me.to.avoid.doing.things.or.speaking.to.people.",
   "Q2" =  "Rating.Scale.object.2.I.avoid.activities.in.which.I.am.the.center.of.attention.",
   "Q3" = "Rating.Scale.object.2.Being.embarrassed.or.looking.stupid.are.among.my.worst.fears."
  )

df_att_spin_p2 <- df_att_spin_p2 %>%
  rowwise() %>%
  mutate(mini_SPIN_total = sum(c(Q1, Q2, Q3), na.rm = TRUE)) %>%
  ungroup()


df_attention_spin_p2 <- merge(df_attention_p2, df_att_spin_p2[, c("Random_ID", "mini_SPIN_total")], by = "Random_ID", all.x = TRUE)

df_attention_spin_p2$Social_Anxiety <- ifelse(df_attention_spin_p2$mini_SPIN_total >= 6, "high", "low")


```


```{r echo=FALSE, warning=FALSE, message=FALSE}

df_attention_spin_f1_p2 <- df_attention_spin_p2 %>% dplyr::filter(Display != "m_hist")
random_ids <- unique(df_attention_spin_p2$Random_ID)

unique_high_anxiety_ids <- df_attention_spin_f1_p2 %>%
  dplyr::filter(Social_Anxiety == "high") %>%
  distinct(Random_ID) %>%
  nrow()

total_n <- length(unique(df_attention_spin_f1_p2$Random_ID))
message_to_print <- paste(unique_high_anxiety_ids, "subjects out of", total_n,"had high social anxiety")
print(message_to_print)

df_attention_spin_notrials_p2 <- subset(df_attention_spin_f1_p2, Display != "Trials - Externally Focused Attention")

df_attention_spin_notrials_p2 <- df_attention_spin_notrials_p2 %>%
  mutate(Display = case_when(
    Display == "Anxiety (Self-focused attention) " ~ "Anxiety_IN",
    Display == "Anxiety (External attention) " ~ "Anxiety_OUT",
    Display == "Mood (Self-focused attention)" ~ "Mood_IN",
    Display == "Mood (External attention)" ~ "Mood_OUT",
    TRUE ~ Display  
  ))

df_attenttion_p2_all_trials  <- df_attention_spin_notrials_p2

list_of_dfs <- list()

for (i in seq_along(random_ids)) {
  x <- random_ids[i]  # Get the current value from random_ids
  df_si <- subset(df_attention_spin_notrials_p2, Random_ID == x)  # Create the subset
  list_of_dfs[[paste0("df_s", i)]] <- df_si  # Add the subset to list_of_df10s
}

plot_function <- function(df_attention_spin_notrials_p2, title) {
  p <- ggplot(df_attention_spin_notrials_p2, aes(x = Display, y = Response, fill = Social_Anxiety, color = counterbalance.af8t)) +
    geom_boxplot(outlier.colour = "black", outlier.shape = 16, 
                 outlier.size = 2, notch = TRUE) +
    geom_point(position = position_jitter(width = 0.2), alpha = 0.5) +
    theme_minimal() +
    labs(x = "Display", y = "Response", fill = "Social Anxiety") +
    scale_fill_manual(values = c("low" = "blue", "high" = "red")) +
    scale_y_continuous(breaks = seq(0, 100, by = 10), limits = c(0, 100)) +
    ggtitle(paste("Anxiety and Mood ratings for subject:", title)) +
    xlab("") + 
    ylab("Mood/Anxiety ratings") +
    facet_wrap(~Display, scales = "free")

  return(p)
}

list_of_plots <- Map(plot_function, list_of_dfs, random_ids)

for (i in seq_along(list_of_plots)) {
  print(list_of_plots[[i]])
}

```




```{r echo=FALSE, warning=FALSE, message=FALSE}

avg_response <- df_attention_spin_notrials_p2 %>%
  group_by(Random_ID, Display) %>%
  summarise(avg_Response = mean(Response, na.rm = TRUE)) %>%
  ungroup()

wide_avg_response <- avg_response %>%
  pivot_wider(names_from = Display, values_from = avg_Response)

df_attention_spin_notrials_p2 <- df_attention_spin_notrials_p2 %>%
  select(Random_ID, mini_SPIN_total, Social_Anxiety, counterbalance.af8t) %>%
  distinct(Random_ID, .keep_all = TRUE) %>%
  left_join(wide_avg_response, by = "Random_ID") %>%
  pivot_longer(
    cols = c("Anxiety_IN", "Anxiety_OUT", "Mood_IN", "Mood_OUT"),
    names_to = "Display",
    values_to = "Response"
  )

df_ax_p2 <- df_attention_spin_notrials_p2 %>% dplyr::filter(Display == "Anxiety_IN" | Display == "Anxiety_OUT")
df_M_p2 <-  df_attention_spin_notrials_p2 %>% dplyr::filter(Display == "Mood_IN" | Display == "Mood_OUT")

```

```{r echo=FALSE, warning=FALSE, message=FALSE}
ggplot(df_ax_p2, aes(x = Display, y = Response, color = counterbalance.af8t)) +
    geom_boxplot(outlier.colour = "black", outlier.shape = 16, 
                 outlier.size = 2, notch = TRUE) +
    geom_point(position = position_jitter(width = 0.2), alpha = 0.5) +
    theme_minimal() +
    labs(x = "Display", y = "Response", fill = "Social Anxiety") +
    # scale_fill_manual(values = c("low" = "blue", "high" = "red")) +
    scale_y_continuous(breaks = seq(0, 100, by = 10), limits = c(0, 100)) +
    ggtitle(paste("Average anxiety ratings in IN (internal) & OUT (external) attention conditions")) +
    xlab("") + 
    ylab("Average Anxiety Ratings") +
    facet_wrap(~counterbalance.af8t, scales = "free")

```

```{r echo=FALSE, warning=FALSE, message=FALSE}
result <- df_ax_p2 %>%
  group_by(counterbalance.af8t, Display) %>%
  summarize(
    mean_response = mean(Response, na.rm = TRUE),
    sd_response = sd(Response, na.rm = TRUE)
  )
print(result)
# 
# 
# lmer_results <- lmer(Response ~ counterbalance.af8t * Display + (1 | Random_ID), data = df_ax)
# summary(lmer_results)
```


```{r echo=FALSE, warning=FALSE, message=FALSE}
ggplot(df_M_p2, aes(x = Display, y = Response, color = counterbalance.af8t)) +
    geom_boxplot(outlier.colour = "black", outlier.shape = 16, 
                 outlier.size = 2, notch = TRUE) +
    geom_point(position = position_jitter(width = 0.2), alpha = 0.5) +
    theme_minimal() +
    labs(x = "Display", y = "Response", fill = "Social Anxiety") +
    # scale_fill_manual(values = c("low" = "blue", "high" = "red")) +
    scale_y_continuous(breaks = seq(0, 100, by = 10), limits = c(0, 100)) +
    ggtitle(paste("Average mood ratings in IN (internal) & OUT (external) attention conditions")) +
    xlab("") + 
    ylab("Average Mood Ratings") +
    facet_wrap(~counterbalance.af8t, scales = "free")

```

```{r echo=FALSE, warning=FALSE, message=FALSE}
result <- df_M_p2 %>%
  group_by(counterbalance.af8t, Display) %>%
  summarize(
    mean_response = mean(Response, na.rm = TRUE),
    sd_response = sd(Response, na.rm = TRUE)
  )
print(result)
# 
# 
# lmer_results <- lmer(Response ~ counterbalance.af8t * Display + (1 | Random_ID), data = df_ax)
# summary(lmer_results)
```


\newpage
# Relationship between mini_SPIN and momentary mood ratings 
The plot below show the relationship between (average) mood ratings on the task and the total mini_SPIN scores.  

```{r echo=FALSE, warning=FALSE, message=FALSE}
correlations_M <- df_M_p2 %>%
  group_by(Display) %>%
  summarise(correlation = cor(mini_SPIN_total, Response, use = "complete.obs")) %>%
  mutate(label = paste("R = ", round(correlation, digits = 2)))  

average_correlation_M <- mean(correlations_M$correlation, na.rm = TRUE)
message_to_print <- paste("correlation between mini_SPIN_total and average mood ratings:", average_correlation_M)
print(message_to_print)


ggplot(df_M_p2, aes(x=mini_SPIN_total, y=Response)) +
  geom_point(aes(color="Data Points", alpha = 0.5)) +
  geom_smooth(method = "lm", color="blue") +     
  labs(color="Legend") +
  facet_wrap(~ Display, scales = "free") +
  theme_minimal() +
  xlab("mini_SPIN_total") + 
  ylab("Average Momentary Mood Ratings") +
  geom_text(data=correlations_M, aes(x=Inf, y=Inf, label=label, group=Display), hjust=1.5, vjust=4.1, size=2.7, fontface = "bold", inherit.aes=FALSE) 
```


\newpage
# Relationship between mini_SPIN and momentary mood ratings 
The plot below show the relationship between (average) anxiety ratings on the task and the total mini_SPIN scores.  

```{r echo=FALSE, warning=FALSE, message=FALSE}
correlations_ax <- df_ax_p2 %>%
  group_by(Display) %>%
  summarise(correlation = cor(mini_SPIN_total, Response, use = "complete.obs")) %>%
  mutate(label = paste("R = ", round(correlation, digits = 2)))  

average_correlation_ax <- mean(correlations_ax$correlation, na.rm = TRUE)
message_to_print <- paste("correlation between mini_SPIN_total and average anxiety ratings:", average_correlation_ax)
print(message_to_print)


ggplot(df_ax_p2, aes(x=mini_SPIN_total, y=Response)) +
  geom_point(aes(color="Data Points", alpha = 0.5)) +
  geom_smooth(method = "lm", color="blue") +     
  labs(color="Legend") +
  facet_wrap(~ Display, scales = "free") +
  theme_minimal() +
  xlab("mini_SPIN_total") + 
  ylab("Average Momentary Anxiety Ratings") +
  geom_text(data=correlations_ax, aes(x=Inf, y=Inf, label=label, group=Display), hjust=1.5, vjust=4.1, size=2.7, fontface = "bold", inherit.aes=FALSE) 

```


\newpage
# Why is the data noisy?

**We can look at the following:**  
1) is it due to social anxiety levels (less people with high social anxiety in the current pilot)?  
2) is it due to order effects (we had externally focused attention first in the previous pilot)?  
3) could it be due to just having less reliable participants (we can compare the externally focused attention first, with the previous pilot as the tasks would be exactly the same)?

\newpage
# Separating people with high social anxiety

This would tell us whether the more "noisy" data we had/flat lines, were due to the fact that we have fewer people with high social anxiety in the second Attention pilot. The group plots seem similar to before, and scanning visually through individual plots above, it does not seem to be the case. Something that seems to be the case is that mood is slightly lower, and anxiety higher in self-focused attention first order, for both conditions when compared to externally focused first AND with a much larger confidence interval (compare the anxiety plot in green with the red one in the next page). 

**Conclusion:**  
**There seems to be an order effect for both mood and anxiety. It becomes more clear when we only look at people with high social anxiety.**

```{r echo=FALSE, warning=FALSE, message=FALSE}
df_SA_M_p2 <- subset(df_M_p2, Social_Anxiety == "high")
SA_nr <- length(unique(df_SA_M_p2$Random_ID))
message_to_print <- paste("Number of people with high social anxiety in this section:", SA_nr)
print(message_to_print)

ggplot(df_SA_M_p2, aes(x = Display, y = Response, color = counterbalance.af8t)) +
    geom_boxplot(outlier.colour = "black", outlier.shape = 16, 
                 outlier.size = 2, notch = TRUE) +
    geom_point(position = position_jitter(width = 0.2), alpha = 0.5) +
    theme_minimal() +
    labs(x = "Display", y = "Response") +
    scale_y_continuous(breaks = seq(0, 100, by = 10), limits = c(0, 100)) +
    ggtitle(paste("Average mood ratings in IN (internal) & OUT (external) attention conditions")) +
    xlab("") + 
    ylab("Average Mood Ratings") +
    facet_wrap(~counterbalance.af8t, scales = "free")


df_SA_ax_p2 <- subset(df_ax_p2, Social_Anxiety == "high")

ggplot(df_SA_ax_p2, aes(x = Display, y = Response, color = counterbalance.af8t)) +
    geom_boxplot(outlier.colour = "black", outlier.shape = 16, 
                 outlier.size = 2, notch = TRUE) +
    geom_point(position = position_jitter(width = 0.2), alpha = 0.5) +
    theme_minimal() +
    labs(x = "Display", y = "Response") +
    scale_y_continuous(breaks = seq(0, 100, by = 10), limits = c(0, 100)) +
    ggtitle(paste("Average anxiety ratings in IN (internal) & OUT (external) attention conditions")) +
    xlab("") + 
    ylab("Average Anxiety Ratings") +
    facet_wrap(~counterbalance.af8t, scales = "free")

```


\newpage

# Comparing the pilots 1 and 2

In pilot 1, we had many people with high social anxiety (and we only selected those ones here), and the task had the same order as pilot 2 externally focused attention condition first, followed by internally focused attention condition. 

If they would be very different, it could possibly be due to two things:  
1) we had more people with high social anxiety (we can check the impact of mini-SPIN scores)  
2) we had less reliable participants in second pilot?  

The plot below shows the average mood ratings across conditions for both pilots. We can see two things: **(A)** people in pilot 2 had in average a higher mood rating in the IN condition, which did not seem to change in the OUT condition. **(B)** The confidence interval is much wider in pilot 2, especially in the OUT condition. This could mean that these findings are just because of sample we had, and having another pilot could possibly show us different results.  

The black circles show the individual data points; the boxes start from the first to the third quartile, with a horizontal line and a notch through the median. The whiskers go from each quartile to the minimum and maximum. The notch approximates a 95% CI for the median. If the notches of 2 boxes do not overlap, this suggests that the medians are significantly different. The points outside whiskers represent the outliers.

```{r echo=FALSE, warning=FALSE, message=FALSE}
# maybe merging them and creating a pilot_nr column, and plotting them next to each other, with x = Display? (need to check whether the column names are exactly the same between the two pilots!), since the column numbers and names are different between pilots, let's first make sure we fix this

df_SA_ax_p2_E1st <- subset(df_SA_ax_p2, counterbalance.af8t == "External_attention_first")
df_SA_ax_p2_E1st <- df_SA_ax_p2_E1st %>%
  select(Random_ID, mini_SPIN_total, Social_Anxiety, Response, Display)
df_SA_ax_p2_E1st$pilot_nr <- "p2"

df_SA_M_p2_E1st <- subset(df_SA_M_p2, counterbalance.af8t == "External_attention_first")
df_SA_M_p2_E1st <- df_SA_M_p2_E1st %>%
  select(Random_ID, mini_SPIN_total, Social_Anxiety, Response, Display)
df_SA_M_p2_E1st$pilot_nr <- "p2"

df_SA_ax_p1 <- subset(df_ax_p1, Social_Anxiety == "high")
df_SA_ax_p1 <- df_SA_ax_p1 %>%
  select(Random_ID, mini_SPIN_total, Social_Anxiety, Response, Screens)
df_SA_ax_p1 <- df_SA_ax_p1 %>% 
              rename(Display = Screens)
df_SA_ax_p1$pilot_nr <- "p1"

df_SA_M_p1 <- subset(df_M_p1, Social_Anxiety == "high")
df_SA_M_p1 <- df_SA_M_p1 %>%
  select(Random_ID, mini_SPIN_total, Social_Anxiety, Response, Screens)
df_SA_M_p1 <- df_SA_M_p1 %>% 
              rename(Display = Screens)
df_SA_M_p1$pilot_nr <- "p1"


df_attention_p1_p2_ax <- rbind(df_SA_ax_p2_E1st, df_SA_ax_p1)
df_attention_p1_p2_M <- rbind(df_SA_M_p2_E1st, df_SA_M_p1)
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
df_attention_p1_p2_M$pilot_nr <- as.factor(df_attention_p1_p2_M$pilot_nr)
# levels(df_attention_p1_p2_M$pilot_nr)

ggplot(df_attention_p1_p2_M, aes(x = Display, y = Response, fill = pilot_nr)) +
    geom_boxplot(outlier.colour = "black", outlier.shape = 16, 
                 outlier.size = 2, notch = TRUE, alpha = 0.4) +
    stat_boxplot(geom = "errorbar",
               width = 0.15) + 
    geom_point(color = "black", position = position_jitter(width = 0.2), alpha = 0.5) +
    theme_minimal() +
    labs(x = "Display", y = "Response") +
    scale_y_continuous(breaks = seq(0, 100, by = 10), limits = c(0, 100)) +
    ggtitle("Average mood ratings in pilots 1 and 2 in socially anxious people") +
    xlab("") + 
    ylab("Average Mood Ratings") +
    facet_wrap(~pilot_nr, scales = "free") +
    scale_fill_manual(values = c("purple", "blue"))



```

\newpage
The plot below shows the same results for average anxiety ratings. For anxiety, the CI is wider in the first pilot which could mean the findings we had were specific to the sample we had before or could have been caused by a few people?

```{r echo=FALSE, warning=FALSE, message=FALSE}
df_attention_p1_p2_ax$pilot_nr <- as.factor(df_attention_p1_p2_ax$pilot_nr)
# levels(df_attention_p1_p2_ax$pilot_nr)

ggplot(df_attention_p1_p2_ax, aes(x = Display, y = Response, fill = pilot_nr)) +
    geom_boxplot(outlier.colour = "black", outlier.shape = 16, 
                 outlier.size = 2, notch = TRUE, alpha = 0.4) +
    stat_boxplot(geom = "errorbar",
               width = 0.15) + 
    geom_point(color = "black", position = position_jitter(width = 0.2), alpha = 0.5) +
    theme_minimal() +
    labs(x = "Display", y = "Response") +
    scale_y_continuous(breaks = seq(0, 100, by = 10), limits = c(0, 100)) +
    ggtitle("Average anxiety ratings in pilots 1 and 2 in socially anxious people") +
    xlab("") + 
    ylab("Average Anxiety Ratings") +
    facet_wrap(~pilot_nr, scales = "free") +
    scale_fill_manual(values = c("purple", "blue"))


```

\newpage 
# Mood over time pilot 1; OUT-1st order

Since our trials were numbered from 1-48, we will not see them as two parallel lines (which is the case in pilot 2, where we have trials 1-24 per condition)

```{r echo=FALSE, warning=FALSE, message=FALSE}

p1_M_alltrials_out1st <- subset(df_attention_spin_f1, ((Trial.Number != 0) & (Display == "Mood_OUT") | (Display == "Mood_IN")))

ggplot(p1_M_alltrials_out1st, aes(x = Trial.Number, y = Response, color = Display, group = Display)) +
  geom_line() +
  theme_minimal() +
  labs(title = "P1: Mood across time with OUT-1st order",
       x = "Trial Number",
       y = "Mood IN/OUT",
       color = "") +
  facet_wrap(~ Random_ID, ncol = 6) + # Separate plot for each ID, one column layout
  theme(strip.text = element_text(size = 6)) +  # you can change the size value as needed
  scale_x_continuous(breaks = seq(0, 50, by = 10), limits = c(0, 50)) +
  scale_y_continuous(breaks = seq(0, 100, by = 20), limits = c(0, 100))+
  theme(axis.text.x = element_text(size = 5),axis.text.y = element_text(size = 5))

```

\newpage
From OUT (trials 1-24) to IN (trials 25-48) condition in pilot 1, there is a slight reduction in mood which is what we expected.

```{r echo=FALSE, warning=FALSE, message=FALSE}
ggplot(p1_M_alltrials_out1st, aes(x = Trial.Number, y = Response)) +
    # geom_line() +
    geom_smooth(method = "lm", se = TRUE, alpha = 0.7) + 
    theme_minimal() +
    labs(title = "P1 (OUT-1st): we expect a decrease in mood over time",  
         x = "Trial Number",
         y = "Mood Ratings",
         color = "") +
    geom_hline(yintercept = 0)

ggplot(p1_M_alltrials_out1st, aes(x = Trial.Number, y = Response, color = Display, group = Display)) +
    # geom_line() +
    geom_smooth(method = "lm", se = TRUE, alpha = 0.7) + 
    theme_minimal() +
    labs(title = "P1 (OUT-1st): we expect a decrease in mood over time",  
         x = "Trial Number",
         y = "Mood Ratings",
         color = "") +
    geom_hline(yintercept = 0)
```


\newpage
# Anxiety over time pilot 1; OUT-1st order

```{r echo=FALSE, warning=FALSE, message=FALSE}
p1_Ax_alltrials_out1st <- subset(df_attention_spin_f1, ((Trial.Number != 0) & (Display == "Anxiety_OUT") | (Display == "Anxiety_IN")))

ggplot(p1_Ax_alltrials_out1st, aes(x = Trial.Number, y = Response, color = Display, group = Display)) +
  geom_line() +
  theme_minimal() +
  labs(title = "P1: Anxiety across time with OUT-1st order",
       x = "Trial Number",
       y = "Anxiety IN/OUT",
       color = "") +
  facet_wrap(~ Random_ID, ncol = 6) + # Separate plot for each ID, one column layout
  theme(strip.text = element_text(size = 6)) +  # you can change the size value as needed
  scale_x_continuous(breaks = seq(0, 50, by = 10), limits = c(0, 50)) +
  scale_y_continuous(breaks = seq(0, 100, by = 20), limits = c(0, 100))+
  theme(axis.text.x = element_text(size = 5),axis.text.y = element_text(size = 5))

```

From OUT (trials 1-24) to IN (trials 25-48) condition in pilot 1, there is a slight increase in anxiety which is what we expected. However, there is a decrease in anxiety within conditions as well, it makes sense for the OUT condition why does this happen in the IN condition? Is it regression to the mean or is it because they realise there is not a real person online?

```{r echo=FALSE, warning=FALSE, message=FALSE}
ggplot(p1_Ax_alltrials_out1st, aes(x = Trial.Number, y = Response)) +
    # geom_line() +
    geom_smooth(method = "lm", se = TRUE, alpha = 0.7) + 
    theme_minimal() +
    labs(title = "P1 (OUT-1st): we expect increase in anxiety over time",  
         x = "Trial Number: first half OUT, second half IN",
         y = "Anxiety Ratings",
         color = "") +
    geom_hline(yintercept = 0)

ggplot(p1_Ax_alltrials_out1st, aes(x = Trial.Number, y = Response, color = Display, group = Display)) +
    # geom_line() +
    geom_smooth(method = "lm", se = TRUE, alpha = 0.7) + 
    theme_minimal() +
    labs(title = "P1 (OUT-1st): we expect increase in anxiety over time",  
         x = "Trial Number: first half OUT, second half IN",
         y = "Anxiety Ratings",
         color = "") +
    geom_hline(yintercept = 0)
```


\newpage 
# Mood over time pilot 2; OUT-1st order

```{r echo=FALSE, warning=FALSE, message=FALSE}
# since in pilot 2 the trial numbers were from 1-24 for IN and OUT condition but in pilor 1 from 1-48, to make the same plots as pilot 1, we will re-number the Trial.Number in pilot 2 to go from 1-48, then we can look at changes across time

df_attenttion_p2_all_trials$Trial.Number <- ifelse(
  df_attenttion_p2_all_trials$counterbalance.af8t == "External_attention_first" & 
  (df_attenttion_p2_all_trials$Display == "Mood_IN" | df_attenttion_p2_all_trials$Display == "Anxiety_IN"),
  df_attenttion_p2_all_trials$Trial.Number + 24,
  df_attenttion_p2_all_trials$Trial.Number
)

df_attenttion_p2_all_trials$Trial.Number <- ifelse(
  df_attenttion_p2_all_trials$counterbalance.af8t == "Self_focused_attention_first" & 
  (df_attenttion_p2_all_trials$Display == "Mood_OUT" | df_attenttion_p2_all_trials$Display == "Anxiety_OUT"),
  df_attenttion_p2_all_trials$Trial.Number + 24,
  df_attenttion_p2_all_trials$Trial.Number
)

p2_M_alltrials_out1st <- subset(df_attenttion_p2_all_trials, (counterbalance.af8t == "External_attention_first") & ((Display == "Mood_OUT") | (Display == "Mood_IN")))

ggplot(p2_M_alltrials_out1st, aes(x = Trial.Number, y = Response, color = Display, group = Display)) +
  geom_line() +
  theme_minimal() +
  labs(title = "Mood across time with OUT-1st order",
       x = "Trial Number",
       y = "Mood IN/OUT",
       color = "") +
  facet_wrap(~ Random_ID, ncol = 6) + # Separate plot for each ID, one column layout
  theme(strip.text = element_text(size = 6)) +  # you can change the size value as needed
  scale_x_continuous(breaks = seq(0, 50, by = 10), limits = c(0, 50)) +
  scale_y_continuous(breaks = seq(0, 100, by = 20), limits = c(0, 100))+
  theme(axis.text.x = element_text(size = 5),axis.text.y = element_text(size = 5))

```
In pilot 2, we don't see any change in mood in OUT-1st condition which is the equivalent of the order in pilot 1.

```{r echo=FALSE, warning=FALSE, message=FALSE}
ggplot(p2_M_alltrials_out1st, aes(x = Trial.Number, y = Response, color = Display, group = Display)) +
    geom_smooth(method = "lm", se = TRUE, alpha = 0.7) + 
    theme_minimal() +
    labs(title = "P2 (OUT-1st): we expect a reduction in mood over time",  
         x = "Trial Number: first half OUT, second half IN",
         y = "Mood Ratings",
         color = "") +
    geom_hline(yintercept = 0)
```


\newpage 
# Mood over time pilot 2; IN-1st order
```{r echo=FALSE, warning=FALSE, message=FALSE}

p2_M_alltrials_in1st <- subset(df_attenttion_p2_all_trials, (counterbalance.af8t == "Self_focused_attention_first") & ((Display == "Mood_OUT") | (Display == "Mood_IN")))

ggplot(p2_M_alltrials_in1st, aes(x = Trial.Number, y = Response, color = Display, group = Display)) +
  geom_line() +
  theme_minimal() +
  labs(title = "Mood across time with IN-1st order",
       x = "Trial Number",
       y = "Mood IN/OUT",
       color = "") +
  facet_wrap(~ Random_ID, ncol = 6) + # Separate plot for each ID, one column layout
  theme(strip.text = element_text(size = 6)) +  # you can change the size value as needed
  scale_x_continuous(breaks = seq(0, 50, by = 10), limits = c(0, 50)) +
  scale_y_continuous(breaks = seq(0, 100, by = 20), limits = c(0, 100))+
  theme(axis.text.x = element_text(size = 5),axis.text.y = element_text(size = 5))

```

\newpage 
We can see that mood goes down over time from IN to OUT condition which is the opposite of what we would expect. However, if we separate these two conditions (in second plot) we can see that mood goes down in the IN condition, but starts going up again in the OUT condition, but won't recover to the baseline mood by the end of the task (we may need to take mood drift over time into account as well?).

```{r echo=FALSE, warning=FALSE, message=FALSE}
ggplot(p2_M_alltrials_in1st, aes(x = Trial.Number, y = Response)) +
    geom_smooth(method = "lm", se = TRUE, alpha = 0.7) + 
    theme_minimal() +
    labs(title = "P2(IN-1st): we expect an increase in mood over time",  
         x = "Trial Number: first half IN, second half OUT",
         y = "Mood Ratings",
         color = "") +
    geom_hline(yintercept = 0)

ggplot(p2_M_alltrials_in1st, aes(x = Trial.Number, y = Response, color = Display, group = Display)) +
    geom_smooth(method = "lm", se = TRUE, alpha = 0.7) + 
    theme_minimal() +
    labs(title = "P2(IN-1st): we expect an increase in mood over time",  
         x = "Trial Number: first half IN, second half OUT",
         y = "Mood Ratings",
         color = "") +
    geom_hline(yintercept = 0)
```


\newpage 
# Anxiety over time pilot 2; OUT-1st order

```{r echo=FALSE, warning=FALSE, message=FALSE}
p2_Ax_alltrials_out1st <- subset(df_attenttion_p2_all_trials, (counterbalance.af8t == "External_attention_first") & ((Display == "Anxiety_OUT") | (Display == "Anxiety_IN")))

ggplot(p2_Ax_alltrials_out1st, aes(x = Trial.Number, y = Response, color = Display, group = Display)) +
  geom_line() +
  theme_minimal() +
  labs(title = "Anxiety across time with OUT-1st order",
       x = "Trial Number",
       y = "Anxiety IN/OUT",
       color = "") +
  facet_wrap(~ Random_ID, ncol = 6) + # Separate plot for each ID, one column layout
  theme(strip.text = element_text(size = 6)) +  # you can change the size value as needed
  scale_x_continuous(breaks = seq(0, 50, by = 10), limits = c(0, 50)) +
  scale_y_continuous(breaks = seq(0, 100, by = 20), limits = c(0, 100))+
  theme(axis.text.x = element_text(size = 5),axis.text.y = element_text(size = 5))

```
\newpage 

Their anxiety goes down in the OUT condition, and starts slightly going up from the IN condition, is it because the instructions make them less anxious and they don't follow the instructions or is it because they don't believe someone is watching them?

```{r echo=FALSE, warning=FALSE, message=FALSE}
ggplot(p2_Ax_alltrials_out1st, aes(x = Trial.Number, y = Response)) +
    geom_smooth(method = "lm", se = TRUE, alpha = 0.7) + 
    theme_minimal() +
    labs(title = "P2(OUT-1st): we expect an increase in anxiety over time",  
         x = "Trial Number: first half OUT, second half IN",
         y = "Anxiety Ratings",
         color = "") +
    geom_hline(yintercept = 0)


ggplot(p2_Ax_alltrials_out1st, aes(x = Trial.Number, y = Response, color = Display, group = Display)) +
    geom_smooth(method = "lm", se = TRUE, alpha = 0.7) + 
    theme_minimal() +
    labs(title = "P2(OUT-1st): we expect an increase in anxiety over time",  
         x = "Trial Number: first half OUT, second half IN",
         y = "Anxiety Ratings",
         color = "") +
    geom_hline(yintercept = 0)
```


\newpage 
# Anxiety over time pilot 2; IN-1st order
Some people, for example subjects xxx start with higher anxiety and then it suddenly drops, is it because they don't believe someone is watching them?

```{r echo=FALSE, warning=FALSE, message=FALSE}
p2_Ax_alltrials_in1st <- subset(df_attenttion_p2_all_trials, (counterbalance.af8t == "Self_focused_attention_first") & ((Display == "Anxiety_OUT") | (Display == "Anxiety_IN")))

ggplot(p2_Ax_alltrials_in1st, aes(x = Trial.Number, y = Response, color = Display, group = Display)) +
  geom_line() +
  theme_minimal() +
  labs(title = "Anxiety across time with IN-1st order",
       x = "Trial Number",
       y = "Anxiety IN/OUT",
       color = "") +
  facet_wrap(~ Random_ID, ncol = 6) + # Separate plot for each ID, one column layout
  theme(strip.text = element_text(size = 6)) +  # you can change the size value as needed
  scale_x_continuous(breaks = seq(0, 50, by = 10), limits = c(0, 50)) +
  scale_y_continuous(breaks = seq(0, 100, by = 20), limits = c(0, 100))+
  theme(axis.text.x = element_text(size = 5),axis.text.y = element_text(size = 5))

```

\newpage 

If we look at the first plot we think great we managed to reduce anxiety, but if we look at the second plot, we can see the reduction in anxiety started to happen even before change in condition. In fact, the reduction was more stip in the IN condition.

```{r echo=FALSE, warning=FALSE, message=FALSE}
ggplot(p2_Ax_alltrials_in1st, aes(x = Trial.Number, y = Response)) +
    geom_smooth(method = "lm", se = TRUE, alpha = 0.7) + 
    theme_minimal() +
    labs(title = "P2(IN-1st): we expect an decrease in anxiety over time",  
         x = "Trial Number: first half IN, second half OUT",
         y = "Anxiety Ratings",
         color = "") +
    geom_hline(yintercept = 0)

ggplot(p2_Ax_alltrials_in1st, aes(x = Trial.Number, y = Response, color = Display, group = Display)) +
    geom_smooth(method = "lm", se = TRUE, alpha = 0.7) + 
    theme_minimal() +
    labs(title = "P2(IN-1st): we expect an decrease in anxiety over time",  
         x = "Trial Number: first half IN, second half OUT",
         y = "Anxiety Ratings",
         color = "") +
    geom_hline(yintercept = 0)
```

