---
title: "Group_plots_SubjPE_Mood"
author: "Marjan Biria"
date: "2023-11-27"
output: 
    pdf_document:
    toc: true
    toc_depth: 2
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(root.dir = "aim_lab_1", echo = TRUE)
```


```{r echo=FALSE, warning=FALSE, message=FALSE}
library(dplyr)
library(ggplot2)
library(tidyr)
library(lme4)
library(parameters)
```

\newpage
# Figure description
The figure below shows the relationship between subjective prediction error (feedback - prediction) and the average histogram values. Each subplot represents one pilot study. I am not plotting the MTurk data here due to the very low quality. \

Pilot 6 (n = ; socially anxious): feedback + text/no video (Prolific)\
Pilot 7 (n = ; socially anxious): bigger feedback (1/judge) + text/no video (Prolific)\
Pilot 8 (n = ; general population): max feedback (1/judge) + text/no video (Prolific)\
Pilot 9 (n = ; general population): bigger feedback (1/judge) + text/no video (Prolific)\
Pilot 10 (n = ; general population): feedback + video + incorporating feedback from YPAG (Prolific)\

```{r echo=FALSE, warning=FALSE, message=FALSE}
# Let's read all these pilot data, add a column about their pilot number

df6 <- read.csv("/Users/marjan/Desktop/pilot_surprise_SeptOCT2023/Pilot_surprise/SUP_PRF_pilot_fdbk_nrand_typing_novid_v3_task_main.csv")  
df7 <- read.csv("/Users/marjan/Desktop/pilot_surprise_SeptOCT2023/Pilot_surprise/SUP_PRF_pilot_fdbk_bignrnd_typ_v3_task_main.csv")
df8 <- read.csv("/Users/marjan/Desktop/pilot_surprise_SeptOCT2023/Pilot_surprise/SUP_PRF_pilot_fdbk_biggestnrnd_typ_v3_task_main.csv")
df9 <- read.csv("/Users/marjan/Desktop/pilot_surprise_SeptOCT2023/Pilot_surprise/SUP_PRF_pilot_fdbk_bignrnd_typ_YPAG_v6_task_main.csv")
df10 <- read.csv("/Users/marjan/Desktop/pilot_surprise_SeptOCT2023/Pilot_surprise//SUP_PRF_pilot_fdbk_bignrnd_YPAG_vid_v5_task_main.csv")

# Let's add a column that we may want to use as their pilot description
df6$pilot_nr <- "Pilot 6"
df6$pilot_details <- "Pilot 6: feedback + text"

df7$pilot_nr <- "Pilot 7"
df7$pilot_details <- "Pilot 7: bigger feedback + text"

df8$pilot_nr <- "Pilot 8"
df8$pilot_details <- "Pilot 8: max feedback + text"

df9$pilot_nr <- "Pilot 9"
df9$pilot_details <- "Pilot 9: bigger feedback + text"

df10$pilot_nr <- "Pilot 10"
df10$pilot_details <- "Pilot 10: bigger feedback + video"

# Let's select the columns we want, because some pilots have some additional columns we may not need so we need to first make sure we have the same headers
# before bindings the df's

df6 <- df6[, c("Event.Index", "Trial.Number", "Random_ID", "pilot_details", "pilot_nr", "Spreadsheet..Feedback", "Spreadsheet..Histogram", "Screen", "Display", "Response", "Response.Type" )]

df7 <- df7[, c("Event.Index", "Trial.Number", "Random_ID", "pilot_details", "pilot_nr", "Spreadsheet..Feedback", "Spreadsheet..Histogram", "Screen", "Display", "Response", "Response.Type" )]

df8 <- df8[, c("Event.Index", "Trial.Number", "Random_ID", "pilot_details", "pilot_nr", "Spreadsheet..Feedback", "Spreadsheet..Histogram", "Screen", "Display", "Response", "Response.Type" )]

df9 <- df9[, c("Event.Index", "Trial.Number", "Random_ID", "pilot_details", "pilot_nr", "Spreadsheet..Feedback", "Spreadsheet..Histogram", "Screen", "Display", "Response", "Response.Type" )]

df10 <- df10[, c("Event.Index", "Trial.Number", "Random_ID", "pilot_details", "pilot_nr", "Spreadsheet..Feedback", "Spreadsheet..Histogram", "Screen", "Display", "Response", "Response.Type" )]


# Let's concatenate them, so that we can use the pilot_nr column in a facet_wrap
all_pilots <- rbind(df6, df7, df8, df9, df10)

```

```{r echo=FALSE, warning=FALSE, message=FALSE}
# Let's add the histogram mean values in a column

# defining histogram means
all_pilots$m_hist <- ifelse(all_pilots$Spreadsheet..Histogram == "h1.png", 20,
                       ifelse(all_pilots$Spreadsheet..Histogram == "h2.png", 29,
                              ifelse(all_pilots$Spreadsheet..Histogram == "h3.png", 37,
                                     ifelse(all_pilots$Spreadsheet..Histogram == "h4.png", 46,
                                            ifelse(all_pilots$Spreadsheet..Histogram == "h5.png", 54,
                                                   ifelse(all_pilots$Spreadsheet..Histogram == "h6.png", 63,
                                                          ifelse(all_pilots$Spreadsheet..Histogram == "h7.png", 71,
                                                                 ifelse(all_pilots$Spreadsheet..Histogram == "h8.png", 80, NA))))))))


# get rid of the rows we don't need: practice runs, continue button presses etc. and only keep Trials, Anxiety and Mood that include all variables we are interested in:
all_pilots <- all_pilots %>%
  dplyr::filter(
    (Display == "Trials ") |
      (Display == "Anxiety " & !Trial.Number %in% c(1, 2)) |
      (Display == "Mood " & !Trial.Number %in% c(1, 2)) 
  )

# setting Mood and Anxiety trial numbers to match the trials starting from 1 (since we removed the baseline ones above)
all_pilots$Trial.Number <- ifelse(all_pilots$Display == 'Mood ' | all_pilots$Display == 'Anxiety ', all_pilots$Trial.Number - 2, all_pilots$Trial.Number)
all_pilots$Display <- ifelse(all_pilots$Display == 'Mood ' | all_pilots$Display == 'Anxiety ', "Trials", all_pilots$Display)

# renaming the feedback column to fdbk
names(all_pilots)[names(all_pilots) == 'Spreadsheet..Feedback'] <- 'fdbk'

# Now let's create columns for PE (fdbk-hist) and Subj_PE (fdbk_Prediction)

all_pilots <- all_pilots %>%
  mutate(Response = as.numeric(as.character(Response))) %>%
  dplyr::filter(!is.na(Response))


all_pilots$SubjPE <- ifelse(all_pilots$Screen == "Prediction ", all_pilots$fdbk - all_pilots$Response, NA)
all_pilots$PE <- ifelse(all_pilots$Screen == "Prediction ", all_pilots$fdbk - all_pilots$m_hist, NA)
# to keep just one repetition of feedback and mean histogram per trial per subject 
# and replace the rest with NA so that when we want to convert to long format we won't have duplicates
all_pilots$fdbk <- ifelse(all_pilots$Screen == "Prediction ", all_pilots$fdbk, NA)
all_pilots$m_hist <- ifelse(all_pilots$Screen == "Prediction ", all_pilots$m_hist, NA)


long_all_pilots <- all_pilots %>%
  dplyr::select(Random_ID, Trial.Number, fdbk, m_hist, PE, SubjPE) %>%
  pivot_longer(cols = c(fdbk, m_hist, PE, SubjPE),
               names_to = "Screen",
               values_to = "Response")


# This will keep only the rows where 'Response' is not NA
long_all_pilots <- long_all_pilots[!is.na(long_all_pilots$Response), ]


# Selecting relevant columns from the original all_pilots
all_pilots <- all_pilots %>%
  dplyr::select(-c(fdbk, m_hist, PE, SubjPE))

# Binding the rows together
all_pilots <- bind_rows(all_pilots, long_all_pilots)

all_pilots$Response <- as.numeric(all_pilots$Response)


# looking at the relationship between PE and SubjPE
all_pilots_PE <- subset(all_pilots, Screen == "PE")
names(all_pilots_PE)[names(all_pilots_PE) == "Screen"] <- "Screen_PE"
names(all_pilots_PE)[names(all_pilots_PE) == "Response"] <- "PE"

all_pilots_SubjPE <- subset(all_pilots, Screen == "SubjPE")
names(all_pilots_SubjPE)[names(all_pilots_SubjPE) == "Screen"] <- "Screen_SubjPE"
names(all_pilots_SubjPE)[names(all_pilots_SubjPE) == "Response"] <- "SubjPE"

all_pilots_fdbk <- subset(all_pilots, Screen == "fdbk")
names(all_pilots_fdbk)[names(all_pilots_fdbk) == "Screen"] <- "Screen_fdbk"
names(all_pilots_fdbk)[names(all_pilots_fdbk) == "Response"] <- "fdbk"

all_pilots_hist <- subset(all_pilots, Screen == "m_hist")
names(all_pilots_hist)[names(all_pilots_hist) == "Screen"] <- "Screen_m_hist"
names(all_pilots_hist)[names(all_pilots_hist) == "Response"] <- "m_hist"

all_pilots_predic <- subset(all_pilots, Screen == "Prediction ")
names(all_pilots_predic)[names(all_pilots_predic) == "Screen"] <- "Screen_pred"
names(all_pilots_predic)[names(all_pilots_predic) == "Response"] <- "Prediction"

all_pilots_cert <- subset(all_pilots, Screen == "Certainty rating ")
names(all_pilots_cert)[names(all_pilots_cert) == "Screen"] <- "Screen_certainty"
names(all_pilots_cert)[names(all_pilots_cert) == "Response"] <- "Certainty_Rating"

all_pilots_Anxious <- subset(all_pilots, Screen == "Anxious")
names(all_pilots_Anxious)[names(all_pilots_Anxious) == "Screen"] <- "Screen_Ax"
names(all_pilots_Anxious)[names(all_pilots_Anxious) == "Response"] <- "Anxiety"

all_pilots_Happy <- subset(all_pilots, Screen == "Happy")
names(all_pilots_Happy)[names(all_pilots_Happy) == "Screen"] <- "Screen_H"
names(all_pilots_Happy)[names(all_pilots_Happy) == "Response"] <- "Mood"

list_of_all_dfs <- list(all_pilots_PE, all_pilots_fdbk, all_pilots_hist, all_pilots_predic, all_pilots_cert, all_pilots_SubjPE, all_pilots_Anxious, all_pilots_Happy)

# Using reduce with inner_join
all_pilots_wide_8var <- reduce(list_of_all_dfs, inner_join, by = c("Random_ID", "Trial.Number"))


# subset only the columns we are interested in
all_pilots_wide_8var <- all_pilots_wide_8var[c("Trial.Number", "Random_ID", "Mood", "Anxiety", "fdbk", "SubjPE", "PE", "Certainty_Rating", "m_hist", "Prediction", "pilot_nr.x.x.x", "pilot_details.x.x.x")]

names(all_pilots_wide_8var)[names(all_pilots_wide_8var) == "pilot_details.x.x.x"] <- "pilot_details"
names(all_pilots_wide_8var)[names(all_pilots_wide_8var) == "pilot_nr.x.x.x"] <- "pilot_nr"


write.csv(all_pilots_wide_8var, file = "all_pilots_wide_8var.csv", row.names = FALSE)
```



\newpage For Argyris:

```{r echo=FALSE, warning=FALSE, message=FALSE}
# standardise before model fitting?
all_pilots_wide_8var$SubjPE <- scale(all_pilots_wide_8var$SubjPE)


model2 <- lme4::lmer(Mood ~ SubjPE + (SubjPE | Random_ID), data = all_pilots_wide_8var, control=lmerControl(optimizer="bobyqa"))                        
# optCtrl=list(maxfun=2e5)

coef_fixed <- fixef(model2)
intercept <- coef_fixed[1]
slope <- coef_fixed[2]

# Calculate correlations for each subject
subject_correlations <- all_pilots_wide_8var %>%
  group_by(Random_ID) %>%
  summarize(correlation = cor(Mood, SubjPE, use = "complete.obs")) %>%
  na.omit()  # Remove NA values

average_correlation <- mean(subject_correlations$correlation, na.rm = TRUE)
# ###############################################################################
#       how can we standardise the intercept and slope before plotting?        #           
# standardize_parameters(model2, method = "pseudo", ci_method = "satterthwaite")


ggplot(all_pilots_wide_8var, aes(x=Mood, y=SubjPE)) +
  geom_smooth(method = "lm", color = "#0000FF44", size = 0.4, se = FALSE, aes(group=Random_ID)) +
  geom_abline(intercept = intercept, slope = slope, color="red", linetype="dashed") +
  xlab("Mood") + 
  ylab("SubjPE: feedback - prediction") +
  theme_minimal() +
  # scale_x_continuous(breaks = seq(0, 100, by = 10), limits = c(0, 100)) +
  scale_y_continuous(breaks = seq(-100, 100, by = 20), limits = c(-100, 100)) +
  theme(axis.text.x = element_text(size = 5), axis.text.y = element_text(size = 5))

```





\newpage Simpson Paradox: 
```{r echo=FALSE, warning=FALSE, message=FALSE}


all_pilots_wide_8var$pilot_nr <- factor(all_pilots_wide_8var$pilot_nr, levels = c("Pilot 6", "Pilot 7", "Pilot 8","Pilot 9", "Pilot 10"))
all_pilots_wide_8var$pilot_details <- factor(all_pilots_wide_8var$pilot_details, levels = c("Pilot 6: feedback + text", "Pilot 7: bigger feedback + text", "Pilot 8: max feedback + text","Pilot 9: bigger feedback + text", "Pilot 10: bigger feedback + video"))


model1 <- lme4::lmer(Mood ~ SubjPE + (1 | Random_ID) , data = all_pilots_wide_8var)
AIC(model1)
summary(model1)

# better than model 3, use this for the moment, also more parsimonious
model2 <- lme4::lmer(Mood ~ SubjPE + (SubjPE | Random_ID) , data = all_pilots_wide_8var)
AIC(model2)
summary(model2)

# standardize_parameters scales the model's coefficients (fixed effects) relative to the variability in our data, making them more interpretable and comparable across different people
standardize_parameters(model2, method = "pseudo", ci_method = "satterthwaite")

anova(model1, model2)

indiv_slopes <- nlme::ranef(model2)
indiv_slopes_df <- indiv_slopes$Random_ID
# df_rane <- data.frame(nlme::ranef(model2))

library(lattice)
dotplot(nlme::ranef(model2))
mean(indiv_slopes_df$SubjPE)

# take into account that subjects have been from possibly different samples/different experiments
# so taking Random_ID and pilot_nr as nested effects
model3 <- lme4::lmer(Mood ~ SubjPE + (SubjPE | Random_ID/pilot_nr) , data = all_pilots_wide_8var)
AIC(model3)
summary(model3)

model2 <- lme4::lmer(Mood ~ SubjPE +  (SubjPE | Random_ID), data = all_pilots_wide_8var) #(1 | pilot_nr) +
standardize_parameters(model2, method = "pseudo", ci_method = "satterthwaite")

model <- lme4::lmer(Mood ~ SubjPE +  (1 | Random_ID), data = all_pilots_wide_8var) #(1 | pilot_nr) +

# calculating correlations within subjects, averaged per pilot
correlations <- all_pilots_wide_8var %>%
  group_by(Random_ID) %>%
  summarize(correlation = cor(SubjPE, Mood, use = "complete.obs")) %>%
  na.omit()  # Remove NA values that might result from insufficient data per group

average_correlations <- all_pilots_wide_8var %>%
  select(Random_ID, pilot_details) %>%
  distinct() %>%
  inner_join(correlations, by = "Random_ID") %>%
  group_by(pilot_details) %>%
  summarize(average_correlation = mean(correlation))

# average_correlations <- average_correlations %>%
#   mutate(label = sprintf("%.2f", average_correlation))  # Formats the correlation value to a string with 2 decimal places

# paste(nlme::ranef(model2)), replace with the whole LME model
average_correlations <- average_correlations %>%
  mutate(label = paste("r =", sprintf("%.2f", average_correlation)))  # Adds "r =" before the correlation value

# average_correlations <- average_correlations %>%
#   mutate(label = paste(nlme::ranef(model2)))  # to replace average correlation with the LME output


# model2 was the best model, so we want to use it to overlay on the plot:
lme_model <- lme4::lmer(Mood ~ SubjPE + (SubjPE | Random_ID), data = all_pilots_wide_8var)
all_pilots_wide_8var$Mood_Predicted <- predict(lme_model, newdata = all_pilots_wide_8var, re.form = NULL)
summary_df <- all_pilots_wide_8var %>%
  group_by(SubjPE) %>%
  summarize(Mean_Mood_Predicted = mean(Mood_Predicted))


ggplot(all_pilots_wide_8var, aes(x=Mood, y=SubjPE)) +
  geom_smooth(method = "lm", color = "#0000FF44", size = 0.4, se = FALSE, aes(group=Random_ID)) +
  geom_line(data = summary_df, aes(x = Mean_Mood_Predicted, y = SubjPE), color = "red", size = 0.4) +
  theme_minimal() +
  xlab("Mood") + 
  ylab("SubjPE: feedback - prediction") +
  # Add the correlation labels
  # geom_text(data=average_correlations, aes(x=Inf, y=Inf, label=label, group=pilot_details), hjust=1.1, vjust=1.1, size=2.7, fontface = "bold", inherit.aes=FALSE) +
  geom_text(data = average_correlations, aes(x = Inf, y = Inf, label = label, group = pilot_details), hjust = 2.1, vjust = 2.7, size = 2.7,    
  fontface = "bold", inherit.aes = FALSE) +
     # Adjust the size of the facet labels
  theme(strip.text = element_text(size = 9)) +  # you can change the size value as needed
  scale_x_continuous(breaks = seq(0, 100, by = 10), limits = c(0, 100)) +
  scale_y_continuous(breaks = seq(-40, 40, by = 20), limits = c(-40, 40))+
  theme(axis.text.x = element_text(size = 5),axis.text.y = element_text(size = 5))
  


# our best model
model2 <- lme4::lmer(Mood ~ SubjPE + (SubjPE | Random_ID), data = all_pilots_wide_8var)


df6_spin <- read.csv("/Users/marjan/Documents/GitHub/aim_lab_1/SUP_PRF_pilot_fdbk_nrand_typing_novid/SUP_PRF_pilot_fdbk_nrand_typing_novid_v3/SUP_PRF_pilot_fdbk_nrand_typing_novid_v3_mini_spin.csv")  

df7_spin <- read.csv("/Users/marjan/Desktop/pilot_surprise_SeptOCT2023/Pilot_surprise/SUP_PRF_pilot_fdbk_bignrnd_typ_v3_mini_spin.csv")   

df8_spin <- read.csv("/Users/marjan/Desktop/pilot_surprise_SeptOCT2023/Pilot_surprise/SUP_PRF_pilot_fdbk_biggestnrnd_typ_v3_mini_spin.csv")

df9_spin <- read.csv("/Users/marjan/Desktop/pilot_surprise_SeptOCT2023/Pilot_surprise/SUP_PRF_pilot_fdbk_bignrnd_typ_YPAG_v6_mini_spin.csv")

df10_spin <- read.csv("/Users/marjan/Desktop/pilot_surprise_SeptOCT2023/Pilot_surprise/SUP_PRF_pilot_fdbk_bignrnd_YPAG_vid_v5_mini_spin.csv")

all_pilots_wide_8var <- read.csv("/Users/marjan/Desktop/aim_lab_1/all_pilots_wide_8var.csv")


# Let's merge these, and then select Random_ID and the total scores
all_spins <- rbind(df6_spin, df7_spin, df8_spin, df9_spin, df10_spin)


all_spins <- all_spins %>%
  rename(
   "Q1" =  "Rating.Scale.object.2.Fear.of.embarrassment.causes.me.to.avoid.doing.things.or.speaking.to.people.",
   "Q2" =  "Rating.Scale.object.2.I.avoid.activities.in.which.I.am.the.center.of.attention.",
   "Q3" = "Rating.Scale.object.2.Being.embarrassed.or.looking.stupid.are.among.my.worst.fears."
  )

all_spins <- all_spins %>%
  rowwise() %>%
  mutate(mini_SPIN_total = sum(c(Q1, Q2, Q3), na.rm = TRUE)) %>%
  ungroup()


all_pilots_wide_8var <- merge(correlations_Ax_excludedoutliers, df7_spin, by = "Random_ID")

all_pilots_with_mini_spin <- merge(all_pilots_wide_8var, all_spins[, c("Random_ID", "mini_SPIN_total")], by = "Random_ID", all.x = TRUE)

all_pilots_with_mini_spin$Social_Anxiety <- ifelse(all_pilots_with_mini_spin$mini_SPIN_total >= 6, "high", "low")


write.csv(all_pilots_with_mini_spin, file = "all_pilots_with_mini_spin.csv", row.names = FALSE)


correlations_per_subject <- all_pilots_with_mini_spin %>%
  group_by(Random_ID) %>%
  summarize(correlation = cor(Mood, SubjPE, use = "complete.obs"))

average_correlations <- all_pilots_with_mini_spin %>%
  left_join(correlations_per_subject, by = "Random_ID") %>%
  group_by(Social_Anxiety) %>%
  summarize(average_correlation = mean(correlation, na.rm = TRUE))

average_low <- average_correlations$average_correlation[average_correlations$Social_Anxiety == "low"]
average_high <- average_correlations$average_correlation[average_correlations$Social_Anxiety == "high"]


ggplot(all_pilots_with_mini_spin, aes(x = Mood, y = SubjPE, color = Social_Anxiety)) +
  geom_point(aes(color= Social_Anxiety, alpha = 0.3)) +
  geom_smooth(method = "lm", color="yellow") +     
  # labs(color="Legend") +
  theme_minimal() +
  xlab("Happiness/Mood") + 
  ylab("SubjPE: feedback - prediction") +
    # facet_wrap(~ Random_ID, scales = "free") +
    theme(strip.text = element_text(size = 6))+
    geom_text(data=correlations, aes(x=Inf, y=Inf, label=label, group=Random_ID), hjust=1.1, vjust=1.1, size=2.7, fontface = "bold", inherit.aes=FALSE) +
     # Adjust the size of the facet labels
  # Add the correlation labels
    theme(
    strip.text.x = element_text(face = "bold"),  # For horizontal facet titles
    strip.text.y = element_text(face = "bold"),  # For vertical facet titles
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.background = element_blank()) +
    scale_color_manual(values = c("Red", "Blue"))



```





