---
title: "Surprise study pilot 13"
author: "Marjan Biria"
date: "2024-01-16"
output: 
    pdf_document:
    toc: true
    toc_depth: 2
    toc_float: true
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(root.dir = "aim_lab_1", echo = TRUE)
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
library(dplyr)
library(ggplot2)
library(tidyr)
library(lme4)
library(parameters)
library(broom.mixed)
library(purrr)
library(conflicted)
library(stringr)
library(readxl)
```


\newpage
# Study description

This study has the same version as pilots 10 and 11, however, we have now added bigger negative PE's once per judge. More specifically, we have replaced one negative PE per judge by subtracting 10 from the smallest negative PE we had before for each judge. So this is how the feedback was calculated before to have 2 positive, 2 negative, and 2 neutral PE's per judge (8 judges x 6 trials= 48 trials).

The Gorilla experiment is the following: https://app.gorilla.sc/admin/project/119459
The task is the following: https://app.gorilla.sc/admin/task/736716/editor

**Goal:** we would like to see whether having a bigger range for PE's would influence the relationship between subj-PE and anxiety.

I will write this here as well for us to have, if we forget again:  
**Positive PE:** we selected numbers from a normal distribution ranging from 12-20, added this number to the mean of the histogram.  
**Negative PE:** we selected numbers from a normal distribution ranging from 12-20, subtracted this number to the mean of the histogram.  
**Big positive PE:** Per judge, we added 10 to the biggest positive feedback we had generated before.  
**Big negative PE:** Per judge, we subtracted 10 to the smallest negative feedback we had generated before.  
**Neutral PE: ** we added -1, 0, 1 to the mean of the histograms  

Notes: In this pilot, some people did the questionnaires but had technical difficulties so could not do the task, so we must remember to merge by ID's in the task rather than mini-SPIN/CES-D. Also, we start counting mood and anxiety from instructions and also BL, so we need to create a column naming the within experiment mood and anxiety "trials", the very first one "instructions", and the second one "BL", in the first one they are explained what they need to do, and in BL they are instructed to rate their anxiety and mood. It would be good to compare "instruction", "BL" and also the first ratings in the task using ICC, and also look at the relationship between questionnaires and each of these ratings.

```{r echo=FALSE, warning=FALSE, message=FALSE}
# In this pilot, remember that some people did the questionnaires but had technical difficulties so could not do the task, so merge by ID's in the task rather than mini-SPIN
# Also, we start counting mood and anxiety from instructions and also BL, create a column naming the task mood and anxiety "trials", the very first one "instructions", and the second one "BL", in the first one they are explained what they need to do, and in BL they are instructed to rate their anxiety and mood. It would be good to compare both.

df13_raw <- read.csv("/Users/marjan/Desktop/aim_lab_1/SUP_PRF_pilot_vid_big_pos_neg_PE/SUP_PRF_pilot_vid_big_pos_neg_PE_v5/SUP_PRF_pilot_vid_big_pos_neg_PE_v5_task_main.csv")
df13_spin <- read.csv("/Users/marjan/Desktop/aim_lab_1/SUP_PRF_pilot_vid_big_pos_neg_PE/SUP_PRF_pilot_vid_big_pos_neg_PE_v5/SUP_PRF_pilot_vid_big_pos_neg_PE_v5_mini_spin.csv")
df13_cesd <- read.csv("/Users/marjan/Desktop/aim_lab_1/SUP_PRF_pilot_vid_big_pos_neg_PE/SUP_PRF_pilot_vid_big_pos_neg_PE_v5/SUP_PRF_pilot_vid_big_pos_neg_PE_v5_ces_d.csv")
```


```{r echo=FALSE, warning=FALSE, message=FALSE}
# extract CES-D scores
CESD_data_clean <- df13_cesd[, c(32, 34, 36, 38, 40, 42, 44, 46,48,50,
                                 52, 54, 56, 58, 60, 62, 64, 66, 68, 70, 71 )]
# Identify non-ID variable columns
non_id_cols <- setdiff(names(CESD_data_clean), "Random_ID")

# Convert non-ID variables to numeric
CESD_data_clean[, non_id_cols] <- lapply(CESD_data_clean[, non_id_cols], as.numeric)

#change numbers to match CES-D scoring system
excluded_columns <-  c("Random_ID", "Multiple.Choice.Grid.object.3.4...I.felt.I.was.just.as.good.as.other.people..Quantised",
                       "Multiple.Choice.Grid.object.3.8...I.felt.hopeful.about.the.future..Quantised",
                       "Multiple.Choice.Grid.object.3.12...I.was.happy..Quantised",
                       "Multiple.Choice.Grid.object.3.16...I.enjoyed.life..Quantised")
                  

CESD_data_clean<- CESD_data_clean %>%
  mutate(across(-excluded_columns , ~ case_when(
    . == 1 ~ 0,
    . == 2 ~ 1,
    . == 3 ~ 2,
    . == 4 ~ 3,
    TRUE ~ .
  )))


other_columns <- c("Multiple.Choice.Grid.object.3.4...I.felt.I.was.just.as.good.as.other.people..Quantised",
                   "Multiple.Choice.Grid.object.3.8...I.felt.hopeful.about.the.future..Quantised",
                   "Multiple.Choice.Grid.object.3.12...I.was.happy..Quantised",
                   "Multiple.Choice.Grid.object.3.16...I.enjoyed.life..Quantised")
CESD_data_clean<- CESD_data_clean %>%
  mutate(across(other_columns , ~ case_when(
    . == 1 ~ 3,
    . == 2 ~ 2,
    . == 3 ~ 1,
    . == 4 ~ 0,
    TRUE ~ .
  )))

#scoring----
CESD_scores <-  numeric(length(CESD_data_clean$Random_ID))
CESD_scores <- 0
Questions <- c(1:20)

for (i in 1:nrow(CESD_data_clean)) {
  CESD_score <- sum(CESD_data_clean[i, Questions])
  CESD_scores[i] <- CESD_score
}

CESD_data_clean$CESD_score <-  CESD_scores

CESD_data_clean$Depression_Threshold<- 0
CESD_data_clean$Depression_status <- "Not_Depressed"

#Assign "1" if they meet Depression threshold 
for (i in 1:nrow(CESD_data_clean)) {
  if (CESD_data_clean$CESD_score[i] >= 16) {
    CESD_data_clean$Depression_Threshold[i] <- 1
    CESD_data_clean$Depression_status[i] <- "Depressed"
  }
}
```


```{r echo=FALSE, warning=FALSE, message=FALSE}

df13_spin <- df13_spin %>%
  rename(
   "Q1" =  "Rating.Scale.object.2.Fear.of.embarrassment.causes.me.to.avoid.doing.things.or.speaking.to.people.",
   "Q2" =  "Rating.Scale.object.2.I.avoid.activities.in.which.I.am.the.center.of.attention.",
   "Q3" = "Rating.Scale.object.2.Being.embarrassed.or.looking.stupid.are.among.my.worst.fears."
  )

df13_spin <- df13_spin %>%
  rowwise() %>%
  mutate(mini_SPIN_total = sum(c(Q1, Q2, Q3), na.rm = TRUE)) %>%
  ungroup()


# create a new df13 that only keeps the columns we need
df13 <- df13_raw[, c("Trial.Number", "Display", "Screen", "Response.Type", "Response", 
                     "Reaction.Time", "Spreadsheet..Histogram", "Spreadsheet..Feedback", "Random_ID")]

df13 <- df13 %>%
  mutate(Response = as.numeric(as.character(Response))) %>%
  dplyr::filter(!is.na(Response))

df13$Screen <- ifelse(df13$Trial.Number == 1 & (df13$Display == "Mood " | df13$Display == "Anxiety "), "BL_1",
                      ifelse(df13$Trial.Number == 2 & (df13$Display == "Mood " | df13$Display == "Anxiety "), "BL_2", 
                             df13$Screen))

df13$m_hist <- ifelse(df13$Spreadsheet..Histogram == "h1.png", 20,
                      ifelse(df13$Spreadsheet..Histogram == "h2.png", 29,
                             ifelse(df13$Spreadsheet..Histogram == "h3.png", 37,
                                    ifelse(df13$Spreadsheet..Histogram == "h4.png", 46,
                                           ifelse(df13$Spreadsheet..Histogram == "h5.png", 54,
                                                  ifelse(df13$Spreadsheet..Histogram == "h6.png", 63,
                                                         ifelse(df13$Spreadsheet..Histogram == "h7.png", 71,
                                                                ifelse(df13$Spreadsheet..Histogram == "h8.png", 80, NA))))))))  


# get rid of the rows we don't need: practice runs, continue button presses etc. and only keep Trials, Anxiety and Mood that include all variables we are interested in:
df13 <- df13 %>%
  dplyr::filter(
    (Display == "Trials ") |
      (Display == "Anxiety " & !Trial.Number %in% c(1, 2)) |
      (Display == "Mood " & !Trial.Number %in% c(1, 2))
  )

# # setting Mood and Anxiety trial numbers to match the trials starting from 1 (since we removed the baseline ones above)
df13$Trial.Number <- ifelse(df13$Display == 'Mood ' | df13$Display == 'Anxiety ', df13$Trial.Number - 2, df13$Trial.Number)
df13$Display <- ifelse(df13$Display == 'Mood ' | df13$Display == 'Anxiety ', "Trials", df13$Display)

# renaming the feedback column to fdbk
names(df13)[names(df13) == 'Spreadsheet..Feedback'] <- 'fdbk'

# Now let's create columns for PE (fdbk-hist) and Subj_PE (fdbk_Prediction)

df13$SubjPE <- ifelse(df13$Screen == "Prediction ", df13$fdbk - df13$Response, NA)
df13$PE <- ifelse(df13$Screen == "Prediction ", df13$fdbk - df13$m_hist, NA)
# to keep just one repetition of feedback and mean histogram per trial per subject 
# and replace the rest with NA so that when we want to convert to long format we won't have duplicates
df13$fdbk <- ifelse(df13$Screen == "Prediction ", df13$fdbk, NA)
df13$m_hist <- ifelse(df13$Screen == "Prediction ", df13$m_hist, NA)


long_df13 <- df13 %>%
  select(Random_ID, Trial.Number, fdbk, m_hist, PE, SubjPE) %>%
  pivot_longer(cols = c(fdbk, m_hist, PE, SubjPE),
               names_to = "Screen",
               values_to = "Response")


# This will keep only the rows where 'Response' is not NA
long_df13 <- long_df13[!is.na(long_df13$Response), ]

# Selecting relevant columns from the original df13
df13 <- df13 %>%
  select(-c(fdbk, m_hist, PE, SubjPE))

# Binding the rows together
df13 <- bind_rows(df13, long_df13)

df13$Response <- as.numeric(df13$Response)

# looking at the relationship between PE and SubjPE
df13_PE <- subset(df13, Screen == "PE")
names(df13_PE)[names(df13_PE) == "Screen"] <- "Screen_PE"
names(df13_PE)[names(df13_PE) == "Response"] <- "Response_PE"

df13_SubjPE <- subset(df13, Screen == "SubjPE")
names(df13_SubjPE)[names(df13_SubjPE) == "Screen"] <- "Screen_SubjPE"
names(df13_SubjPE)[names(df13_SubjPE) == "Response"] <- "Response_SubjPE"

df13_fdbk <- subset(df13, Screen == "fdbk")
names(df13_fdbk)[names(df13_fdbk) == "Screen"] <- "Screen_fdbk"
names(df13_fdbk)[names(df13_fdbk) == "Response"] <- "Response_fdbk"

df13_hist <- subset(df13, Screen == "m_hist")
names(df13_hist)[names(df13_hist) == "Screen"] <- "Screen_m_hist"
names(df13_hist)[names(df13_hist) == "Response"] <- "Response_m_hist"

df13_predic <- subset(df13, Screen == "Prediction ")
names(df13_predic)[names(df13_predic) == "Screen"] <- "Screen_pred"
names(df13_predic)[names(df13_predic) == "Response"] <- "Response_pred"

df13_cert <- subset(df13, Screen == "Certainty rating ")
names(df13_cert)[names(df13_cert) == "Screen"] <- "Screen_certainty"
names(df13_cert)[names(df13_cert) == "Response"] <- "Response_certainty"

list_of_dfs_12 <- list(df13_PE, df13_fdbk, df13_hist, df13_predic, df13_cert, df13_SubjPE)

# Using reduce with inner_join
merged_df13 <- reduce(list_of_dfs_12, inner_join, by = c("Random_ID", "Trial.Number"))

df13_Anxious <- subset(df13, Screen == "Anxious")
names(df13_Anxious)[names(df13_Anxious) == "Screen"] <- "Screen_Ax"
names(df13_Anxious)[names(df13_Anxious) == "Response"] <- "Response_Ax"

df13_Happy <- subset(df13, Screen == "Happy")
# df13_fdbk <- subset(df13, Screen == "Prediction")
names(df13_Happy)[names(df13_Happy) == "Screen"] <- "Screen_H"
names(df13_Happy)[names(df13_Happy) == "Response"] <- "Response_H"

final_df13 <- merged_df13 %>%
  inner_join(df13_Anxious, by = c("Random_ID", "Trial.Number")) %>%
  inner_join(df13_Happy, by = c("Random_ID", "Trial.Number"))


# subset only the columns we are interested in
final_df13 <- final_df13[c("Trial.Number", "Random_ID", "Response_H", "Response_Ax", "Response_fdbk", "Response_SubjPE", "Response_PE", "Response_certainty", "Response_m_hist", "Response_pred")]

final_df13 <- final_df13 %>%
  left_join(df13_spin %>% select(Random_ID, mini_SPIN_total), by = "Random_ID")

final_df13 <- final_df13 %>%
  left_join(CESD_data_clean %>% select(Random_ID, CESD_score, Depression_Threshold, Depression_status), by = "Random_ID")

final_df13$Social_Anxiety <- ifelse(final_df13$mini_SPIN_total >= 6, "high", "low")

write.csv(final_df13, "pilot_13_variables.csv", row.names = FALSE)

print("It seems everyone has done all the 48 trials, except subject SUPPRF02872 who has done 40 trials:") 
final_df13 %>%
  group_by(Random_ID) %>%
  summarise(Trial_Count = n())
```
\newpage 
# Relationship between Anxiety and SubjPE


```{r echo=FALSE, warning=FALSE, message=FALSE}

correlations <- final_df13 %>%
  group_by(Random_ID) %>%
  summarise(correlation = cor(Response_Ax, Response_SubjPE, use = "complete.obs")) %>%
  mutate(label = paste("R = ", round(correlation, digits = 2))) 

# calculate the average correlation across all individuals and print it 
average_correlation <- mean(correlations$correlation, na.rm = TRUE)
message_to_print_Ax <- paste("average correlation between anxiety and SubjPE:", average_correlation)

print(message_to_print_Ax)

ggplot(final_df13, aes(x = Response_SubjPE, y = Response_Ax, color = Social_Anxiety, group= Social_Anxiety)) +
  geom_point(aes(color=Social_Anxiety, alpha = 0.3)) +
  geom_smooth(method = "lm", color="blue", aes(group=Random_ID)) + 
  # labs(color="Legend") +
  theme_minimal() +
  xlab("SubjPE: feedback - prediction") + 
  ylab("Anxiety") +
    facet_wrap(~ Random_ID, scales = "free") +
    geom_text(data=correlations, aes(x=Inf, y=Inf, label=label, group=Random_ID), hjust=1.1, vjust=1.1, size=2.7, fontface = "bold", inherit.aes=FALSE) +
    theme(strip.text = element_text(size = 6),
        axis.text.x = element_text(size = 5.5),  
        axis.text.y = element_text(size = 5.5),  
        strip.text.x = element_text(face = "bold"),  
        strip.text.y = element_text(face = "bold"),  
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank()) 
# +
  # ylim(c(0, 100)) + 
  # scale_y_continuous(breaks = seq(0, 100, by = 25), limits = c(0, 100))+
  # xlim(c(-100, 100)) + 
  # scale_x_continuous(breaks = seq(-80, 80, by = 50), limits = c(-80,80))
```

\newpage 
# Relationship between Mood and SubjPE


```{r echo=FALSE, warning=FALSE, message=FALSE}

correlations <- final_df13 %>%
  group_by(Random_ID) %>%
  summarise(correlation = cor(Response_H, Response_SubjPE, use = "complete.obs")) %>%
  mutate(label = paste("R = ", round(correlation, digits = 2))) 

# calculate the average correlation across all individuals and print it 
average_correlation <- mean(correlations$correlation, na.rm = TRUE)
message_to_print_H <- paste("average correlation between mood and SubjPE:", average_correlation)

print(message_to_print_H)

ggplot(final_df13, aes(x = Response_SubjPE, y = Response_H, color = Social_Anxiety, group= Social_Anxiety)) +
  geom_point(aes(color=Social_Anxiety, alpha = 0.3)) +
  geom_smooth(method = "lm", color="blue", aes(group=Random_ID)) + 
  # labs(color="Legend") +
  theme_minimal() +
  xlab("SubjPE: feedback - prediction") + 
  ylab("Mood") +
    facet_wrap(~ Random_ID, scales = "free") +
    geom_text(data=correlations, aes(x=Inf, y=Inf, label=label, group=Random_ID), hjust=1.1, vjust=1.1, size=2.7, fontface = "bold", inherit.aes=FALSE) +
    theme(strip.text = element_text(size = 6),
        axis.text.x = element_text(size = 5.5),  
        axis.text.y = element_text(size = 5.5),  
        strip.text.x = element_text(face = "bold"),  
        strip.text.y = element_text(face = "bold"),  
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank()) +
  ylim(c(0, 100)) + 
  scale_y_continuous(breaks = seq(0, 100, by = 25), limits = c(0, 100))+
  xlim(c(-100, 100)) + 
  scale_x_continuous(breaks = seq(-80, 80, by = 50), limits = c(-80,80))
  
```

\newpage 
# Relationship between Mood and feedback

```{r echo=FALSE, warning=FALSE, message=FALSE}
correlations <- final_df13 %>%
  group_by(Random_ID) %>%
  summarise(correlation = cor(Response_H, Response_fdbk, use = "complete.obs")) %>%
  mutate(label = paste("R = ", round(correlation, digits = 2))) 

# calculate the average correlation across all individuals and print it 
average_correlation <- mean(correlations$correlation, na.rm = TRUE)
message_to_print_H <- paste("average correlation between mood and feedback:", average_correlation)

print(message_to_print_H)

ggplot(final_df13, aes(x = Response_fdbk, y = Response_H, color = Social_Anxiety, group= Social_Anxiety)) +
  geom_point(aes(color=Social_Anxiety, alpha = 0.3)) +
  geom_smooth(method = "lm", color="blue", aes(group=Random_ID)) + 
  # labs(color="Legend") +
  theme_minimal() +
  xlab("Feedback") + 
  ylab("Mood") +
    facet_wrap(~ Random_ID, scales = "free") +
    geom_text(data=correlations, aes(x=Inf, y=Inf, label=label, group=Random_ID), hjust=1.1, vjust=1.1, size=2.7, fontface = "bold", inherit.aes=FALSE) +
    theme(strip.text = element_text(size = 6),
        axis.text.x = element_text(size = 5.5),  
        axis.text.y = element_text(size = 5.5),  
        strip.text.x = element_text(face = "bold"),  
        strip.text.y = element_text(face = "bold"),  
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank()) +
  ylim(c(0, 100)) + 
  scale_y_continuous(breaks = seq(0, 100, by = 25), limits = c(0, 100))+
  xlim(c(-100, 100)) + 
  scale_x_continuous(breaks = seq(0, 100, by = 25), limits = c(0,100))
  
```

\newpage

The group plot for the relationship between Mood and SubjPE


```{r echo=FALSE, warning=FALSE, message=FALSE}
ggplot(final_df13, aes(x = Response_SubjPE, y = Response_H)) +
  geom_smooth(method = "lm", color="blue") + 
  theme_minimal() +
  xlab("SubjPE = feedback - prediction") + 
  ylab("Mood") +
    # facet_wrap(~ Random_ID, scales = "free") +
    theme(strip.text = element_text(size = 6),
        axis.text.x = element_text(size = 5.5),  
        axis.text.y = element_text(size = 5.5),  
        strip.text.x = element_text(face = "bold"),  
        strip.text.y = element_text(face = "bold"),  
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank()) +
  ylim(c(0, 100)) + 
  scale_y_continuous(breaks = seq(0, 100, by = 25), limits = c(0, 100))+
  xlim(c(-100, 100)) + 
  scale_x_continuous(breaks = seq(-80, 80, by = 50), limits = c(-80,80))
  
```


\newpage

The group plot for the relationship between Mood and feedback

```{r echo=FALSE, warning=FALSE, message=FALSE}
ggplot(final_df13, aes(x = Response_fdbk, y = Response_H)) +
  geom_smooth(method = "lm", color="blue") + 
  theme_minimal() +
  xlab("Feedback") + 
  ylab("Mood") +
    theme(strip.text = element_text(size = 6),
        axis.text.x = element_text(size = 5.5),  
        axis.text.y = element_text(size = 5.5),  
        strip.text.x = element_text(face = "bold"),  
        strip.text.y = element_text(face = "bold"),  
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank()) +
  ylim(c(0, 100)) + 
  scale_y_continuous(breaks = seq(0, 100, by = 25), limits = c(0, 100))+
  xlim(c(-100, 100)) + 
  scale_x_continuous(breaks = seq(0, 100, by = 20), limits = c(0,100))
  
```

\newpage 
# Relationship between Mood and prediction

```{r echo=FALSE, warning=FALSE, message=FALSE}
correlations <- final_df13 %>%
  group_by(Random_ID) %>%
  summarise(correlation = cor(Response_H, Response_pred, use = "complete.obs")) %>%
  mutate(label = paste("R = ", round(correlation, digits = 2))) 

# calculate the average correlation across all individuals and print it 
average_correlation <- mean(correlations$correlation, na.rm = TRUE)
message_to_print_H <- paste("average correlation between mood and prediction:", average_correlation)

print(message_to_print_H)

ggplot(final_df13, aes(x = Response_pred, y = Response_H, color = Social_Anxiety, group= Social_Anxiety)) +
  geom_point(aes(color=Social_Anxiety, alpha = 0.3)) +
  geom_smooth(method = "lm", color="blue", aes(group=Random_ID)) + 
  # labs(color="Legend") +
  theme_minimal() +
  xlab("Prediction") + 
  ylab("Mood") +
    facet_wrap(~ Random_ID, scales = "free") +
    geom_text(data=correlations, aes(x=Inf, y=Inf, label=label, group=Random_ID), hjust=1.1, vjust=1.1, size=2.7, fontface = "bold", inherit.aes=FALSE) +
    theme(strip.text = element_text(size = 6),
        axis.text.x = element_text(size = 5.5),  
        axis.text.y = element_text(size = 5.5),  
        strip.text.x = element_text(face = "bold"),  
        strip.text.y = element_text(face = "bold"),  
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank()) +
  ylim(c(0, 100)) + 
  scale_y_continuous(breaks = seq(0, 100, by = 25), limits = c(0, 100))+
  xlim(c(-100, 100)) + 
  scale_x_continuous(breaks = seq(0, 100, by = 25), limits = c(0,100))
  
```


\newpage 
# Relationship between Anxiety and prediction

```{r echo=FALSE, warning=FALSE, message=FALSE}
correlations <- final_df13 %>%
  group_by(Random_ID) %>%
  summarise(correlation = cor(Response_Ax, Response_pred, use = "complete.obs")) %>%
  mutate(label = paste("R = ", round(correlation, digits = 2))) 

# calculate the average correlation across all individuals and print it 
average_correlation <- mean(correlations$correlation, na.rm = TRUE)
message_to_print_H <- paste("average correlation between anxiety and prediction:", average_correlation)

print(message_to_print_H)

ggplot(final_df13, aes(x = Response_pred, y = Response_Ax, color = Social_Anxiety, group= Social_Anxiety)) +
  geom_point(aes(color=Social_Anxiety, alpha = 0.3)) +
  geom_smooth(method = "lm", color="blue", aes(group=Random_ID)) + 
  # labs(color="Legend") +
  theme_minimal() +
  xlab("Prediction") + 
  ylab("Mood") +
    facet_wrap(~ Random_ID, scales = "free") +
    geom_text(data=correlations, aes(x=Inf, y=Inf, label=label, group=Random_ID), hjust=1.1, vjust=1.1, size=2.7, fontface = "bold", inherit.aes=FALSE) +
    theme(strip.text = element_text(size = 6),
        axis.text.x = element_text(size = 5.5),  
        axis.text.y = element_text(size = 5.5),  
        strip.text.x = element_text(face = "bold"),  
        strip.text.y = element_text(face = "bold"),  
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank()) +
  ylim(c(0, 100)) + 
  scale_y_continuous(breaks = seq(0, 100, by = 25), limits = c(0, 100))+
  xlim(c(-100, 100)) + 
  scale_x_continuous(breaks = seq(0, 100, by = 25), limits = c(0,100))
  
```

\newpage 
# Relationship between Anxiety and feedback

```{r echo=FALSE, warning=FALSE, message=FALSE}
correlations <- final_df13 %>%
  group_by(Random_ID) %>%
  summarise(correlation = cor(Response_Ax, Response_fdbk, use = "complete.obs")) %>%
  mutate(label = paste("R = ", round(correlation, digits = 2))) 

# calculate the average correlation across all individuals and print it 
average_correlation <- mean(correlations$correlation, na.rm = TRUE)
message_to_print_H <- paste("average correlation between anxiety and feedback:", average_correlation)

print(message_to_print_H)

ggplot(final_df13, aes(x = Response_fdbk, y = Response_Ax, color = Social_Anxiety, group= Social_Anxiety)) +
  geom_point(aes(color=Social_Anxiety, alpha = 0.3)) +
  geom_smooth(method = "lm", color="blue", aes(group=Random_ID)) + 
  # labs(color="Legend") +
  theme_minimal() +
  xlab("Feedback") + 
  ylab("Anxiety") +
    facet_wrap(~ Random_ID, scales = "free") +
    geom_text(data=correlations, aes(x=Inf, y=Inf, label=label, group=Random_ID), hjust=1.1, vjust=1.1, size=2.7, fontface = "bold", inherit.aes=FALSE) +
    theme(strip.text = element_text(size = 6),
        axis.text.x = element_text(size = 5.5),  
        axis.text.y = element_text(size = 5.5),  
        strip.text.x = element_text(face = "bold"),  
        strip.text.y = element_text(face = "bold"),  
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank()) +
  ylim(c(0, 100)) + 
  scale_y_continuous(breaks = seq(0, 100, by = 25), limits = c(0, 100))+
  xlim(c(-100, 100)) + 
  scale_x_continuous(breaks = seq(0, 100, by = 25), limits = c(0,100))
  
```

\newpage 
# Relationship between mean histogram and prediction


```{r echo=FALSE, warning=FALSE, message=FALSE}
correlations <- final_df13 %>%
  group_by(Random_ID) %>%
  summarise(correlation = cor(Response_m_hist, Response_pred, use = "complete.obs")) %>%
  mutate(label = paste("R = ", round(correlation, digits = 2)))

# calculate the average correlation across all individuals and print it
average_correlation <- mean(correlations$correlation, na.rm = TRUE)
message_to_print_H <- paste("average correlation between histogram mean and prediction:", average_correlation)

print(message_to_print_H)
# 
ggplot(final_df13, aes(x = Response_pred, y = Response_m_hist, color = Social_Anxiety, group= Social_Anxiety)) +
  geom_point(aes(color=Social_Anxiety, alpha = 0.3)) +
  geom_smooth(method = "lm", color="blue", aes(group=Random_ID)) +
  # labs(color="Legend") +
  theme_minimal() +
  xlab("Prediction") +
  ylab("mean_histogram") +
    facet_wrap(~ Random_ID, scales = "free") +
    # geom_text(data=correlations, aes(x=Inf, y=Inf, label=label, group=Random_ID), hjust=1.1, vjust=1.1, size=2.7, fontface = "bold", inherit.aes=FALSE) +
    theme(strip.text = element_text(size = 6),
        axis.text.x = element_text(size = 5.5),
        axis.text.y = element_text(size = 5.5),
        strip.text.x = element_text(face = "bold"),
        strip.text.y = element_text(face = "bold"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank()) +
  ylim(c(0, 100)) +
  scale_y_continuous(breaks = seq(0, 100, by = 25), limits = c(0, 100))+
  xlim(c(0, 100)) +
  scale_x_continuous(breaks = seq(0, 100, by = 25), limits = c(0,100))

ggplot(final_df13, aes(x = Response_pred, y = Response_m_hist, color = Social_Anxiety, group= Social_Anxiety)) +
  # geom_point(aes(color=Social_Anxiety, alpha = 0.3)) +
  geom_smooth(method = "lm", color="blue") + 
  # labs(color="Legend") +
  theme_minimal() +
  xlab("Prediction") + 
  ylab("mean_histogram") +
    # facet_wrap(~ Random_ID, scales = "free") +
    # geom_text(data=correlations, aes(x=Inf, y=Inf, label=label, group=Random_ID), hjust=1.1, vjust=1.1, size=2.7, fontface = "bold", inherit.aes=FALSE) +
    theme(strip.text = element_text(size = 6),
        axis.text.x = element_text(size = 5.5),  
        axis.text.y = element_text(size = 5.5),  
        strip.text.x = element_text(face = "bold"),  
        strip.text.y = element_text(face = "bold"),  
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank()) +
  ylim(c(0, 100)) + 
  scale_y_continuous(breaks = seq(0, 100, by = 25), limits = c(0, 100))+
  xlim(c(0, 100)) + 
  scale_x_continuous(breaks = seq(0, 100, by = 25), limits = c(0,100))
  
```


```{r echo=FALSE, warning=FALSE, message=FALSE}
# trying to keep the BL_1 and BL_2 mood and anxiety ratings
df13_with_BL <- df13_raw[, c("Trial.Number", "Display", "Screen", "Response.Type", "Response", 
                     "Reaction.Time", "Spreadsheet..Histogram", "Spreadsheet..Feedback", "Random_ID")]

df13_with_BL <- df13_with_BL %>%
  mutate(Response = as.numeric(as.character(Response))) %>%
  dplyr::filter(!is.na(Response))

df13_with_BL$Screen <- ifelse(df13_with_BL$Trial.Number == 1 & (df13_with_BL$Display == "Mood " | df13_with_BL$Display == "Anxiety "), "BL_1",
                      ifelse(df13_with_BL$Trial.Number == 2 & (df13_with_BL$Display == "Mood " | df13_with_BL$Display == "Anxiety "), "BL_2", 
                             df13_with_BL$Screen))

df13_with_BL$m_hist <- ifelse(df13_with_BL$Spreadsheet..Histogram == "h1.png", 20,
                      ifelse(df13_with_BL$Spreadsheet..Histogram == "h2.png", 212,
                             ifelse(df13_with_BL$Spreadsheet..Histogram == "h3.png", 37,
                                    ifelse(df13_with_BL$Spreadsheet..Histogram == "h4.png", 46,
                                           ifelse(df13_with_BL$Spreadsheet..Histogram == "h5.png", 54,
                                                  ifelse(df13_with_BL$Spreadsheet..Histogram == "h6.png", 63,
                                                         ifelse(df13_with_BL$Spreadsheet..Histogram == "h7.png", 71,
                                                                ifelse(df13_with_BL$Spreadsheet..Histogram == "h8.png", 80, NA))))))))  


# get rid of the rows we don't need: practice runs, continue button presses etc. and only keep Trials, Anxiety and Mood that include all variables we are interested in:
df13_with_BL <- df13_with_BL %>%
  dplyr::filter(
    (Display == "Trials ") |
      (Display == "Anxiety ") |
      (Display == "Mood ")
  )

# # setting Mood and Anxiety trial numbers to match the trials starting from 1 (since we removed the baseline ones above)
df13_with_BL$Trial.Number <- ifelse(df13_with_BL$Display == 'Mood ' | df13_with_BL$Display == 'Anxiety ', df13_with_BL$Trial.Number - 2, df13_with_BL$Trial.Number)
# df13_with_BL$Display <- ifelse(df13_with_BL$Display == 'Mood ' | df13_with_BL$Display == 'Anxiety ', "Trials", df13_with_BL$Display)

final_df13_with_BL <- df13_with_BL[c("Trial.Number", "Display", "Screen", "Response", "Random_ID")]

final_df13_with_BL <- final_df13_with_BL %>%
  left_join(df13_spin %>% select(Random_ID, mini_SPIN_total), by = "Random_ID")

final_df13_with_BL <- final_df13_with_BL %>%
  left_join(CESD_data_clean %>% select(Random_ID, CESD_score, Depression_Threshold, Depression_status), by = "Random_ID")

final_df13_with_BL$Social_Anxiety <- ifelse(final_df13_with_BL$mini_SPIN_total >= 6, "high", "low")
```



\newpage 
# Mood over time 

Our trials were numbered from 1-50, but the mood and anxiety in trial 1 were asked during the instructions as the task was explained and the one in trial 2, were asked during practice run and before performing the task. It would be interesting to see how these change, especially relevant if at the start they assumed talking to real people but then they change abruptly once they learn/believe they are not talking to real peopele.

```{r echo=FALSE, warning=FALSE, message=FALSE}
df13_BL_ax <- subset(final_df13_with_BL, Display == "Anxiety ")
df13_BL_H <- subset(final_df13_with_BL,Display == "Mood ")

ggplot(df13_BL_H, aes(x = Trial.Number, y = Response, color = Display, group = Display)) +
  geom_line(color = "blue") +
  geom_vline(xintercept = 1, linetype = "dashed", color = "red") + # Adding a vertical line at Trial.Number == 1
  theme_minimal() +
  labs(title = "Mood across time",
       x = "Trial Number",
       y = "Mood",
       color = "") +
  facet_wrap(~ Random_ID, ncol = 6) + 
  theme(strip.text = element_text(size = 6)) +  
  scale_x_continuous(breaks = seq(-1, 48, by = 10), limits = c(-1, 48)) +
  scale_y_continuous(breaks = seq(0, 100, by = 20), limits = c(0, 100))+
  theme(axis.text.x = element_text(size = 5),axis.text.y = element_text(size = 5))

```

\newpage 
# Anxiety over time 
```{r echo=FALSE, warning=FALSE, message=FALSE}
ggplot(df13_BL_ax, aes(x = Trial.Number, y = Response, color = Display, group = Display)) +
  geom_line(color = "blue") +
  geom_vline(xintercept = 1, linetype = "dashed", color = "red") + # Adding a vertical line at Trial.Number == 1
  theme_minimal() +
  labs(title = "Anxiety across time",
       x = "Trial Number",
       y = "Anxiety",
       color = "") +
  facet_wrap(~ Random_ID, ncol = 6) + 
  theme(strip.text = element_text(size = 6)) +  
  scale_x_continuous(breaks = seq(-1, 48, by = 10), limits = c(-1, 48)) +
  scale_y_continuous(breaks = seq(0, 100, by = 20), limits = c(0, 100))+
  theme(axis.text.x = element_text(size = 5),axis.text.y = element_text(size = 5))

```

```{r echo=FALSE, warning=FALSE, message=FALSE}
model2 <- lme4::lmer(Response_H ~ Response_SubjPE + (Response_SubjPE | Random_ID), data = final_df13, control=lmerControl(optimizer="bobyqa"))

coef_fixed <- fixef(model2)
intercept_Mood <- coef_fixed[1]
slope_Mood <- coef_fixed[2]
standard_beta_subjPE <- parameters:: standardise_parameters (model2)
```


\newpage 
# Individual plots with LME for Mood with SubjPE


```{r echo=FALSE, warning=FALSE, message=FALSE}

ggplot(final_df13, aes(x=Response_SubjPE, y=Response_H)) +
  geom_smooth(method = "lm", size = 0.5, se = FALSE, aes(group=Random_ID, color=Social_Anxiety)) +
  scale_color_manual(values = c("low" = "lightblue", "high" = "pink")) +
  geom_abline(intercept = intercept_Mood, slope = slope_Mood, color="purple", linetype="dashed", size=1) +
  xlab("Subjective PE") + 
  ylab("Mood") +
  ggtitle("Relationship between mood and subjective PE",
          subtitle = paste("estimated slopes of the association in n = ", 
                           length(unique(final_df13$Random_ID))))+
  theme(plot.title = element_text(size=14), plot.subtitle = element_text(size = 10))+
  theme(legend.title = element_text(size = 9), legend.text = element_text(size = 8))+
  theme(axis.title = element_text(size = 10))+
  annotate("label", x = 32, y = 55, label = paste("beta = ", round(standard_beta_subjPE$Std_Coefficient[2],2), ", 95%CI = ",
                                                 round(standard_beta_subjPE$CI_low[2],2), "-", 
                                                 round(standard_beta_subjPE$CI_high[2],2))) +
  scale_y_continuous(breaks = seq(0, 100, by = 20), limits = c(0, 100)) +
  scale_x_continuous(breaks = seq(-80, 80, by = 40), limits = c(-80, 80))

# ggsave(filename = "p13_m.png", plot = p13_m, dpi = 300, width = 6, height = 4)
  
```


```{r echo=FALSE, warning=FALSE, message=FALSE}
model2 <- lme4::lmer(Response_Ax ~ Response_SubjPE + (Response_SubjPE | Random_ID), data = final_df13, control=lmerControl(optimizer="bobyqa"))

coef_fixed <- fixef(model2)
intercept_Mood <- coef_fixed[1]
slope_Mood <- coef_fixed[2]
standard_beta_subjPE <- parameters:: standardise_parameters (model2)
```


\newpage 
# Individual plots with LME for Anxiety with SubjPE


```{r echo=FALSE, warning=FALSE, message=FALSE}

ggplot(final_df13, aes(x=Response_SubjPE, y=Response_Ax)) +
  geom_smooth(method = "lm", size = 0.5, se = FALSE, aes(group=Random_ID, color=Social_Anxiety)) +
  scale_color_manual(values = c("low" = "lightblue", "high" = "pink")) +
  geom_abline(intercept = intercept_Mood, slope = slope_Mood, color="purple", linetype="dashed", size=1) +
  xlab("Subjective PE") + 
  ylab("Anxiety") +
  ggtitle("Relationship between Anxiety and subjective PE",
          subtitle = paste("estimated slopes of the association in n = ", 
                           length(unique(final_df13$Random_ID))))+
  theme(plot.title = element_text(size=14), plot.subtitle = element_text(size = 10))+
  theme(legend.title = element_text(size = 9), legend.text = element_text(size = 8))+
  theme(axis.title = element_text(size = 10))+
  annotate("label", x = 32, y = 55, label = paste("beta = ", round(standard_beta_subjPE$Std_Coefficient[2],2), ", 95%CI = ",
                                                 round(standard_beta_subjPE$CI_low[2],2), "-", 
                                                 round(standard_beta_subjPE$CI_high[2],2))) +
  scale_y_continuous(breaks = seq(0, 100, by = 20), limits = c(0, 100)) +
  scale_x_continuous(breaks = seq(-80, 80, by = 40), limits = c(-80, 80))

# ggsave(filename = "p13_ax.png", plot = p13_ax, dpi = 300, width = 6, height = 4)
  
```

\newpage 
# ICC for anxiety

we will now look at the ICC outcome for anxiety
<br> The ICC for anxiety is 0.71, which is moderate according to guidelines by Koo and Li (2016):<br>
<br> below 0.50: poor<br>
<br>between 0.50 and 0.75: moderate<br>
<br>between 0.75 and 0.90: good<br>
<br>above 0.90: excellent<br>
```{r echo=FALSE, warning=FALSE, message=FALSE}
library(irr)
library(lme4)
library(psych)

# change name to model null (same for all others)
model <- lme4::lmer(Response_Ax ~ 1 + (1 | Random_ID), data = final_df13)
# Extract variance components
var_components <- VarCorr(model)
subject_variance <- as.numeric(var_components[1])
residual_variance <- as.numeric(attr(var_components, "sc")^2)

# Calculate ICC
icc <- subject_variance / (subject_variance + residual_variance)
print("lmer for anxiety with just the intercept")
print(icc)

confint(model)
```


\newpage 
# ICC for mood 

The ICC for mood is 0.44, which is lower than anxiety and is actually  within the poor category, according to guidelines by Koo and Li (2016):<br>
<br> below 0.50: poor<br>
<br>between 0.50 and 0.75: moderate<br>
<br>between 0.75 and 0.90: good<br>
<br>above 0.90: excellent<br>
```{r echo=FALSE, warning=FALSE, message=FALSE}
# change name to model null (same for all others)
model <- lme4::lmer(Response_H ~ 1 + (1 | Random_ID), data = final_df13)
# Extract variance components
var_components <- VarCorr(model)
subject_variance <- as.numeric(var_components[1])
residual_variance <- as.numeric(attr(var_components, "sc")^2)

# Calculate ICC
icc <- subject_variance / (subject_variance + residual_variance)
print("lmer for mood with just the intercept")
print(icc)

confint(model)
```