---
title: "Surprise study pilot 15"
author: "Marjan Biria"
date: "2024-02-07"
output: 
    pdf_document:
    toc: true
    toc_depth: 2
    toc_float: true
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(root.dir = "aim_lab_1", echo = TRUE)
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
library(dplyr)
library(ggplot2)
library(tidyr)
library(lme4)
library(parameters)
library(broom.mixed)
library(purrr)
library(conflicted)
library(stringr)
library(readxl)
```


\newpage
# Study description

This study is the same as pilot 14, but we brought the old judge pictures back, and changed the narrative around public speaking. Instead we say "getting better at speaking to others". There have been few other changes such as saying the judge will rate "you" rather than "your description" as we have made the task more social by sharing some criteria they will be rated on that are not just about the description. There have been other minor edits to make the instructions read better and change font sizes etc.

The Gorilla experiment is the following: https://app.gorilla.sc/admin/project/125338
The task is the following: https://app.gorilla.sc/admin/task/768786/editor



```{r echo=FALSE, warning=FALSE, message=FALSE}
df15_raw <- read.csv("/Users/marjan/Desktop/aim_lab_1/SUP_PRF_pilot_vid_big_PE_narr2_oldjudges/SUP_PRF_pilot_vid_big_PE_narr2_oldjudges_v4/SUP_PRF_pilot_vid_big_PE_narr2_oldjudges_v4_task_main.csv")
df15_spin <- read.csv("/Users/marjan/Desktop/aim_lab_1/SUP_PRF_pilot_vid_big_PE_narr2_oldjudges/SUP_PRF_pilot_vid_big_PE_narr2_oldjudges_v4/SUP_PRF_pilot_vid_big_PE_narr2_oldjudges_v4_mini_spin.csv")
df15_cesd <- read.csv("/Users/marjan/Desktop/aim_lab_1/SUP_PRF_pilot_vid_big_PE_narr2_oldjudges/SUP_PRF_pilot_vid_big_PE_narr2_oldjudges_v4/SUP_PRF_pilot_vid_big_PE_narr2_oldjudges_v4_ces_d.csv")

```


```{r echo=FALSE, warning=FALSE, message=FALSE}
# extract CES-D scores
CESD_data_clean <- df15_cesd[, c(32, 34, 36, 38, 40, 42, 44, 46,48,50,
                                 52, 54, 56, 58, 60, 62, 64, 66, 68, 70, 71 )]
# Identify non-ID variable columns
non_id_cols <- setdiff(names(CESD_data_clean), "Random_ID")

# Convert non-ID variables to numeric
CESD_data_clean[, non_id_cols] <- lapply(CESD_data_clean[, non_id_cols], as.numeric)

#change numbers to match CES-D scoring system
excluded_columns <-  c("Random_ID", "Multiple.Choice.Grid.object.3.4...I.felt.I.was.just.as.good.as.other.people..Quantised",
                       "Multiple.Choice.Grid.object.3.8...I.felt.hopeful.about.the.future..Quantised",
                       "Multiple.Choice.Grid.object.3.12...I.was.happy..Quantised",
                       "Multiple.Choice.Grid.object.3.16...I.enjoyed.life..Quantised")
                  

CESD_data_clean<- CESD_data_clean %>%
  mutate(across(-excluded_columns , ~ case_when(
    . == 1 ~ 0,
    . == 2 ~ 1,
    . == 3 ~ 2,
    . == 4 ~ 3,
    TRUE ~ .
  )))


other_columns <- c("Multiple.Choice.Grid.object.3.4...I.felt.I.was.just.as.good.as.other.people..Quantised",
                   "Multiple.Choice.Grid.object.3.8...I.felt.hopeful.about.the.future..Quantised",
                   "Multiple.Choice.Grid.object.3.12...I.was.happy..Quantised",
                   "Multiple.Choice.Grid.object.3.16...I.enjoyed.life..Quantised")
CESD_data_clean<- CESD_data_clean %>%
  mutate(across(other_columns , ~ case_when(
    . == 1 ~ 3,
    . == 2 ~ 2,
    . == 3 ~ 1,
    . == 4 ~ 0,
    TRUE ~ .
  )))

#scoring----
CESD_scores <-  numeric(length(CESD_data_clean$Random_ID))
CESD_scores <- 0
Questions <- c(1:20)

for (i in 1:nrow(CESD_data_clean)) {
  CESD_score <- sum(CESD_data_clean[i, Questions])
  CESD_scores[i] <- CESD_score
}

CESD_data_clean$CESD_score <-  CESD_scores

CESD_data_clean$Depression_Threshold<- 0
CESD_data_clean$Depression_status <- "Not_Depressed"

#Assign "1" if they meet Depression threshold 
for (i in 1:nrow(CESD_data_clean)) {
  if (CESD_data_clean$CESD_score[i] >= 16) {
    CESD_data_clean$Depression_Threshold[i] <- 1
    CESD_data_clean$Depression_status[i] <- "Depressed"
  }
}
```


```{r echo=FALSE, warning=FALSE, message=FALSE}

df15_spin <- df15_spin %>%
  rename(
   "Q1" =  "Rating.Scale.object.2.Fear.of.embarrassment.causes.me.to.avoid.doing.things.or.speaking.to.people.",
   "Q2" =  "Rating.Scale.object.2.I.avoid.activities.in.which.I.am.the.center.of.attention.",
   "Q3" = "Rating.Scale.object.2.Being.embarrassed.or.looking.stupid.are.among.my.worst.fears."
  )

df15_spin <- df15_spin %>%
  rowwise() %>%
  mutate(mini_SPIN_total = sum(c(Q1, Q2, Q3), na.rm = TRUE)) %>%
  ungroup()


# create a new df15 that only keeps the columns we need
df15 <- df15_raw[, c("Trial.Number", "Display", "Screen", "Response.Type", "Response", 
                     "Reaction.Time", "Spreadsheet..Histogram", "Spreadsheet..Feedback", "Random_ID")]

df15 <- df15 %>%
  mutate(Response = as.numeric(as.character(Response))) %>%
  dplyr::filter(!is.na(Response))

df15$Screen <- ifelse(df15$Trial.Number == 1 & (df15$Display == "Mood " | df15$Display == "Anxiety "), "BL_1",
                      ifelse(df15$Trial.Number == 2 & (df15$Display == "Mood " | df15$Display == "Anxiety "), "BL_2", 
                             df15$Screen))

df15$m_hist <- ifelse(df15$Spreadsheet..Histogram == "h1.png", 20,
                      ifelse(df15$Spreadsheet..Histogram == "h2.png", 29,
                             ifelse(df15$Spreadsheet..Histogram == "h3.png", 37,
                                    ifelse(df15$Spreadsheet..Histogram == "h4.png", 46,
                                           ifelse(df15$Spreadsheet..Histogram == "h5.png", 54,
                                                  ifelse(df15$Spreadsheet..Histogram == "h6.png", 63,
                                                         ifelse(df15$Spreadsheet..Histogram == "h7.png", 71,
                                                                ifelse(df15$Spreadsheet..Histogram == "h8.png", 80, NA))))))))  


# get rid of the rows we don't need: practice runs, continue button presses etc. and only keep Trials, Anxiety and Mood that include all variables we are interested in:
df15 <- df15 %>%
  dplyr::filter(
    (Display == "Trials ") |
      (Display == "Exit") |
      (Display == "Anxiety " & !Trial.Number %in% c(1, 2)) |
      (Display == "Mood " & !Trial.Number %in% c(1, 2))
  )

# # setting Mood and Anxiety trial numbers to match the trials starting from 1 (since we removed the baseline ones above)
df15$Trial.Number <- ifelse(df15$Display == 'Mood ' | df15$Display == 'Anxiety ', df15$Trial.Number - 2, df15$Trial.Number)
df15$Display <- ifelse(df15$Display == 'Mood ' | df15$Display == 'Anxiety ', "Trials", df15$Display)

# renaming the feedback column to fdbk
names(df15)[names(df15) == 'Spreadsheet..Feedback'] <- 'fdbk'

# Now let's create columns for PE (fdbk-hist) and Subj_PE (fdbk_Prediction)

df15$SubjPE <- ifelse(df15$Screen == "Prediction ", df15$fdbk - df15$Response, NA)
df15$PE <- ifelse(df15$Screen == "Prediction ", df15$fdbk - df15$m_hist, NA)
# to keep just one repetition of feedback and mean histogram per trial per subject 
# and replace the rest with NA so that when we want to convert to long format we won't have duplicates
df15$fdbk <- ifelse(df15$Screen == "Prediction ", df15$fdbk, NA)
df15$m_hist <- ifelse(df15$Screen == "Prediction ", df15$m_hist, NA)
df15$stress_level <- ifelse(df15$Screen == "Screen 12", df15$Response, NA)

long_df15 <- df15 %>%
  select(Random_ID, Trial.Number, fdbk, m_hist, PE, SubjPE, stress_level) %>%
  pivot_longer(cols = c(fdbk, m_hist, PE, SubjPE, stress_level),
               names_to = "Screen",
               values_to = "Response")

# This will keep only the rows where 'Response' is not NA
long_df15 <- long_df15[!is.na(long_df15$Response), ]

# Selecting relevant columns from the original df15
df15 <- df15 %>%
  select(-c(fdbk, m_hist, PE, SubjPE, stress_level))

# Binding the rows together
df15 <- bind_rows(df15, long_df15)

df15$Response <- as.numeric(df15$Response)

# looking at the relationship between PE and SubjPE
df15_PE <- subset(df15, Screen == "PE")
names(df15_PE)[names(df15_PE) == "Screen"] <- "Screen_PE"
names(df15_PE)[names(df15_PE) == "Response"] <- "Response_PE"

df15_SubjPE <- subset(df15, Screen == "SubjPE")
names(df15_SubjPE)[names(df15_SubjPE) == "Screen"] <- "Screen_SubjPE"
names(df15_SubjPE)[names(df15_SubjPE) == "Response"] <- "Response_SubjPE"

df15_fdbk <- subset(df15, Screen == "fdbk")
names(df15_fdbk)[names(df15_fdbk) == "Screen"] <- "Screen_fdbk"
names(df15_fdbk)[names(df15_fdbk) == "Response"] <- "Response_fdbk"

df15_hist <- subset(df15, Screen == "m_hist")
names(df15_hist)[names(df15_hist) == "Screen"] <- "Screen_m_hist"
names(df15_hist)[names(df15_hist) == "Response"] <- "Response_m_hist"

df15_stress_level <- subset(df15, Screen == "Screen 12")
names(df15_stress_level)[names(df15_stress_level) == "Screen"] <- "Screen_stress_level"
names(df15_stress_level)[names(df15_stress_level) == "Response"] <- "Response_stress_level"

df15_predic <- subset(df15, Screen == "Prediction ")
names(df15_predic)[names(df15_predic) == "Screen"] <- "Screen_pred"
names(df15_predic)[names(df15_predic) == "Response"] <- "Response_pred"

df15_cert <- subset(df15, Screen == "Certainty rating ")
names(df15_cert)[names(df15_cert) == "Screen"] <- "Screen_certainty"
names(df15_cert)[names(df15_cert) == "Response"] <- "Response_certainty"

list_of_dfs_15 <- list(df15_PE, df15_fdbk, df15_hist, df15_predic, df15_cert, df15_SubjPE)

# Using reduce with inner_join
merged_df15 <- reduce(list_of_dfs_15, inner_join, by = c("Random_ID", "Trial.Number"))

df15_Anxious <- subset(df15, Screen == "Anxious")
names(df15_Anxious)[names(df15_Anxious) == "Screen"] <- "Screen_Ax"
names(df15_Anxious)[names(df15_Anxious) == "Response"] <- "Response_Ax"

df15_Happy <- subset(df15, Screen == "Happy")
# df15_fdbk <- subset(df15, Screen == "Prediction")
names(df15_Happy)[names(df15_Happy) == "Screen"] <- "Screen_H"
names(df15_Happy)[names(df15_Happy) == "Response"] <- "Response_H"

final_df15 <- merged_df15 %>%
  inner_join(df15_Anxious, by = c("Random_ID", "Trial.Number")) %>%
  inner_join(df15_Happy, by = c("Random_ID", "Trial.Number"))


# subset only the columns we are interested in
final_df15 <- final_df15[c("Trial.Number", "Random_ID", "Response_H", "Response_Ax", "Response_fdbk", "Response_SubjPE", "Response_PE", "Response_certainty", "Response_m_hist", "Response_pred")]

final_df15 <- final_df15 %>%
  left_join(df15_spin %>% select(Random_ID, mini_SPIN_total), by = "Random_ID")

final_df15 <- final_df15 %>%
  left_join(df15_stress_level %>% select(Random_ID, Response_stress_level), by = "Random_ID")

final_df15 <- final_df15 %>%
  left_join(CESD_data_clean %>% select(Random_ID, CESD_score, Depression_Threshold, Depression_status), by = "Random_ID")

final_df15$Social_Anxiety <- ifelse(final_df15$mini_SPIN_total >= 6, "high", "low")

write.csv(final_df15, "pilot_15_variables.csv", row.names = FALSE)

# print("It seems everyone has done all the 48 trials, except subjects SUPPRF05583 (trial_nr = 26), SUPPRF08160 (trial_nr = 39),  SUPPRF68822 (47), SUPPRF80696 (51??! how?? this person was stuck on trial 13, their answer and PE were repeated so I wonder whether for some reason this happened once but saved 3 times when writing the output file? we should ask Gorilla what happened there!):") 
final_df15 %>%
  group_by(Random_ID) %>%
  summarise(Trial.Number = n())

write.csv(final_df15, "final_df15_with_stresslevels.csv", row.names = FALSE)

```

\newpage 
# Relationship between prediction and mean histogram

```{r echo=FALSE, warning=FALSE, message=FALSE}
correlations <- final_df15 %>%
  group_by(Random_ID) %>%
  summarise(correlation = cor(Response_m_hist, Response_pred, use = "complete.obs")) %>%
  mutate(label = paste("R = ", round(correlation, digits = 2))) 

# calculate the average correlation across all individuals and print it 
average_correlation <- mean(correlations$correlation, na.rm = TRUE)
message_to_print_H <- paste("average correlation between mean_hist and prediction:", average_correlation)

print(message_to_print_H)

ggplot(final_df15, aes(x = Response_m_hist, y = Response_pred, color = Social_Anxiety, group= Social_Anxiety)) +
  geom_point(aes(color=Social_Anxiety, alpha = 0.3)) +
  geom_smooth(method = "lm", color="blue", aes(group=Random_ID)) + 
  # labs(color="Legend") +
  theme_minimal() +
  xlab("prediction") + 
  ylab("mean_histogram") +
    facet_wrap(~ Random_ID, scales = "free") +
    geom_text(data=correlations, aes(x=Inf, y=Inf, label=label, group=Random_ID), hjust=1.1, vjust=1.1, size=2.7, fontface = "bold", inherit.aes=FALSE) +
    theme(strip.text = element_text(size = 6),
        axis.text.x = element_text(size = 5.5),  
        axis.text.y = element_text(size = 5.5),  
        strip.text.x = element_text(face = "bold"),  
        strip.text.y = element_text(face = "bold"),  
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank()) 
# +
  # ylim(c(0, 100)) + 
  # scale_y_continuous(breaks = seq(0, 100, by = 25), limits = c(0, 100))+
  # xlim(c(-100, 100)) + 
  # scale_x_continuous(breaks = seq(0, 100, by = 25), limits = c(0,100))
  
```

\newpage 
# Relationship between Anxiety and SubjPE


```{r echo=FALSE, warning=FALSE, message=FALSE}
correlations_Ax <- final_df15 %>%
  group_by(Random_ID) %>%
  summarise(correlation = cor(Response_Ax, Response_SubjPE, use = "complete.obs")) %>%
  mutate(label = paste("R = ", round(correlation, digits = 2))) 

# calculate the average correlation across all individuals and print it 
average_correlation <- mean(correlations_Ax$correlation, na.rm = TRUE)
message_to_print_Ax <- paste("average correlation between anxiety and SubjPE:", average_correlation)

print(message_to_print_Ax)

ggplot(final_df15, aes(x = Response_SubjPE, y = Response_Ax, color = Social_Anxiety, group= Social_Anxiety)) +
  geom_point(aes(color=Social_Anxiety, alpha = 0.3)) +
  geom_smooth(method = "lm", color="blue", aes(group=Random_ID)) + 
  # labs(color="Legend") +
  theme_minimal() +
  xlab("SubjPE: feedback - prediction") + 
  ylab("Anxiety") +
    facet_wrap(~ Random_ID, scales = "free") +
    geom_text(data=correlations_Ax, aes(x=Inf, y=Inf, label=label, group=Random_ID), hjust=1.1, vjust=1.1, size=2.7, fontface = "bold", inherit.aes=FALSE) +
    theme(strip.text = element_text(size = 6),
        axis.text.x = element_text(size = 5.5),  
        axis.text.y = element_text(size = 5.5),  
        strip.text.x = element_text(face = "bold"),  
        strip.text.y = element_text(face = "bold"),  
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank()) +
ylim(c(0, 100)) +
scale_y_continuous(breaks = seq(0, 100, by = 25), limits = c(0, 100))+
xlim(c(-100, 100)) +
scale_x_continuous(breaks = seq(-80, 80, by = 50), limits = c(-80,80))
```

\newpage 
# Relationship between Mood and SubjPE


```{r echo=FALSE, warning=FALSE, message=FALSE}

correlations_M <- final_df15 %>%
  group_by(Random_ID) %>%
  summarise(correlation = cor(Response_H, Response_SubjPE, use = "complete.obs")) %>%
  mutate(label = paste("R = ", round(correlation, digits = 2))) 

# calculate the average correlation across all individuals and print it 
average_correlation <- mean(correlations_M$correlation, na.rm = TRUE)
message_to_print_H <- paste("average correlation between mood and SubjPE:", average_correlation)

print(message_to_print_H)

ggplot(final_df15, aes(x = Response_SubjPE, y = Response_H, color = Social_Anxiety, group= Social_Anxiety)) +
  geom_point(aes(color=Social_Anxiety, alpha = 0.3)) +
  geom_smooth(method = "lm", color="blue", aes(group=Random_ID)) + 
  # labs(color="Legend") +
  theme_minimal() +
  xlab("SubjPE: feedback - prediction") + 
  ylab("Mood") +
    facet_wrap(~ Random_ID, scales = "free") +
    geom_text(data=correlations_M, aes(x=Inf, y=Inf, label=label, group=Random_ID), hjust=1.1, vjust=1.1, size=2.7, fontface = "bold", inherit.aes=FALSE) +
    theme(strip.text = element_text(size = 6),
        axis.text.x = element_text(size = 5.5),  
        axis.text.y = element_text(size = 5.5),  
        strip.text.x = element_text(face = "bold"),  
        strip.text.y = element_text(face = "bold"),  
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank()) +
  ylim(c(0, 100)) + 
  scale_y_continuous(breaks = seq(0, 100, by = 25), limits = c(0, 100))+
  xlim(c(-100, 100)) + 
  scale_x_continuous(breaks = seq(-80, 80, by = 50), limits = c(-80,80))
  
```

\newpage 
# Relationship between Mood and feedback

The relationship between mood and feedback seems to be stronger than mood and subjective PE (0.24 vs 0.17), so it seems people may care more about the feedback as receiving reward or punishment, rather than social PE? The relationship between subjective PE with both anxiety and mood has been the weakest across all pilots. We need to make sure it is only because of changing the pictures of virtual players, maybe by changing the narrative they would assume that the other players are also learning how to do public speaking (less intimidating than someone who is an expert?).

To be sure, I wonder if we want to repeat the pilot and just replace the images?

```{r echo=FALSE, warning=FALSE, message=FALSE}
correlations_Mfd <- final_df15 %>%
  group_by(Random_ID) %>%
  summarise(correlation = cor(Response_H, Response_fdbk, use = "complete.obs")) %>%
  mutate(label = paste("R = ", round(correlation, digits = 2))) 

# calculate the average correlation across all individuals and print it 
average_correlation <- mean(correlations_Mfd$correlation, na.rm = TRUE)
message_to_print_H <- paste("average correlation between mood and feedback:", average_correlation)

print(message_to_print_H)

ggplot(final_df15, aes(x = Response_fdbk, y = Response_H, color = Social_Anxiety, group= Social_Anxiety)) +
  geom_point(aes(color=Social_Anxiety, alpha = 0.3)) +
  geom_smooth(method = "lm", color="blue", aes(group=Random_ID)) + 
  # labs(color="Legend") +
  theme_minimal() +
  xlab("Feedback") + 
  ylab("Mood") +
    facet_wrap(~ Random_ID, scales = "free") +
    geom_text(data=correlations_Mfd, aes(x=Inf, y=Inf, label=label, group=Random_ID), hjust=1.1, vjust=1.1, size=2.7, fontface = "bold", inherit.aes=FALSE) +
    theme(strip.text = element_text(size = 6),
        axis.text.x = element_text(size = 5.5),  
        axis.text.y = element_text(size = 5.5),  
        strip.text.x = element_text(face = "bold"),  
        strip.text.y = element_text(face = "bold"),  
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank()) +
  ylim(c(0, 100)) + 
  scale_y_continuous(breaks = seq(0, 100, by = 25), limits = c(0, 100))+
  xlim(c(-100, 100)) + 
  scale_x_continuous(breaks = seq(0, 100, by = 25), limits = c(0,100))
  
```



\newpage 
# Relationship between Mood and prediction

```{r echo=FALSE, warning=FALSE, message=FALSE}
correlations <- final_df15 %>%
  group_by(Random_ID) %>%
  summarise(correlation = cor(Response_H, Response_pred, use = "complete.obs")) %>%
  mutate(label = paste("R = ", round(correlation, digits = 2))) 

# calculate the average correlation across all individuals and print it 
average_correlation <- mean(correlations$correlation, na.rm = TRUE)
message_to_print_H <- paste("average correlation between mood and prediction:", average_correlation)

print(message_to_print_H)

ggplot(final_df15, aes(x = Response_pred, y = Response_H, color = Social_Anxiety, group= Social_Anxiety)) +
  geom_point(aes(color=Social_Anxiety, alpha = 0.3)) +
  geom_smooth(method = "lm", color="blue", aes(group=Random_ID)) + 
  # labs(color="Legend") +
  theme_minimal() +
  xlab("Prediction") + 
  ylab("Mood") +
    facet_wrap(~ Random_ID, scales = "free") +
    geom_text(data=correlations, aes(x=Inf, y=Inf, label=label, group=Random_ID), hjust=1.1, vjust=1.1, size=2.7, fontface = "bold", inherit.aes=FALSE) +
    theme(strip.text = element_text(size = 6),
        axis.text.x = element_text(size = 5.5),  
        axis.text.y = element_text(size = 5.5),  
        strip.text.x = element_text(face = "bold"),  
        strip.text.y = element_text(face = "bold"),  
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank()) +
  ylim(c(0, 100)) + 
  scale_y_continuous(breaks = seq(0, 100, by = 25), limits = c(0, 100))+
  xlim(c(-100, 100)) + 
  scale_x_continuous(breaks = seq(0, 100, by = 25), limits = c(0,100))
  
```


\newpage 
# Relationship between Anxiety and prediction

```{r echo=FALSE, warning=FALSE, message=FALSE}
correlations <- final_df15 %>%
  group_by(Random_ID) %>%
  summarise(correlation = cor(Response_Ax, Response_pred, use = "complete.obs")) %>%
  mutate(label = paste("R = ", round(correlation, digits = 2))) 

# calculate the average correlation across all individuals and print it 
average_correlation <- mean(correlations$correlation, na.rm = TRUE)
message_to_print_H <- paste("average correlation between anxiety and prediction:", average_correlation)

print(message_to_print_H)

ggplot(final_df15, aes(x = Response_pred, y = Response_Ax, color = Social_Anxiety, group= Social_Anxiety)) +
  geom_point(aes(color=Social_Anxiety, alpha = 0.3)) +
  geom_smooth(method = "lm", color="blue", aes(group=Random_ID)) + 
  # labs(color="Legend") +
  theme_minimal() +
  xlab("Prediction") + 
  ylab("Mood") +
    facet_wrap(~ Random_ID, scales = "free") +
    geom_text(data=correlations, aes(x=Inf, y=Inf, label=label, group=Random_ID), hjust=1.1, vjust=1.1, size=2.7, fontface = "bold", inherit.aes=FALSE) +
    theme(strip.text = element_text(size = 6),
        axis.text.x = element_text(size = 5.5),  
        axis.text.y = element_text(size = 5.5),  
        strip.text.x = element_text(face = "bold"),  
        strip.text.y = element_text(face = "bold"),  
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank()) +
  ylim(c(0, 100)) + 
  scale_y_continuous(breaks = seq(0, 100, by = 25), limits = c(0, 100))+
  xlim(c(-100, 100)) + 
  scale_x_continuous(breaks = seq(0, 100, by = 25), limits = c(0,100))
  
```

\newpage 
# Relationship between Anxiety and feedback

```{r echo=FALSE, warning=FALSE, message=FALSE}
correlations <- final_df15 %>%
  group_by(Random_ID) %>%
  summarise(correlation = cor(Response_Ax, Response_fdbk, use = "complete.obs")) %>%
  mutate(label = paste("R = ", round(correlation, digits = 2))) 

# calculate the average correlation across all individuals and print it 
average_correlation <- mean(correlations$correlation, na.rm = TRUE)
message_to_print_H <- paste("average correlation between anxiety and feedback:", average_correlation)

print(message_to_print_H)

ggplot(final_df15, aes(x = Response_fdbk, y = Response_Ax, color = Social_Anxiety, group= Social_Anxiety)) +
  geom_point(aes(color=Social_Anxiety, alpha = 0.3)) +
  geom_smooth(method = "lm", color="blue", aes(group=Random_ID)) + 
  # labs(color="Legend") +
  theme_minimal() +
  xlab("Feedback") + 
  ylab("Anxiety") +
    facet_wrap(~ Random_ID, scales = "free") +
    geom_text(data=correlations, aes(x=Inf, y=Inf, label=label, group=Random_ID), hjust=1.1, vjust=1.1, size=2.7, fontface = "bold", inherit.aes=FALSE) +
    theme(strip.text = element_text(size = 6),
        axis.text.x = element_text(size = 5.5),  
        axis.text.y = element_text(size = 5.5),  
        strip.text.x = element_text(face = "bold"),  
        strip.text.y = element_text(face = "bold"),  
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank()) +
  ylim(c(0, 100)) + 
  scale_y_continuous(breaks = seq(0, 100, by = 25), limits = c(0, 100))+
  xlim(c(-100, 100)) + 
  scale_x_continuous(breaks = seq(0, 100, by = 25), limits = c(0,100))
  
```


```{r echo=FALSE, warning=FALSE, message=FALSE}
# trying to keep the BL_1 and BL_2 mood and anxiety ratings
df15_with_BL <- df15_raw[, c("Trial.Number", "Display", "Screen", "Response.Type", "Response", 
                     "Reaction.Time", "Spreadsheet..Histogram", "Spreadsheet..Feedback", "Random_ID")]

df15_with_BL <- df15_with_BL %>%
  mutate(Response = as.numeric(as.character(Response))) %>%
  dplyr::filter(!is.na(Response))

df15_with_BL$Screen <- ifelse(df15_with_BL$Trial.Number == 1 & (df15_with_BL$Display == "Mood " | df15_with_BL$Display == "Anxiety "), "BL_1",
                      ifelse(df15_with_BL$Trial.Number == 2 & (df15_with_BL$Display == "Mood " | df15_with_BL$Display == "Anxiety "), "BL_2", 
                             df15_with_BL$Screen))

df15_with_BL$m_hist <- ifelse(df15_with_BL$Spreadsheet..Histogram == "h1.png", 20,
                      ifelse(df15_with_BL$Spreadsheet..Histogram == "h2.png", 29,
                             ifelse(df15_with_BL$Spreadsheet..Histogram == "h3.png", 37,
                                    ifelse(df15_with_BL$Spreadsheet..Histogram == "h4.png", 46,
                                           ifelse(df15_with_BL$Spreadsheet..Histogram == "h5.png", 54,
                                                  ifelse(df15_with_BL$Spreadsheet..Histogram == "h6.png", 63,
                                                         ifelse(df15_with_BL$Spreadsheet..Histogram == "h7.png", 71,
                                                                ifelse(df15_with_BL$Spreadsheet..Histogram == "h8.png", 80, NA))))))))  


# get rid of the rows we don't need: practice runs, continue button presses etc. and only keep Trials, Anxiety and Mood that include all variables we are interested in:
df15_with_BL <- df15_with_BL %>%
  dplyr::filter(
    (Display == "Trials ") |
      (Display == "Anxiety ") |
      (Display == "Mood ")
  )

# # setting Mood and Anxiety trial numbers to match the trials starting from 1 (since we removed the baseline ones above)
df15_with_BL$Trial.Number <- ifelse(df15_with_BL$Display == 'Mood ' | df15_with_BL$Display == 'Anxiety ', df15_with_BL$Trial.Number - 2, df15_with_BL$Trial.Number)
# df15_with_BL$Display <- ifelse(df15_with_BL$Display == 'Mood ' | df15_with_BL$Display == 'Anxiety ', "Trials", df15_with_BL$Display)

final_df15_with_BL <- df15_with_BL[c("Trial.Number", "Display", "Screen", "Response", "Random_ID")]

final_df15_with_BL <- final_df15_with_BL %>%
  left_join(df15_spin %>% select(Random_ID, mini_SPIN_total), by = "Random_ID")

final_df15_with_BL <- final_df15_with_BL %>%
  left_join(CESD_data_clean %>% select(Random_ID, CESD_score, Depression_Threshold, Depression_status), by = "Random_ID")

final_df15_with_BL$Social_Anxiety <- ifelse(final_df15_with_BL$mini_SPIN_total >= 6, "high", "low")
```



\newpage 
# Mood over time 


```{r echo=FALSE, warning=FALSE, message=FALSE}
df15_BL_ax <- subset(final_df15_with_BL, Display == "Anxiety ")
df15_BL_H <- subset(final_df15_with_BL,Display == "Mood ")

ggplot(df15_BL_H, aes(x = Trial.Number, y = Response, color = Display, group = Display)) +
  geom_line(color = "blue") +
  geom_vline(xintercept = 1, linetype = "dashed", color = "red") + # Adding a vertical line at Trial.Number == 1
  theme_minimal() +
  labs(title = "Mood across time",
       x = "Trial Number",
       y = "Mood",
       color = "") +
  facet_wrap(~ Random_ID, ncol = 6) + 
  theme(strip.text = element_text(size = 6)) +  
  scale_x_continuous(breaks = seq(-1, 48, by = 10), limits = c(-1, 48)) +
  scale_y_continuous(breaks = seq(0, 100, by = 20), limits = c(0, 100))+
  theme(axis.text.x = element_text(size = 5),axis.text.y = element_text(size = 5))

```

\newpage 
# Anxiety over time 
```{r echo=FALSE, warning=FALSE, message=FALSE}
ggplot(df15_BL_ax, aes(x = Trial.Number, y = Response, color = Display, group = Display)) +
  geom_line(color = "blue") +
  geom_vline(xintercept = 1, linetype = "dashed", color = "red") + # Adding a vertical line at Trial.Number == 1
  theme_minimal() +
  labs(title = "Anxiety across time",
       x = "Trial Number",
       y = "Anxiety",
       color = "") +
  facet_wrap(~ Random_ID, ncol = 6) + 
  theme(strip.text = element_text(size = 6)) +  
  scale_x_continuous(breaks = seq(-1, 48, by = 10), limits = c(-1, 48)) +
  scale_y_continuous(breaks = seq(0, 100, by = 20), limits = c(0, 100))+
  theme(axis.text.x = element_text(size = 5),axis.text.y = element_text(size = 5))

```


\newpage
# LME models for Mood and SubjPE

When looking at subjective PE, the best model is  Mood ~ SubjPE  + (SubjPE | Random_ID) with an AIC of 11681.18
When including feedback the best model is Mood ~ feedback  + (feedback | Random_ID) with an AIC of 11615
```{r echo=FALSE, warning=FALSE, message=FALSE}
model1 <- lme4::lmer(Response_H ~ Response_SubjPE + (1 | Random_ID), data = final_df15, control=lmerControl(optimizer="bobyqa"))
model2 <- lme4::lmer(Response_H ~ Response_SubjPE + (Response_SubjPE | Random_ID), data = final_df15, control=lmerControl(optimizer="bobyqa"))
model3 <- lme4::lmer(Response_H ~ Response_SubjPE * mini_SPIN_total + (Response_SubjPE | Random_ID), data = final_df15, control=lmerControl(optimizer="bobyqa"))

model4 <- lme4::lmer(Response_H ~ Response_fdbk + (1 | Random_ID), data = final_df15, control=lmerControl(optimizer="bobyqa"))
model5 <- lme4::lmer(Response_H ~ Response_fdbk + (Response_fdbk | Random_ID), data = final_df15, control=lmerControl(optimizer="bobyqa"))
model6 <- lme4::lmer(Response_H ~ Response_fdbk * mini_SPIN_total + (Response_fdbk | Random_ID), data = final_df15, control=lmerControl(optimizer="bobyqa"))

summary(model1)
summary(model2)
summary(model3)
summary(model4)
summary(model5)
summary(model6)

AIC(model1)
AIC(model2)
AIC(model3)
AIC(model4)
AIC(model5)
AIC(model6)

# anova(model2, model5)

coef_fixed <- fixef(model5)
intercept_Mood <- coef_fixed[1]
slope_Mood <- coef_fixed[2]
standard_beta_fdbk <- parameters:: standardise_parameters (model5)
standard_beta_subjPE <- parameters:: standardise_parameters (model2)
# test <- model5 %>% broom.mixed::tidy("fixed") 
```

\newpage 
# Individual plots with LME for Mood with SubjPE
When looking at subjective PE, the best model is  Mood ~ SubjPE  + (SubjPE | Random_ID) with an AIC of 11681.18

```{r echo=FALSE, warning=FALSE, message=FALSE}

ggplot(final_df15, aes(x=Response_SubjPE, y=Response_H)) +
  geom_smooth(method = "lm", size = 0.5, se = FALSE, aes(group=Random_ID, color=Social_Anxiety)) +
  scale_color_manual(values = c("low" = "lightblue", "high" = "pink")) +
  geom_abline(intercept = intercept_Mood, slope = slope_Mood, color="purple", linetype="dashed", size=1) +
  xlab("Subjective PE") + 
  ylab("Mood") +
  ggtitle("Relationship between Mood and subjective PE",
          subtitle = paste("estimated slopes of the association in n = ", 
                           length(unique(final_df15$Random_ID))))+
  theme(plot.title = element_text(size=15), plot.subtitle = element_text(size = 10))+
  theme(legend.title = element_text(size = 9), legend.text = element_text(size = 8))+
  theme(axis.title = element_text(size = 10))+
  annotate("label", x = 32, y = 55, label = paste("beta = ", round(standard_beta_subjPE$Std_Coefficient[2],2), ", 95%CI = ",
                                                 round(standard_beta_subjPE$CI_low[2],2), "-", 
                                                 round(standard_beta_subjPE$CI_high[2],2))) +
  scale_y_continuous(breaks = seq(0, 100, by = 20), limits = c(0, 100))+
  scale_x_continuous(breaks = seq(-80, 80, by = 40), limits = c(-80, 80))

# ggsave(filename = "p15_m.png", plot = p15_m, dpi = 300, width = 6, height = 4)
  
```


\newpage 
# Individual plots with LME for Mood with feedback instead of SubjPE

When including feedback the best model is Mood ~ feedback  + (feedback | Random_ID) with an AIC of 11615.

```{r echo=FALSE, warning=FALSE, message=FALSE}

ggplot(final_df15, aes(x=Response_fdbk, y=Response_H)) +
  geom_smooth(method = "lm", size = 0.5, se = FALSE, aes(group=Random_ID, color=Social_Anxiety)) +
  scale_color_manual(values = c("low" = "lightblue", "high" = "pink")) +
  geom_abline(intercept = intercept_Mood, slope = slope_Mood, color="purple", linetype="dashed", size=1) +
  xlab("Feedback") + 
  ylab("Mood") +
  ggtitle("Relationship between Mood and Feedback",
          subtitle = paste("estimated slopes of the association in n = ", 
                           length(unique(final_df15$Random_ID))))+
  theme(plot.title = element_text(size=15), plot.subtitle = element_text(size = 10))+
  theme(legend.title = element_text(size = 9), legend.text = element_text(size = 8))+
  theme(axis.title = element_text(size = 10))+
  annotate("label", x = 32, y = 55, label = paste("beta = ", round(standard_beta_fdbk$Std_Coefficient[2],2), ", 95%CI = ",
                                                 round(standard_beta_fdbk$CI_low[2],2), "-", 
                                                 round(standard_beta_fdbk$CI_high[2],2))) 
  
```

\newpage
# LME models for Anxiety and SubjPE

When looking at subjective PE, the best model is  Anxiety ~ SubjPE  + (SubjPE | Random_ID) with an AIC of 11764.61
When including feedback the best model is Anxiety ~ feedback  + (Random_ID) with an AIC of 11705.6

```{r echo=FALSE, warning=FALSE, message=FALSE}
model1 <- lme4::lmer(Response_Ax ~ Response_SubjPE + (1 | Random_ID), data = final_df15, control=lmerControl(optimizer="bobyqa"))
model2 <- lme4::lmer(Response_Ax ~ Response_SubjPE + (Response_SubjPE | Random_ID), data = final_df15, control=lmerControl(optimizer="bobyqa"))
model3 <- lme4::lmer(Response_Ax ~ Response_SubjPE * mini_SPIN_total + (Response_SubjPE | Random_ID), data = final_df15, control=lmerControl(optimizer="bobyqa"))

model4 <- lme4::lmer(Response_Ax ~ Response_fdbk + (1 | Random_ID), data = final_df15, control=lmerControl(optimizer="bobyqa"))
model5 <- lme4::lmer(Response_Ax ~ Response_fdbk + (Response_fdbk | Random_ID), data = final_df15, control=lmerControl(optimizer="bobyqa"))
model6 <- lme4::lmer(Response_Ax ~ Response_fdbk * mini_SPIN_total + (Response_fdbk | Random_ID), data = final_df15, control=lmerControl(optimizer="bobyqa"))

summary(model1)
summary(model2)
summary(model3)
summary(model4)
summary(model5)
summary(model6)

AIC(model1)
AIC(model2)
AIC(model3)
AIC(model4)
AIC(model5)
AIC(model6)

# anova(model2, model5)

coef_fixed <- fixef(model4)
intercept_Mood <- coef_fixed[1]
slope_Mood <- coef_fixed[2]
standard_beta_fdbk <- parameters:: standardise_parameters (model4)
standard_beta_subjPE <- parameters:: standardise_parameters (model2)
```


\newpage 
# Individual plots with LME for Anxiety with SubjPE
When looking at subjective PE, the best model is  Anxiety ~ SubjPE  + (SubjPE | Random_ID) with an AIC of 11764.61

```{r echo=FALSE, warning=FALSE, message=FALSE}

ggplot(final_df15, aes(x=Response_SubjPE, y=Response_Ax)) +
  geom_smooth(method = "lm", size = 0.5, se = FALSE, aes(group=Random_ID, color=Social_Anxiety)) +
  scale_color_manual(values = c("low" = "lightblue", "high" = "pink")) +
  geom_abline(intercept = intercept_Mood, slope = slope_Mood, color="purple", linetype="dashed", size=1) +
  xlab("Subjective PE") + 
  ylab("Anxiety") +
  ggtitle("Relationship between Anxiety and subjective PE",
          subtitle = paste("estimated slopes of the association in n = ", 
                           length(unique(final_df15$Random_ID))))+
  theme(plot.title = element_text(size=15), plot.subtitle = element_text(size = 10))+
  theme(legend.title = element_text(size = 9), legend.text = element_text(size = 8))+
  theme(axis.title = element_text(size = 10))+
  annotate("label", x = 32, y = 55, label = paste("beta = ", round(standard_beta_subjPE$Std_Coefficient[2],2), ", 95%CI = ",
                                                 round(standard_beta_subjPE$CI_low[2],2), "-", 
                                                 round(standard_beta_subjPE$CI_high[2],2))) +
  scale_y_continuous(breaks = seq(0, 100, by = 20), limits = c(0, 100))+
  scale_x_continuous(breaks = seq(-80, 80, by = 40), limits = c(-80, 80))

# ggsave(filename = "p15_ax.png", plot = p15_ax, dpi = 300, width = 6, height = 4)
  
```


\newpage 
# Individual plots with LME for Anxiety with feedback instead of SubjPE

When including feedback the best model is Anxiety ~ feedback  + (Random_ID) with an AIC of 11705.6

```{r echo=FALSE, warning=FALSE, message=FALSE}

ggplot(final_df15, aes(x=Response_fdbk, y=Response_Ax)) +
  geom_smooth(method = "lm", size = 0.5, se = FALSE, aes(group=Random_ID, color=Social_Anxiety)) +
  scale_color_manual(values = c("low" = "lightblue", "high" = "pink")) +
  geom_abline(intercept = intercept_Mood, slope = slope_Mood, color="purple", linetype="dashed", size=1) +
  xlab("Feedback") + 
  ylab("Mood") +
  ggtitle("Relationship between Anxiety and Feedback",
          subtitle = paste("estimated slopes of the association in n = ", 
                           length(unique(final_df15$Random_ID))))+
  theme(plot.title = element_text(size=15), plot.subtitle = element_text(size = 10))+
  theme(legend.title = element_text(size = 9), legend.text = element_text(size = 8))+
  theme(axis.title = element_text(size = 10))+
  annotate("label", x = 32, y = 55, label = paste("beta = ", round(standard_beta_fdbk$Std_Coefficient[2],2), ", 95%CI = ",
                                                 round(standard_beta_fdbk$CI_low[2],2), "-", 
                                                 round(standard_beta_fdbk$CI_high[2],2))) 
  
```

\newpage
# Relationship average anxiety on the task and how stressful they rated the task

We have only one scale at the end when asking feedback, and we ask them "How stressful was this as a social situation?" on a scale of 0-100. Let's look at the relationshio between this score and anxiety on the task, but also the average score in people with high and low social anxiety.

```{r echo=FALSE, warning=FALSE, message=FALSE}
filter_final_df15 <- subset(final_df15, final_df15$Trial.Number == 1)

high <- filter_final_df15[filter_final_df15$Social_Anxiety == "high", ]$Response_stress_level
low <- filter_final_df15[filter_final_df15$Social_Anxiety == "low", ]$Response_stress_level

shapiro_test_high <- shapiro.test(high)
shapiro_test_low <- shapiro.test(low)

if (shapiro_test_high$p.value <= 0.05 || shapiro_test_low$p.value <= 0.05) {
  # At least one group is not normally distributed, use Mann-Whitney U test
  mw_test_result <- wilcox.test(high, low)
  print(mw_test_result)
}

ggplot(filter_final_df15, aes(x = Social_Anxiety, y = Response_stress_level , fill = Social_Anxiety)) +
  geom_boxplot(outlier.colour = "black") +
  stat_boxplot(geom = "errorbar",
               width = 0.15) + 
  geom_point(color = "black", position = position_jitter(width = 0.2), alpha = 0.7) +
  theme_minimal() +
  # labs(x = "Display", y = "Response") +
  # scale_y_continuous(breaks = seq(0, 100, by = 10), limits = c(0, 100)) +
  # ggtitle("Average anxiety ratings in pilots 1 and 2 in socially anxious people") +
  xlab("") + 
  ylab("stress levels (0-10)") +
  # facet_wrap(~group, scales = "free", ncol = 4) +
  # scale_fill_manual(values = c("black", "purple", "darkgreen", "blue"))+
  # ylim(c(50, 100)) + 
  # scale_y_continuous(breaks = seq(50, 100, by = 10), limits = c(50, 100))+
  theme(
    panel.grid.major = element_blank(),  # Removes major grid lines
    panel.grid.minor = element_blank(),  # Removes minor grid lines
    panel.border = element_blank(),      # Removes the border line
    axis.line = element_blank(),          # Removes axis lines
    plot.background = element_rect(fill = "white", colour = NA)   # Ensure plot background is white
  )

```




