---
title: "all_pilots_LME_plots"
author: "Marjan Biria"
date: "2024-02-28"
output: 
    pdf_document:
    toc: true
    toc_depth: 2
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(root.dir = "aim_lab_1", echo = TRUE)
```


```{r echo=FALSE, warning=FALSE, message=FALSE}
library(dplyr)
library(ggplot2)
library(tidyr)
library(lme4)
library(parameters)
library(broom.mixed)
```

\newpage
In this document we are running an LME for all pilots and plotting it separately for mood and anxiety.





```{r echo=FALSE, warning=FALSE, message=FALSE}
all_pilots_with_mini_spin <- read.csv("/Users/marjan/Desktop/aim_lab_1/all_pilots_with_mini_spin.csv")

df16_data <- subset(all_pilots_with_mini_spin, pilot_nr == 16)
df15_data <- subset(all_pilots_with_mini_spin, pilot_nr == 15)
df14_data <- subset(all_pilots_with_mini_spin, pilot_nr == 14)
df13_data <- subset(all_pilots_with_mini_spin, pilot_nr == 13)
df12_data <- subset(all_pilots_with_mini_spin, pilot_nr == 12)
df11_data <- subset(all_pilots_with_mini_spin, pilot_nr == 11)
df10_data <- subset(all_pilots_with_mini_spin, pilot_nr == 10)
df9_data <- subset(all_pilots_with_mini_spin, pilot_nr == 9)
df8_data <- subset(all_pilots_with_mini_spin, pilot_nr == 8)
df7_data <- subset(all_pilots_with_mini_spin, pilot_nr == 7)
df6_data <- subset(all_pilots_with_mini_spin, pilot_nr == 6)
```


# Individual plots with LME for Anxiety with SubjPE pilot 16

```{r echo=FALSE, warning=FALSE, message=FALSE}
model2 <- lme4::lmer(Anxiety ~ SubjPE + (SubjPE | Random_ID), data = df16_data, control=lmerControl(optimizer="bobyqa"))

coef_fixed <- fixef(model2)
intercept_Mood <- coef_fixed[1]
slope_Mood <- coef_fixed[2]
standard_beta_subjPE <- parameters:: standardise_parameters (model2)

p16_ax <- ggplot(df16_data, aes(x=SubjPE, y=Anxiety)) +
  geom_smooth(method = "lm", size = 0.5, se = FALSE, aes(group=Random_ID, color=Social_Anxiety)) +
  scale_color_manual(values = c("low" = "lightblue", "high" = "pink")) +
  geom_abline(intercept = intercept_Mood, slope = slope_Mood, color="purple", linetype="dashed", size=1) +
  xlab("Subjective PE") + 
  ylab("Anxiety") +
  ggtitle("Relationship between anxiety and subjective PE",
          subtitle = paste("estimated slopes of the association in n = ", 
                           length(unique(df16_data$Random_ID))))+
  theme(plot.title = element_text(size=14), plot.subtitle = element_text(size = 10))+
  theme(legend.title = element_text(size = 9), legend.text = element_text(size = 8))+
  theme(axis.title = element_text(size = 10))+
  annotate("label", x = 32, y = 55, label = paste("beta = ", round(standard_beta_subjPE$Std_Coefficient[2],2), ", 95%CI = ",
                                                 round(standard_beta_subjPE$CI_low[2],2), "-", 
                                                 round(standard_beta_subjPE$CI_high[2],2))) +
  scale_y_continuous(breaks = seq(0, 100, by = 20), limits = c(0, 100)) +
  scale_x_continuous(breaks = seq(-80, 80, by = 40), limits = c(-80, 80))

ggsave(filename = "p16_ax.png", plot = p16_ax, dpi = 300, width = 6, height = 4)
  
```

# Individual plots with LME for Mood with SubjPE pilot 16

```{r echo=FALSE, warning=FALSE, message=FALSE}
model2 <- lme4::lmer(Mood ~ SubjPE + (SubjPE | Random_ID), data = df16_data, control=lmerControl(optimizer="bobyqa"))

coef_fixed <- fixef(model2)
intercept_Mood <- coef_fixed[1]
slope_Mood <- coef_fixed[2]
standard_beta_subjPE <- parameters:: standardise_parameters (model2)

p16_m <- ggplot(df16_data, aes(x=SubjPE, y=Mood)) +
  geom_smooth(method = "lm", size = 0.5, se = FALSE, aes(group=Random_ID, color=Social_Anxiety)) +
  scale_color_manual(values = c("low" = "lightblue", "high" = "pink")) +
  geom_abline(intercept = intercept_Mood, slope = slope_Mood, color="purple", linetype="dashed", size=1) +
  xlab("Subjective PE") + 
  ylab("Mood") +
  ggtitle("Relationship between anxiety and subjective PE",
          subtitle = paste("estimated slopes of the association in n = ", 
                           length(unique(df16_data$Random_ID))))+
  theme(plot.title = element_text(size=14), plot.subtitle = element_text(size = 10))+
  theme(legend.title = element_text(size = 9), legend.text = element_text(size = 8))+
  theme(axis.title = element_text(size = 10))+
  annotate("label", x = 32, y = 55, label = paste("beta = ", round(standard_beta_subjPE$Std_Coefficient[2],2), ", 95%CI = ",
                                                 round(standard_beta_subjPE$CI_low[2],2), "-", 
                                                 round(standard_beta_subjPE$CI_high[2],2))) +
  scale_y_continuous(breaks = seq(0, 100, by = 20), limits = c(0, 100)) +
  scale_x_continuous(breaks = seq(-80, 80, by = 40), limits = c(-80, 80))

ggsave(filename = "p16_m.png", plot = p16_m, dpi = 300, width = 6, height = 4)
  
```


# Individual plots with LME for Anxiety with SubjPE pilot 15

```{r echo=FALSE, warning=FALSE, message=FALSE}
model2 <- lme4::lmer(Anxiety ~ SubjPE + (SubjPE | Random_ID), data = df15_data, control=lmerControl(optimizer="bobyqa"))

coef_fixed <- fixef(model2)
intercept_Mood <- coef_fixed[1]
slope_Mood <- coef_fixed[2]
standard_beta_subjPE <- parameters:: standardise_parameters (model2)

p15_ax <- ggplot(df15_data, aes(x=SubjPE, y=Anxiety)) +
  geom_smooth(method = "lm", size = 0.5, se = FALSE, aes(group=Random_ID, color=Social_Anxiety)) +
  scale_color_manual(values = c("low" = "lightblue", "high" = "pink")) +
  geom_abline(intercept = intercept_Mood, slope = slope_Mood, color="purple", linetype="dashed", size=1) +
  xlab("Subjective PE") + 
  ylab("Anxiety") +
  ggtitle("Relationship between anxiety and subjective PE",
          subtitle = paste("estimated slopes of the association in n = ", 
                           length(unique(df15_data$Random_ID))))+
  theme(plot.title = element_text(size=14), plot.subtitle = element_text(size = 10))+
  theme(legend.title = element_text(size = 9), legend.text = element_text(size = 8))+
  theme(axis.title = element_text(size = 10))+
  annotate("label", x = 32, y = 55, label = paste("beta = ", round(standard_beta_subjPE$Std_Coefficient[2],2), ", 95%CI = ",
                                                 round(standard_beta_subjPE$CI_low[2],2), "-", 
                                                 round(standard_beta_subjPE$CI_high[2],2))) +
  scale_y_continuous(breaks = seq(0, 100, by = 20), limits = c(0, 100)) +
  scale_x_continuous(breaks = seq(-80, 80, by = 40), limits = c(-80, 80))

ggsave(filename = "p15_ax.png", plot = p15_ax, dpi = 300, width = 6, height = 4)
  
```

# Individual plots with LME for Mood with SubjPE pilot 15

```{r echo=FALSE, warning=FALSE, message=FALSE}
model2 <- lme4::lmer(Mood ~ SubjPE + (SubjPE | Random_ID), data = df15_data, control=lmerControl(optimizer="bobyqa"))

coef_fixed <- fixef(model2)
intercept_Mood <- coef_fixed[1]
slope_Mood <- coef_fixed[2]
standard_beta_subjPE <- parameters:: standardise_parameters (model2)

p15_m <- ggplot(df15_data, aes(x=SubjPE, y=Mood)) +
  geom_smooth(method = "lm", size = 0.5, se = FALSE, aes(group=Random_ID, color=Social_Anxiety)) +
  scale_color_manual(values = c("low" = "lightblue", "high" = "pink")) +
  geom_abline(intercept = intercept_Mood, slope = slope_Mood, color="purple", linetype="dashed", size=1) +
  xlab("Subjective PE") + 
  ylab("Mood") +
  ggtitle("Relationship between anxiety and subjective PE",
          subtitle = paste("estimated slopes of the association in n = ", 
                           length(unique(df15_data$Random_ID))))+
  theme(plot.title = element_text(size=14), plot.subtitle = element_text(size = 10))+
  theme(legend.title = element_text(size = 9), legend.text = element_text(size = 8))+
  theme(axis.title = element_text(size = 10))+
  annotate("label", x = 32, y = 55, label = paste("beta = ", round(standard_beta_subjPE$Std_Coefficient[2],2), ", 95%CI = ",
                                                 round(standard_beta_subjPE$CI_low[2],2), "-", 
                                                 round(standard_beta_subjPE$CI_high[2],2))) +
  scale_y_continuous(breaks = seq(0, 100, by = 20), limits = c(0, 100)) +
  scale_x_continuous(breaks = seq(-80, 80, by = 40), limits = c(-80, 80))

ggsave(filename = "p15_m.png", plot = p15_m, dpi = 300, width = 6, height = 4)
  
```


# Individual plots with LME for Anxiety with SubjPE pilot 14

```{r echo=FALSE, warning=FALSE, message=FALSE}
model2 <- lme4::lmer(Anxiety ~ SubjPE + (SubjPE | Random_ID), data = df14_data, control=lmerControl(optimizer="bobyqa"))

coef_fixed <- fixef(model2)
intercept_Mood <- coef_fixed[1]
slope_Mood <- coef_fixed[2]
standard_beta_subjPE <- parameters:: standardise_parameters (model2)

p14_ax <- ggplot(df14_data, aes(x=SubjPE, y=Anxiety)) +
  geom_smooth(method = "lm", size = 0.5, se = FALSE, aes(group=Random_ID, color=Social_Anxiety)) +
  scale_color_manual(values = c("low" = "lightblue", "high" = "pink")) +
  geom_abline(intercept = intercept_Mood, slope = slope_Mood, color="purple", linetype="dashed", size=1) +
  xlab("Subjective PE") + 
  ylab("Anxiety") +
  ggtitle("Relationship between anxiety and subjective PE",
          subtitle = paste("estimated slopes of the association in n = ", 
                           length(unique(df14_data$Random_ID))))+
  theme(plot.title = element_text(size=14), plot.subtitle = element_text(size = 10))+
  theme(legend.title = element_text(size = 9), legend.text = element_text(size = 8))+
  theme(axis.title = element_text(size = 10))+
  annotate("label", x = 32, y = 55, label = paste("beta = ", round(standard_beta_subjPE$Std_Coefficient[2],2), ", 95%CI = ",
                                                 round(standard_beta_subjPE$CI_low[2],2), "-", 
                                                 round(standard_beta_subjPE$CI_high[2],2))) +
  scale_y_continuous(breaks = seq(0, 100, by = 20), limits = c(0, 100)) +
  scale_x_continuous(breaks = seq(-80, 80, by = 40), limits = c(-80, 80))

ggsave(filename = "p14_ax.png", plot = p14_ax, dpi = 300, width = 6, height = 4)
  
```

# Individual plots with LME for Mood with SubjPE pilot 14

```{r echo=FALSE, warning=FALSE, message=FALSE}
model2 <- lme4::lmer(Mood ~ SubjPE + (SubjPE | Random_ID), data = df14_data, control=lmerControl(optimizer="bobyqa"))

coef_fixed <- fixef(model2)
intercept_Mood <- coef_fixed[1]
slope_Mood <- coef_fixed[2]
standard_beta_subjPE <- parameters:: standardise_parameters (model2)

p14_m <- ggplot(df14_data, aes(x=SubjPE, y=Mood)) +
  geom_smooth(method = "lm", size = 0.5, se = FALSE, aes(group=Random_ID, color=Social_Anxiety)) +
  scale_color_manual(values = c("low" = "lightblue", "high" = "pink")) +
  geom_abline(intercept = intercept_Mood, slope = slope_Mood, color="purple", linetype="dashed", size=1) +
  xlab("Subjective PE") + 
  ylab("Mood") +
  ggtitle("Relationship between anxiety and subjective PE",
          subtitle = paste("estimated slopes of the association in n = ", 
                           length(unique(df14_data$Random_ID))))+
  theme(plot.title = element_text(size=14), plot.subtitle = element_text(size = 10))+
  theme(legend.title = element_text(size = 9), legend.text = element_text(size = 8))+
  theme(axis.title = element_text(size = 10))+
  annotate("label", x = 32, y = 55, label = paste("beta = ", round(standard_beta_subjPE$Std_Coefficient[2],2), ", 95%CI = ",
                                                 round(standard_beta_subjPE$CI_low[2],2), "-", 
                                                 round(standard_beta_subjPE$CI_high[2],2))) +
  scale_y_continuous(breaks = seq(0, 100, by = 20), limits = c(0, 100)) +
  scale_x_continuous(breaks = seq(-80, 80, by = 40), limits = c(-80, 80))

ggsave(filename = "p14_m.png", plot = p14_m, dpi = 300, width = 6, height = 4)
  
```


# Individual plots with LME for Anxiety with SubjPE pilot 13

```{r echo=FALSE, warning=FALSE, message=FALSE}
model2 <- lme4::lmer(Anxiety ~ SubjPE + (SubjPE | Random_ID), data = df13_data, control=lmerControl(optimizer="bobyqa"))

coef_fixed <- fixef(model2)
intercept_Mood <- coef_fixed[1]
slope_Mood <- coef_fixed[2]
standard_beta_subjPE <- parameters:: standardise_parameters (model2)

p13_ax <- ggplot(df13_data, aes(x=SubjPE, y=Anxiety)) +
  geom_smooth(method = "lm", size = 0.5, se = FALSE, aes(group=Random_ID, color=Social_Anxiety)) +
  scale_color_manual(values = c("low" = "lightblue", "high" = "pink")) +
  geom_abline(intercept = intercept_Mood, slope = slope_Mood, color="purple", linetype="dashed", size=1) +
  xlab("Subjective PE") + 
  ylab("Anxiety") +
  ggtitle("Relationship between anxiety and subjective PE",
          subtitle = paste("estimated slopes of the association in n = ", 
                           length(unique(df13_data$Random_ID))))+
  theme(plot.title = element_text(size=14), plot.subtitle = element_text(size = 10))+
  theme(legend.title = element_text(size = 9), legend.text = element_text(size = 8))+
  theme(axis.title = element_text(size = 10))+
  annotate("label", x = 32, y = 55, label = paste("beta = ", round(standard_beta_subjPE$Std_Coefficient[2],2), ", 95%CI = ",
                                                 round(standard_beta_subjPE$CI_low[2],2), "-", 
                                                 round(standard_beta_subjPE$CI_high[2],2))) +
  scale_y_continuous(breaks = seq(0, 100, by = 20), limits = c(0, 100)) +
  scale_x_continuous(breaks = seq(-80, 80, by = 40), limits = c(-80, 80))

ggsave(filename = "p13_ax.png", plot = p13_ax, dpi = 300, width = 6, height = 4)
  
```

# Individual plots with LME for Mood with SubjPE pilot 13

```{r echo=FALSE, warning=FALSE, message=FALSE}
model2 <- lme4::lmer(Mood ~ SubjPE + (SubjPE | Random_ID), data = df13_data, control=lmerControl(optimizer="bobyqa"))

coef_fixed <- fixef(model2)
intercept_Mood <- coef_fixed[1]
slope_Mood <- coef_fixed[2]
standard_beta_subjPE <- parameters:: standardise_parameters (model2)

p13_m <- ggplot(df13_data, aes(x=SubjPE, y=Mood)) +
  geom_smooth(method = "lm", size = 0.5, se = FALSE, aes(group=Random_ID, color=Social_Anxiety)) +
  scale_color_manual(values = c("low" = "lightblue", "high" = "pink")) +
  geom_abline(intercept = intercept_Mood, slope = slope_Mood, color="purple", linetype="dashed", size=1) +
  xlab("Subjective PE") + 
  ylab("Mood") +
  ggtitle("Relationship between anxiety and subjective PE",
          subtitle = paste("estimated slopes of the association in n = ", 
                           length(unique(df13_data$Random_ID))))+
  theme(plot.title = element_text(size=14), plot.subtitle = element_text(size = 10))+
  theme(legend.title = element_text(size = 9), legend.text = element_text(size = 8))+
  theme(axis.title = element_text(size = 10))+
  annotate("label", x = 32, y = 55, label = paste("beta = ", round(standard_beta_subjPE$Std_Coefficient[2],2), ", 95%CI = ",
                                                 round(standard_beta_subjPE$CI_low[2],2), "-", 
                                                 round(standard_beta_subjPE$CI_high[2],2))) +
  scale_y_continuous(breaks = seq(0, 100, by = 20), limits = c(0, 100)) +
  scale_x_continuous(breaks = seq(-80, 80, by = 40), limits = c(-80, 80))

ggsave(filename = "p13_m.png", plot = p13_m, dpi = 300, width = 6, height = 4)
  
```


# Individual plots with LME for Anxiety with SubjPE pilot 12

```{r echo=FALSE, warning=FALSE, message=FALSE}
model2 <- lme4::lmer(Anxiety ~ SubjPE + (SubjPE | Random_ID), data = df12_data, control=lmerControl(optimizer="bobyqa"))

coef_fixed <- fixef(model2)
intercept_Mood <- coef_fixed[1]
slope_Mood <- coef_fixed[2]
standard_beta_subjPE <- parameters:: standardise_parameters (model2)

p12_ax <- ggplot(df12_data, aes(x=SubjPE, y=Anxiety)) +
  geom_smooth(method = "lm", size = 0.5, se = FALSE, aes(group=Random_ID, color=Social_Anxiety)) +
  scale_color_manual(values = c("low" = "lightblue", "high" = "pink")) +
  geom_abline(intercept = intercept_Mood, slope = slope_Mood, color="purple", linetype="dashed", size=1) +
  xlab("Subjective PE") + 
  ylab("Anxiety") +
  ggtitle("Relationship between anxiety and subjective PE",
          subtitle = paste("estimated slopes of the association in n = ", 
                           length(unique(df12_data$Random_ID))))+
  theme(plot.title = element_text(size=14), plot.subtitle = element_text(size = 10))+
  theme(legend.title = element_text(size = 9), legend.text = element_text(size = 8))+
  theme(axis.title = element_text(size = 10))+
  annotate("label", x = 32, y = 55, label = paste("beta = ", round(standard_beta_subjPE$Std_Coefficient[2],2), ", 95%CI = ",
                                                 round(standard_beta_subjPE$CI_low[2],2), "-", 
                                                 round(standard_beta_subjPE$CI_high[2],2))) +
  scale_y_continuous(breaks = seq(0, 100, by = 20), limits = c(0, 100)) +
  scale_x_continuous(breaks = seq(-80, 80, by = 40), limits = c(-80, 80))

ggsave(filename = "p12_ax.png", plot = p12_ax, dpi = 300, width = 6, height = 4)
  
```

# Individual plots with LME for Mood with SubjPE pilot 12

```{r echo=FALSE, warning=FALSE, message=FALSE}
model2 <- lme4::lmer(Mood ~ SubjPE + (SubjPE | Random_ID), data = df12_data, control=lmerControl(optimizer="bobyqa"))

coef_fixed <- fixef(model2)
intercept_Mood <- coef_fixed[1]
slope_Mood <- coef_fixed[2]
standard_beta_subjPE <- parameters:: standardise_parameters (model2)

p12_m <- ggplot(df12_data, aes(x=SubjPE, y=Mood)) +
  geom_smooth(method = "lm", size = 0.5, se = FALSE, aes(group=Random_ID, color=Social_Anxiety)) +
  scale_color_manual(values = c("low" = "lightblue", "high" = "pink")) +
  geom_abline(intercept = intercept_Mood, slope = slope_Mood, color="purple", linetype="dashed", size=1) +
  xlab("Subjective PE") + 
  ylab("Mood") +
  ggtitle("Relationship between anxiety and subjective PE",
          subtitle = paste("estimated slopes of the association in n = ", 
                           length(unique(df12_data$Random_ID))))+
  theme(plot.title = element_text(size=14), plot.subtitle = element_text(size = 10))+
  theme(legend.title = element_text(size = 9), legend.text = element_text(size = 8))+
  theme(axis.title = element_text(size = 10))+
  annotate("label", x = 32, y = 55, label = paste("beta = ", round(standard_beta_subjPE$Std_Coefficient[2],2), ", 95%CI = ",
                                                 round(standard_beta_subjPE$CI_low[2],2), "-", 
                                                 round(standard_beta_subjPE$CI_high[2],2))) +
  scale_y_continuous(breaks = seq(0, 100, by = 20), limits = c(0, 100)) +
  scale_x_continuous(breaks = seq(-80, 80, by = 40), limits = c(-80, 80))

ggsave(filename = "p12_m.png", plot = p12_m, dpi = 300, width = 6, height = 4)
  
```


# Individual plots with LME for Anxiety with SubjPE pilot 11

```{r echo=FALSE, warning=FALSE, message=FALSE}
model2 <- lme4::lmer(Anxiety ~ SubjPE + (SubjPE | Random_ID), data = df11_data, control=lmerControl(optimizer="bobyqa"))

coef_fixed <- fixef(model2)
intercept_Mood <- coef_fixed[1]
slope_Mood <- coef_fixed[2]
standard_beta_subjPE <- parameters:: standardise_parameters (model2)

p11_ax <- ggplot(df11_data, aes(x=SubjPE, y=Anxiety)) +
  geom_smooth(method = "lm", size = 0.5, se = FALSE, aes(group=Random_ID, color=Social_Anxiety)) +
  scale_color_manual(values = c("low" = "lightblue", "high" = "pink")) +
  geom_abline(intercept = intercept_Mood, slope = slope_Mood, color="purple", linetype="dashed", size=1) +
  xlab("Subjective PE") + 
  ylab("Anxiety") +
  ggtitle("Relationship between anxiety and subjective PE",
          subtitle = paste("estimated slopes of the association in n = ", 
                           length(unique(df11_data$Random_ID))))+
  theme(plot.title = element_text(size=14), plot.subtitle = element_text(size = 10))+
  theme(legend.title = element_text(size = 9), legend.text = element_text(size = 8))+
  theme(axis.title = element_text(size = 10))+
  annotate("label", x = 32, y = 55, label = paste("beta = ", round(standard_beta_subjPE$Std_Coefficient[2],2), ", 95%CI = ",
                                                 round(standard_beta_subjPE$CI_low[2],2), "-", 
                                                 round(standard_beta_subjPE$CI_high[2],2))) +
  scale_y_continuous(breaks = seq(0, 100, by = 20), limits = c(0, 100)) +
  scale_x_continuous(breaks = seq(-80, 80, by = 40), limits = c(-80, 80))

ggsave(filename = "p11_ax.png", plot = p11_ax, dpi = 300, width = 6, height = 4)
  
```

# Individual plots with LME for Mood with SubjPE pilot 11
```{r echo=FALSE, warning=FALSE, message=FALSE}
model2 <- lme4::lmer(Mood ~ SubjPE + (SubjPE | Random_ID), data = df11_data, control=lmerControl(optimizer="bobyqa"))

coef_fixed <- fixef(model2)
intercept_Mood <- coef_fixed[1]
slope_Mood <- coef_fixed[2]
standard_beta_subjPE <- parameters:: standardise_parameters (model2)

p11_m <- ggplot(df11_data, aes(x=SubjPE, y=Mood)) +
  geom_smooth(method = "lm", size = 0.5, se = FALSE, aes(group=Random_ID, color=Social_Anxiety)) +
  scale_color_manual(values = c("low" = "lightblue", "high" = "pink")) +
  geom_abline(intercept = intercept_Mood, slope = slope_Mood, color="purple", linetype="dashed", size=1) +
  xlab("Subjective PE") + 
  ylab("Mood") +
  ggtitle("Relationship between anxiety and subjective PE",
          subtitle = paste("estimated slopes of the association in n = ", 
                           length(unique(df11_data$Random_ID))))+
  theme(plot.title = element_text(size=14), plot.subtitle = element_text(size = 10))+
  theme(legend.title = element_text(size = 9), legend.text = element_text(size = 8))+
  theme(axis.title = element_text(size = 10))+
  annotate("label", x = 32, y = 55, label = paste("beta = ", round(standard_beta_subjPE$Std_Coefficient[2],2), ", 95%CI = ",
                                                 round(standard_beta_subjPE$CI_low[2],2), "-", 
                                                 round(standard_beta_subjPE$CI_high[2],2))) +
  scale_y_continuous(breaks = seq(0, 100, by = 20), limits = c(0, 100)) +
  scale_x_continuous(breaks = seq(-80, 80, by = 40), limits = c(-80, 80))

ggsave(filename = "p11_m.png", plot = p11_m, dpi = 300, width = 6, height = 4)
  
```


# Individual plots with LME for Anxiety with SubjPE pilot 10
```{r echo=FALSE, warning=FALSE, message=FALSE}
model2 <- lme4::lmer(Anxiety ~ SubjPE + (SubjPE | Random_ID), data = df10_data, control=lmerControl(optimizer="bobyqa"))

coef_fixed <- fixef(model2)
intercept_Mood <- coef_fixed[1]
slope_Mood <- coef_fixed[2]
standard_beta_subjPE <- parameters:: standardise_parameters (model2)

p10_ax <- ggplot(df10_data, aes(x=SubjPE, y=Anxiety)) +
  geom_smooth(method = "lm", size = 0.5, se = FALSE, aes(group=Random_ID, color=Social_Anxiety)) +
  scale_color_manual(values = c("low" = "lightblue", "high" = "pink")) +
  geom_abline(intercept = intercept_Mood, slope = slope_Mood, color="purple", linetype="dashed", size=1) +
  xlab("Subjective PE") + 
  ylab("Anxiety") +
  ggtitle("Relationship between anxiety and subjective PE",
          subtitle = paste("estimated slopes of the association in n = ", 
                           length(unique(df10_data$Random_ID))))+
  theme(plot.title = element_text(size=14), plot.subtitle = element_text(size = 10))+
  theme(legend.title = element_text(size = 9), legend.text = element_text(size = 8))+
  theme(axis.title = element_text(size = 10))+
  annotate("label", x = 32, y = 55, label = paste("beta = ", round(standard_beta_subjPE$Std_Coefficient[2],2), ", 95%CI = ",
                                                 round(standard_beta_subjPE$CI_low[2],2), "-", 
                                                 round(standard_beta_subjPE$CI_high[2],2))) +
  scale_y_continuous(breaks = seq(0, 100, by = 20), limits = c(0, 100)) +
  scale_x_continuous(breaks = seq(-80, 80, by = 40), limits = c(-80, 80))

ggsave(filename = "p10_ax.png", plot = p10_ax, dpi = 300, width = 6, height = 4)
  
```


# Individual plots with LME for Mood with SubjPE pilot 10
```{r echo=FALSE, warning=FALSE, message=FALSE}
model2 <- lme4::lmer(Mood ~ SubjPE + (SubjPE | Random_ID), data = df10_data, control=lmerControl(optimizer="bobyqa"))

coef_fixed <- fixef(model2)
intercept_Mood <- coef_fixed[1]
slope_Mood <- coef_fixed[2]
standard_beta_subjPE <- parameters:: standardise_parameters (model2)

p10_m <- ggplot(df10_data, aes(x=SubjPE, y=Mood)) +
  geom_smooth(method = "lm", size = 0.5, se = FALSE, aes(group=Random_ID, color=Social_Anxiety)) +
  scale_color_manual(values = c("low" = "lightblue", "high" = "pink")) +
  geom_abline(intercept = intercept_Mood, slope = slope_Mood, color="purple", linetype="dashed", size=1) +
  xlab("Subjective PE") + 
  ylab("Mood") +
  ggtitle("Relationship between anxiety and subjective PE",
          subtitle = paste("estimated slopes of the association in n = ", 
                           length(unique(df10_data$Random_ID))))+
  theme(plot.title = element_text(size=14), plot.subtitle = element_text(size = 10))+
  theme(legend.title = element_text(size = 9), legend.text = element_text(size = 8))+
  theme(axis.title = element_text(size = 10))+
  annotate("label", x = 32, y = 55, label = paste("beta = ", round(standard_beta_subjPE$Std_Coefficient[2],2), ", 95%CI = ",
                                                 round(standard_beta_subjPE$CI_low[2],2), "-", 
                                                 round(standard_beta_subjPE$CI_high[2],2))) +
  scale_y_continuous(breaks = seq(0, 100, by = 20), limits = c(0, 100)) +
  scale_x_continuous(breaks = seq(-80, 80, by = 40), limits = c(-80, 80))

ggsave(filename = "p10_m.png", plot = p10_m, dpi = 300, width = 6, height = 4)
  
```


# Individual plots with LME for Anxiety with SubjPE pilot 9
```{r echo=FALSE, warning=FALSE, message=FALSE}
model2 <- lme4::lmer(Anxiety ~ SubjPE + (SubjPE | Random_ID), data = df9_data, control=lmerControl(optimizer="bobyqa"))

coef_fixed <- fixef(model2)
intercept_Mood <- coef_fixed[1]
slope_Mood <- coef_fixed[2]
standard_beta_subjPE <- parameters:: standardise_parameters (model2)

p9_ax <- ggplot(df9_data, aes(x=SubjPE, y=Anxiety)) +
  geom_smooth(method = "lm", size = 0.5, se = FALSE, aes(group=Random_ID, color=Social_Anxiety)) +
  scale_color_manual(values = c("low" = "lightblue", "high" = "pink")) +
  geom_abline(intercept = intercept_Mood, slope = slope_Mood, color="purple", linetype="dashed", size=1) +
  xlab("Subjective PE") + 
  ylab("Anxiety") +
  ggtitle("Relationship between anxiety and subjective PE",
          subtitle = paste("estimated slopes of the association in n = ", 
                           length(unique(df9_data$Random_ID))))+
  theme(plot.title = element_text(size=14), plot.subtitle = element_text(size = 10))+
  theme(legend.title = element_text(size = 9), legend.text = element_text(size = 8))+
  theme(axis.title = element_text(size = 10))+
  annotate("label", x = 32, y = 55, label = paste("beta = ", round(standard_beta_subjPE$Std_Coefficient[2],2), ", 95%CI = ",
                                                 round(standard_beta_subjPE$CI_low[2],2), "-", 
                                                 round(standard_beta_subjPE$CI_high[2],2))) +
  scale_y_continuous(breaks = seq(0, 100, by = 20), limits = c(0, 100)) +
  scale_x_continuous(breaks = seq(-80, 80, by = 40), limits = c(-80, 80))

ggsave(filename = "p9_ax.png", plot = p9_ax, dpi = 300, width = 6, height = 4)
  
```

# Individual plots with LME for Mood with SubjPE pilot 9
```{r echo=FALSE, warning=FALSE, message=FALSE}
model2 <- lme4::lmer(Mood ~ SubjPE + (SubjPE | Random_ID), data = df9_data, control=lmerControl(optimizer="bobyqa"))

coef_fixed <- fixef(model2)
intercept_Mood <- coef_fixed[1]
slope_Mood <- coef_fixed[2]
standard_beta_subjPE <- parameters:: standardise_parameters (model2)

p9_m <- ggplot(df9_data, aes(x=SubjPE, y=Mood)) +
  geom_smooth(method = "lm", size = 0.5, se = FALSE, aes(group=Random_ID, color=Social_Anxiety)) +
  scale_color_manual(values = c("low" = "lightblue", "high" = "pink")) +
  geom_abline(intercept = intercept_Mood, slope = slope_Mood, color="purple", linetype="dashed", size=1) +
  xlab("Subjective PE") + 
  ylab("Mood") +
  ggtitle("Relationship between anxiety and subjective PE",
          subtitle = paste("estimated slopes of the association in n = ", 
                           length(unique(df9_data$Random_ID))))+
  theme(plot.title = element_text(size=14), plot.subtitle = element_text(size = 10))+
  theme(legend.title = element_text(size = 9), legend.text = element_text(size = 8))+
  theme(axis.title = element_text(size = 10))+
  annotate("label", x = 32, y = 55, label = paste("beta = ", round(standard_beta_subjPE$Std_Coefficient[2],2), ", 95%CI = ",
                                                 round(standard_beta_subjPE$CI_low[2],2), "-", 
                                                 round(standard_beta_subjPE$CI_high[2],2))) +
  scale_y_continuous(breaks = seq(0, 100, by = 20), limits = c(0, 100)) +
  scale_x_continuous(breaks = seq(-80, 80, by = 40), limits = c(-80, 80))

ggsave(filename = "p9_m.png", plot = p9_m, dpi = 300, width = 6, height = 4)
  
```

# Individual plots with LME for Anxiety with SubjPE pilot 8

```{r echo=FALSE, warning=FALSE, message=FALSE}
model2 <- lme4::lmer(Anxiety ~ SubjPE + (SubjPE | Random_ID), data = df8_data, control=lmerControl(optimizer="bobyqa"))

coef_fixed <- fixef(model2)
intercept_Mood <- coef_fixed[1]
slope_Mood <- coef_fixed[2]
standard_beta_subjPE <- parameters:: standardise_parameters (model2)

p8_ax <- ggplot(df8_data, aes(x=SubjPE, y=Anxiety)) +
  geom_smooth(method = "lm", size = 0.5, se = FALSE, aes(group=Random_ID, color=Social_Anxiety)) +
  scale_color_manual(values = c("low" = "lightblue", "high" = "pink")) +
  geom_abline(intercept = intercept_Mood, slope = slope_Mood, color="purple", linetype="dashed", size=1) +
  xlab("Subjective PE") + 
  ylab("Anxiety") +
  ggtitle("Relationship between anxiety and subjective PE",
          subtitle = paste("estimated slopes of the association in n = ", 
                           length(unique(df8_data$Random_ID))))+
  theme(plot.title = element_text(size=14), plot.subtitle = element_text(size = 10))+
  theme(legend.title = element_text(size = 9), legend.text = element_text(size = 8))+
  theme(axis.title = element_text(size = 10))+
  annotate("label", x = 32, y = 55, label = paste("beta = ", round(standard_beta_subjPE$Std_Coefficient[2],2), ", 95%CI = ",
                                                 round(standard_beta_subjPE$CI_low[2],2), "-", 
                                                 round(standard_beta_subjPE$CI_high[2],2))) +
  scale_y_continuous(breaks = seq(0, 100, by = 20), limits = c(0, 100)) +
  scale_x_continuous(breaks = seq(-80, 80, by = 40), limits = c(-80, 80))

ggsave(filename = "p8_ax.png", plot = p8_ax, dpi = 300, width = 6, height = 4)
  
```


# Individual plots with LME for Mood with SubjPE pilot 8
```{r echo=FALSE, warning=FALSE, message=FALSE}
model2 <- lme4::lmer(Mood ~ SubjPE + (SubjPE | Random_ID), data = df8_data, control=lmerControl(optimizer="bobyqa"))

coef_fixed <- fixef(model2)
intercept_Mood <- coef_fixed[1]
slope_Mood <- coef_fixed[2]
standard_beta_subjPE <- parameters:: standardise_parameters (model2)

p8_m <- ggplot(df8_data, aes(x=SubjPE, y=Mood)) +
  geom_smooth(method = "lm", size = 0.5, se = FALSE, aes(group=Random_ID, color=Social_Anxiety)) +
  scale_color_manual(values = c("low" = "lightblue", "high" = "pink")) +
  geom_abline(intercept = intercept_Mood, slope = slope_Mood, color="purple", linetype="dashed", size=1) +
  xlab("Subjective PE") + 
  ylab("Mood") +
  ggtitle("Relationship between anxiety and subjective PE",
          subtitle = paste("estimated slopes of the association in n = ", 
                           length(unique(df8_data$Random_ID))))+
  theme(plot.title = element_text(size=14), plot.subtitle = element_text(size = 10))+
  theme(legend.title = element_text(size = 9), legend.text = element_text(size = 8))+
  theme(axis.title = element_text(size = 10))+
  annotate("label", x = 32, y = 55, label = paste("beta = ", round(standard_beta_subjPE$Std_Coefficient[2],2), ", 95%CI = ",
                                                 round(standard_beta_subjPE$CI_low[2],2), "-", 
                                                 round(standard_beta_subjPE$CI_high[2],2))) +
  scale_y_continuous(breaks = seq(0, 100, by = 20), limits = c(0, 100)) +
  scale_x_continuous(breaks = seq(-80, 80, by = 40), limits = c(-80, 80))

ggsave(filename = "p8_m.png", plot = p8_m, dpi = 300, width = 6, height = 4)
  
```


# Individual plots with LME for Anxiety with SubjPE pilot 7

```{r echo=FALSE, warning=FALSE, message=FALSE}
model2 <- lme4::lmer(Anxiety ~ SubjPE + (SubjPE | Random_ID), data = df7_data, control=lmerControl(optimizer="bobyqa"))

coef_fixed <- fixef(model2)
intercept_Mood <- coef_fixed[1]
slope_Mood <- coef_fixed[2]
standard_beta_subjPE <- parameters:: standardise_parameters (model2)

p7_ax <- ggplot(df7_data, aes(x=SubjPE, y=Anxiety)) +
  geom_smooth(method = "lm", size = 0.5, se = FALSE, aes(group=Random_ID, color=Social_Anxiety)) +
  scale_color_manual(values = c("low" = "lightblue", "high" = "pink")) +
  geom_abline(intercept = intercept_Mood, slope = slope_Mood, color="purple", linetype="dashed", size=1) +
  xlab("Subjective PE") + 
  ylab("Anxiety") +
  ggtitle("Relationship between anxiety and subjective PE",
          subtitle = paste("estimated slopes of the association in n = ", 
                           length(unique(df7_data$Random_ID))))+
  theme(plot.title = element_text(size=14), plot.subtitle = element_text(size = 10))+
  theme(legend.title = element_text(size = 9), legend.text = element_text(size = 8))+
  theme(axis.title = element_text(size = 10))+
  annotate("label", x = 32, y = 55, label = paste("beta = ", round(standard_beta_subjPE$Std_Coefficient[2],2), ", 95%CI = ",
                                                 round(standard_beta_subjPE$CI_low[2],2), "-", 
                                                 round(standard_beta_subjPE$CI_high[2],2))) +
  scale_y_continuous(breaks = seq(0, 100, by = 20), limits = c(0, 100)) +
  scale_x_continuous(breaks = seq(-80, 80, by = 40), limits = c(-80, 80))

ggsave(filename = "p7_ax.png", plot = p7_ax, dpi = 300, width = 6, height = 4)
  
```

# Individual plots with LME for Mood with SubjPE pilot 7

```{r echo=FALSE, warning=FALSE, message=FALSE}
model2 <- lme4::lmer(Mood ~ SubjPE + (SubjPE | Random_ID), data = df7_data, control=lmerControl(optimizer="bobyqa"))

coef_fixed <- fixef(model2)
intercept_Mood <- coef_fixed[1]
slope_Mood <- coef_fixed[2]
standard_beta_subjPE <- parameters:: standardise_parameters (model2)

p7_m <- ggplot(df7_data, aes(x=SubjPE, y=Mood)) +
  geom_smooth(method = "lm", size = 0.5, se = FALSE, aes(group=Random_ID, color=Social_Anxiety)) +
  scale_color_manual(values = c("low" = "lightblue", "high" = "pink")) +
  geom_abline(intercept = intercept_Mood, slope = slope_Mood, color="purple", linetype="dashed", size=1) +
  xlab("Subjective PE") + 
  ylab("Mood") +
  ggtitle("Relationship between anxiety and subjective PE",
          subtitle = paste("estimated slopes of the association in n = ", 
                           length(unique(df7_data$Random_ID))))+
  theme(plot.title = element_text(size=14), plot.subtitle = element_text(size = 10))+
  theme(legend.title = element_text(size = 9), legend.text = element_text(size = 8))+
  theme(axis.title = element_text(size = 10))+
  annotate("label", x = 32, y = 55, label = paste("beta = ", round(standard_beta_subjPE$Std_Coefficient[2],2), ", 95%CI = ",
                                                 round(standard_beta_subjPE$CI_low[2],2), "-", 
                                                 round(standard_beta_subjPE$CI_high[2],2))) +
  scale_y_continuous(breaks = seq(0, 100, by = 20), limits = c(0, 100)) +
  scale_x_continuous(breaks = seq(-80, 80, by = 40), limits = c(-80, 80))

ggsave(filename = "p7_m.png", plot = p7_m, dpi = 300, width = 6, height = 4)
  
```


# Individual plots with LME for Anxiety with SubjPE pilot 6
```{r echo=FALSE, warning=FALSE, message=FALSE}
model2 <- lme4::lmer(Anxiety ~ SubjPE + (SubjPE | Random_ID), data = df6_data, control=lmerControl(optimizer="bobyqa"))

coef_fixed <- fixef(model2)
intercept_Mood <- coef_fixed[1]
slope_Mood <- coef_fixed[2]
standard_beta_subjPE <- parameters:: standardise_parameters (model2)

p6_ax <- ggplot(df6_data, aes(x=SubjPE, y=Anxiety)) +
  geom_smooth(method = "lm", size = 0.5, se = FALSE, aes(group=Random_ID, color=Social_Anxiety)) +
  scale_color_manual(values = c("low" = "lightblue", "high" = "pink")) +
  geom_abline(intercept = intercept_Mood, slope = slope_Mood, color="purple", linetype="dashed", size=1) +
  xlab("Subjective PE") + 
  ylab("Anxiety") +
  ggtitle("Relationship between anxiety and subjective PE",
          subtitle = paste("estimated slopes of the association in n = ", 
                           length(unique(df6_data$Random_ID))))+
  theme(plot.title = element_text(size=14), plot.subtitle = element_text(size = 6))+
  theme(legend.title = element_text(size = 9), legend.text = element_text(size = 8))+
  theme(axis.title = element_text(size = 6))+
  annotate("label", x = 32, y = 55, label = paste("beta = ", round(standard_beta_subjPE$Std_Coefficient[2],2), ", 95%CI = ",
                                                 round(standard_beta_subjPE$CI_low[2],2), "-", 
                                                 round(standard_beta_subjPE$CI_high[2],2))) +
  scale_y_continuous(breaks = seq(0, 60, by = 20), limits = c(0, 60)) +
  scale_x_continuous(breaks = seq(-80, 80, by = 40), limits = c(-80, 80))

ggsave(filename = "p6_ax.png", plot = p6_ax, dpi = 300, width = 6, height = 4)
  
```

# Individual plots with LME for Mood with SubjPE pilot 6

```{r echo=FALSE, warning=FALSE, message=FALSE}
model2 <- lme4::lmer(Mood ~ SubjPE + (SubjPE | Random_ID), data = df6_data, control=lmerControl(optimizer="bobyqa"))

coef_fixed <- fixef(model2)
intercept_Mood <- coef_fixed[1]
slope_Mood <- coef_fixed[2]
standard_beta_subjPE <- parameters:: standardise_parameters (model2)

p6_m <- ggplot(df6_data, aes(x=SubjPE, y=Mood)) +
  geom_smooth(method = "lm", size = 0.5, se = FALSE, aes(group=Random_ID, color=Social_Anxiety)) +
  scale_color_manual(values = c("low" = "lightblue", "high" = "pink")) +
  geom_abline(intercept = intercept_Mood, slope = slope_Mood, color="purple", linetype="dashed", size=1) +
  xlab("Subjective PE") + 
  ylab("Mood") +
  ggtitle("Relationship between anxiety and subjective PE",
          subtitle = paste("estimated slopes of the association in n = ", 
                           length(unique(df6_data$Random_ID))))+
  theme(plot.title = element_text(size=14), plot.subtitle = element_text(size = 6))+
  theme(legend.title = element_text(size = 9), legend.text = element_text(size = 8))+
  theme(axis.title = element_text(size = 6))+
  annotate("label", x = 32, y = 55, label = paste("beta = ", round(standard_beta_subjPE$Std_Coefficient[2],2), ", 95%CI = ",
                                                 round(standard_beta_subjPE$CI_low[2],2), "-", 
                                                 round(standard_beta_subjPE$CI_high[2],2))) +
  scale_y_continuous(breaks = seq(0, 100, by = 20), limits = c(0, 100)) +
  scale_x_continuous(breaks = seq(-80, 80, by = 40), limits = c(-80, 80))

ggsave(filename = "p6_m.png", plot = p6_m, dpi = 300, width = 6, height = 4)
  
```