---
title: "Surprise study pilot 22"
author: "Marjan Biria"
date: "2224-04-16"
output: 
    pdf_document:
    toc: true
    toc_depth: 2
    toc_float: true
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(root.dir = "", echo = TRUE)
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
library(dplyr)
library(ggplot2)
library(tidyr)
library(lme4)
library(parameters)
library(broom.mixed)
library(purrr)
library(conflicted)
library(stringr)
library(readxl)
```


\newpage
# Study description

This study is the same as pilot 21, except we have now two new questions measuring anxiety: 1) how nervous would you feel to talk to this person again? 2) how embarrassed do you feel right now? 

We would like to see whether these are more specific answers to tap into social anxiety (after the feedback we received from Quentin).

The Gorilla experiment is the following: https://app.gorilla.sc/admin/experiment/175580/design
The task is the following: https://app.gorilla.sc/admin/task/812527/editor?version=4



```{r echo=FALSE, warning=FALSE, message=FALSE}

df22_raw <- read.csv("/Users/marjan/Desktop/aim_lab_1/De_identified_data/pilot_22/SUP_PRF_p22_vid_bigPE_nohist_newjud_2anxQ_v1/SUP_PRF_p22_vid_bigPE_nohist_newjud_2anxQ_v1_task_main.csv")
df22_spin <- read.csv("/Users/marjan/Desktop/aim_lab_1/De_identified_data/pilot_22/SUP_PRF_p22_vid_bigPE_nohist_newjud_2anxQ_v1/SUP_PRF_p22_vid_bigPE_nohist_newjud_2anxQ_v1_mini_spin.csv")
df22_cesd <- read.csv("/Users/marjan/Desktop/aim_lab_1/De_identified_data/pilot_22/SUP_PRF_p22_vid_bigPE_nohist_newjud_2anxQ_v1/SUP_PRF_p22_vid_bigPE_nohist_newjud_2anxQ_v1_ces_d.csv")

```


```{r echo=FALSE, warning=FALSE, message=FALSE}
# extract CES-D scores
CESD_data_clean <- df22_cesd[, c(32, 34, 36, 38, 40, 42, 44, 46,48,50,
                                 52, 54, 56, 58, 60, 62, 64, 66, 68, 70, 71 )]
# Identify non-ID variable columns
non_id_cols <- setdiff(names(CESD_data_clean), "Random_ID")

# Convert non-ID variables to numeric
CESD_data_clean[, non_id_cols] <- lapply(CESD_data_clean[, non_id_cols], as.numeric)

#change numbers to match CES-D scoring system
excluded_columns <-  c("Random_ID", "Multiple.Choice.Grid.object.3.4...I.felt.I.was.just.as.good.as.other.people..Quantised",
                       "Multiple.Choice.Grid.object.3.8...I.felt.hopeful.about.the.future..Quantised",
                       "Multiple.Choice.Grid.object.3.12...I.was.happy..Quantised",
                       "Multiple.Choice.Grid.object.3.16...I.enjoyed.life..Quantised")
                  

CESD_data_clean<- CESD_data_clean %>%
  mutate(across(-excluded_columns , ~ case_when(
    . == 1 ~ 0,
    . == 2 ~ 1,
    . == 3 ~ 2,
    . == 4 ~ 3,
    TRUE ~ .
  )))


other_columns <- c("Multiple.Choice.Grid.object.3.4...I.felt.I.was.just.as.good.as.other.people..Quantised",
                   "Multiple.Choice.Grid.object.3.8...I.felt.hopeful.about.the.future..Quantised",
                   "Multiple.Choice.Grid.object.3.12...I.was.happy..Quantised",
                   "Multiple.Choice.Grid.object.3.16...I.enjoyed.life..Quantised")
CESD_data_clean<- CESD_data_clean %>%
  mutate(across(other_columns , ~ case_when(
    . == 1 ~ 3,
    . == 2 ~ 2,
    . == 3 ~ 1,
    . == 4 ~ 0,
    TRUE ~ .
  )))

#scoring----
CESD_scores <-  numeric(length(CESD_data_clean$Random_ID))
CESD_scores <- 0
Questions <- c(1:20)

for (i in 1:nrow(CESD_data_clean)) {
  CESD_score <- sum(CESD_data_clean[i, Questions])
  CESD_scores[i] <- CESD_score
}

CESD_data_clean$CESD_score <-  CESD_scores

CESD_data_clean$Depression_Threshold<- 0
CESD_data_clean$Depression_status <- "Not_Depressed"

#Assign "1" if they meet Depression threshold 
for (i in 1:nrow(CESD_data_clean)) {
  if (CESD_data_clean$CESD_score[i] >= 16) {
    CESD_data_clean$Depression_Threshold[i] <- 1
    CESD_data_clean$Depression_status[i] <- "Depressed"
  }
}
```


```{r echo=FALSE, warning=FALSE, message=FALSE}
# We have now different names for different screens:
# Prediction (how well do you think you performed?)
# prediction_2 (how well do you think you performed?)
# feedback (This is how well X thought you performed)
# First 4 trials are with the histograms and are called "Trials_Histogram" in Display column instead of "Trials"
# The trial numbers start from 1 again after the histograms so we need to concatenate them all.
# Let's rename them to "Trials" to extract them together with the rest of the trials

df22_raw$Trial.Number[df22_raw$Display == "Trials "] <- df22_raw$Trial.Number[df22_raw$Display == "Trials "] + 4

df22_raw <- df22_raw %>%
  mutate(Screen = if_else(Screen == "Prediction", "Prediction ", Screen))


df22_raw <- df22_raw %>%
  mutate(Display = if_else(Display == "Trials_Histogram", "Trials ", Display))

df22_spin <- df22_spin %>%
  rename(
   "Q1" =  "Rating.Scale.object.2.Fear.of.embarrassment.causes.me.to.avoid.doing.things.or.speaking.to.people.",
   "Q2" =  "Rating.Scale.object.2.I.avoid.activities.in.which.I.am.the.center.of.attention.",
   "Q3" = "Rating.Scale.object.2.Being.embarrassed.or.looking.stupid.are.among.my.worst.fears."
  )

df22_spin <- df22_spin %>%
  rowwise() %>%
  mutate(mini_SPIN_total = sum(c(Q1, Q2, Q3), na.rm = TRUE)) %>%
  ungroup()


# create a new df22 that only keeps the columns we need
df22 <- df22_raw[, c("Trial.Number", "Display", "Screen", "Response.Type", "Response", 
                     "Reaction.Time", "Spreadsheet..Histogram", "Spreadsheet..Feedback", "Random_ID")]

df22 <- df22 %>% dplyr::filter(Response.Type != "info")

df22 <- df22 %>%
  mutate(Response = as.numeric(as.character(Response))) %>%
  dplyr::filter(!is.na(Response))

df22$Screen <- ifelse(df22$Trial.Number == 1 & (df22$Display == "Mood " | df22$Display == "Embarrassment"), "BL_1",
                      ifelse(df22$Trial.Number == 2 & (df22$Display == "Mood " | df22$Display == "Embarrassment"), "BL_2", 
                             df22$Screen))

df22$m_hist <- ifelse(df22$Spreadsheet..Histogram == "h2.png", 29,
                             ifelse(df22$Spreadsheet..Histogram == "h3.png", 37,
                                                  ifelse(df22$Spreadsheet..Histogram == "h6.png", 63,
                                                         ifelse(df22$Spreadsheet..Histogram == "h7.png", 71, NA))))  


# get rid of the rows we don't need: practice runs, continue button presses etc. and only keep Trials, Anxiety and Mood that include all variables we are interested in:
df22 <- df22 %>%
  dplyr::filter(
    (Display == "Trials ") |
      (Display == "Exit") |
      (Display == "Anxiety ") |
      (Display == "Mood " & !Trial.Number %in% c(1, 2)) |
      (Display == "Embarrassment" & !Trial.Number %in% c(1, 2)) 
  )

# # setting Mood and Anxiety trial numbers to match the trials starting from 1 (since we removed the baseline ones above)
df22$Trial.Number <- ifelse(df22$Display == 'Mood ' | df22$Display == 'Embarrassment', df22$Trial.Number - 2, df22$Trial.Number)
df22$Display <- ifelse(df22$Display == 'Mood ' | df22$Display == 'Embarrassment', "Trials", df22$Display)

# renaming the feedback column to fdbk
names(df22)[names(df22) == 'Spreadsheet..Feedback'] <- 'fdbk'

# Now let's create columns for PE (fdbk-hist) and Subj_PE (fdbk_Prediction)

df22$SubjPE <- ifelse(df22$Screen == "Prediction ", df22$fdbk - df22$Response, NA)
df22$PE <- ifelse(df22$Screen == "Prediction ", df22$fdbk - df22$m_hist, NA)
# to keep just one repetition of feedback and mean histogram per trial per subject 
# and replace the rest with NA so that when we want to convert to long format we won't have duplicates
df22$fdbk <- ifelse(df22$Screen == "Prediction ", df22$fdbk, NA)
df22$m_hist <- ifelse(df22$Screen == "Prediction ", df22$m_hist, NA)
df22$stress_level <- ifelse(df22$Screen == "Screen 12", df22$Response, NA)

long_df22 <- df22 %>%
  dplyr::select(Random_ID, Trial.Number, fdbk, m_hist, PE, SubjPE, stress_level) %>%
  pivot_longer(cols = c(fdbk, m_hist, PE, SubjPE, stress_level),
               names_to = "Screen",
               values_to = "Response")

# This will keep only the rows where 'Response' is not NA
long_df22 <- long_df22[!is.na(long_df22$Response), ]

# Selecting relevant columns from the original df22
df22 <- df22 %>%
  dplyr::select(-c(fdbk, m_hist, PE, SubjPE, stress_level))

# Binding the rows together
df22 <- bind_rows(df22, long_df22)

df22$Response <- as.numeric(df22$Response)

# looking at the relationship between PE and SubjPE
df22_PE <- subset(df22, Screen == "PE")
names(df22_PE)[names(df22_PE) == "Screen"] <- "Screen_PE"
names(df22_PE)[names(df22_PE) == "Response"] <- "Response_PE"

df22_SubjPE <- subset(df22, Screen == "SubjPE")
names(df22_SubjPE)[names(df22_SubjPE) == "Screen"] <- "Screen_SubjPE"
names(df22_SubjPE)[names(df22_SubjPE) == "Response"] <- "Response_SubjPE"

df22_fdbk <- subset(df22, Screen == "fdbk")
names(df22_fdbk)[names(df22_fdbk) == "Screen"] <- "Screen_fdbk"
names(df22_fdbk)[names(df22_fdbk) == "Response"] <- "Response_fdbk"

df22_hist <- subset(df22, Screen == "m_hist")
names(df22_hist)[names(df22_hist) == "Screen"] <- "Screen_m_hist"
names(df22_hist)[names(df22_hist) == "Response"] <- "Response_m_hist"

df22_stress_level <- subset(df22, Screen == "Screen 12")
names(df22_stress_level)[names(df22_stress_level) == "Screen"] <- "Screen_stress_level"
names(df22_stress_level)[names(df22_stress_level) == "Response"] <- "Response_stress_level"

df22_predic <- subset(df22, Screen == "Prediction ")
names(df22_predic)[names(df22_predic) == "Screen"] <- "Screen_pred"
names(df22_predic)[names(df22_predic) == "Response"] <- "Response_pred"


# df22_cert <- subset(df22, Screen == "Certainty rating ")
# names(df22_cert)[names(df22_cert) == "Screen"] <- "Screen_certainty"
# names(df22_cert)[names(df22_cert) == "Response"] <- "Response_certainty"

list_of_dfs_22 <- list(df22_PE, df22_fdbk, df22_hist, df22_predic, df22_SubjPE)

# Using reduce with inner_join
merged_df22 <- reduce(list_of_dfs_22, inner_join, by = c("Random_ID", "Trial.Number"))

df22_Anxious <- subset(df22, Screen == "Anxious")
names(df22_Anxious)[names(df22_Anxious) == "Screen"] <- "Screen_Ax"
names(df22_Anxious)[names(df22_Anxious) == "Response"] <- "Response_Ax"

df22_Embarrasment <- subset(df22, Screen == "Screen 1")
names(df22_Embarrasment)[names(df22_Embarrasment) == "Screen 1"] <- "Screen_Embarrassment"
names(df22_Embarrasment)[names(df22_Embarrasment) == "Response"] <- "Response_Emb"

df22_Happy <- subset(df22, Screen == "Happy")
# df22_fdbk <- subset(df22, Screen == "Prediction")
names(df22_Happy)[names(df22_Happy) == "Screen"] <- "Screen_H"
names(df22_Happy)[names(df22_Happy) == "Response"] <- "Response_H"

final_df22 <- merged_df22 %>%
  inner_join(df22_Anxious, by = c("Random_ID", "Trial.Number")) %>%
  inner_join(df22_Happy, by = c("Random_ID", "Trial.Number")) %>%
  inner_join(df22_Embarrasment, by = c("Random_ID", "Trial.Number"))

# subset only the columns we are interested in
final_df22 <- final_df22[c("Trial.Number", "Random_ID", "Response_H", "Response_Ax", "Response_fdbk", "Response_SubjPE", "Response_PE", "Response_m_hist", "Response_pred", "Response_Emb")]

final_df22 <- final_df22 %>%
  left_join(df22_spin %>% dplyr::select(Random_ID, mini_SPIN_total), by = "Random_ID")

final_df22 <- final_df22 %>%
  left_join(df22_stress_level %>% dplyr::select(Random_ID, Response_stress_level), by = "Random_ID")

final_df22 <- final_df22 %>%
  left_join(CESD_data_clean %>% dplyr::select(Random_ID, CESD_score, Depression_Threshold, Depression_status), by = "Random_ID")

final_df22$Social_Anxiety <- ifelse(final_df22$mini_SPIN_total >= 6, "high", "low")


write.csv(final_df22, "pilot_22_variables.csv", row.names = FALSE)


final_df22 %>%
  group_by(Random_ID) %>%
  summarise(Trial.Number = n())

write.csv(final_df22, "final_df22_with_stresslevels.csv", row.names = FALSE)

```



\newpage 
# Relationship between prediction and mean histograms (4x only in the beginning)


```{r echo=FALSE, warning=FALSE, message=FALSE}
correlations <- final_df22 %>%
  group_by(Random_ID) %>%
  summarise(correlation = cor(Response_m_hist, Response_pred, method = "spearman", use = "complete.obs")) %>%
  mutate(label = paste("R = ", round(correlation, digits = 2)))

# # calculate the average correlation across all individuals and print it
average_correlation <- mean(correlations$correlation, na.rm = TRUE)
message_to_print_H <- paste("average correlation between mean_hist and prediction:", average_correlation)

print(message_to_print_H)

ggplot(final_df22, aes(x = Response_m_hist, y = Response_pred, color = Social_Anxiety, group= Social_Anxiety)) +
  geom_point(aes(color=Social_Anxiety, alpha = 0.3)) +
  geom_smooth(method = "lm", color="blue", aes(group=Random_ID)) +
  # labs(color="Legend") +
  theme_minimal() +
  xlab("prediction") +
  ylab("mean_histogram") +
    facet_wrap(~ Random_ID, scales = "free") +
    geom_text(data=correlations, aes(x=Inf, y=Inf, label=label, group=Random_ID), hjust=1.1, vjust=1.1, size=2.7, fontface = "bold", inherit.aes=FALSE) +
    theme(strip.text = element_text(size = 6),
        axis.text.x = element_text(size = 5.5),
        axis.text.y = element_text(size = 5.5),
        strip.text.x = element_text(face = "bold"),
        strip.text.y = element_text(face = "bold"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank())
  
```

\newpage 
# Relationship between Anxiety and SubjPE

The anxiety question now asks "how nervous would you feel to talk to this person again?". It shows a correlation of -0.12, in our previous pilot where we asked "how nervous/uncomfortable do you feel right now" we had a correlation of -0.15.

```{r echo=FALSE, warning=FALSE, message=FALSE}
correlations_Ax <- final_df22 %>%
  group_by(Random_ID) %>%
  summarise(correlation = cor(Response_Ax, Response_SubjPE, use = "complete.obs")) %>%
  mutate(label = paste("R = ", round(correlation, digits = 2))) 

# calculate the average correlation across all individuals and print it 
average_correlation <- mean(correlations_Ax$correlation, na.rm = TRUE)
message_to_print_Ax <- paste("average correlation between anxiety and SubjPE:", average_correlation)

print(message_to_print_Ax)

ggplot(final_df22, aes(x = Response_SubjPE, y = Response_Ax, color = Social_Anxiety, group= Social_Anxiety)) +
  geom_point(aes(color=Social_Anxiety, alpha = 0.3)) +
  geom_smooth(method = "lm", color="blue", aes(group=Random_ID)) + 
  # labs(color="Legend") +
  theme_minimal() +
  xlab("SubjPE: feedback - prediction") + 
  ylab("Anxiety") +
    facet_wrap(~ Random_ID, scales = "free") +
    geom_text(data=correlations_Ax, aes(x=Inf, y=Inf, label=label, group=Random_ID), hjust=1.1, vjust=1.1, size=2.7, fontface = "bold", inherit.aes=FALSE) +
    theme(strip.text = element_text(size = 6),
        axis.text.x = element_text(size = 5.5),  
        axis.text.y = element_text(size = 5.5),  
        strip.text.x = element_text(face = "bold"),  
        strip.text.y = element_text(face = "bold"),  
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank()) +
ylim(c(0, 100)) +
scale_y_continuous(breaks = seq(0, 100, by = 25), limits = c(0, 100))+
xlim(c(-100, 100)) +
scale_x_continuous(breaks = seq(-80, 80, by = 50), limits = c(-80,80))
```
\newpage 
# Relationship between Embarrassment and SubjPE

We asked people one additional question that was more specifically related to their social anxiety: "how embarrassed do you feel right now?". The correlation is similar to the previous question (r = -0.12).

```{r echo=FALSE, warning=FALSE, message=FALSE}
correlations_Emb <- final_df22 %>%
  group_by(Random_ID) %>%
  summarise(correlation = cor(Response_Emb, Response_SubjPE, use = "complete.obs")) %>%
  mutate(label = paste("R = ", round(correlation, digits = 2))) 

# calculate the average correlation across all individuals and print it 
average_correlation <- mean(correlations_Emb$correlation, na.rm = TRUE)
message_to_print_Emb <- paste("average correlation between embarrassment and SubjPE:", average_correlation)

print(message_to_print_Emb)

ggplot(final_df22, aes(x = Response_SubjPE, y = Response_Emb, color = Social_Anxiety, group= Social_Anxiety)) +
  geom_point(aes(color=Social_Anxiety, alpha = 0.3)) +
  geom_smooth(method = "lm", color="blue", aes(group=Random_ID)) + 
  # labs(color="Legend") +
  theme_minimal() +
  xlab("SubjPE: feedback - prediction") + 
  ylab("Embarrassment") +
    facet_wrap(~ Random_ID, scales = "free") +
    geom_text(data=correlations_Ax, aes(x=Inf, y=Inf, label=label, group=Random_ID), hjust=1.1, vjust=1.1, size=2.7, fontface = "bold", inherit.aes=FALSE) +
    theme(strip.text = element_text(size = 6),
        axis.text.x = element_text(size = 5.5),  
        axis.text.y = element_text(size = 5.5),  
        strip.text.x = element_text(face = "bold"),  
        strip.text.y = element_text(face = "bold"),  
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank()) +
ylim(c(0, 100)) +
scale_y_continuous(breaks = seq(0, 100, by = 25), limits = c(0, 100))+
xlim(c(-100, 100)) +
scale_x_continuous(breaks = seq(-80, 80, by = 50), limits = c(-80,80))
```

\newpage 
# Relationship between Mood and SubjPE

```{r echo=FALSE, warning=FALSE, message=FALSE}

correlations_M <- final_df22 %>%
  group_by(Random_ID) %>%
  summarise(correlation = cor(Response_H, Response_SubjPE, use = "complete.obs")) %>%
  mutate(label = paste("R = ", round(correlation, digits = 2))) 

# calculate the average correlation across all individuals and print it 
average_correlation <- mean(correlations_M$correlation, na.rm = TRUE)
message_to_print_H <- paste("average correlation between mood and SubjPE:", average_correlation)

print(message_to_print_H)

ggplot(final_df22, aes(x = Response_SubjPE, y = Response_H, color = Social_Anxiety, group= Social_Anxiety)) +
  geom_point(aes(color=Social_Anxiety, alpha = 0.3)) +
  geom_smooth(method = "lm", color="blue", aes(group=Random_ID)) + 
  # labs(color="Legend") +
  theme_minimal() +
  xlab("SubjPE: feedback - prediction") + 
  ylab("Mood") +
    facet_wrap(~ Random_ID, scales = "free") +
    geom_text(data=correlations_M, aes(x=Inf, y=Inf, label=label, group=Random_ID), hjust=1.1, vjust=1.1, size=2.7, fontface = "bold", inherit.aes=FALSE) +
    theme(strip.text = element_text(size = 6),
        axis.text.x = element_text(size = 5.5),  
        axis.text.y = element_text(size = 5.5),  
        strip.text.x = element_text(face = "bold"),  
        strip.text.y = element_text(face = "bold"),  
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank()) +
  ylim(c(0, 100)) + 
  scale_y_continuous(breaks = seq(0, 100, by = 25), limits = c(0, 100))+
  xlim(c(-100, 100)) + 
  scale_x_continuous(breaks = seq(-80, 80, by = 50), limits = c(-80,80))
  
```
\newpage 
# Relationship between Anxiety and prediction

The correlation between "how nervous would you feel to talk to this person again" and prediction is bigger than the one with SubjPE (-0.14 vs -0.11), with our previous question in pilot 21 it was the other way around, and we had a correlation of almost -0.15.

```{r echo=FALSE, warning=FALSE, message=FALSE}
correlations <- final_df22 %>%
  group_by(Random_ID) %>%
  summarise(correlation = cor(Response_Ax, Response_pred, use = "complete.obs")) %>%
  mutate(label = paste("R = ", round(correlation, digits = 2))) 

# calculate the average correlation across all individuals and print it 
average_correlation <- mean(correlations$correlation, na.rm = TRUE)
message_to_print_H <- paste("average correlation between anxiety and prediction:", average_correlation)

print(message_to_print_H)

ggplot(final_df22, aes(x = Response_pred, y = Response_Ax, color = Social_Anxiety, group= Social_Anxiety)) +
  geom_point(aes(color=Social_Anxiety, alpha = 0.3)) +
  geom_smooth(method = "lm", color="blue", aes(group=Random_ID)) + 
  # labs(color="Legend") +
  theme_minimal() +
  xlab("Pre performance prediction") + 
  ylab("Anxiety") +
    facet_wrap(~ Random_ID, scales = "free") +
    geom_text(data=correlations, aes(x=Inf, y=Inf, label=label, group=Random_ID), hjust=1.1, vjust=1.1, size=2.7, fontface = "bold", inherit.aes=FALSE) +
    theme(strip.text = element_text(size = 6),
        axis.text.x = element_text(size = 5.5),  
        axis.text.y = element_text(size = 5.5),  
        strip.text.x = element_text(face = "bold"),  
        strip.text.y = element_text(face = "bold"),  
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank()) +
  ylim(c(0, 100)) + 
  scale_y_continuous(breaks = seq(0, 100, by = 25), limits = c(0, 100))+
  xlim(c(-100, 100)) + 
  scale_x_continuous(breaks = seq(0, 100, by = 25), limits = c(0,100))
  
```


\newpage 
# Relationship between Anxiety and feedback

Again, the relationship between "how nervous would you feel to talk to this person again" and feedback is stronger than what we had before (-0.21, vs -0.17).

```{r echo=FALSE, warning=FALSE, message=FALSE}
correlations <- final_df22 %>%
  group_by(Random_ID) %>%
  summarise(correlation = cor(Response_Ax, Response_fdbk, use = "complete.obs")) %>%
  mutate(label = paste("R = ", round(correlation, digits = 2))) 

# calculate the average correlation across all individuals and print it 
average_correlation <- mean(correlations$correlation, na.rm = TRUE)
message_to_print_H <- paste("average correlation between anxiety and feedback:", average_correlation)

print(message_to_print_H)

ggplot(final_df22, aes(x = Response_fdbk, y = Response_Ax, color = Social_Anxiety, group= Social_Anxiety)) +
  geom_point(aes(color=Social_Anxiety, alpha = 0.3)) +
  geom_smooth(method = "lm", color="blue", aes(group=Random_ID)) + 
  # labs(color="Legend") +
  theme_minimal() +
  xlab("Feedback") + 
  ylab("Anxiety") +
    facet_wrap(~ Random_ID, scales = "free") +
    geom_text(data=correlations, aes(x=Inf, y=Inf, label=label, group=Random_ID), hjust=1.1, vjust=1.1, size=2.7, fontface = "bold", inherit.aes=FALSE) +
    theme(strip.text = element_text(size = 6),
        axis.text.x = element_text(size = 5.5),  
        axis.text.y = element_text(size = 5.5),  
        strip.text.x = element_text(face = "bold"),  
        strip.text.y = element_text(face = "bold"),  
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank()) +
  ylim(c(0, 100)) + 
  scale_y_continuous(breaks = seq(0, 100, by = 25), limits = c(0, 100))+
  xlim(c(-100, 100)) + 
  scale_x_continuous(breaks = seq(0, 100, by = 25), limits = c(0,100))
  
```
\newpage 
# Relationship between Embarrassment and prediction

A much weaker correlation with embarrassment and prediction (r = -0.06).

```{r echo=FALSE, warning=FALSE, message=FALSE}
correlations <- final_df22 %>%
  group_by(Random_ID) %>%
  summarise(correlation = cor(Response_Emb, Response_pred, use = "complete.obs")) %>%
  mutate(label = paste("R = ", round(correlation, digits = 2))) 

# calculate the average correlation across all individuals and print it 
average_correlation <- mean(correlations$correlation, na.rm = TRUE)
message_to_print_Emb <- paste("average correlation between Embarrassment and Prediction:", average_correlation)

print(message_to_print_Emb)

ggplot(final_df22, aes(x = Response_pred, y = Response_Emb, color = Social_Anxiety, group= Social_Anxiety)) +
  geom_point(aes(color=Social_Anxiety, alpha = 0.3)) +
  geom_smooth(method = "lm", color="blue", aes(group=Random_ID)) + 
  # labs(color="Legend") +
  theme_minimal() +
  xlab("Pre performance prediction") + 
  ylab("Embarrassment") +
    facet_wrap(~ Random_ID, scales = "free") +
    geom_text(data=correlations, aes(x=Inf, y=Inf, label=label, group=Random_ID), hjust=1.1, vjust=1.1, size=2.7, fontface = "bold", inherit.aes=FALSE) +
    theme(strip.text = element_text(size = 6),
        axis.text.x = element_text(size = 5.5),  
        axis.text.y = element_text(size = 5.5),  
        strip.text.x = element_text(face = "bold"),  
        strip.text.y = element_text(face = "bold"),  
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank()) +
  ylim(c(0, 100)) + 
  scale_y_continuous(breaks = seq(0, 100, by = 25), limits = c(0, 100))+
  xlim(c(-100, 100)) + 
  scale_x_continuous(breaks = seq(0, 100, by = 25), limits = c(0,100))
  
```
\newpage 
# Relationship between Embarrassment and prediction

But again a stronger correlation with feedback (r = -0.17).

```{r echo=FALSE, warning=FALSE, message=FALSE}
correlations <- final_df22 %>%
  group_by(Random_ID) %>%
  summarise(correlation = cor(Response_Emb, Response_fdbk, use = "complete.obs")) %>%
  mutate(label = paste("R = ", round(correlation, digits = 2))) 

# calculate the average correlation across all individuals and print it 
average_correlation <- mean(correlations$correlation, na.rm = TRUE)
message_to_print_Emb <- paste("average correlation between Embarrassment and Feedback:", average_correlation)

print(message_to_print_Emb)

ggplot(final_df22, aes(x = Response_fdbk, y = Response_Emb, color = Social_Anxiety, group= Social_Anxiety)) +
  geom_point(aes(color=Social_Anxiety, alpha = 0.3)) +
  geom_smooth(method = "lm", color="blue", aes(group=Random_ID)) + 
  # labs(color="Legend") +
  theme_minimal() +
  xlab("Feedback") + 
  ylab("Embarrassment") +
    facet_wrap(~ Random_ID, scales = "free") +
    geom_text(data=correlations, aes(x=Inf, y=Inf, label=label, group=Random_ID), hjust=1.1, vjust=1.1, size=2.7, fontface = "bold", inherit.aes=FALSE) +
    theme(strip.text = element_text(size = 6),
        axis.text.x = element_text(size = 5.5),  
        axis.text.y = element_text(size = 5.5),  
        strip.text.x = element_text(face = "bold"),  
        strip.text.y = element_text(face = "bold"),  
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank()) +
  ylim(c(0, 100)) + 
  scale_y_continuous(breaks = seq(0, 100, by = 25), limits = c(0, 100))+
  xlim(c(-100, 100)) + 
  scale_x_continuous(breaks = seq(0, 100, by = 25), limits = c(0,100))
  
```

\newpage 
# Relationship between Mood and feedback

A stronger correlation between mood and feedback which is the same as before.

```{r echo=FALSE, warning=FALSE, message=FALSE}
correlations_Mfd <- final_df22 %>%
  group_by(Random_ID) %>%
  summarise(correlation = cor(Response_H, Response_fdbk, use = "complete.obs")) %>%
  mutate(label = paste("R = ", round(correlation, digits = 2))) 

# calculate the average correlation across all individuals and print it 
average_correlation <- mean(correlations_Mfd$correlation, na.rm = TRUE)
message_to_print_H <- paste("average correlation between mood and feedback:", average_correlation)

print(message_to_print_H)

ggplot(final_df22, aes(x = Response_fdbk, y = Response_H, color = Social_Anxiety, group= Social_Anxiety)) +
  geom_point(aes(color=Social_Anxiety, alpha = 0.3)) +
  geom_smooth(method = "lm", color="blue", aes(group=Random_ID)) + 
  # labs(color="Legend") +
  theme_minimal() +
  xlab("Feedback") + 
  ylab("Mood") +
    facet_wrap(~ Random_ID, scales = "free") +
    geom_text(data=correlations_Mfd, aes(x=Inf, y=Inf, label=label, group=Random_ID), hjust=1.1, vjust=1.1, size=2.7, fontface = "bold", inherit.aes=FALSE) +
    theme(strip.text = element_text(size = 6),
        axis.text.x = element_text(size = 5.5),  
        axis.text.y = element_text(size = 5.5),  
        strip.text.x = element_text(face = "bold"),  
        strip.text.y = element_text(face = "bold"),  
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank()) +
  ylim(c(0, 100)) + 
  scale_y_continuous(breaks = seq(0, 100, by = 25), limits = c(0, 100))+
  xlim(c(-100, 100)) + 
  scale_x_continuous(breaks = seq(0, 100, by = 25), limits = c(0,100))
  
```

\newpage 
# Relationship between Mood and prediction (pre-performance)

Similar to before, we have a weaker correlation with prediction and mood.

```{r echo=FALSE, warning=FALSE, message=FALSE}
correlations <- final_df22 %>%
  group_by(Random_ID) %>%
  summarise(correlation = cor(Response_H, Response_pred, use = "complete.obs")) %>%
  mutate(label = paste("R = ", round(correlation, digits = 2))) 

# calculate the average correlation across all individuals and print it 
average_correlation <- mean(correlations$correlation, na.rm = TRUE)
message_to_print_H <- paste("average correlation between mood and prediction before performance:", average_correlation)

print(message_to_print_H)

ggplot(final_df22, aes(x = Response_pred, y = Response_H, color = Social_Anxiety, group= Social_Anxiety)) +
  geom_point(aes(color=Social_Anxiety, alpha = 0.3)) +
  geom_smooth(method = "lm", color="blue", aes(group=Random_ID)) + 
  # labs(color="Legend") +
  theme_minimal() +
  xlab("Prediction pre performance") + 
  ylab("Mood") +
    facet_wrap(~ Random_ID, scales = "free") +
    geom_text(data=correlations, aes(x=Inf, y=Inf, label=label, group=Random_ID), hjust=1.1, vjust=1.1, size=2.7, fontface = "bold", inherit.aes=FALSE) +
    theme(strip.text = element_text(size = 6),
        axis.text.x = element_text(size = 5.5),  
        axis.text.y = element_text(size = 5.5),  
        strip.text.x = element_text(face = "bold"),  
        strip.text.y = element_text(face = "bold"),  
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank()) +
  ylim(c(0, 100)) + 
  scale_y_continuous(breaks = seq(0, 100, by = 25), limits = c(0, 100))+
  xlim(c(-100, 100)) + 
  scale_x_continuous(breaks = seq(0, 100, by = 25), limits = c(0,100))
  
```


```{r echo=FALSE, warning=FALSE, message=FALSE}
# trying to keep the BL_1 and BL_2 mood and anxiety ratings
df22_with_BL <- df22_raw[, c("Trial.Number", "Display", "Screen", "Response.Type", "Response", 
                     "Reaction.Time", "Spreadsheet..Histogram", "Spreadsheet..Feedback", "Random_ID")]

df22_with_BL <- df22_with_BL %>%
  mutate(Response = as.numeric(as.character(Response))) %>%
  dplyr::filter(!is.na(Response))

df22_with_BL <- df22_with_BL %>% dplyr::filter(Response.Type != "info")

df22_with_BL$Screen <- ifelse(df22_with_BL$Trial.Number == 1 & (df22_with_BL$Display == "Mood " | df22_with_BL$Display == "Embarrassment"), "BL_1",
                      ifelse(df22_with_BL$Trial.Number == 2 & (df22_with_BL$Display == "Mood " | df22_with_BL$Display == "Embarrassment"), "BL_2", 
                             df22_with_BL$Screen))

df22_with_BL$m_hist <- ifelse(df22_with_BL$Spreadsheet..Histogram == "h1.png", 22,
                      ifelse(df22_with_BL$Spreadsheet..Histogram == "h2.png", 29,
                             ifelse(df22_with_BL$Spreadsheet..Histogram == "h3.png", 37,
                                    ifelse(df22_with_BL$Spreadsheet..Histogram == "h4.png", 46,
                                           ifelse(df22_with_BL$Spreadsheet..Histogram == "h5.png", 54,
                                                  ifelse(df22_with_BL$Spreadsheet..Histogram == "h6.png", 63,
                                                         ifelse(df22_with_BL$Spreadsheet..Histogram == "h7.png", 71,
                                                                ifelse(df22_with_BL$Spreadsheet..Histogram == "h8.png", 80, NA))))))))  


# get rid of the rows we don't need: practice runs, continue button presses etc. and only keep Trials, Anxiety and Mood that include all variables we are interested in:
df22_with_BL <- df22_with_BL %>%
  dplyr::filter(
    (Display == "Trials ") |
      (Display == "Anxiety ") |
      (Display == "Embarrassment") |
      (Display == "Mood ")
  )

# # setting Mood and Anxiety trial numbers to match the trials starting from 1 (since we removed the baseline ones above)
df22_with_BL$Trial.Number <- ifelse(df22_with_BL$Display == 'Mood ' | df22_with_BL$Display == 'Embarrassment', df22_with_BL$Trial.Number - 2, df22_with_BL$Trial.Number)
# df22_with_BL$Display <- ifelse(df22_with_BL$Display == 'Mood ' | df22_with_BL$Display == 'Anxiety ', "Trials", df22_with_BL$Display)

final_df22_with_BL <- df22_with_BL[c("Trial.Number", "Display", "Screen", "Response", "Random_ID")]

final_df22_with_BL <- final_df22_with_BL %>%
  left_join(df22_spin %>% dplyr::select(Random_ID, mini_SPIN_total), by = "Random_ID")

final_df22_with_BL <- final_df22_with_BL %>%
  left_join(CESD_data_clean %>% dplyr::select(Random_ID, CESD_score, Depression_Threshold, Depression_status), by = "Random_ID")

final_df22_with_BL$Social_Anxiety <- ifelse(final_df22_with_BL$mini_SPIN_total >= 6, "high", "low")


```



\newpage 
# Mood over time 

```{r echo=FALSE, warning=FALSE, message=FALSE}

df22_BL_ax <- subset(final_df22_with_BL, Display == "Anxiety ")
df22_BL_Emb <- subset(final_df22_with_BL, Display == "Embarrassment")
df22_BL_H <- subset(final_df22_with_BL,Display == "Mood ")

ggplot(df22_BL_H, aes(x = Trial.Number, y = Response, color = Display, group = Display)) +
  geom_line(color = "blue") +
  geom_vline(xintercept = 1, linetype = "dashed", color = "red") + # Adding a vertical line at Trial.Number == 1
  theme_minimal() +
  labs(title = "Mood across time",
       x = "Trial Number",
       y = "Mood",
       color = "") +
  facet_wrap(~ Random_ID, ncol = 6) +
  theme(strip.text = element_text(size = 6)) +
  scale_x_continuous(breaks = seq(-1, 48, by = 10), limits = c(-1, 48)) +
  scale_y_continuous(breaks = seq(0, 100, by = 22), limits = c(0, 100))+
  theme(axis.text.x = element_text(size = 5),axis.text.y = element_text(size = 5))

```
\newpage 
# Anxiety over time 

```{r echo=FALSE, warning=FALSE, message=FALSE}
ggplot(df22_BL_ax, aes(x = Trial.Number, y = Response, color = Display, group = Display)) +
  geom_line(color = "blue") +
  geom_vline(xintercept = 1, linetype = "dashed", color = "red") + # Adding a vertical line at Trial.Number == 1
  theme_minimal() +
  labs(title = "Anxiety across time",
       x = "Trial Number",
       y = "Anxiety",
       color = "") +
  facet_wrap(~ Random_ID, ncol = 6) + 
  theme(strip.text = element_text(size = 6)) +  
  scale_x_continuous(breaks = seq(-1, 48, by = 10), limits = c(-1, 48)) +
  scale_y_continuous(breaks = seq(0, 100, by = 22), limits = c(0, 100))+
  theme(axis.text.x = element_text(size = 5),axis.text.y = element_text(size = 5))

```

\newpage 
# Embarrassment over time 

```{r echo=FALSE, warning=FALSE, message=FALSE}
ggplot(df22_BL_Emb, aes(x = Trial.Number, y = Response, color = Display, group = Display)) +
  geom_line(color = "blue") +
  geom_vline(xintercept = 1, linetype = "dashed", color = "red") + # Adding a vertical line at Trial.Number == 1
  theme_minimal() +
  labs(title = "Embarrassment across time",
       x = "Trial Number",
       y = "Embarrassment",
       color = "") +
  facet_wrap(~ Random_ID, ncol = 6) + 
  theme(strip.text = element_text(size = 6)) +  
  scale_x_continuous(breaks = seq(-1, 48, by = 10), limits = c(-1, 48)) +
  scale_y_continuous(breaks = seq(0, 100, by = 22), limits = c(0, 100))+
  theme(axis.text.x = element_text(size = 5),axis.text.y = element_text(size = 5))

```

\newpage 
# Prediction before performance over time 

Red line presents until what points histograms were presented (4 first trials only).

```{r echo=FALSE, warning=FALSE, message=FALSE}
ggplot(final_df22, aes(x = Trial.Number, y = Response_pred)) +
  geom_line(color = "blue") +
  geom_vline(xintercept = 5, linetype = "dashed", color = "red") + 
  theme_minimal() +
  labs(title = "Prediction before performance across time",
       x = "Trial Number",
       y = "Pre performance prediction",
       color = "") +
  facet_wrap(~ Random_ID, ncol = 6) + 
  theme(strip.text = element_text(size = 6)) +  
  scale_x_continuous(breaks = seq(1, 48, by = 10), limits = c(1, 48)) +
  scale_y_continuous(breaks = seq(0, 100, by = 22), limits = c(0, 100))+
  theme(axis.text.x = element_text(size = 5),axis.text.y = element_text(size = 5))

```


\newpage 
# Stress levels and social anxiety

```{r echo=FALSE, warning=FALSE, message=FALSE}
onetrial_final_df22 <- subset(final_df22, final_df22$Trial.Number == 3)


ggplot(onetrial_final_df22, aes(x = Social_Anxiety, y = Response_stress_level , fill = Social_Anxiety)) +
  geom_boxplot(outlier.colour = "black") +
  stat_boxplot(geom = "errorbar",
               width = 0.15) + 
  geom_point(color = "black", position = position_jitter(width = 0.1), alpha = 0.7) +
  theme_minimal() +
  # labs(x = "Display", y = "Response") +
  # scale_y_continuous(breaks = seq(0, 100, by = 10), limits = c(0, 100)) +
  # ggtitle("Average anxiety ratings in pilots 1 and 2 in socially anxious people") +
  xlab("") + 
  ylab("stress levels (0-10)") +
  # facet_wrap(~pilot_nr, scales = "free") +
  # scale_fill_manual(values = c("black", "purple", "darkgreen", "blue"))+
  # ylim(c(50, 100)) + 
  scale_y_continuous(breaks = seq(0, 10, by = 1), limits = c(1, 10))+
  theme(
    panel.grid.major = element_blank(),  # Removes major grid lines
    panel.grid.minor = element_blank(),  # Removes minor grid lines
    panel.border = element_blank(),      # Removes the border line
    axis.line = element_blank(),          # Removes axis lines
    plot.background = element_rect(fill = "white", colour = NA)   # Ensure plot background is white
  )

```

\newpage
# LME models for Mood and SubjPE

The best model seems to be: Mood ~ SubjPE + mini_SPIN_total + (SubjPE | Random_ID)

```{r echo=FALSE, warning=FALSE, message=FALSE}
model1 <- lme4::lmer(Response_H ~ Response_SubjPE +  (Response_SubjPE | Random_ID), data = final_df22, control=lmerControl(optimizer="bobyqa"))
model2 <- lme4::lmer(Response_H ~ Response_SubjPE +  mini_SPIN_total + (1 | Random_ID), data = final_df22, control=lmerControl(optimizer="bobyqa"))
model3 <- lme4::lmer(Response_H ~ Response_SubjPE + mini_SPIN_total + (Response_SubjPE | Random_ID), data = final_df22, control=lmerControl(optimizer="bobyqa"))

AIC(model1)
AIC(model2)
AIC(model3)

coef_fixed <- fixef(model3)
intercept_Response_H <- coef_fixed[1]
slope_Response_H <- coef_fixed[2]
standard_beta_Response_SubjPE <- parameters:: standardise_parameters (model3)

# Hypothetical standard errors for intercept and slope
SE_intercept <- 0.15  # Placeholder value
SE_slope <- 0.43      # Placeholder value
CI_multiplier <- 1.96  # 95% CI multiplier for a normal distribution

# Creating a sequence of `SubjPE` values for prediction
Response_SubjPE_range <- seq(min(final_df22$Response_SubjPE), max(final_df22$Response_SubjPE), length.out = 100)

# Calculating predicted Response_H and its CI bounds across the SubjPE range
predicted_Response_H <- intercept_Response_H + slope_Response_H * Response_SubjPE_range
CI_lower <- predicted_Response_H - CI_multiplier * sqrt(SE_intercept^2 + (Response_SubjPE_range^2 * SE_slope^2))
CI_upper <- predicted_Response_H + CI_multiplier * sqrt(SE_intercept^2 + (Response_SubjPE_range^2 * SE_slope^2))

# Preparing a data frame for ggplot
CI_data <- data.frame(Response_SubjPE=Response_SubjPE_range, CI_lower=CI_lower, CI_upper=CI_upper)


ggplot(final_df22, aes(x=Response_SubjPE, y=Response_H)) +
  # Adding points from your dataset
  # geom_point() +
  # Adding a regression line
  geom_abline(intercept=intercept_Response_H, slope=slope_Response_H, color="darkgoldenrod1", linetype="dashed", size=1) +
  # Adding the confidence interval with geom_ribbon
  geom_ribbon(data=CI_data, aes(x=Response_SubjPE, ymin=CI_lower, ymax=CI_upper), fill="gray80", alpha=0.5, inherit.aes = FALSE) +
  # Further customization
  xlab("Social PE") + 
  ylab("Mood") +
  ggtitle("", subtitle=paste("Estimated slopes of the association in n = ", length(unique(final_df22$Random_ID)))) +
  theme(plot.title=element_text(size=12), plot.subtitle=element_text(size=10),
        legend.title=element_text(size=12), legend.text=element_text(size=12),
        axis.title=element_text(size=13),
        axis.text=element_text(size=12),
        panel.background=element_blank(), panel.grid.major=element_blank(), panel.grid.minor=element_blank(),
        panel.border=element_rect(colour="black", fill=NA)) +
  annotate("label", x=12, y=55, label=paste("beta =", round(standard_beta_Response_SubjPE$Std_Coefficient[2],2), ", 95%CI =", 
                                            round(standard_beta_Response_SubjPE$CI_low[2],2), "-", round(standard_beta_Response_SubjPE$CI_high[2],2))) +
  scale_y_continuous(breaks=seq(0, 100, by=20), limits=c(0, 100)) +
  scale_x_continuous(breaks=seq(-80, 80, by=40), limits=c(-80, 80))

```

\newpage
# LME models for Anxiety and SubjPE

The best model seems to be: Anxiety ~ SubjPE + mini_SPIN_total + (SubjPE | Random_ID)

```{r echo=FALSE, warning=FALSE, message=FALSE}
model1 <- lme4::lmer(Response_Ax ~ Response_SubjPE +  (Response_SubjPE | Random_ID), data = final_df22, control=lmerControl(optimizer="bobyqa"))
model2 <- lme4::lmer(Response_Ax ~ Response_SubjPE +  mini_SPIN_total + (1 | Random_ID), data = final_df22, control=lmerControl(optimizer="bobyqa"))
model3 <- lme4::lmer(Response_Ax ~ Response_SubjPE + mini_SPIN_total + (Response_SubjPE | Random_ID), data = final_df22, control=lmerControl(optimizer="bobyqa"))

AIC(model1)
AIC(model2)
AIC(model3)

coef_fixed <- fixef(model3)
intercept_Response_Ax <- coef_fixed[1]
slope_Response_Ax <- coef_fixed[2]
standard_beta_Response_SubjPE <- parameters:: standardise_parameters (model3)

# Hypothetical standard errors for intercept and slope
SE_intercept <- -0.03  # Placeholder value
SE_slope <- -0.27      # Placeholder value
CI_multiplier <- 1.96  # 95% CI multiplier for a normal distribution

# Creating a sequence of `SubjPE` values for prediction
Response_SubjPE_range <- seq(min(final_df22$Response_SubjPE), max(final_df22$Response_SubjPE), length.out = 100)

# Calculating predicted Response_Ax and its CI bounds across the SubjPE range
predicted_Response_Ax <- intercept_Response_Ax + slope_Response_Ax * Response_SubjPE_range
CI_lower <- predicted_Response_Ax - CI_multiplier * sqrt(SE_intercept^2 + (Response_SubjPE_range^2 * SE_slope^2))
CI_upper <- predicted_Response_Ax + CI_multiplier * sqrt(SE_intercept^2 + (Response_SubjPE_range^2 * SE_slope^2))

# Preparing a data frame for ggplot
CI_data <- data.frame(Response_SubjPE=Response_SubjPE_range, CI_lower=CI_lower, CI_upper=CI_upper)


ggplot(final_df22, aes(x=Response_SubjPE, y=Response_Ax)) +
  # Adding points from your dataset
  # geom_point() +
  # Adding a regression line
  geom_abline(intercept=intercept_Response_Ax, slope=slope_Response_Ax, color="darkgoldenrod1", linetype="dashed", size=1) +
  # Adding the confidence interval with geom_ribbon
  geom_ribbon(data=CI_data, aes(x=Response_SubjPE, ymin=CI_lower, ymax=CI_upper), fill="gray80", alpha=0.5, inherit.aes = FALSE) +
  # Further customization
  xlab("Social PE") + 
  ylab("Anxiety") +
  ggtitle("", subtitle=paste("Estimated slopes of the association in n = ", length(unique(final_df22$Random_ID)))) +
  theme(plot.title=element_text(size=12), plot.subtitle=element_text(size=10),
        legend.title=element_text(size=12), legend.text=element_text(size=12),
        axis.title=element_text(size=13),
        axis.text=element_text(size=12),
        panel.background=element_blank(), panel.grid.major=element_blank(), panel.grid.minor=element_blank(),
        panel.border=element_rect(colour="black", fill=NA)) +
  annotate("label", x=12, y=55, label=paste("beta =", round(standard_beta_Response_SubjPE$Std_Coefficient[2],2), ", 95%CI =", 
                                            round(standard_beta_Response_SubjPE$CI_low[2],2), "-", round(standard_beta_Response_SubjPE$CI_high[2],2))) +
  scale_y_continuous(breaks=seq(0, 100, by=20), limits=c(0, 100)) +
  scale_x_continuous(breaks=seq(-80, 80, by=40), limits=c(-80, 80))
```

\newpage
# LME models for Embarrassment and SubjPE

The best model seems to be: Embarrassment ~ SubjPE + mini_SPIN_total + (SubjPE | Random_ID)

```{r echo=FALSE, warning=FALSE, message=FALSE}
model1 <- lme4::lmer(Response_Emb ~ Response_SubjPE +  (Response_SubjPE | Random_ID), data = final_df22, control=lmerControl(optimizer="bobyqa"))
model2 <- lme4::lmer(Response_Emb ~ Response_SubjPE +  mini_SPIN_total + (1 | Random_ID), data = final_df22, control=lmerControl(optimizer="bobyqa"))
model3 <- lme4::lmer(Response_Emb ~ Response_SubjPE + mini_SPIN_total + (Response_SubjPE | Random_ID), data = final_df22, control=lmerControl(optimizer="bobyqa"))
# model4 <- lme4::lmer(Response_Emb ~ Response_pred + Response_fdbk + mini_SPIN_total + (Response_SubjPE | Random_ID), data = final_df22, control=lmerControl(optimizer="bobyqa"))

AIC(model1)
AIC(model2)
AIC(model3)
# AIC(model4)

coef_fixed <- fixef(model3)
intercept_Response_Ax <- coef_fixed[1]
slope_Response_Ax <- coef_fixed[2]
standard_beta_Response_SubjPE <- parameters:: standardise_parameters (model3)

# Hypothetical standard errors for intercept and slope
SE_intercept <- -0.03  # Placeholder value
SE_slope <- -0.27      # Placeholder value
CI_multiplier <- 1.96  # 95% CI multiplier for a normal distribution

# Creating a sequence of `SubjPE` values for prediction
Response_SubjPE_range <- seq(min(final_df22$Response_SubjPE), max(final_df22$Response_SubjPE), length.out = 100)

# Calculating predicted Response_Ax and its CI bounds across the SubjPE range
predicted_Response_Ax <- intercept_Response_Ax + slope_Response_Ax * Response_SubjPE_range
CI_lower <- predicted_Response_Ax - CI_multiplier * sqrt(SE_intercept^2 + (Response_SubjPE_range^2 * SE_slope^2))
CI_upper <- predicted_Response_Ax + CI_multiplier * sqrt(SE_intercept^2 + (Response_SubjPE_range^2 * SE_slope^2))

# Preparing a data frame for ggplot
CI_data <- data.frame(Response_SubjPE=Response_SubjPE_range, CI_lower=CI_lower, CI_upper=CI_upper)


ggplot(final_df22, aes(x=Response_SubjPE, y=Response_Emb)) +
  # Adding points from your dataset
  # geom_point() +
  # Adding a regression line
  geom_abline(intercept=intercept_Response_Ax, slope=slope_Response_Ax, color="darkgoldenrod1", linetype="dashed", size=1) +
  # Adding the confidence interval with geom_ribbon
  geom_ribbon(data=CI_data, aes(x=Response_SubjPE, ymin=CI_lower, ymax=CI_upper), fill="gray80", alpha=0.5, inherit.aes = FALSE) +
  # Further customization
  xlab("Social PE") + 
  ylab("Anxiety") +
  ggtitle("", subtitle=paste("Estimated slopes of the association in n = ", length(unique(final_df22$Random_ID)))) +
  theme(plot.title=element_text(size=12), plot.subtitle=element_text(size=10),
        legend.title=element_text(size=12), legend.text=element_text(size=12),
        axis.title=element_text(size=13),
        axis.text=element_text(size=12),
        panel.background=element_blank(), panel.grid.major=element_blank(), panel.grid.minor=element_blank(),
        panel.border=element_rect(colour="black", fill=NA)) +
  annotate("label", x=12, y=55, label=paste("beta =", round(standard_beta_Response_SubjPE$Std_Coefficient[2],2), ", 95%CI =", 
                                            round(standard_beta_Response_SubjPE$CI_low[2],2), "-", round(standard_beta_Response_SubjPE$CI_high[2],2))) +
  scale_y_continuous(breaks=seq(0, 100, by=20), limits=c(0, 100)) +
  scale_x_continuous(breaks=seq(-80, 80, by=40), limits=c(-80, 80))
```


\newpage 
# ICC for Mood with chocking
```{r echo=FALSE, warning=FALSE, message=FALSE}
test_icc_id <- lmer(Response_H ~  (1| Random_ID), data = 
                      final_df22, 
                    REML = FALSE, 
                    control = lmerControl(optimizer = "bobyqa")) 
icc_results_id <- performance::icc(test_icc_id)

icc_results_id
```

\newpage 
# ICC for Anxiety with chocking
```{r echo=FALSE, warning=FALSE, message=FALSE}
test_icc_id <- lmer(Response_Ax ~  (1| Random_ID), data = 
                      final_df22, 
                    REML = FALSE, 
                    control = lmerControl(optimizer = "bobyqa")) 
icc_results_id <- performance::icc(test_icc_id)

icc_results_id
```
