---
title: "Surprise study pilot 18"
author: "Elena Bagdades"
date: "2024-02-29"
output: 
    pdf_document:
    toc: true
    toc_depth: 2
    toc_float: true
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(root.dir = "aim_lab_1", echo = TRUE)
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
library(dplyr)
library(ggplot2)
library(tidyr)
library(lme4)
library(parameters)
library(broom.mixed)
library(purrr)
library(conflicted)
library(stringr)
library(readxl)
```


\newpage
# Study description

This study is the same as pilot 17, but now we have counter balanced the order of chocking and non-chocking blocks.

The Gorilla experiment is the following: https://app.gorilla.sc/admin/project/127963
The task is the following: https://app.gorilla.sc/admin/task/785720/editor


```{r echo=FALSE, warning=FALSE, message=FALSE}
df18_raw <- read.csv("/Users/marjan/Desktop/aim_lab_1/De_identified_data/pilot_18/SUP_PRF_p18_vid_bigPE_nar2_earlypred_chk_cbal_v4/SUP_PRF_p18_vid_bigPE_nar2_earlypred_chk_cbal_v4_task_main.csv")
df18_spin <- read.csv("/Users/marjan/Desktop/aim_lab_1/De_identified_data/pilot_18/SUP_PRF_p18_vid_bigPE_nar2_earlypred_chk_cbal_v4/SUP_PRF_p18_vid_bigPE_nar2_earlypred_chk_cbal_v4_mini_spin.csv")
df18_cesd <- read.csv("/Users/marjan/Desktop/aim_lab_1/De_identified_data/pilot_18/SUP_PRF_p18_vid_bigPE_nar2_earlypred_chk_cbal_v4/SUP_PRF_p18_vid_bigPE_nar2_earlypred_chk_cbal_v4_ces_d.csv")
```



```{r echo=FALSE, warning=FALSE, message=FALSE}
# extract CES-D scores
CESD_data_clean <- df18_cesd[, c(33,35,37,39,41,43,45,47,49,51,53,55,57,59,61,63,65,67,69,71,72)]
# Identify non-ID variable columns
non_id_cols <- setdiff(names(CESD_data_clean), "Random_ID")

# Convert non-ID variables to numeric
CESD_data_clean[, non_id_cols] <- lapply(CESD_data_clean[, non_id_cols], as.numeric)

#change numbers to match CES-D scoring system
excluded_columns <-  c("Random_ID", "Multiple.Choice.Grid.object.3.4...I.felt.I.was.just.as.good.as.other.people..Quantised",
                       "Multiple.Choice.Grid.object.3.8...I.felt.hopeful.about.the.future..Quantised",
                       "Multiple.Choice.Grid.object.3.12...I.was.happy..Quantised",
                       "Multiple.Choice.Grid.object.3.16...I.enjoyed.life..Quantised")


# numbers_plus_one <- c(33, 35, 37, 39, 41, 43, 45, 47, 49, 51, 53, 55, 57, 59, 61, 63, 65, 67, 69, 71, 72)
# 
# # Extract the column names using the indices
# column_names <- colnames(df18_cesd)[numbers_plus_one]
# 
# # Print the column names
# print(column_names)

CESD_data_clean<- CESD_data_clean %>%
  mutate(across(-excluded_columns , ~ case_when(
    . == 1 ~ 0,
    . == 2 ~ 1,
    . == 3 ~ 2,
    . == 4 ~ 3,
    TRUE ~ .
  )))


other_columns <- c("Multiple.Choice.Grid.object.3.4...I.felt.I.was.just.as.good.as.other.people..Quantised",
                   "Multiple.Choice.Grid.object.3.8...I.felt.hopeful.about.the.future..Quantised",
                   "Multiple.Choice.Grid.object.3.12...I.was.happy..Quantised",
                   "Multiple.Choice.Grid.object.3.16...I.enjoyed.life..Quantised")
CESD_data_clean<- CESD_data_clean %>%
  mutate(across(other_columns , ~ case_when(
    . == 1 ~ 3,
    . == 2 ~ 2,
    . == 3 ~ 1,
    . == 4 ~ 0,
    TRUE ~ .
  )))

#scoring----
CESD_scores <-  numeric(length(CESD_data_clean$Random_ID))
CESD_scores <- 0
Questions <- c(1:20)

for (i in 1:nrow(CESD_data_clean)) {
  CESD_score <- sum(CESD_data_clean[i, Questions])
  CESD_scores[i] <- CESD_score
}

CESD_data_clean$CESD_score <-  CESD_scores

CESD_data_clean$Depression_Threshold<- 0
CESD_data_clean$Depression_status <- "Not_Depressed"

#Assign "1" if they meet Depression threshold 
for (i in 1:nrow(CESD_data_clean)) {
  if (CESD_data_clean$CESD_score[i] >= 16) {
    CESD_data_clean$Depression_Threshold[i] <- 1
    CESD_data_clean$Depression_status[i] <- "Depressed"
  }
}
```


```{r echo=FALSE, warning=FALSE, message=FALSE}

df18_spin <- df18_spin %>%
  rename(
   "Q1" =  "Rating.Scale.object.2.Fear.of.embarrassment.causes.me.to.avoid.doing.things.or.speaking.to.people.",
   "Q2" =  "Rating.Scale.object.2.I.avoid.activities.in.which.I.am.the.center.of.attention.",
   "Q3" = "Rating.Scale.object.2.Being.embarrassed.or.looking.stupid.are.among.my.worst.fears."
  )

df18_spin <- df18_spin %>%
  rowwise() %>%
  mutate(mini_SPIN_total = sum(c(Q1, Q2, Q3), na.rm = TRUE)) %>%
  ungroup()

```




```{r echo=FALSE, warning=FALSE, message=FALSE}
df18_raw <- df18_raw %>%
  mutate(Trial.Number = ifelse(counterbalance.huxg == "Chocking_second" & Display == "Trials-Chocking ",
                                Trial.Number + 24,
                                Trial.Number))

df18_raw <- df18_raw %>%
  mutate(Trial.Number = ifelse(counterbalance.huxg == "Chocking_first" & Display == "Trials ",
                                Trial.Number + 24,
                                Trial.Number))

names(df18_raw)[names(df18_raw) == 'counterbalance.huxg'] <- 'counterbalance_order'

# since in this version for the checking block prediction and certainty rating screens are not named accordingly, we need to rename them to match the Trials block:
df18_raw$Screen[df18_raw$Screen == "Screen 2"] <- "Prediction "
df18_raw$Screen[df18_raw$Screen == "Screen 3"] <- "Certainty rating "

# create a new df18 that only keeps the columns we need
df18 <- df18_raw[, c("Trial.Number", "Display", "Screen", "Response.Type", "Response", 
                     "Reaction.Time", "Spreadsheet..Histogram", "Spreadsheet..Feedback", "Random_ID","counterbalance_order" )]

df18 <- df18 %>%
  mutate(Response = as.numeric(as.character(Response))) %>%
  dplyr::filter(!is.na(Response))

df18$Screen <- ifelse(df18$Trial.Number == 1 & (df18$Display == "Mood " | df18$Display == "Anxiety "), "BL_1",
                      ifelse(df18$Trial.Number == 2 & (df18$Display == "Mood " | df18$Display == "Anxiety "), "BL_2", 
                             df18$Screen))

df18$m_hist <- ifelse(df18$Spreadsheet..Histogram == "h1.png", 20,
                      ifelse(df18$Spreadsheet..Histogram == "h2.png", 29,
                             ifelse(df18$Spreadsheet..Histogram == "h3.png", 37,
                                    ifelse(df18$Spreadsheet..Histogram == "h4.png", 46,
                                           ifelse(df18$Spreadsheet..Histogram == "h5.png", 54,
                                                  ifelse(df18$Spreadsheet..Histogram == "h6.png", 63,
                                                         ifelse(df18$Spreadsheet..Histogram == "h7.png", 71,
                                                                ifelse(df18$Spreadsheet..Histogram == "h8.png", 80, NA))))))))  


# get rid of the rows we don't need: practice runs, continue button presses etc. and only keep Trials, Anxiety and Mood that include all variables we are interested in:
df18 <- df18 %>%
  dplyr::filter(
    (Display == "Trials ") |
      (Display == "Exit") |
      (Display == "Anxiety " & !Trial.Number %in% c(1, 2)) |
      (Display == "Mood " & !Trial.Number %in% c(1, 2))|
       (Response.Type == "tooEarly") |
       (Display == "Trials-Chocking ") 
  )


# # setting Mood and Anxiety trial numbers to match the trials starting from 1 (since we removed the baseline ones above)
df18$Trial.Number <- ifelse(df18$Display == 'Mood ' | df18$Display == 'Anxiety ', df18$Trial.Number - 2, df18$Trial.Number)
df18$Display <- ifelse(df18$Display == 'Mood ' | df18$Display == 'Anxiety ', "Trials ", df18$Display)

df18 <- df18 %>%
  mutate(Display = ifelse(counterbalance_order == "Chocking_second" & Trial.Number > 24,
                                "Trials-Chocking ",
                                Display))
df18 <- df18 %>%
  mutate(Display = ifelse(counterbalance_order == "Chocking_first" & Trial.Number < 25,
                                "Trials-Chocking ",
                                Display))



# renaming the feedback column to fdbk
names(df18)[names(df18) == 'Spreadsheet..Feedback'] <- 'fdbk'

# Now let's create columns for PE (fdbk-hist) and Subj_PE (fdbk_Prediction)

df18$SubjPE <- ifelse(df18$Screen == "Prediction ", df18$fdbk - df18$Response, NA)
df18$PE <- ifelse(df18$Screen == "Prediction ", df18$fdbk - df18$m_hist, NA)
# to keep just one repetition of feedback and mean histogram per trial per subject 
# and replace the rest with NA so that when we want to convert to long format we won't have duplicates
df18$fdbk <- ifelse(df18$Screen == "Prediction ", df18$fdbk, NA)
df18$m_hist <- ifelse(df18$Screen == "Prediction ", df18$m_hist, NA)
df18$stress_level <- ifelse(df18$Screen == "Screen 12", df18$Response, NA)


long_df18 <- df18 %>%
  select(Random_ID, Trial.Number, fdbk, m_hist, PE, SubjPE, stress_level, counterbalance_order) %>%
  pivot_longer(cols = c(fdbk, m_hist, PE, SubjPE, stress_level),
               names_to = "Screen",
               values_to = "Response")


# This will keep only the rows where 'Response' is not NA
long_df18 <- long_df18[!is.na(long_df18$Response), ]

# Selecting relevant columns from the original df18
df18 <- df18 %>%
  select(-c(fdbk, m_hist, PE, SubjPE, stress_level))

# Binding the rows together
df18 <- bind_rows(df18, long_df18)

df18$Response <- as.numeric(df18$Response)

# looking at the relationship between PE and SubjPE
df18_PE <- subset(df18, Screen == "PE")
names(df18_PE)[names(df18_PE) == "Screen"] <- "Screen_PE"
names(df18_PE)[names(df18_PE) == "Response"] <- "Response_PE"

df18_SubjPE <- subset(df18, Screen == "SubjPE")
names(df18_SubjPE)[names(df18_SubjPE) == "Screen"] <- "Screen_SubjPE"
names(df18_SubjPE)[names(df18_SubjPE) == "Response"] <- "Response_SubjPE"

df18_fdbk <- subset(df18, Screen == "fdbk")
names(df18_fdbk)[names(df18_fdbk) == "Screen"] <- "Screen_fdbk"
names(df18_fdbk)[names(df18_fdbk) == "Response"] <- "Response_fdbk"

df18_hist <- subset(df18, Screen == "m_hist")
names(df18_hist)[names(df18_hist) == "Screen"] <- "Screen_m_hist"
names(df18_hist)[names(df18_hist) == "Response"] <- "Response_m_hist"

df18_stress_level <- subset(df18, Screen == "Screen 12")
names(df18_stress_level)[names(df18_stress_level) == "Screen"] <- "Screen_stress_level"
names(df18_stress_level)[names(df18_stress_level) == "Response"] <- "Response_stress_level"

df18_predic <- subset(df18, Screen == "Prediction ")
names(df18_predic)[names(df18_predic) == "Screen"] <- "Screen_pred"
names(df18_predic)[names(df18_predic) == "Response"] <- "Response_pred"

df18_cert <- subset(df18, Screen == "Certainty rating ")
names(df18_cert)[names(df18_cert) == "Screen"] <- "Screen_certainty"
names(df18_cert)[names(df18_cert) == "Response"] <- "Response_certainty"

list_of_dfs_18 <- list(df18_PE, df18_fdbk, df18_hist, df18_predic, df18_cert, df18_SubjPE)

# Using reduce with inner_join
merged_df18 <- reduce(list_of_dfs_18, inner_join, by = c("Random_ID", "Trial.Number"))



df18_Anxious <- subset(df18, Screen == "Anxious")
names(df18_Anxious)[names(df18_Anxious) == "Screen"] <- "Screen_Ax"
names(df18_Anxious)[names(df18_Anxious) == "Response"] <- "Response_Ax"

df18_Happy <- subset(df18, Screen == "Happy")
# df18_fdbk <- subset(df18, Screen == "Prediction")
names(df18_Happy)[names(df18_Happy) == "Screen"] <- "Screen_H"
names(df18_Happy)[names(df18_Happy) == "Response"] <- "Response_H"

final_df18 <- merged_df18 %>%
  inner_join(df18_Anxious, by = c("Random_ID", "Trial.Number")) %>%
  inner_join(df18_Happy, by = c("Random_ID", "Trial.Number"))


# subset only the columns we are interested in
final_df18 <- final_df18[c("Trial.Number", "Random_ID", "Response_H", "Response_Ax", "Response_fdbk", "Response_SubjPE", "Response_PE", "Response_certainty", "Response_m_hist", "Response_pred", "counterbalance_order.x", "Display.y.y")]

final_df18 <- final_df18 %>%
  left_join(df18_spin %>% select(Random_ID, mini_SPIN_total), by = "Random_ID")

final_df18 <- final_df18 %>%
  left_join(df18_stress_level %>% select(Random_ID, Response_stress_level), by = "Random_ID")

final_df18 <- final_df18 %>%
  left_join(CESD_data_clean %>% select(Random_ID, CESD_score, Depression_Threshold, Depression_status), by = "Random_ID")

final_df18$Social_Anxiety <- ifelse(final_df18$mini_SPIN_total >= 6, "high", "low")


names(final_df18)[names(final_df18) == 'Display.y.y'] <- 'chocking_order'


write.csv(final_df18, "pilot_18_variables.csv", row.names = FALSE)

# print("It seems everyone has done all the 48 trials, Elena managed to fix the issue some people were experiencing, possibly not seeing the next button. There is only 1 participant who did 46 trials due to an emergency from their side.") 
final_df18 %>%
  group_by(Random_ID) %>%
  summarise(Trial.Number = n())

# write.csv(final_df18, "final_df18_with_stresslevels.csv", row.names = FALSE)
```


\newpage 
# Relationship between Anxiety and SubjPE


```{r echo=FALSE, warning=FALSE, message=FALSE}
df18_choking <- subset(final_df18, chocking_order == "Trials-Chocking ")
df18_nonchoking <- subset(final_df18, chocking_order == "Trials ") 

correlations_ch <- df18_choking %>%
  group_by(Random_ID) %>%
  summarise(correlation = cor(Response_Ax, Response_SubjPE, use = "complete.obs")) %>%
  mutate(label = paste("R = ", round(correlation, digits = 2))) 

# calculate the average correlation across all individuals and print it 
average_correlation <- mean(correlations_ch$correlation, na.rm = TRUE)
message_to_print_ch <- paste("average correlation between anxiety and SubjPE for the chocking block:", average_correlation)

print(message_to_print_ch)


correlations_noch <- df18_nonchoking %>%
  group_by(Random_ID) %>%
  summarise(correlation = cor(Response_Ax, Response_SubjPE, use = "complete.obs")) %>%
  mutate(label = paste("R = ", round(correlation, digits = 2))) 

# calculate the average correlation across all individuals and print it 
average_correlation <- mean(correlations_noch$correlation, na.rm = TRUE)
message_to_print_nocho <- paste("average correlation between anxiety and SubjPE for the non-chocking block:", average_correlation)

print(message_to_print_nocho)


# ggplot(final_df18, aes(x = Response_SubjPE, y = Response_Ax, color = chocking_order, group= chocking_order)) +
#   geom_point(aes(color=chocking_order, alpha = 0.3)) +
#   geom_smooth(method = "lm", color="blue", aes(group=Random_ID)) + 
#   # labs(color="Legend") +
#   theme_minimal() +
#   xlab("SubjPE: feedback - prediction") + 
#   ylab("Anxiety") +
#     facet_wrap(~ Random_ID, scales = "free") +
#     geom_text(data=correlations_Ax, aes(x=Inf, y=Inf, label=label, group=Random_ID), hjust=1.1, vjust=1.1, size=2.7, fontface = "bold", inherit.aes=FALSE) +
#     theme(strip.text = element_text(size = 6),
#         axis.text.x = element_text(size = 5.5),  
#         axis.text.y = element_text(size = 5.5),  
#         strip.text.x = element_text(face = "bold"),  
#         strip.text.y = element_text(face = "bold"),  
#         panel.grid.major = element_blank(),
#         panel.grid.minor = element_blank(),
#         panel.background = element_blank()) +
# ylim(c(0, 100)) +
# scale_y_continuous(breaks = seq(0, 100, by = 25), limits = c(0, 100))+
# xlim(c(-100, 100)) +
# scale_x_continuous(breaks = seq(-80, 80, by = 50), limits = c(-80,80))
```

\newpage 
# Relationship between Mood and SubjPE


```{r echo=FALSE, warning=FALSE, message=FALSE}

correlations_ch <- df18_choking %>%
  group_by(Random_ID) %>%
  summarise(correlation = cor(Response_H, Response_SubjPE, use = "complete.obs")) %>%
  mutate(label = paste("R = ", round(correlation, digits = 2))) 

# calculate the average correlation across all individuals and print it 
average_correlation <- mean(correlations_ch$correlation, na.rm = TRUE)
message_to_print_ch <- paste("average correlation between mood and SubjPE for the chocking block:", average_correlation)

print(message_to_print_ch)


correlations_noch <- df18_nonchoking %>%
  group_by(Random_ID) %>%
  summarise(correlation = cor(Response_H, Response_SubjPE, use = "complete.obs")) %>%
  mutate(label = paste("R = ", round(correlation, digits = 2))) 

# calculate the average correlation across all individuals and print it 
average_correlation <- mean(correlations_noch$correlation, na.rm = TRUE)
message_to_print_nocho <- paste("average correlation between mood and SubjPE for the non-chocking block:", average_correlation)

print(message_to_print_nocho)
```


\newpage 
# Anxiety over time Chocking first

```{r echo=FALSE, warning=FALSE, message=FALSE}
# subset anxiety and choking_1st
# same for mood
# same for chocking second etc
df18_ch1st <- subset(final_df18, counterbalance_order.x == "Chocking_first")
df18_ch2nd <- subset(final_df18, counterbalance_order.x == "Chocking_second")

ggplot(df18_ch1st, aes(x = Trial.Number, y = Response_Ax, color = counterbalance_order.x, group = counterbalance_order.x)) +
  geom_line(color = "blue") +
  geom_vline(xintercept = 24, linetype = "dashed", color = "red") + # Adding a vertical line at Trial.Number == 1
  theme_minimal() +
  labs(title = "Anxiety across time (Chocking first)",
       x = "Trial Number",
       y = "Anxiety",
       color = "") +
  facet_wrap(~ Random_ID, ncol = 6) + 
  theme(strip.text = element_text(size = 6)) 

```

\newpage 
# Anxiety over time Chocking second

```{r echo=FALSE, warning=FALSE, message=FALSE}
ggplot(df18_ch2nd, aes(x = Trial.Number, y = Response_Ax, color = counterbalance_order.x, group = counterbalance_order.x)) +
  geom_line(color = "blue") +
  geom_vline(xintercept = 24, linetype = "dashed", color = "red") + # Adding a vertical line at Trial.Number == 1
  theme_minimal() +
  labs(title = "Anxiety across time (Chocking second)",
       x = "Trial Number",
       y = "Anxiety",
       color = "") +
  facet_wrap(~ Random_ID, ncol = 6) + 
  theme(strip.text = element_text(size = 6)) 

```

\newpage 
# Mood over time Chocking first

```{r echo=FALSE, warning=FALSE, message=FALSE}
ggplot(df18_ch1st, aes(x = Trial.Number, y = Response_H, color = counterbalance_order.x, group = counterbalance_order.x)) +
  geom_line(color = "blue") +
  geom_vline(xintercept = 24, linetype = "dashed", color = "red") + # Adding a vertical line at Trial.Number == 1
  theme_minimal() +
  labs(title = "Mood across time (Chocking first)",
       x = "Trial Number",
       y = "Mood",
       color = "") +
  facet_wrap(~ Random_ID, ncol = 6) + 
  theme(strip.text = element_text(size = 6)) 

```


\newpage 
# Mood over time Chocking second

```{r echo=FALSE, warning=FALSE, message=FALSE}
ggplot(df18_ch2nd, aes(x = Trial.Number, y = Response_H, color = counterbalance_order.x, group = counterbalance_order.x)) +
  geom_line(color = "blue") +
  geom_vline(xintercept = 24, linetype = "dashed", color = "red") + # Adding a vertical line at Trial.Number == 1
  theme_minimal() +
  labs(title = "Mood across time (Chocking second)",
       x = "Trial Number",
       y = "Mood",
       color = "") +
  facet_wrap(~ Random_ID, ncol = 6) + 
  theme(strip.text = element_text(size = 6)) +  
  scale_x_continuous(breaks = seq(-1, 48, by = 10), limits = c(-1, 48)) +
  scale_y_continuous(breaks = seq(0, 100, by = 20), limits = c(0, 100))+
  theme(axis.text.x = element_text(size = 5),axis.text.y = element_text(size = 5))

```


\newpage 
# ICC for Mood with chocking
```{r echo=FALSE, warning=FALSE, message=FALSE}
test_icc_id <- lmer(Response_H ~  (1| Random_ID), data = 
                      df18_choking, 
                    REML = FALSE, 
                    control = lmerControl(optimizer = "bobyqa")) 
icc_results_id <- performance::icc(test_icc_id)

icc_results_id
```

\newpage 
# ICC for Anxiety with chocking
```{r echo=FALSE, warning=FALSE, message=FALSE}
test_icc_id <- lmer(Response_Ax ~  (1| Random_ID), data = 
                      df18_choking, 
                    REML = FALSE, 
                    control = lmerControl(optimizer = "bobyqa")) 
icc_results_id <- performance::icc(test_icc_id)

icc_results_id
```


