---
title: "Surprise study pilot 11"
author: "Marjan Biria"
date: "2023-12-05"
output: 
    pdf_document:
    toc: true
    toc_depth: 2
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(root.dir = "aim_lab_1", echo = TRUE)
```


```{r echo=FALSE, warning=FALSE, message=FALSE}
library(dplyr)
library(ggplot2)
library(tidyr)
library(lme4)
library(parameters)
library(broom.mixed)
```

\newpage
# Study description
In this pilot we screened people for high social anxiety. The task itself, is the same as pilot 10 (re-introducing the video). During the screening, we selected people scoring 6 or higher for mini in pilot 11, but when we collected this information again during the testing session, some people scored lower than 6 (5 or 6 people out of 28). We will also add 14 people from pilot 10 who scored high on mini-spin reaching a total sample of 42. This is the task version used for this pilot: https://app.gorilla.sc/admin/task/698788/editor?version=6  

**QUESTION**: which mini-spin score shall we use in the analysis for people who scored lower than 6 the second time?


```{r echo=FALSE, warning=FALSE, message=FALSE}
all_pilots_with_mini_spin <- read.csv("/Users/marjan/Desktop/aim_lab_1/all_pilots_with_mini_spin.csv")


df11_data <- subset(all_pilots_with_mini_spin, pilot_nr == 11)
df10_data <- subset(all_pilots_with_mini_spin, pilot_nr == 10)

# Let's merge pilots that used the same task version (video re-introduced and colour code the anxiety levels)
df_all_vid <- rbind(df11_data, df10_data)

# let's select pilot 11 only, and merge them with socially anxious people from pilot 10 which was exactly the same
# df10_anxious <- subset(df10_data, mini_SPIN_total >= 6)
# pilot_11 <- rbind(df11_data, df10_anxious)
```


\newpage 
# Relationship Mood and SubjPE

When looking at pilot 11 alone (people with high social anxiety) the correlation is 0.32 (n = 28), when adding the 14 people with high social anxiety from pilot 10, the correlation becomes 0.28 (n = 42). When adding the remaining people from pilot 10 with low social anxiety, the group correlation becomes 0.24 (n = 67). 
```{r echo=FALSE, warning=FALSE, message=FALSE}
df_all_vid   |> summarise(length(unique(Random_ID)), .by = pilot_nr)

correlations <- df_all_vid %>%
  group_by(Random_ID) %>%
  summarise(correlation = cor(Mood, SubjPE, use = "complete.obs")) %>%
  mutate(label = paste("R = ", round(correlation, digits = 2)))  # create a label for the plot

# calculate the average correlation across all individuals and print it 
average_correlation <- mean(correlations$correlation, na.rm = TRUE)
message_to_print_Mood <- paste("average correlation between Mood and SubjPE:", average_correlation)
print(message_to_print_Mood)


ggplot(df_all_vid, aes(x = SubjPE, y = Mood, color = Social_Anxiety, group= Social_Anxiety)) +
  geom_point(aes(color=Social_Anxiety, alpha = 0.3)) +
  geom_smooth(method = "lm", color="blue", aes(group=Random_ID)) + 
  # labs(color="Legend") +
  theme_minimal() +
  xlab("SubjPE: feedback - prediction") + 
  ylab("Happiness/Mood") +
    facet_wrap(~ Random_ID, scales = "free") +
    theme(strip.text = element_text(size = 5))+
    geom_text(data=correlations, aes(x=Inf, y=Inf, label=label, group=Random_ID), hjust=1.1, vjust=1.1, size=2.7, fontface = "bold", inherit.aes=FALSE) +
    theme(
    strip.text.x = element_text(face = "bold"),  # For horizontal facet titles
    strip.text.y = element_text(face = "bold"),  # For vertical facet titles
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.background = element_blank())
```

\newpage 
# Relationship Anxiety and SubjPE

```{r echo=FALSE, warning=FALSE, message=FALSE}

correlations <- df_all_vid %>%
  group_by(Random_ID) %>%
  summarise(correlation = cor(Anxiety, SubjPE, use = "complete.obs")) %>%
  mutate(label = paste("R = ", round(correlation, digits = 2)))  # create a label for the plot

# calculate the average correlation across all individuals and print it 
average_correlation <- mean(correlations$correlation, na.rm = TRUE)
message_to_print_Ax <- paste("average correlation between Mood and SubjPE:", average_correlation)

print(message_to_print_Ax)

ggplot(df_all_vid, aes(x = SubjPE, y = Anxiety, color = Social_Anxiety, group= Social_Anxiety)) +
  geom_point(aes(color=Social_Anxiety, alpha = 0.3)) +
  geom_smooth(method = "lm", color="blue", aes(group=Random_ID)) + 
  # labs(color="Legend") +
  theme_minimal() +
  xlab("SubjPE: feedback - prediction") + 
  ylab("Anxiety") +
    facet_wrap(~ Random_ID, scales = "free") +
    theme(strip.text = element_text(size = 5))+
    geom_text(data=correlations, aes(x=Inf, y=Inf, label=label, group=Random_ID), hjust=1.1, vjust=1.1, size=2.7, fontface = "bold", inherit.aes=FALSE) +
    theme(
    strip.text.x = element_text(face = "bold"),  # For horizontal facet titles
    strip.text.y = element_text(face = "bold"),  # For vertical facet titles
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.background = element_blank())
```


```{r echo=FALSE, warning=FALSE, message=FALSE}
# list_of_df11s <- split(pilot_11, pilot_11$Random_ID)
# random_ids <- unique(pilot_11$Random_ID)
# 
# # making the data long format
# long_df11 <- pilot_11 %>%
#   dplyr::select(Random_ID, Trial.Number, fdbk, m_hist, PE, SubjPE, Mood, Anxiety, Certainty_Rating, Prediction) %>%
#   pivot_longer(cols = c(fdbk, m_hist, PE, SubjPE,Mood, Anxiety, Certainty_Rating, Prediction),
#                names_to = "Screen",
#                values_to = "Response")
# 
# 
# # This will keep only the rows where 'Response' is not NA
# long_df11 <- long_df11[!is.na(long_df11$Response), ]

  
# Selecting relevant columns from the original df10
# df10 <- df10 %>%
#   dplyr::select(-c(fdbk, m_hist, PE, SubjPE))
# 
# # # Binding the rows together
# df10 <- bind_rows(df10, long_df10)
# df10_longformat <- bind_rows(df10, long_df10)


# make individual plots
# plot_function <- function(long_df11, title) {
#   p <- ggplot(long_df11, aes(x = Trial.Number, y = Response, color = Screen, group = Screen)) +
#     geom_line() +
#     geom_smooth(method = "lm", se = TRUE, alpha = 0.7) + 
#     theme_minimal() +
#     labs(title = title,  # Set the title to the Random_ID
#          x = "Trial Number",
#          y = "Mood Ratings/Expectations/ PE",
#          color = "") +
#     facet_wrap(~ Screen, ncol = 2) +
#     geom_hline(yintercept = 0)
#   
#   return(p)
# }
# 
# # Use Map or mapply to apply the plot_function to each data frame and title in the list
# list_of_plots <- Map(plot_function, list_of_df11s, random_ids)
# 
# for (i in seq_along(list_of_plots)) {
#   print(list_of_plots[[i]])
# }
```

\newpage 
# LME models for Mood and SubjPE
This is the best model: Mood ~ SubjPE * mini_SPIN_total + (SubjPE | Random_ID)

```{r echo=FALSE, warning=FALSE, message=FALSE}
model1 <- lme4::lmer(Mood ~ SubjPE + (1 | Random_ID), data = df_all_vid, control=lmerControl(optimizer="bobyqa"))
model2 <- lme4::lmer(Mood ~ SubjPE + (SubjPE | Random_ID), data = df_all_vid, control=lmerControl(optimizer="bobyqa"))

# model2_p11 <- lme4::lmer(Mood ~ PE + (PE | Random_ID), data = df11_data, control=lmerControl(optimizer="bobyqa"))
# summary(model2_p11)

anova(model1, model2)
summary(model1)
summary(model2)
AIC(model1)
AIC(model2)


model3 <- lme4::lmer(Mood ~ SubjPE * mini_SPIN_total + (SubjPE | Random_ID), data = df_all_vid, control=lmerControl(optimizer="bobyqa"))

anova(model2, model3)

# summary(model3)
AIC(model3)

coef_fixed <- fixef(model3)
intercept_Mood <- coef_fixed[1]
slope_Mood <- coef_fixed[2]

model3 %>% broom.mixed::tidy("fixed") 
```

\newpage 
# Individual plots with LME for Mood

```{r echo=FALSE, warning=FALSE, message=FALSE}
# ggplot(df_all_vid, aes(x=SubjPE, y=Mood)) +
#   geom_smooth(method = "lm", color = "#0000FF44", size = 0.4, se = FALSE, aes(group=Random_ID)) +
#   geom_abline(intercept = intercept_Mood, slope = slope_Mood, color="red", linetype="dashed") +
#   xlab("SubjPE: feedback - prediction") + 
#   ylab("Mood") +
#   theme_minimal() +
#   theme(axis.text.x = element_text(size = 5), axis.text.y = element_text(size = 5))

ggplot(df_all_vid, aes(x=SubjPE, y=Mood)) +
  geom_smooth(method = "lm", size = 0.5, se = FALSE, aes(group=Random_ID, color=Social_Anxiety)) +
  scale_color_manual(values = c("low" = "lightblue", "high" = "pink")) +
  geom_abline(intercept = intercept_Mood, slope = slope_Mood, color="purple", linetype="dashed", size=1) +
  xlab("Subjective Prediction Error: feedback - prediction") + 
  ylab("Mood") +
  # theme_minimal() +
  # theme(axis.text.x = element_text(size = 9), axis.text.y = element_text(size = 9)) +
  # annotate("text", x = Inf, y = Inf, label = paste("positive slope without social anxiety =", 100*round(perc_pos_slop[1,2],2), "%"), hjust = 1.1, vjust = 90, color = "black", size = 3.7) +
  # annotate("text", x = Inf, y = Inf, label = paste("positive slope with social anxiety =", 100*round(perc_pos_slop[2,2],2), "%"), hjust = 1.1, vjust = 92, color = "black", size = 3.7)+
   # annotate("text", x = Inf, y = Inf, label = paste("positive slope with social anxiety =", 100*round(perc_pos_slop[2,2],2), "%"), hjust = 1.1, vjust = 92, color = "black", size = 3.7)+
  ggtitle("Relationship between Mood and Surprises",
          subtitle = paste("estimated slopes of the association in n = ", 
                           length(unique(df_all_vid$Random_ID))))+
  theme(plot.title = element_text(size=14), plot.subtitle = element_text(size = 10))+
  theme(legend.title = element_text(size = 9), legend.text = element_text(size = 8))+
  theme(axis.title = element_text(size = 10))
```



\newpage 
# LME models for Anxiety and SubjPE
This is the best model: Anxiety ~ SubjPE * mini_SPIN_total + (SubjPE | Random_ID)

```{r echo=FALSE, warning=FALSE, message=FALSE}
model1 <- lme4::lmer(Anxiety ~ SubjPE + (1 | Random_ID), data = df_all_vid, control=lmerControl(optimizer="bobyqa"))
model2 <- lme4::lmer(Anxiety ~ SubjPE + (SubjPE | Random_ID), data = df_all_vid, control=lmerControl(optimizer="bobyqa"))
anova(model1, model2)
# summary(model1)
# summary(model2)
# AIC(model1)
# AIC(model2)


model3 <- lme4::lmer(Anxiety ~ SubjPE * mini_SPIN_total + (SubjPE | Random_ID), data = df_all_vid, control=lmerControl(optimizer="bobyqa"))

anova(model2, model3)

summary(model3)

coef_fixed <- fixef(model3)
intercept_Ax <- coef_fixed[1]
slope_Ax <- coef_fixed[2]
model3 %>% broom.mixed::tidy("fixed") 
```

\newpage 
# Individual plots with LME for Anxiety

```{r echo=FALSE, warning=FALSE, message=FALSE}
# ggplot(df_all_vid, aes(x=SubjPE, y=Anxiety)) +
#   geom_smooth(method = "lm", color = "#0000FF44", size = 0.4, se = FALSE, aes(group=Random_ID)) +
#   geom_abline(intercept = intercept_Ax, slope = slope_Ax, color="red", linetype="dashed") +
#   xlab("SubjPE: feedback - prediction") + 
#   ylab("Anxiety") +
#   theme_minimal() +
#   theme(axis.text.x = element_text(size = 5), axis.text.y = element_text(size = 5))



ggplot(df_all_vid, aes(x=SubjPE, y=Anxiety)) +
  geom_smooth(method = "lm", size = 0.5, se = FALSE, aes(group=Random_ID, color=Social_Anxiety)) +
  scale_color_manual(values = c("low" = "lightblue", "high" = "pink")) +
  geom_abline(intercept = intercept_Ax, slope = slope_Ax, color="purple", linetype="dashed", size=1) +
  xlab("Subjective Prediction Error: feedback - prediction") + 
  ylab("Mood") +
  # theme_minimal() +
  # theme(axis.text.x = element_text(size = 9), axis.text.y = element_text(size = 9)) +
  # annotate("text", x = Inf, y = Inf, label = paste("positive slope without social anxiety =", 100*round(perc_pos_slop[1,2],2), "%"), hjust = 1.1, vjust = 90, color = "black", size = 3.7) +
  # annotate("text", x = Inf, y = Inf, label = paste("positive slope with social anxiety =", 100*round(perc_pos_slop[2,2],2), "%"), hjust = 1.1, vjust = 92, color = "black", size = 3.7)+
  ggtitle("Relationship between Anxiety and Surprises",
          subtitle = paste("estimated slopes of the association in n = ", 
                           length(unique(df_all_vid$Random_ID))))+
  theme(plot.title = element_text(size=14), plot.subtitle = element_text(size = 10))+
  theme(legend.title = element_text(size = 9), legend.text = element_text(size = 8))+
  theme(axis.title = element_text(size = 10)) 
  # + annotate("label", x = 0, y = 55, label = paste("beta = ", round(standard_beta$Std_Coefficient[2],2), ", 95%CI = ",
  #                                                round(standard_beta$CI_low[2],2), "-", 
  #                                                round(standard_beta$CI_high[2],2))) 

```


\newpage 
# ICC for anxiety

we will now look at the ICC outcome for anxiety
<br> The ICC for anxiety is 0.51, which is moderate according to guidelines by Koo and Li (2016):<br>
<br> below 0.50: poor<br>
<br>between 0.50 and 0.75: moderate<br>
<br>between 0.75 and 0.90: good<br>
<br>above 0.90: excellent<br>
```{r echo=FALSE, warning=FALSE, message=FALSE}
library(irr)
library(lme4)
library(psych)

# change name to model null (same for all others)
model <- lme4::lmer(Anxiety ~ 1 + (1 | Random_ID), data = df_all_vid)
# Extract variance components
var_components <- VarCorr(model)
subject_variance <- as.numeric(var_components[1])
residual_variance <- as.numeric(attr(var_components, "sc")^2)

# Calculate ICC
icc <- subject_variance / (subject_variance + residual_variance)
print("lmer for anxiety with just the intercept")
print(icc)

confint(model)
```


\newpage 
# ICC for mood 

The ICC for mood is 0.42, which is lower than anxiety and is actually  within the poor category, according to guidelines by Koo and Li (2016):<br>
<br> below 0.50: poor<br>
<br>between 0.50 and 0.75: moderate<br>
<br>between 0.75 and 0.90: good<br>
<br>above 0.90: excellent<br>
```{r echo=FALSE, warning=FALSE, message=FALSE}
# change name to model null (same for all others)
model <- lme4::lmer(Mood ~ 1 + (1 | Random_ID), data = df_all_vid)
# Extract variance components
var_components <- VarCorr(model)
subject_variance <- as.numeric(var_components[1])
residual_variance <- as.numeric(attr(var_components, "sc")^2)

# Calculate ICC
icc <- subject_variance / (subject_variance + residual_variance)
print("lmer for mood with just the intercept")
print(icc)

confint(model)
```





