---
title: "Surprise study analysis"
author: "Marjan Biria, Elena Bagdades"
date: "2024-12-12"
output: 
    pdf_document:
    toc: true
    toc_depth: 2
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(root.dir = "aim_lab_1", echo = TRUE)
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
library(dplyr)
library(ggplot2)
library(tidyr)
library(lme4)
library(parameters)
library(broom.mixed)
library(purrr)
library(conflicted)
library(stringr)
library(readxl)
```

\newpage

# Study description

This is the first surprise study using the same task version as pilot 21. We had the following groups of participants with the experiment's corresponding Gorilla link: - Prolific aged 18-25 (n = 30): <https://app.gorilla.sc/admin/experiment/180921/design> - Prolific aged 26-45 (n = 38): <https://app.gorilla.sc/admin/experiment/185160/design> - School students aged 14-18 (n = 30): <https://app.gorilla.sc/admin/experiment/177048/design> - Community participants aged 18-25 (n = 24): <https://app.gorilla.sc/admin/experiment/180348/design>

The sample sizes include participants that potentially need to be excluded.

```{r echo=FALSE, warning=FALSE, message=FALSE}
# v3 and v4 have exactly the same task version, but BIQ was causing a problem due to a Gorilla update and it was changed in version 4

# df_Pro_18_25 <- read.csv("")
# df_Pro_26_45 <- read.csv("")
# df_comm_18_25 <- read.csv("")
df_14_18_1 <- read.csv("/Users/elenabagdades/Library/CloudStorage/OneDrive-UniversityCollegeLondon/Desktop/GitHub/aim_lab_1/De_identified_data/surprise_study_schools/surprise_study_schools_v7/SUP_SCH_v7_task_main.csv")
df_14_18_2 <- read.csv("/Users/elenabagdades/Library/CloudStorage/OneDrive-UniversityCollegeLondon/Desktop/GitHub/aim_lab_1/De_identified_data/surprise_study_schools/surprise_study_schools_v9/SUP_SCH_v9_task_main.csv")

df_14_18 <- rbind(df_14_18_1, df_14_18_2)

df_14_18_spin_1 <- read.csv("/Users/elenabagdades/Library/CloudStorage/OneDrive-UniversityCollegeLondon/Desktop/GitHub/aim_lab_1/De_identified_data/surprise_study_schools/surprise_study_schools_v7/SUP_SCH_v7_mini_spin.csv")
df_14_18_spin_2 <- read.csv("/Users/elenabagdades/Library/CloudStorage/OneDrive-UniversityCollegeLondon/Desktop/GitHub/aim_lab_1/De_identified_data/surprise_study_schools/surprise_study_schools_v9/SUP_SCH_v9_mini_spin.csv")

df_14_18_spin <- rbind(df_14_18_spin_1,df_14_18_spin_2)

df_students_rcads_1 <- read.csv("/Users/elenabagdades/Library/CloudStorage/OneDrive-UniversityCollegeLondon/Desktop/GitHub/aim_lab_1/De_identified_data/surprise_study_schools/surprise_study_schools_v7/SUP_SCH_v7_rcads.csv")

df_students_rcads_2 <- read.csv("/Users/elenabagdades/Library/CloudStorage/OneDrive-UniversityCollegeLondon/Desktop/GitHub/aim_lab_1/De_identified_data/surprise_study_schools/surprise_study_schools_v9/SUP_SCH_v9_rcads.csv")
df_students_rcads_2 <- df_students_rcads_2[, !(colnames(df_students_rcads_2) %in% "Participant.External.Session.ID")]

df_students_rcads<- rbind(df_students_rcads_1,df_students_rcads_2)

```

```{r echo=FALSE, warning=FALSE, message=FALSE}
# extract RCAD scores
 df_students_rcads_clean <- df_students_rcads[,123:129]
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
# We have now different names for different screens:
# Prediction (how well do you think you performed?)
# prediction_2 (how well do you think you performed?)
# feedback (This is how well X thought you performed)
# First 4 trials are with the histograms and are called "Trials_Histogram" in Display column instead of "Trials"
# The trial numbers start from 1 again after the histograms so we need to concatenate them all.
# Let's rename them to "Trials" to extract them together with the rest of the trials

df_14_18$Trial.Number[df_14_18$Display == "Trials "] <- df_14_18$Trial.Number[df_14_18$Display == "Trials "] + 4

df_14_18 <- df_14_18 %>%
  mutate(Screen = if_else(Screen == "Prediction", "Prediction ", Screen))


df_14_18 <- df_14_18 %>%
  mutate(Display = if_else(Display == "Trials_Histogram", "Trials ", Display))

df_14_18_spin <- df_14_18_spin %>%
  rename(
   "Q1" =  "Rating.Scale.object.2.Fear.of.embarrassment.causes.me.to.avoid.doing.things.or.speaking.to.people.",
   "Q2" =  "Rating.Scale.object.2.I.avoid.activities.in.which.I.am.the.center.of.attention.",
   "Q3" = "Rating.Scale.object.2.Being.embarrassed.or.looking.stupid.are.among.my.worst.fears."
  )

df_14_18_spin <- df_14_18_spin %>%
  rowwise() %>%
  mutate(mini_SPIN_total = sum(c(Q1, Q2, Q3), na.rm = TRUE)) %>%
  ungroup()


# create a new df_students that only keeps the columns we need
df_students <- df_14_18[, c("Trial.Number", "Display", "Screen", "Response.Type", "Response", 
                     "Reaction.Time", "Spreadsheet..Histogram", "Spreadsheet..Feedback", "Random_ID_new")]

df_students <- df_students %>% dplyr::filter(Response.Type != "info")

df_students <- df_students %>%
  mutate(Response = as.numeric(as.character(Response))) %>%
  dplyr::filter(!is.na(Response))

df_students$Screen <- ifelse(df_students$Trial.Number == 1 & (df_students$Display == "Mood " | df_students$Display == "Anxiety "), "BL_1",
                      ifelse(df_students$Trial.Number == 2 & (df_students$Display == "Mood " | df_students$Display == "Anxiety "), "BL_2", 
                             df_students$Screen))

df_students$m_hist <- ifelse(df_students$Spreadsheet..Histogram == "h2.png", 29,
                             ifelse(df_students$Spreadsheet..Histogram == "h3.png", 37,
                                                  ifelse(df_students$Spreadsheet..Histogram == "h6.png", 63,
                                                         ifelse(df_students$Spreadsheet..Histogram == "h7.png", 71, NA))))  


# get rid of the rows we don't need: practice runs, continue button presses etc. and only keep Trials, Anxiety and Mood that include all variables we are interested in:
df_students <- df_students %>%
  dplyr::filter(
    (Display == "Trials ") |
      (Display == "Exit") |
      (Display == "Anxiety " & !Trial.Number %in% c(1, 2)) |
      (Display == "Mood " & !Trial.Number %in% c(1, 2)) 
  )

# # setting Mood and Anxiety trial numbers to match the trials starting from 1 (since we removed the baseline ones above)
df_students$Trial.Number <- ifelse(df_students$Display == 'Mood ' | df_students$Display == 'Anxiety ', df_students$Trial.Number - 2, df_students$Trial.Number)
df_students$Display <- ifelse(df_students$Display == 'Mood ' | df_students$Display == 'Anxiety ', "Trials", df_students$Display)

# renaming the feedback column to fdbk
names(df_students)[names(df_students) == 'Spreadsheet..Feedback'] <- 'fdbk'

# Now let's create columns for PE (fdbk-hist) and Subj_PE (fdbk_Prediction)

df_students$SubjPE <- ifelse(df_students$Screen == "Prediction ", df_students$fdbk - df_students$Response, NA)
df_students$PE <- ifelse(df_students$Screen == "Prediction ", df_students$fdbk - df_students$m_hist, NA)
# to keep just one repetition of feedback and mean histogram per trial per subject 
# and replace the rest with NA so that when we want to convert to long format we won't have duplicates
df_students$fdbk <- ifelse(df_students$Screen == "Prediction ", df_students$fdbk, NA)
df_students$m_hist <- ifelse(df_students$Screen == "Prediction ", df_students$m_hist, NA)
df_students$stress_level <- ifelse(df_students$Screen == "Screen 12", df_students$Response, NA)

long_df_students <- df_students %>%
  dplyr::select(Random_ID_new, Trial.Number, fdbk, m_hist, PE, SubjPE, stress_level) %>%
  pivot_longer(cols = c(fdbk, m_hist, PE, SubjPE, stress_level),
               names_to = "Screen",
               values_to = "Response")

# This will keep only the rows where 'Response' is not NA
long_df_students <- long_df_students[!is.na(long_df_students$Response), ]

# Selecting relevant columns from the original df_students
df_students <- df_students %>%
  dplyr::select(-c(fdbk, m_hist, PE, SubjPE, stress_level))

# Binding the rows together
df_students <- bind_rows(df_students, long_df_students)

df_students$Response <- as.numeric(df_students$Response)

# looking at the relationship between PE and SubjPE
df_students_PE <- subset(df_students, Screen == "PE")
names(df_students_PE)[names(df_students_PE) == "Screen"] <- "Screen_PE"
names(df_students_PE)[names(df_students_PE) == "Response"] <- "Response_PE"

df_students_SubjPE <- subset(df_students, Screen == "SubjPE")
names(df_students_SubjPE)[names(df_students_SubjPE) == "Screen"] <- "Screen_SubjPE"
names(df_students_SubjPE)[names(df_students_SubjPE) == "Response"] <- "Response_SubjPE"

df_students_fdbk <- subset(df_students, Screen == "fdbk")
names(df_students_fdbk)[names(df_students_fdbk) == "Screen"] <- "Screen_fdbk"
names(df_students_fdbk)[names(df_students_fdbk) == "Response"] <- "Response_fdbk"

df_students_hist <- subset(df_students, Screen == "m_hist")
names(df_students_hist)[names(df_students_hist) == "Screen"] <- "Screen_m_hist"
names(df_students_hist)[names(df_students_hist) == "Response"] <- "Response_m_hist"

df_students_stress_level <- subset(df_students, Screen == "Screen 12")
names(df_students_stress_level)[names(df_students_stress_level) == "Screen"] <- "Screen_stress_level"
names(df_students_stress_level)[names(df_students_stress_level) == "Response"] <- "Response_stress_level"

df_students_predic <- subset(df_students, Screen == "Prediction ")
names(df_students_predic)[names(df_students_predic) == "Screen"] <- "Screen_pred"
names(df_students_predic)[names(df_students_predic) == "Response"] <- "Response_pred"


# df_students_cert <- subset(df_students, Screen == "Certainty rating ")
# names(df_students_cert)[names(df_students_cert) == "Screen"] <- "Screen_certainty"
# names(df_students_cert)[names(df_students_cert) == "Response"] <- "Response_certainty"

list_of_dfs_21 <- list(df_students_PE, df_students_fdbk, df_students_hist, df_students_predic, df_students_SubjPE)

# Using reduce with inner_join
merged_df_students <- reduce(list_of_dfs_21, inner_join, by = c("Random_ID_new", "Trial.Number"))

df_students_Anxious <- subset(df_students, Screen == "Anxious")
names(df_students_Anxious)[names(df_students_Anxious) == "Screen"] <- "Screen_Ax"
names(df_students_Anxious)[names(df_students_Anxious) == "Response"] <- "Response_Ax"

df_students_Happy <- subset(df_students, Screen == "Happy")
# df_students_fdbk <- subset(df_students, Screen == "Prediction")
names(df_students_Happy)[names(df_students_Happy) == "Screen"] <- "Screen_H"
names(df_students_Happy)[names(df_students_Happy) == "Response"] <- "Response_H"

final_df_students <- merged_df_students %>%
  inner_join(df_students_Anxious, by = c("Random_ID_new", "Trial.Number")) %>%
  inner_join(df_students_Happy, by = c("Random_ID_new", "Trial.Number"))


# subset only the columns we are interested in
final_df_students <- final_df_students[c("Trial.Number", "Random_ID_new", "Response_H", "Response_Ax", "Response_fdbk", "Response_SubjPE", "Response_PE", "Response_m_hist", "Response_pred")]

final_df_students <- final_df_students %>%
  left_join(df_14_18_spin %>% dplyr::select(Random_ID_new, mini_SPIN_total), by = "Random_ID_new")

final_df_students <- 
  left_join(final_df_students,df_students_rcads_clean , by = "Random_ID_new")

final_df_students <- final_df_students %>%
  left_join(df_students_stress_level %>% dplyr::select(Random_ID_new, Response_stress_level), by = "Random_ID_new")

# final_df_students <- final_df_students %>%
#   left_join(CESD_data_clean %>% dplyr::select(Random_ID_new, CESD_score, Depression_Threshold, Depression_status), by = "Random_ID_new")

final_df_students$Social_Anxiety <- ifelse(final_df_students$mini_SPIN_total >= 6, "high", "low")

# excluding people with poor data quality after the video inspection (not doing the task, or laughing with friends etc):


# excluding people with problematic performance according to Jess's video check
final_df_students <- final_df_students[!(final_df_students$Random_ID_new %in% c("SUPSCO12782", "SUPSCO24387", "SUPSCO46030", "SUPSCO12088","SUPSCO70018")), ]



write.csv(final_df_students, "surprise_study_14_18_variables.csv", row.names = FALSE)


final_df_students %>%
  group_by(Random_ID_new) %>%
  summarise(Trial.Number = n())

write.csv(final_df_students, "final_df_students_with_stresslevels.csv", row.names = FALSE)

```

\newpage

# Relationship between prediction and mean histograms (4x only in the beginning)

```{r echo=FALSE, warning=FALSE, message=FALSE}
correlations <- final_df_students %>%
  group_by(Random_ID_new) %>%
  summarise(correlation = cor(Response_m_hist, Response_pred, method = "spearman", use = "complete.obs")) %>%
  mutate(label = paste("R = ", round(correlation, digits = 2)))

# # calculate the average correlation across all individuals and print it
average_correlation <- mean(correlations$correlation, na.rm = TRUE)
message_to_print_H <- paste("average correlation between mean_hist and prediction:", average_correlation)

print(message_to_print_H)

ggplot(final_df_students, aes(x = Response_m_hist, y = Response_pred, color = Social_Anxiety, group= Social_Anxiety)) +
  geom_point(aes(color=Social_Anxiety, alpha = 0.3)) +
  geom_smooth(method = "lm", color="blue", aes(group=Random_ID_new)) +
  # labs(color="Legend") +
  theme_minimal() +
  xlab("prediction") +
  ylab("mean_histogram") +
    facet_wrap(~ Random_ID_new, scales = "free") +
    geom_text(data=correlations, aes(x=Inf, y=Inf, label=label, group=Random_ID_new), hjust=1.1, vjust=1.1, size=2.7, fontface = "bold", inherit.aes=FALSE) +
    theme(strip.text = element_text(size = 6),
        axis.text.x = element_text(size = 5.5),
        axis.text.y = element_text(size = 5.5),
        strip.text.x = element_text(face = "bold"),
        strip.text.y = element_text(face = "bold"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank())
  
```

\newpage

# Relationship between Anxiety and SubjPE

```{r echo=FALSE, warning=FALSE, message=FALSE}
correlations_Ax <- final_df_students %>%
  group_by(Random_ID_new) %>%
  summarise(correlation = cor(Response_Ax, Response_SubjPE, use = "complete.obs")) %>%
  mutate(label = paste("R = ", round(correlation, digits = 2))) 

# calculate the average correlation across all individuals and print it 
average_correlation <- mean(correlations_Ax$correlation, na.rm = TRUE)
message_to_print_Ax <- paste("average correlation between anxiety and SubjPE:", average_correlation)

print(message_to_print_Ax)

ggplot(final_df_students, aes(x = Response_SubjPE, y = Response_Ax, color = Social_Anxiety, group= Social_Anxiety)) +
  geom_point(aes(color=Social_Anxiety, alpha = 0.3)) +
  geom_smooth(method = "lm", color="blue", aes(group=Random_ID_new)) + 
  # labs(color="Legend") +
  theme_minimal() +
  xlab("SubjPE: feedback - prediction") + 
  ylab("Anxiety") +
    facet_wrap(~ Random_ID_new, scales = "free") +
    geom_text(data=correlations_Ax, aes(x=Inf, y=Inf, label=label, group=Random_ID_new), hjust=1.1, vjust=1.1, size=2.7, fontface = "bold", inherit.aes=FALSE) +
    theme(strip.text = element_text(size = 6),
        axis.text.x = element_text(size = 5.5),  
        axis.text.y = element_text(size = 5.5),  
        strip.text.x = element_text(face = "bold"),  
        strip.text.y = element_text(face = "bold"),  
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank()) +
ylim(c(0, 100)) +
scale_y_continuous(breaks = seq(0, 100, by = 25), limits = c(0, 100))+
xlim(c(-100, 100)) +
scale_x_continuous(breaks = seq(-80, 80, by = 50), limits = c(-80,80))
```

\newpage

# Relationship between Mood and SubjPE

```{r echo=FALSE, warning=FALSE, message=FALSE}

# correlations_M <- final_df_students %>%
#   group_by(Random_ID_new) %>%
#   summarise(correlation = cor(Response_H, Response_SubjPE, use = "complete.obs")) %>%
#   mutate(label = paste("R = ", round(correlation, digits = 2))) 

correlations_M <- final_df_students %>%
  group_by(Random_ID_new) %>%
  summarise(
    shapiro_p_H = shapiro.test(Response_H)$p.value,
    shapiro_p_SubjPE = shapiro.test(Response_SubjPE)$p.value,
    correlation = case_when(
      shapiro_p_H <= 0.05 | shapiro_p_SubjPE <= 0.05 ~ cor(Response_H, Response_SubjPE, method = "spearman", use = "complete.obs"),
      TRUE ~ cor(Response_H, Response_SubjPE, method = "pearson", use = "complete.obs")
    )
  ) %>%
  mutate(label = paste("R = ", round(correlation, digits = 2)))


# calculate the average correlation across all individuals and print it 
average_correlation <- mean(correlations_M$correlation, na.rm = TRUE)
message_to_print_H <- paste("average correlation between mood and SubjPE:", average_correlation)

print(message_to_print_H)

ggplot(final_df_students, aes(x = Response_SubjPE, y = Response_H, color = Social_Anxiety, group= Social_Anxiety)) +
  geom_point(aes(color=Social_Anxiety, alpha = 0.3)) +
  geom_smooth(method = "lm", color="blue", aes(group=Random_ID_new)) + 
  # labs(color="Legend") +
  theme_minimal() +
  xlab("SubjPE: feedback - prediction") + 
  ylab("Mood") +
    facet_wrap(~ Random_ID_new, scales = "free") +
    geom_text(data=correlations_M, aes(x=Inf, y=Inf, label=label, group=Random_ID_new), hjust=1.1, vjust=1.1, size=2.7, fontface = "bold", inherit.aes=FALSE) +
    theme(strip.text = element_text(size = 6),
        axis.text.x = element_text(size = 5.5),  
        axis.text.y = element_text(size = 5.5),  
        strip.text.x = element_text(face = "bold"),  
        strip.text.y = element_text(face = "bold"),  
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank()) +
  ylim(c(0, 100)) + 
  scale_y_continuous(breaks = seq(0, 100, by = 25), limits = c(0, 100))+
  xlim(c(-100, 100)) + 
  scale_x_continuous(breaks = seq(-80, 80, by = 50), limits = c(-80,80))


# for some people their data was not normally distributed at all and the correlatrion would lead to completely different results, so I changed the code above to reflect that
# # Step 1: Subset the data
# subset_data <- final_df_students[final_df_students$Random_ID_new == "SUPSCO84507", ]
# 
# # Shapiro-Wilk test for Response_SubjPE
# shapiro_test_SubjPE <- shapiro.test(subset_data$Response_SubjPE)
# 
# # Shapiro-Wilk test for Response_H
# shapiro_test_H <- shapiro.test(subset_data$Response_H)
# 
# # Display the results
# shapiro_test_SubjPE
# shapiro_test_H
# 
# # Histogram for Response_SubjPE
# hist(subset_data$Response_SubjPE, main = "Histogram of Response_SubjPE", xlab = "Response_SubjPE", breaks = 30)
# 
# # Histogram for Response_H
# hist(subset_data$Response_H, main = "Histogram of Response_H", xlab = "Response_H", breaks = 30)
# 
# 
# # Step 2: Calculate the Spearman correlation
# cor(subset_data$Response_SubjPE, subset_data$Response_H, method = "spearman")
# cor(subset_data$Response_SubjPE, subset_data$Response_H, method = "pearson")



```

```{r echo=FALSE, warning=FALSE, message=FALSE}
# trying to keep the BL_1 and BL_2 mood and anxiety ratings
df_14_18_with_BL <- df_14_18[, c("Trial.Number", "Display", "Screen", "Response.Type", "Response", 
                     "Reaction.Time", "Spreadsheet..Histogram", "Spreadsheet..Feedback", "Random_ID_new")]

df_14_18_with_BL <- df_14_18_with_BL %>%
  mutate(Response = as.numeric(as.character(Response))) %>%
  dplyr::filter(!is.na(Response))

df_14_18_with_BL <- df_14_18_with_BL %>% dplyr::filter(Response.Type != "info")

df_14_18_with_BL$Screen <- ifelse(df_14_18_with_BL$Trial.Number == 1 & (df_14_18_with_BL$Display == "Mood " | df_14_18_with_BL$Display == "Anxiety "), "BL_1",
                      ifelse(df_14_18_with_BL$Trial.Number == 2 & (df_14_18_with_BL$Display == "Mood " | df_14_18_with_BL$Display == "Anxiety "), "BL_2", 
                             df_14_18_with_BL$Screen))

df_14_18_with_BL$m_hist <- ifelse(df_14_18_with_BL$Spreadsheet..Histogram == "h1.png", 21,
                      ifelse(df_14_18_with_BL$Spreadsheet..Histogram == "h2.png", 29,
                             ifelse(df_14_18_with_BL$Spreadsheet..Histogram == "h3.png", 37,
                                    ifelse(df_14_18_with_BL$Spreadsheet..Histogram == "h4.png", 46,
                                           ifelse(df_14_18_with_BL$Spreadsheet..Histogram == "h5.png", 54,
                                                  ifelse(df_14_18_with_BL$Spreadsheet..Histogram == "h6.png", 63,
                                                         ifelse(df_14_18_with_BL$Spreadsheet..Histogram == "h7.png", 71,
                                                                ifelse(df_14_18_with_BL$Spreadsheet..Histogram == "h8.png", 80, NA))))))))  


# get rid of the rows we don't need: practice runs, continue button presses etc. and only keep Trials, Anxiety and Mood that include all variables we are interested in:
df_14_18_with_BL <- df_14_18_with_BL %>%
  dplyr::filter(
    (Display == "Trials ") |
      (Display == "Anxiety ") |
      (Display == "Mood ")
  )

# # setting Mood and Anxiety trial numbers to match the trials starting from 1 (since we removed the baseline ones above)
df_14_18_with_BL$Trial.Number <- ifelse(df_14_18_with_BL$Display == 'Mood ' | df_14_18_with_BL$Display == 'Anxiety ', df_14_18_with_BL$Trial.Number - 2, df_14_18_with_BL$Trial.Number)
# df_14_18_with_BL$Display <- ifelse(df_14_18_with_BL$Display == 'Mood ' | df_14_18_with_BL$Display == 'Anxiety ', "Trials", df_14_18_with_BL$Display)

final_df_14_18_with_BL <- df_14_18_with_BL[c("Trial.Number", "Display", "Screen", "Response", "Random_ID_new")]

final_df_14_18_with_BL <- final_df_14_18_with_BL %>%
  left_join(df_14_18_spin %>% dplyr::select(Random_ID_new, mini_SPIN_total), by = "Random_ID_new")

# final_df_14_18_with_BL <- final_df_14_18_with_BL %>%
#   left_join(CESD_data_clean %>% dplyr::select(Random_ID_new, CESD_score, Depression_Threshold, Depression_status), by = "Random_ID_new")

final_df_14_18_with_BL$Social_Anxiety <- ifelse(final_df_14_18_with_BL$mini_SPIN_total >= 6, "high", "low")


```

\newpage

# Mood over time

```{r echo=FALSE, warning=FALSE, message=FALSE}
df_students_BL_ax <- subset(final_df_14_18_with_BL, Display == "Anxiety ")
df_students_BL_H <- subset(final_df_14_18_with_BL,Display == "Mood ")

ggplot(df_students_BL_H, aes(x = Trial.Number, y = Response, color = Display, group = Display)) +
  geom_line(color = "blue") +
  geom_vline(xintercept = 1, linetype = "dashed", color = "red") + # Adding a vertical line at Trial.Number == 1
  theme_minimal() +
  labs(title = "Mood across time",
       x = "Trial Number",
       y = "Mood",
       color = "") +
  facet_wrap(~ Random_ID_new, ncol = 6) + 
  theme(strip.text = element_text(size = 6)) +  
  scale_x_continuous(breaks = seq(-1, 48, by = 10), limits = c(-1, 48)) +
  scale_y_continuous(breaks = seq(0, 100, by = 21), limits = c(0, 100))+
  theme(axis.text.x = element_text(size = 5),axis.text.y = element_text(size = 5))

```

\newpage

# Anxiety over time

```{r echo=FALSE, warning=FALSE, message=FALSE}
ggplot(df_students_BL_ax, aes(x = Trial.Number, y = Response, color = Display, group = Display)) +
  geom_line(color = "blue") +
  geom_vline(xintercept = 1, linetype = "dashed", color = "red") + # Adding a vertical line at Trial.Number == 1
  theme_minimal() +
  labs(title = "Anxiety across time",
       x = "Trial Number",
       y = "Anxiety",
       color = "") +
  facet_wrap(~ Random_ID_new, ncol = 6) + 
  theme(strip.text = element_text(size = 6)) +  
  scale_x_continuous(breaks = seq(-1, 48, by = 10), limits = c(-1, 48)) +
  scale_y_continuous(breaks = seq(0, 100, by = 21), limits = c(0, 100))+
  theme(axis.text.x = element_text(size = 5),axis.text.y = element_text(size = 5))

```

\newpage

# Prediction before performance over time

Red line presents until what points histograms were presented (4 first trials only).

```{r echo=FALSE, warning=FALSE, message=FALSE}
ggplot(final_df_students, aes(x = Trial.Number, y = Response_pred)) +
  geom_line(color = "blue") +
  geom_vline(xintercept = 5, linetype = "dashed", color = "red") + 
  theme_minimal() +
  labs(title = "Prediction before performance across time",
       x = "Trial Number",
       y = "Pre performance prediction",
       color = "") +
  facet_wrap(~ Random_ID_new, ncol = 6) + 
  theme(strip.text = element_text(size = 6)) +  
  scale_x_continuous(breaks = seq(1, 48, by = 10), limits = c(1, 48)) +
  scale_y_continuous(breaks = seq(0, 100, by = 21), limits = c(0, 100))+
  theme(axis.text.x = element_text(size = 5),axis.text.y = element_text(size = 5))

```

\newpage

# Stress levels and social anxiety

```{r echo=FALSE, warning=FALSE, message=FALSE}
onetrial_final_df_students <- subset(final_df_students, final_df_students$Trial.Number == 1)


ggplot(onetrial_final_df_students, aes(x = Social_Anxiety, y = Response_stress_level , fill = Social_Anxiety)) +
  geom_boxplot(outlier.colour = "black") +
  stat_boxplot(geom = "errorbar",
               width = 0.15) + 
  geom_point(color = "black", position = position_jitter(width = 0.1), alpha = 0.7) +
  theme_minimal() +
  # labs(x = "Display", y = "Response") +
  # scale_y_continuous(breaks = seq(0, 100, by = 10), limits = c(0, 100)) +
  # ggtitle("Average anxiety ratings in pilots 1 and 2 in socially anxious people") +
  xlab("") + 
  ylab("stress levels (0-10)") +
  # facet_wrap(~pilot_nr, scales = "free") +
  # scale_fill_manual(values = c("black", "purple", "darkgreen", "blue"))+
  # ylim(c(50, 100)) + 
  scale_y_continuous(breaks = seq(0, 10, by = 1), limits = c(1, 10))+
  theme(
    panel.grid.major = element_blank(),  # Removes major grid lines
    panel.grid.minor = element_blank(),  # Removes minor grid lines
    panel.border = element_blank(),      # Removes the border line
    axis.line = element_blank(),          # Removes axis lines
    plot.background = element_rect(fill = "white", colour = NA)   # Ensure plot background is white
  )

```

\newpage

# LME models for Mood and SubjPE

The best model seems to be: Mood \~ SubjPE + mini_SPIN_total + (SubjPE \| Random_ID_new)

```{r echo=FALSE, warning=FALSE, message=FALSE}
model1 <- lme4::lmer(Response_H ~ Response_SubjPE +  (Response_SubjPE | Random_ID_new), data = final_df_students, control=lmerControl(optimizer="bobyqa"))
model2 <- lme4::lmer(Response_H ~ Response_SubjPE +  mini_SPIN_total + (1 | Random_ID_new), data = final_df_students, control=lmerControl(optimizer="bobyqa"))
model3 <- lme4::lmer(Response_H ~ Response_SubjPE + mini_SPIN_total + (Response_SubjPE | Random_ID_new), data = final_df_students, control=lmerControl(optimizer="bobyqa"))
model4 <- lme4::lmer(Response_H ~ Response_SubjPE + Social_Anxiety + (Response_SubjPE | Random_ID_new), data = final_df_students, control=lmerControl(optimizer="bobyqa"))

AIC(model1)
AIC(model2)
AIC(model3)
AIC(model4)

coef_fixed <- fixef(model4)
intercept_Response_H <- coef_fixed[1]
slope_Response_H <- coef_fixed[2]
standard_beta_Response_SubjPE <- parameters:: standardise_parameters (model4)

CI_multiplier <- 1.96  # 95% CI multiplier for a normal distribution
model_summary <- summary(model3)
SE_intercept <- model_summary$coefficients[1, "Std. Error"]  # Standard error for the intercept
SE_slope <- model_summary$coefficients[2, "Std. Error"]      # Standard error for the slope

# Creating a sequence of `SubjPE` values for prediction
Response_SubjPE_range <- seq(min(final_df_students$Response_SubjPE), max(final_df_students$Response_SubjPE), length.out = 100)

# Calculating predicted Response_H and its CI bounds across the SubjPE range
predicted_Response_H <- intercept_Response_H + slope_Response_H * Response_SubjPE_range
CI_lower <- predicted_Response_H - CI_multiplier * sqrt(SE_intercept^2 + (Response_SubjPE_range^2 * SE_slope^2))
CI_upper <- predicted_Response_H + CI_multiplier * sqrt(SE_intercept^2 + (Response_SubjPE_range^2 * SE_slope^2))

# Preparing a data frame for ggplot
CI_data <- data.frame(Response_SubjPE=Response_SubjPE_range, CI_lower=CI_lower, CI_upper=CI_upper)


ggplot(final_df_students, aes(x=Response_SubjPE, y=Response_H)) +
  # Adding points from your dataset
  # geom_point() +
  # Adding a regression line
  geom_abline(intercept=intercept_Response_H, slope=slope_Response_H, color="darkgoldenrod1", linetype="dashed", size=1) +
  # Adding the confidence interval with geom_ribbon
  geom_ribbon(data=CI_data, aes(x=Response_SubjPE, ymin=CI_lower, ymax=CI_upper), fill="gray80", alpha=0.5, inherit.aes = FALSE) +
  # Further customization
  xlab("Social PE") + 
  ylab("Mood") +
  ggtitle("", subtitle=paste("Estimated slopes of the association in n = ", length(unique(final_df_students$Random_ID_new)))) +
  theme(plot.title=element_text(size=12), plot.subtitle=element_text(size=10),
        legend.title=element_text(size=12), legend.text=element_text(size=12),
        axis.title=element_text(size=13),
        axis.text=element_text(size=12),
        panel.background=element_blank(), panel.grid.major=element_blank(), panel.grid.minor=element_blank(),
        panel.border=element_rect(colour="black", fill=NA)) +
  annotate("label", x=12, y=55, label=paste("beta =", round(standard_beta_Response_SubjPE$Std_Coefficient[2],2), ", 95%CI =", 
                                            round(standard_beta_Response_SubjPE$CI_low[2],2), "-", round(standard_beta_Response_SubjPE$CI_high[2],2))) +
  scale_y_continuous(breaks=seq(0, 100, by=20), limits=c(0, 100)) +
  scale_x_continuous(breaks=seq(-80, 80, by=40), limits=c(-80, 80))

```

\newpage

# LME models for Anxiety and SubjPE

The best model seems to be: Anxiety \~ SubjPE + mini_SPIN_total + (SubjPE \| Random_ID_new)

```{r echo=FALSE, warning=FALSE, message=FALSE}
model1 <- lme4::lmer(Response_Ax ~ Response_SubjPE +  (Response_SubjPE | Random_ID_new), data = final_df_students, control=lmerControl(optimizer="bobyqa"))
model2 <- lme4::lmer(Response_Ax ~ Response_SubjPE +  mini_SPIN_total + (1 | Random_ID_new), data = final_df_students, control=lmerControl(optimizer="bobyqa"))
model3 <- lme4::lmer(Response_Ax ~ Response_SubjPE + mini_SPIN_total + (Response_SubjPE | Random_ID_new), data = final_df_students, control=lmerControl(optimizer="bobyqa"))
model4 <- lme4::lmer(Response_Ax ~ Response_SubjPE + Social_Anxiety + (Response_SubjPE | Random_ID_new), data = final_df_students, control=lmerControl(optimizer="bobyqa"))

AIC(model1)
AIC(model2)
AIC(model3)
AIC(model4)

coef_fixed <- fixef(model4)
intercept_Response_Ax <- coef_fixed[1]
slope_Response_Ax <- coef_fixed[2]
standard_beta_Response_SubjPE <- parameters:: standardise_parameters (model3)


CI_multiplier <- 1.96  # 95% CI multiplier for a normal distribution
model_summary <- summary(model4)
SE_intercept <- model_summary$coefficients[1, "Std. Error"]  # Standard error for the intercept
SE_slope <- model_summary$coefficients[2, "Std. Error"]      # Standard error for the slope

# Creating a sequence of `SubjPE` values for prediction
Response_SubjPE_range <- seq(min(final_df_students$Response_SubjPE), max(final_df_students$Response_SubjPE), length.out = 100)

# Calculating predicted Response_Ax and its CI bounds across the SubjPE range
predicted_Response_Ax <- intercept_Response_Ax + slope_Response_Ax * Response_SubjPE_range
CI_lower <- predicted_Response_Ax - CI_multiplier * sqrt(SE_intercept^2 + (Response_SubjPE_range^2 * SE_slope^2))
CI_upper <- predicted_Response_Ax + CI_multiplier * sqrt(SE_intercept^2 + (Response_SubjPE_range^2 * SE_slope^2))

# Preparing a data frame for ggplot
CI_data <- data.frame(Response_SubjPE=Response_SubjPE_range, CI_lower=CI_lower, CI_upper=CI_upper)


ggplot(final_df_students, aes(x=Response_SubjPE, y=Response_Ax)) +
  # Adding points from your dataset
  # geom_point() +
  # Adding a regression line
  geom_abline(intercept=intercept_Response_Ax, slope=slope_Response_Ax, color="darkgoldenrod1", linetype="dashed", size=1) +
  # Adding the confidence interval with geom_ribbon
  geom_ribbon(data=CI_data, aes(x=Response_SubjPE, ymin=CI_lower, ymax=CI_upper), fill="gray80", alpha=0.5, inherit.aes = FALSE) +
  # Further customization
  xlab("Social PE") + 
  ylab("Anxiety") +
  ggtitle("", subtitle=paste("Estimated slopes of the association in n = ", length(unique(final_df_students$Random_ID_new)))) +
  theme(plot.title=element_text(size=12), plot.subtitle=element_text(size=10),
        legend.title=element_text(size=12), legend.text=element_text(size=12),
        axis.title=element_text(size=13),
        axis.text=element_text(size=12),
        panel.background=element_blank(), panel.grid.major=element_blank(), panel.grid.minor=element_blank(),
        panel.border=element_rect(colour="black", fill=NA)) +
  annotate("label", x=12, y=55, label=paste("beta =", round(standard_beta_Response_SubjPE$Std_Coefficient[2],2), ", 95%CI =", 
                                            round(standard_beta_Response_SubjPE$CI_low[2],2), "-", round(standard_beta_Response_SubjPE$CI_high[2],2))) +
  scale_y_continuous(breaks=seq(0, 100, by=20), limits=c(0, 100)) +
  scale_x_continuous(breaks=seq(-80, 80, by=40), limits=c(-80, 80))
```

\newpage

# LME models for Mood and Expectation

```{r echo=FALSE, warning=FALSE, message=FALSE}
model1 <- lme4::lmer(Response_H ~ Response_pred +  (Response_pred | Random_ID_new), data = final_df_students, control=lmerControl(optimizer="bobyqa"))
model2 <- lme4::lmer(Response_H ~ Response_pred +  mini_SPIN_total + (1 | Random_ID_new), data = final_df_students, control=lmerControl(optimizer="bobyqa"))
model3 <- lme4::lmer(Response_H ~ Response_pred + mini_SPIN_total + (Response_pred | Random_ID_new), data = final_df_students, control=lmerControl(optimizer="bobyqa"))
model4 <- lme4::lmer(Response_H ~ Response_pred + Social_Anxiety + (Response_pred | Random_ID_new), data = final_df_students, control=lmerControl(optimizer="bobyqa"))

AIC(model1)
AIC(model2)
AIC(model3)
AIC(model4)

coef_fixed <- fixef(model4)
intercept_Response_H <- coef_fixed[1]
slope_Response_H <- coef_fixed[2]
standard_beta_Response_pred <- parameters:: standardise_parameters (model4)

CI_multiplier <- 1.96  # 95% CI multiplier for a normal distribution
model_summary <- summary(model3)
SE_intercept <- model_summary$coefficients[1, "Std. Error"]  # Standard error for the intercept
SE_slope <- model_summary$coefficients[2, "Std. Error"]      # Standard error for the slope

# Creating a sequence of `pred` values for prediction
Response_pred_range <- seq(min(final_df_students$Response_pred), max(final_df_students$Response_pred), length.out = 100)

# Calculating predicted Response_H and its CI bounds across the SubjPE range
predicted_Response_H <- intercept_Response_H + slope_Response_H * Response_pred_range
CI_lower <- predicted_Response_H - CI_multiplier * sqrt(SE_intercept^2 + (Response_pred_range^2 * SE_slope^2))
CI_upper <- predicted_Response_H + CI_multiplier * sqrt(SE_intercept^2 + (Response_pred_range^2 * SE_slope^2))

# Preparing a data frame for ggplot
CI_data <- data.frame(Response_pred=Response_pred_range, CI_lower=CI_lower, CI_upper=CI_upper)


ggplot(final_df_students, aes(x=Response_pred, y=Response_H)) +
  # Adding points from your dataset
  # geom_point() +
  # Adding a regression line
  geom_abline(intercept=intercept_Response_H, slope=slope_Response_H, color="darkgoldenrod1", linetype="dashed", size=1) +
  # Adding the confidence interval with geom_ribbon
  geom_ribbon(data=CI_data, aes(x=Response_pred, ymin=CI_lower, ymax=CI_upper), fill="gray80", alpha=0.5, inherit.aes = FALSE) +
  # Further customization
  xlab("Social PE") + 
  ylab("Mood") +
  ggtitle("", subtitle=paste("Estimated slopes of the association in n = ", length(unique(final_df_students$Random_ID_new)))) +
  theme(plot.title=element_text(size=12), plot.subtitle=element_text(size=10),
        legend.title=element_text(size=12), legend.text=element_text(size=12),
        axis.title=element_text(size=13),
        axis.text=element_text(size=12),
        panel.background=element_blank(), panel.grid.major=element_blank(), panel.grid.minor=element_blank(),
        panel.border=element_rect(colour="black", fill=NA)) +
  annotate("label", x=12, y=55, label=paste("beta =", round(standard_beta_Response_pred$Std_Coefficient[2],2), ", 95%CI =", 
                                            round(standard_beta_Response_pred$CI_low[2],2), "-", round(standard_beta_Response_pred$CI_high[2],2))) +
  scale_y_continuous(breaks=seq(0, 100, by=20), limits=c(0, 100)) +
  scale_x_continuous(breaks=seq(0, 100, by=40), limits=c(0, 100))


```

\newpage

# LME models for Anxiety and Expectation

```{r echo=FALSE, warning=FALSE, message=FALSE}
model1 <- lme4::lmer(Response_Ax ~ Response_pred +  (Response_pred | Random_ID_new), data = final_df_students, control=lmerControl(optimizer="bobyqa"))
model2 <- lme4::lmer(Response_Ax ~ Response_pred +  mini_SPIN_total + (1 | Random_ID_new), data = final_df_students, control=lmerControl(optimizer="bobyqa"))
model3 <- lme4::lmer(Response_Ax ~ Response_pred + mini_SPIN_total + (Response_pred | Random_ID_new), data = final_df_students, control=lmerControl(optimizer="bobyqa"))
model4 <- lme4::lmer(Response_Ax ~ Response_pred + Social_Anxiety + (Response_pred | Random_ID_new), data = final_df_students, control=lmerControl(optimizer="bobyqa"))

AIC(model1)
AIC(model2)
AIC(model3)
AIC(model4)

coef_fixed <- fixef(model4)
intercept_Response_Ax <- coef_fixed[1]
slope_Response_Ax <- coef_fixed[2]
standard_beta_Response_pred <- parameters:: standardise_parameters (model4)

CI_multiplier <- 1.96  # 95% CI multiplier for a normal distribution
model_summary <- summary(model3)
SE_intercept <- model_summary$coefficients[1, "Std. Error"]  # Standard error for the intercept
SE_slope <- model_summary$coefficients[2, "Std. Error"]      # Standard error for the slope

# Creating a sequence of `pred` values for prediction
Response_pred_range <- seq(min(final_df_students$Response_pred), max(final_df_students$Response_pred), length.out = 100)

# Calculating predicted Response_H and its CI bounds across the SubjPE range
  predicted_Response_Ax <- intercept_Response_Ax + slope_Response_Ax * Response_pred_range
CI_lower <- predicted_Response_Ax - CI_multiplier * sqrt(SE_intercept^2 + (Response_pred_range^2 * SE_slope^2))
CI_upper <- predicted_Response_Ax + CI_multiplier * sqrt(SE_intercept^2 + (Response_pred_range^2 * SE_slope^2))

# Preparing a data frame for ggplot
CI_data <- data.frame(Response_pred=Response_pred_range, CI_lower=CI_lower, CI_upper=CI_upper)


ggplot(final_df_students, aes(x=Response_pred, y=Response_Ax)) +
  # Adding points from your dataset
  # geom_point() +
  # Adding a regression line
  geom_abline(intercept=intercept_Response_Ax, slope=slope_Response_Ax, color="darkgoldenrod1", linetype="dashed", size=1) +
  # Adding the confidence interval with geom_ribbon
  geom_ribbon(data=CI_data, aes(x=Response_pred, ymin=CI_lower, ymax=CI_upper), fill="gray80", alpha=0.5, inherit.aes = FALSE) +
  # Further customization
  xlab("Social PE") + 
  ylab("Anxiety") +
  ggtitle("", subtitle=paste("Estimated slopes of the association in n = ", length(unique(final_df_students$Random_ID_new)))) +
  theme(plot.title=element_text(size=12), plot.subtitle=element_text(size=10),
        legend.title=element_text(size=12), legend.text=element_text(size=12),
        axis.title=element_text(size=13),
        axis.text=element_text(size=12),
        panel.background=element_blank(), panel.grid.major=element_blank(), panel.grid.minor=element_blank(),
        panel.border=element_rect(colour="black", fill=NA)) +
  annotate("label", x=12, y=55, label=paste("beta =", round(standard_beta_Response_pred$Std_Coefficient[2],2), ", 95%CI =", 
                                            round(standard_beta_Response_pred$CI_low[2],2), "-", round(standard_beta_Response_pred$CI_high[2],2))) +
  scale_y_continuous(breaks=seq(0, 100, by=20), limits=c(0, 100)) +
  scale_x_continuous(breaks=seq(0, 100, by=40), limits=c(0, 100))



```

\newpage

# LME models for Mood and Outcome

```{r}
model1 <- lme4::lmer(Response_H ~ Response_fdbk +  (Response_fdbk | Random_ID_new), data = final_df_students, control=lmerControl(optimizer="bobyqa"))
model2 <- lme4::lmer(Response_H ~ Response_fdbk +  mini_SPIN_total + (1 | Random_ID_new), data = final_df_students, control=lmerControl(optimizer="bobyqa"))
model3 <- lme4::lmer(Response_H ~ Response_fdbk + mini_SPIN_total + (Response_fdbk | Random_ID_new), data = final_df_students, control=lmerControl(optimizer="bobyqa"))
model4 <- lme4::lmer(Response_H ~ Response_fdbk + Social_Anxiety + (Response_fdbk | Random_ID_new), data = final_df_students, control=lmerControl(optimizer="bobyqa"))

AIC(model1)
AIC(model2)
AIC(model3)
AIC(model4)

coef_fixed <- fixef(model4)
intercept_Response_H <- coef_fixed[1]
slope_Response_H <- coef_fixed[2]
standard_beta_Response_fdbk <- parameters:: standardise_parameters (model4)


```

# LME models for Anxiety and Outcome

```{r}
model1 <- lme4::lmer(Response_Ax ~ Response_fdbk +  (Response_fdbk | Random_ID_new), data = final_df_students, control=lmerControl(optimizer="bobyqa"))
model2 <- lme4::lmer(Response_Ax ~ Response_fdbk +  mini_SPIN_total + (1 | Random_ID_new), data = final_df_students, control=lmerControl(optimizer="bobyqa"))
model3 <- lme4::lmer(Response_Ax ~ Response_fdbk + mini_SPIN_total + (Response_fdbk | Random_ID_new), data = final_df_students, control=lmerControl(optimizer="bobyqa"))
model4 <- lme4::lmer(Response_Ax ~ Response_fdbk + Social_Anxiety + (Response_fdbk | Random_ID_new), data = final_df_students, control=lmerControl(optimizer="bobyqa"))

AIC(model1)
AIC(model2)
AIC(model3)
AIC(model4)

coef_fixed <- fixef(model4)
intercept_Response_Ax <- coef_fixed[1]
slope_Response_Ax <- coef_fixed[2]
standard_beta_Response_fdbk <- parameters:: standardise_parameters (model4)

CI_multiplier <- 1.96  # 95% CI multiplier for a normal distribution
model_summary <- summary(model3)
SE_intercept <- model_summary$coefficients[1, "Std. Error"]  # Standard error for the intercept
SE_slope <- model_summary$coefficients[2, "Std. Error"]      # Standard error for the slope

# Creating a sequence of `fdbk` values for prediction
Response_fdbk_range <- seq(min(final_df_students$Response_fdbk), max(final_df_students$Response_fdbk), length.out = 100)

# Calculating predicted Response_H and its CI bounds across the SubjPE range
  predicted_Response_Ax <- intercept_Response_Ax + slope_Response_Ax * Response_fdbk_range
CI_lower <- predicted_Response_Ax - CI_multiplier * sqrt(SE_intercept^2 + (Response_fdbk_range^2 * SE_slope^2))
CI_upper <- predicted_Response_Ax + CI_multiplier * sqrt(SE_intercept^2 + (Response_fdbk_range^2 * SE_slope^2))

# Preparing a data frame for ggplot
CI_data <- data.frame(Response_fdbk=Response_fdbk_range, CI_lower=CI_lower, CI_upper=CI_upper)



ggplot(final_df_students, aes(x=Response_fdbk, y=Response_Ax)) +
  # Adding points from your dataset
  # geom_point() +
  # Adding a regression line
  geom_abline(intercept=intercept_Response_Ax, slope=slope_Response_Ax, color="darkgoldenrod1", linetype="dashed", size=1) +
  # Adding the confidence interval with geom_ribbon
  geom_ribbon(data=CI_data, aes(x=Response_fdbk, ymin=CI_lower, ymax=CI_upper), fill="gray80", alpha=0.5, inherit.aes = FALSE) +
  # Further customization
  xlab("Outcome") + 
  ylab("Anxiety") +
  ggtitle("", subtitle=paste("Estimated slopes of the association in n = ", length(unique(final_df_students$Random_ID_new)))) +
  theme(plot.title=element_text(size=12), plot.subtitle=element_text(size=10),
        legend.title=element_text(size=12), legend.text=element_text(size=12),
        axis.title=element_text(size=13),
        axis.text=element_text(size=12),
        panel.background=element_blank(), panel.grid.major=element_blank(), panel.grid.minor=element_blank(),
        panel.border=element_rect(colour="black", fill=NA)) +
  annotate("label", x=12, y=55, label=paste("beta =", round(standard_beta_Response_fdbk$Std_Coefficient[2],2), ", 95%CI =", 
                                            round(standard_beta_Response_fdbk$CI_low[2],2), "-", round(standard_beta_Response_fdbk$CI_high[2],2))) +
  scale_y_continuous(breaks=seq(0, 100, by=20), limits=c(0, 100)) +
  scale_x_continuous(breaks=seq(0, 100, by=40), limits=c(0, 100))




```

\newpage

# ICC for Mood

```{r echo=FALSE, warning=FALSE, message=FALSE}
test_icc_id <- lmer(Response_H ~  (1| Random_ID_new), data = 
                      final_df_students, 
                    REML = FALSE, 
                    control = lmerControl(optimizer = "bobyqa")) 
icc_results_id <- performance::icc(test_icc_id)

icc_results_id
```

\newpage

# ICC for Anxiety

```{r echo=FALSE, warning=FALSE, message=FALSE}
test_icc_id <- lmer(Response_Ax ~  (1| Random_ID_new), data = 
                      final_df_students, 
                    REML = FALSE, 
                    control = lmerControl(optimizer = "bobyqa")) 
icc_results_id <- performance::icc(test_icc_id)

icc_results_id
```
