---
title: "Surprise study analysis"
author: "Marjan Biria"
date: "2024-08-19"
output: 
    pdf_document:
    toc: true
    toc_depth: 2
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(root.dir = "aim_lab_1", echo = TRUE)
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
library(dplyr)
library(ggplot2)
library(tidyr)
library(lme4)
library(parameters)
library(broom.mixed)
library(purrr)
library(conflicted)
library(stringr)
library(readxl)
```

\newpage


```{r echo=FALSE, warning=FALSE, message=FALSE}


df_merged <- read.csv("/Users/elenabagdades/Library/CloudStorage/OneDrive-UniversityCollegeLondon/Desktop/GitHub/aim_lab_1/Surprise_task_data_analysis/surprise_task_merged_data.csv")

```

\newpage

# Relationship between prediction and mean histograms (4x only in the beginning)

```{r echo=FALSE, warning=FALSE, message=FALSE}
correlations <- df_merged %>%
  group_by(Random_ID) %>%
  summarise(correlation = cor(Response_m_hist, Response_pred, method = "spearman", use = "complete.obs")) %>%
  mutate(label = paste("R = ", round(correlation, digits = 2)))

# # calculate the average correlation across all individuals and print it
average_correlation <- mean(correlations$correlation, na.rm = TRUE)
message_to_print_H <- paste("average correlation between mean_hist and prediction:", average_correlation)

print(message_to_print_H)

ggplot(df_merged, aes(x = Response_m_hist, y = Response_pred, color = Social_Anxiety, group= Social_Anxiety)) +
  geom_point(aes(color=Social_Anxiety, alpha = 0.3)) +
  geom_smooth(method = "lm", color="blue", aes(group=Random_ID)) +
  # labs(color="Legend") +
  theme_minimal() +
  xlab("prediction") +
  ylab("mean_histogram") +
    facet_wrap(~ Random_ID, scales = "free") +
    geom_text(data=correlations, aes(x=Inf, y=Inf, label=label, group=Random_ID), hjust=1.1, vjust=1.1, size=2.7, fontface = "bold", inherit.aes=FALSE) +
    theme(strip.text = element_text(size = 6),
        axis.text.x = element_text(size = 5.5),
        axis.text.y = element_text(size = 5.5),
        strip.text.x = element_text(face = "bold"),
        strip.text.y = element_text(face = "bold"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank())
  
```

\newpage

# Relationship between Anxiety and SubjPE

```{r echo=FALSE, warning=FALSE, message=FALSE}
correlations_Ax <- df_merged %>%
  group_by(Random_ID) %>%
  summarise(correlation = cor(Response_Ax, Response_SubjPE, use = "complete.obs")) %>%
  mutate(label = paste("R = ", round(correlation, digits = 2))) 

# calculate the average correlation across all individuals and print it 
average_correlation <- mean(correlations_Ax$correlation, na.rm = TRUE)
message_to_print_Ax <- paste("average correlation between anxiety and SubjPE:", average_correlation)

print(message_to_print_Ax)

ggplot(df_merged, aes(x = Response_SubjPE, y = Response_Ax, color = Social_Anxiety, group= Social_Anxiety)) +
  geom_point(aes(color=Social_Anxiety, alpha = 0.3)) +
  geom_smooth(method = "lm", color="blue", aes(group=Random_ID)) + 
  # labs(color="Legend") +
  theme_minimal() +
  xlab("SubjPE: feedback - prediction") + 
  ylab("Anxiety") +
    facet_wrap(~ Random_ID, scales = "free") +
    geom_text(data=correlations_Ax, aes(x=Inf, y=Inf, label=label, group=Random_ID), hjust=1.1, vjust=1.1, size=2.7, fontface = "bold", inherit.aes=FALSE) +
    theme(strip.text = element_text(size = 6),
        axis.text.x = element_text(size = 5.5),  
        axis.text.y = element_text(size = 5.5),  
        strip.text.x = element_text(face = "bold"),  
        strip.text.y = element_text(face = "bold"),  
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank()) +
ylim(c(0, 100)) +
scale_y_continuous(breaks = seq(0, 100, by = 25), limits = c(0, 100))+
xlim(c(-100, 100)) +
scale_x_continuous(breaks = seq(-80, 80, by = 50), limits = c(-80,80))
```

\newpage

# Relationship between Mood and SubjPE

```{r echo=FALSE, warning=FALSE, message=FALSE}

correlations_M <- df_merged %>%
  group_by(Random_ID) %>%
  summarise(correlation = cor(Response_H, Response_SubjPE, use = "complete.obs")) %>%
  mutate(label = paste("R = ", round(correlation, digits = 2))) 

# calculate the average correlation across all individuals and print it 
average_correlation <- mean(correlations_M$correlation, na.rm = TRUE)
message_to_print_H <- paste("average correlation between mood and SubjPE:", average_correlation)

print(message_to_print_H)

ggplot(df_merged, aes(x = Response_SubjPE, y = Response_H, color = Social_Anxiety, group= Social_Anxiety)) +
  geom_point(aes(color=Social_Anxiety, alpha = 0.3)) +
  geom_smooth(method = "lm", color="blue", aes(group=Random_ID)) + 
  # labs(color="Legend") +
  theme_minimal() +
  xlab("SubjPE: feedback - prediction") + 
  ylab("Mood") +
    facet_wrap(~ Random_ID, scales = "free") +
    geom_text(data=correlations_M, aes(x=Inf, y=Inf, label=label, group=Random_ID), hjust=1.1, vjust=1.1, size=2.7, fontface = "bold", inherit.aes=FALSE) +
    theme(strip.text = element_text(size = 6),
        axis.text.x = element_text(size = 5.5),  
        axis.text.y = element_text(size = 5.5),  
        strip.text.x = element_text(face = "bold"),  
        strip.text.y = element_text(face = "bold"),  
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank()) +
  ylim(c(0, 100)) + 
  scale_y_continuous(breaks = seq(0, 100, by = 25), limits = c(0, 100))+
  xlim(c(-100, 100)) + 
  scale_x_continuous(breaks = seq(-80, 80, by = 50), limits = c(-80,80))
  
```



\newpage



\newpage

# Prediction before performance over time

Red line presents until what points histograms were presented (4 first trials only).

```{r echo=FALSE, warning=FALSE, message=FALSE}
ggplot(df_merged, aes(x = Trial.Number, y = Response_pred)) +
  geom_line(color = "blue") +
  geom_vline(xintercept = 5, linetype = "dashed", color = "red") + 
  theme_minimal() +
  labs(title = "Prediction before performance across time",
       x = "Trial Number",
       y = "Pre performance prediction",
       color = "") +
  facet_wrap(~ Random_ID, ncol = 6) + 
  theme(strip.text = element_text(size = 6)) +  
  scale_x_continuous(breaks = seq(1, 48, by = 10), limits = c(1, 48)) +
  scale_y_continuous(breaks = seq(0, 100, by = 21), limits = c(0, 100))+
  theme(axis.text.x = element_text(size = 5),axis.text.y = element_text(size = 5))

```

\newpage

# Stress levels and social anxiety


```

\newpage

# LME models for Mood and SubjPE

The best model seems to be: Mood \~ SubjPE + mini_SPIN_total + (SubjPE \| Random_ID)

```{r echo=FALSE, warning=FALSE, message=FALSE}

model1 <- lme4::lmer(Response_H ~ Response_SubjPE +  (Response_SubjPE | Random_ID), data = df_merged, control=lmerControl(optimizer="bobyqa"))
model2 <- lme4::lmer(Response_H ~ Response_SubjPE +  mini_SPIN_total + (1 | Random_ID), data = df_merged, control=lmerControl(optimizer="bobyqa"))
model3 <- lme4::lmer(Response_H ~ Response_SubjPE + mini_SPIN_total + (Response_SubjPE | Random_ID), data = df_merged, control=lmerControl(optimizer="bobyqa"))
model4 <- lme4::lmer(Response_H ~ Response_SubjPE + Social_Anxiety + (Response_SubjPE | Random_ID), data = df_merged, control=lmerControl(optimizer="bobyqa"))
AIC(model1)
AIC(model2)
AIC(model3)
AIC(model4)


coef_fixed <- fixef(model3)
intercept_Response_H <- coef_fixed[1]
slope_Response_H <- coef_fixed[2]
standard_beta_Response_SubjPE <- parameters:: standardise_parameters (model3)

# standard errors for intercept and slope
CI_multiplier <- 1.96  # 95% CI multiplier for a normal distribution
# Extract the standard errors for intercept and slope from the model summary
model_summary <- summary(model3)
SE_intercept <- model_summary$coefficients[1, "Std. Error"]  # Standard error for the intercept
SE_slope <- model_summary$coefficients[2, "Std. Error"]      # Standard error for the slope



# Creating a sequence of `SubjPE` values for prediction
Response_SubjPE_range <- seq(min(df_merged$Response_SubjPE), max(df_merged$Response_SubjPE), length.out = 100)

# Calculating predicted Response_Ax and its CI bounds across the SubjPE range
predicted_Response_H <- intercept_Response_H + slope_Response_H * Response_SubjPE_range
CI_lower <- predicted_Response_H - CI_multiplier * sqrt(SE_intercept^2 + (Response_SubjPE_range^2 * SE_slope^2))
CI_upper <- predicted_Response_H + CI_multiplier * sqrt(SE_intercept^2 + (Response_SubjPE_range^2 * SE_slope^2))

# Preparing a data frame for ggplot
CI_data <- data.frame(Response_SubjPE=Response_SubjPE_range, CI_lower=CI_lower, CI_upper=CI_upper)


ggplot(df_merged, aes(x=Response_SubjPE, y=Response_H)) +
  # Adding points from your dataset
  # geom_point() +
  # Adding a regression line
  geom_abline(intercept=intercept_Response_H, slope=slope_Response_H, color="darkgoldenrod1", linetype="dashed", size=1) +
  # Adding the confidence interval with geom_ribbon
  geom_ribbon(data=CI_data, aes(x=Response_SubjPE, ymin=CI_lower, ymax=CI_upper), fill="gray80", alpha=0.5, inherit.aes = FALSE) +
  # Further customization
  xlab("Social PE") + 
  ylab("Mood") +
  ggtitle("", subtitle=paste("Estimated slopes of the association in n = ", length(unique(df_merged$Random_ID)))) +
  theme(plot.title=element_text(size=12), plot.subtitle=element_text(size=10),
        legend.title=element_text(size=12), legend.text=element_text(size=12),
        axis.title=element_text(size=13),
        axis.text=element_text(size=12),
        panel.background=element_blank(), panel.grid.major=element_blank(), panel.grid.minor=element_blank(),
        panel.border=element_rect(colour="black", fill=NA)) +
  annotate("label", x=12, y=55, label=paste("beta =", round(standard_beta_Response_SubjPE$Std_Coefficient[2],2), ", 95%CI =", 
                                            round(standard_beta_Response_SubjPE$CI_low[2],2), "-", round(standard_beta_Response_SubjPE$CI_high[2],2))) +
  scale_y_continuous(breaks=seq(0, 100, by=20), limits=c(0, 100)) +
  scale_x_continuous(breaks=seq(-80, 80, by=40), limits=c(-80, 80))

```

\newpage

# LME models for Anxiety and SubjPE

The best model seems to be: Anxiety \~ SubjPE + mini_SPIN_total + (SubjPE \| Random_ID)

```{r echo=FALSE, warning=FALSE, message=FALSE}
model1 <- lme4::lmer(Response_Ax ~ Response_SubjPE +  (Response_SubjPE | Random_ID), data = df_merged, control=lmerControl(optimizer="bobyqa"))
model2 <- lme4::lmer(Response_Ax ~ Response_SubjPE +  mini_SPIN_total + (1 | Random_ID), data = df_merged, control=lmerControl(optimizer="bobyqa"))
model3 <- lme4::lmer(Response_Ax ~ Response_SubjPE + mini_SPIN_total + (Response_SubjPE | Random_ID), data = df_merged, control=lmerControl(optimizer="bobyqa"))
model4 <- lme4::lmer(Response_Ax ~ Response_SubjPE + Social_Anxiety + (Response_SubjPE | Random_ID), data = df_merged, control=lmerControl(optimizer="bobyqa"))

AIC(model1)
AIC(model2)
AIC(model3)
AIC(model4)
coef_fixed <- fixef(model3)
intercept_Response_Ax <- coef_fixed[1]
slope_Response_Ax <- coef_fixed[2]
standard_beta_Response_SubjPE <- parameters:: standardise_parameters (model3)

#standard errors for intercept and slope
CI_multiplier <- 1.96  # 95% CI multiplier for a normal distribution
# Extract the standard errors for intercept and slope from the model summary
model_summary <- summary(model3)
SE_intercept <- model_summary$coefficients[1, "Std. Error"]  # Standard error for the intercept
SE_slope <- model_summary$coefficients[2, "Std. Error"]      # Standard error for the slope



# Creating a sequence of `SubjPE` values for prediction
Response_SubjPE_range <- seq(min(df_merged$Response_SubjPE), max(df_merged$Response_SubjPE), length.out = 100)

# Calculating predicted Response_Ax and its CI bounds across the SubjPE range
predicted_Response_Ax <- intercept_Response_Ax + slope_Response_Ax * Response_SubjPE_range
CI_lower <- predicted_Response_Ax - CI_multiplier * sqrt(SE_intercept^2 + (Response_SubjPE_range^2 * SE_slope^2))
CI_upper <- predicted_Response_Ax + CI_multiplier * sqrt(SE_intercept^2 + (Response_SubjPE_range^2 * SE_slope^2))

# Preparing a data frame for ggplot
CI_data <- data.frame(Response_SubjPE=Response_SubjPE_range, CI_lower=CI_lower, CI_upper=CI_upper)


ggplot(df_merged, aes(x=Response_SubjPE, y=Response_Ax)) +
  # Adding points from your dataset
  # geom_point() +
  # Adding a regression line
  geom_abline(intercept=intercept_Response_Ax, slope=slope_Response_Ax, color="darkgoldenrod1", linetype="dashed", size=1) +
  # Adding the confidence interval with geom_ribbon
  geom_ribbon(data=CI_data, aes(x=Response_SubjPE, ymin=CI_lower, ymax=CI_upper), fill="gray80", alpha=0.5, inherit.aes = FALSE) +
  # Further customization
  xlab("Social PE") + 
  ylab("Anxiety") +
  ggtitle("", subtitle=paste("Estimated slopes of the association in n = ", length(unique(final_df_18_25_Pro$Random_ID)))) +
  theme(plot.title=element_text(size=12), plot.subtitle=element_text(size=10),
        legend.title=element_text(size=12), legend.text=element_text(size=12),
        axis.title=element_text(size=13),
        axis.text=element_text(size=12),
        panel.background=element_blank(), panel.grid.major=element_blank(), panel.grid.minor=element_blank(),
        panel.border=element_rect(colour="black", fill=NA)) +
  annotate("label", x=12, y=55, label=paste("beta =", round(standard_beta_Response_SubjPE$Std_Coefficient[2],2), ", 95%CI =", 
                                            round(standard_beta_Response_SubjPE$CI_low[2],2), "-", round(standard_beta_Response_SubjPE$CI_high[2],2))) +
  scale_y_continuous(breaks=seq(0, 100, by=20), limits=c(0, 100)) +
  scale_x_continuous(breaks=seq(-80, 80, by=40), limits=c(-80, 80))
```

\newpage

# LME models for Mood and Expectation

```{r echo=FALSE, warning=FALSE, message=FALSE}
model1 <- lme4::lmer(Response_H ~ Response_pred +  (Response_pred | Random_ID), data = df_merged, control=lmerControl(optimizer="bobyqa"))
model2 <- lme4::lmer(Response_H ~ Response_pred +  mini_SPIN_total + (1 | Random_ID), data = df_merged, control=lmerControl(optimizer="bobyqa"))
model3 <- lme4::lmer(Response_H ~ Response_pred + mini_SPIN_total + (Response_pred | Random_ID), data = df_merged, control=lmerControl(optimizer="bobyqa"))
model4 <- lme4::lmer(Response_H ~ Response_pred + Social_Anxiety + (Response_pred | Random_ID), data = df_merged, control=lmerControl(optimizer="bobyqa"))

AIC(model1)
AIC(model2)
AIC(model3)
AIC(model4)

coef_fixed <- fixef(model4)
intercept_Response_H <- coef_fixed[1]
slope_Response_H <- coef_fixed[2]
standard_beta_Response_pred <- parameters:: standardise_parameters (model4)

CI_multiplier <- 1.96  # 95% CI multiplier for a normal distribution
model_summary <- summary(model3)
SE_intercept <- model_summary$coefficients[1, "Std. Error"]  # Standard error for the intercept
SE_slope <- model_summary$coefficients[2, "Std. Error"]      # Standard error for the slope

# Creating a sequence of `pred` values for prediction
Response_pred_range <- seq(min(df_merged$Response_pred), max(df_merged$Response_pred), length.out = 100)

# Calculating predicted Response_H and its CI bounds across the SubjPE range
predicted_Response_H <- intercept_Response_H + slope_Response_H * Response_pred_range
CI_lower <- predicted_Response_H - CI_multiplier * sqrt(SE_intercept^2 + (Response_pred_range^2 * SE_slope^2))
CI_upper <- predicted_Response_H + CI_multiplier * sqrt(SE_intercept^2 + (Response_pred_range^2 * SE_slope^2))

# Preparing a data frame for ggplot
CI_data <- data.frame(Response_pred=Response_pred_range, CI_lower=CI_lower, CI_upper=CI_upper)


ggplot(df_merged, aes(x=Response_pred, y=Response_H)) +
  # Adding points from your dataset
  # geom_point() +
  # Adding a regression line
  geom_abline(intercept=intercept_Response_H, slope=slope_Response_H, color="darkgoldenrod1", linetype="dashed", size=1) +
  # Adding the confidence interval with geom_ribbon
  geom_ribbon(data=CI_data, aes(x=Response_pred, ymin=CI_lower, ymax=CI_upper), fill="gray80", alpha=0.5, inherit.aes = FALSE) +
  # Further customization
  xlab("Social PE") + 
  ylab("Mood") +
  ggtitle("", subtitle=paste("Estimated slopes of the association in n = ", length(unique(final_df_students$Random_ID)))) +
  theme(plot.title=element_text(size=12), plot.subtitle=element_text(size=10),
        legend.title=element_text(size=12), legend.text=element_text(size=12),
        axis.title=element_text(size=13),
        axis.text=element_text(size=12),
        panel.background=element_blank(), panel.grid.major=element_blank(), panel.grid.minor=element_blank(),
        panel.border=element_rect(colour="black", fill=NA)) +
  annotate("label", x=12, y=55, label=paste("beta =", round(standard_beta_Response_pred$Std_Coefficient[2],2), ", 95%CI =", 
                                            round(standard_beta_Response_pred$CI_low[2],2), "-", round(standard_beta_Response_pred$CI_high[2],2))) +
  scale_y_continuous(breaks=seq(0, 100, by=20), limits=c(0, 100)) +
  scale_x_continuous(breaks=seq(-80, 80, by=40), limits=c(-80, 80))





```

\newpage

# LME models for Anxiety and Expectation

```{r echo=FALSE, warning=FALSE, message=FALSE}
model1 <- lme4::lmer(Response_Ax ~ Response_pred +  (Response_pred | Random_ID), data = df_merged, control=lmerControl(optimizer="bobyqa"))
model2 <- lme4::lmer(Response_Ax ~ Response_pred +  mini_SPIN_total + (1 | Random_ID), data = df_merged, control=lmerControl(optimizer="bobyqa"))
model3 <- lme4::lmer(Response_Ax ~ Response_pred + mini_SPIN_total + (Response_pred | Random_ID), data = df_merged, control=lmerControl(optimizer="bobyqa"))
model4 <- lme4::lmer(Response_Ax ~ Response_pred + Social_Anxiety + (Response_pred | Random_ID), data = df_merged, control=lmerControl(optimizer="bobyqa"))

AIC(model1)
AIC(model2)
AIC(model3)
AIC(model4)

coef_fixed <- fixef(model4)
intercept_Response_Ax <- coef_fixed[1]
slope_Response_Ax <- coef_fixed[2]
standard_beta_Response_pred <- parameters:: standardise_parameters (model4)

CI_multiplier <- 1.96  # 95% CI multiplier for a normal distribution
model_summary <- summary(model3)
SE_intercept <- model_summary$coefficients[1, "Std. Error"]  # Standard error for the intercept
SE_slope <- model_summary$coefficients[2, "Std. Error"]      # Standard error for the slope

# Creating a sequence of `pred` values for prediction
Response_pred_range <- seq(min(df_merged$Response_pred), max(df_merged$Response_pred), length.out = 100)

# Calculating predicted Response_H and its CI bounds across the SubjPE range
  predicted_Response_Ax <- intercept_Response_Ax + slope_Response_Ax * Response_pred_range
CI_lower <- predicted_Response_Ax - CI_multiplier * sqrt(SE_intercept^2 + (Response_pred_range^2 * SE_slope^2))
CI_upper <- predicted_Response_Ax + CI_multiplier * sqrt(SE_intercept^2 + (Response_pred_range^2 * SE_slope^2))

# Preparing a data frame for ggplot
CI_data <- data.frame(Response_pred=Response_pred_range, CI_lower=CI_lower, CI_upper=CI_upper)


ggplot(df_merged, aes(x=Response_pred, y=Response_Ax)) +
  # Adding points from your dataset
  # geom_point() +
  # Adding a regression line
  geom_abline(intercept=intercept_Response_Ax, slope=slope_Response_Ax, color="darkgoldenrod1", linetype="dashed", size=1) +
  # Adding the confidence interval with geom_ribbon
  geom_ribbon(data=CI_data, aes(x=Response_pred, ymin=CI_lower, ymax=CI_upper), fill="gray80", alpha=0.5, inherit.aes = FALSE) +
  # Further customization
  xlab("Social PE") + 
  ylab("Mood") +
  ggtitle("", subtitle=paste("Estimated slopes of the association in n = ", length(unique(final_df_students$Random_ID_new)))) +
  theme(plot.title=element_text(size=12), plot.subtitle=element_text(size=10),
        legend.title=element_text(size=12), legend.text=element_text(size=12),
        axis.title=element_text(size=13),
        axis.text=element_text(size=12),
        panel.background=element_blank(), panel.grid.major=element_blank(), panel.grid.minor=element_blank(),
        panel.border=element_rect(colour="black", fill=NA)) +
  annotate("label", x=12, y=55, label=paste("beta =", round(standard_beta_Response_pred$Std_Coefficient[2],2), ", 95%CI =", 
                                            round(standard_beta_Response_pred$CI_low[2],2), "-", round(standard_beta_Response_pred$CI_high[2],2))) +
  scale_y_continuous(breaks=seq(0, 100, by=20), limits=c(0, 100)) +
  scale_x_continuous(breaks=seq(-80, 80, by=40), limits=c(-80, 80))





```

# LME models for Mood and Outcome

```{r}
model1 <- lme4::lmer(Response_H ~ Response_fdbk +  (Response_fdbk | Random_ID), data = df_merged, control=lmerControl(optimizer="bobyqa"))
model2 <- lme4::lmer(Response_H ~ Response_fdbk +  mini_SPIN_total + (1 | Random_ID), data = df_merged, control=lmerControl(optimizer="bobyqa"))
model3 <- lme4::lmer(Response_H ~ Response_fdbk + mini_SPIN_total + (Response_fdbk | Random_ID), data = df_merged, control=lmerControl(optimizer="bobyqa"))
model4 <- lme4::lmer(Response_H ~ Response_fdbk + Social_Anxiety + (Response_fdbk | Random_ID), data = df_merged, control=lmerControl(optimizer="bobyqa"))

AIC(model1)
AIC(model2)
AIC(model3)
AIC(model4)

coef_fixed <- fixef(model4)
intercept_Response_H <- coef_fixed[1]
slope_Response_H <- coef_fixed[2]
standard_beta_Response_fdbk <- parameters:: standardise_parameters (model4)
```

# LME models for Anxiety and Outcome

```{r}
model1 <- lme4::lmer(Response_Ax ~ Response_fdbk +  (Response_fdbk | Random_ID), data = df_merged, control=lmerControl(optimizer="bobyqa"))
model2 <- lme4::lmer(Response_Ax ~ Response_fdbk +  mini_SPIN_total + (1 | Random_ID), data = df_merged, control=lmerControl(optimizer="bobyqa"))
model3 <- lme4::lmer(Response_Ax ~ Response_fdbk + mini_SPIN_total + (Response_fdbk | Random_ID), data = df_merged, control=lmerControl(optimizer="bobyqa"))
model4 <- lme4::lmer(Response_Ax ~ Response_fdbk + Social_Anxiety + (Response_fdbk | Random_ID), data = df_merged, control=lmerControl(optimizer="bobyqa"))

AIC(model1)
AIC(model2)
AIC(model3)
AIC(model4)

coef_fixed <- fixef(model4)
intercept_Response_Ax <- coef_fixed[1]
slope_Response_Ax <- coef_fixed[2]
standard_beta_Response_fdbk <- parameters:: standardise_parameters (model4)
```

\newpage

# ICC for Mood

```{r echo=FALSE, warning=FALSE, message=FALSE}
test_icc_id <- lmer(Response_H ~  (1| Random_ID), data = 
                      df_merged, 
                    REML = FALSE, 
                    control = lmerControl(optimizer = "bobyqa")) 
icc_results_id <- performance::icc(test_icc_id)

icc_results_id
```

\newpage

# ICC for Anxiety

```{r echo=FALSE, warning=FALSE, message=FALSE}
test_icc_id <- lmer(Response_Ax ~  (1| Random_ID), data = 
                      df_merged, 
                    REML = FALSE, 
                    control = lmerControl(optimizer = "bobyqa")) 
icc_results_id <- performance::icc(test_icc_id)

icc_results_id
```
