---
title: "Surprise study pilot 21"
author: "Marjan Biria"
date: "2124-04-08"
output: 
    pdf_document:
    toc: true
    toc_depth: 2
    toc_float: true
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(root.dir = "aim_lab_1", echo = TRUE)
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
library(dplyr)
library(ggplot2)
library(tidyr)
library(lme4)
library(parameters)
library(broom.mixed)
library(purrr)
library(conflicted)
library(stringr)
library(readxl)
```


\newpage
# Study description

This study is the same as pilot 19, except we have now removed the second prediction after the feedback and replaced the image of the judges with real images of our relatives/friends.

The Gorilla experiment is the following: https://app.gorilla.sc/admin/project/130203
The task is the following: https://app.gorilla.sc/admin/task/799523/editor



```{r echo=FALSE, warning=FALSE, message=FALSE}
# v3 and v4 have exactly the same task version, but BIQ was causing a problem due to a Gorilla update and it was changed in version 4
df21_raw_part1 <- read.csv("/Users/elenabagdades/Library/CloudStorage/OneDrive-UniversityCollegeLondon/Desktop/GitHub/aim_lab_1/De_identified_data/surprise_pilot_21/SUP_PRF_p21_vid_bigPE_nohist_newjud_v3/SUP_PRF_p21_vid_bigPE_nohist_newjud_v3_task_main.csv")
df21_spin_part1 <- read.csv("/Users/elenabagdades/Library/CloudStorage/OneDrive-UniversityCollegeLondon/Desktop/GitHub/aim_lab_1/De_identified_data/surprise_pilot_21/SUP_PRF_p21_vid_bigPE_nohist_newjud_v3/SUP_PRF_p21_vid_bigPE_nohist_newjud_v3_mini_spin.csv")
df21_cesd_part1 <- read.csv("/Users/elenabagdades/Library/CloudStorage/OneDrive-UniversityCollegeLondon/Desktop/GitHub/aim_lab_1/De_identified_data/surprise_pilot_21/SUP_PRF_p21_vid_bigPE_nohist_newjud_v3/SUP_PRF_p21_vid_bigPE_nohist_newjud_v3_ces_d.csv")

df21_raw_part2 <- read.csv("/Users/elenabagdades/Library/CloudStorage/OneDrive-UniversityCollegeLondon/Desktop/GitHub/aim_lab_1/De_identified_data/surprise_pilot_21/SUP_PRF_p21_vid_bigPE_nohist_newjud_v4/SUP_PRF_p21_vid_bigPE_nohist_newjud_v4_task_main.csv")
df21_spin_part2 <- read.csv("/Users/elenabagdades/Library/CloudStorage/OneDrive-UniversityCollegeLondon/Desktop/GitHub/aim_lab_1/De_identified_data/surprise_pilot_21/SUP_PRF_p21_vid_bigPE_nohist_newjud_v4/SUP_PRF_p21_vid_bigPE_nohist_newjud_v4_mini_spin.csv")
df21_cesd_part2 <- read.csv("/Users/elenabagdades/Library/CloudStorage/OneDrive-UniversityCollegeLondon/Desktop/GitHub/aim_lab_1/De_identified_data/surprise_pilot_21/SUP_PRF_p21_vid_bigPE_nohist_newjud_v4/SUP_PRF_p21_vid_bigPE_nohist_newjud_v4_ces_d.csv")

df21_raw <- rbind(df21_raw_part1, df21_raw_part2)
df21_spin <- rbind(df21_spin_part1, df21_spin_part2)
df21_cesd <- rbind(df21_cesd_part1, df21_cesd_part2)

```


```{r echo=FALSE, warning=FALSE, message=FALSE}
# extract CES-D scores
CESD_data_clean <- df21_cesd[, c(32, 34, 36, 38, 40, 42, 44, 46,48,50,
                                 52, 54, 56, 58, 60, 62, 64, 66, 68, 70, 71 )]
# Identify non-ID variable columns
non_id_cols <- setdiff(names(CESD_data_clean), "Random_ID")

# Convert non-ID variables to numeric
CESD_data_clean[, non_id_cols] <- lapply(CESD_data_clean[, non_id_cols], as.numeric)

#change numbers to match CES-D scoring system
excluded_columns <-  c("Random_ID", "Multiple.Choice.Grid.object.3.4...I.felt.I.was.just.as.good.as.other.people..Quantised",
                       "Multiple.Choice.Grid.object.3.8...I.felt.hopeful.about.the.future..Quantised",
                       "Multiple.Choice.Grid.object.3.12...I.was.happy..Quantised",
                       "Multiple.Choice.Grid.object.3.16...I.enjoyed.life..Quantised")
                  

CESD_data_clean<- CESD_data_clean %>%
  mutate(across(-excluded_columns , ~ case_when(
    . == 1 ~ 0,
    . == 2 ~ 1,
    . == 3 ~ 2,
    . == 4 ~ 3,
    TRUE ~ .
  )))


other_columns <- c("Multiple.Choice.Grid.object.3.4...I.felt.I.was.just.as.good.as.other.people..Quantised",
                   "Multiple.Choice.Grid.object.3.8...I.felt.hopeful.about.the.future..Quantised",
                   "Multiple.Choice.Grid.object.3.12...I.was.happy..Quantised",
                   "Multiple.Choice.Grid.object.3.16...I.enjoyed.life..Quantised")
CESD_data_clean<- CESD_data_clean %>%
  mutate(across(other_columns , ~ case_when(
    . == 1 ~ 3,
    . == 2 ~ 2,
    . == 3 ~ 1,
    . == 4 ~ 0,
    TRUE ~ .
  )))

#scoring----
CESD_scores <-  numeric(length(CESD_data_clean$Random_ID))
CESD_scores <- 0
Questions <- c(1:20)

for (i in 1:nrow(CESD_data_clean)) {
  CESD_score <- sum(CESD_data_clean[i, Questions])
  CESD_scores[i] <- CESD_score
}

CESD_data_clean$CESD_score <-  CESD_scores

CESD_data_clean$Depression_Threshold<- 0
CESD_data_clean$Depression_status <- "Not_Depressed"

#Assign "1" if they meet Depression threshold 
for (i in 1:nrow(CESD_data_clean)) {
  if (CESD_data_clean$CESD_score[i] >= 16) {
    CESD_data_clean$Depression_Threshold[i] <- 1
    CESD_data_clean$Depression_status[i] <- "Depressed"
  }
}
```


```{r echo=FALSE, warning=FALSE, message=FALSE}
# We have now different names for different screens:
# Prediction (how well do you think you performed?)
# prediction_2 (how well do you think you performed?)
# feedback (This is how well X thought you performed)
# First 4 trials are with the histograms and are called "Trials_Histogram" in Display column instead of "Trials"
# The trial numbers start from 1 again after the histograms so we need to concatenate them all.
# Let's rename them to "Trials" to extract them together with the rest of the trials

df21_raw$Trial.Number[df21_raw$Display == "Trials "] <- df21_raw$Trial.Number[df21_raw$Display == "Trials "] + 4

df21_raw <- df21_raw %>%
  mutate(Screen = if_else(Screen == "Prediction", "Prediction ", Screen))


df21_raw <- df21_raw %>%
  mutate(Display = if_else(Display == "Trials_Histogram", "Trials ", Display))

df21_spin <- df21_spin %>%
  rename(
   "Q1" =  "Rating.Scale.object.2.Fear.of.embarrassment.causes.me.to.avoid.doing.things.or.speaking.to.people.",
   "Q2" =  "Rating.Scale.object.2.I.avoid.activities.in.which.I.am.the.center.of.attention.",
   "Q3" = "Rating.Scale.object.2.Being.embarrassed.or.looking.stupid.are.among.my.worst.fears."
  )

df21_spin <- df21_spin %>%
  rowwise() %>%
  mutate(mini_SPIN_total = sum(c(Q1, Q2, Q3), na.rm = TRUE)) %>%
  ungroup()


# create a new df21 that only keeps the columns we need
df21 <- df21_raw[, c("Trial.Number", "Display", "Screen", "Response.Type", "Response", 
                     "Reaction.Time", "Spreadsheet..Histogram", "Spreadsheet..Feedback", "Random_ID")]

df21 <- df21 %>% dplyr::filter(Response.Type != "info")

df21 <- df21 %>%
  mutate(Response = as.numeric(as.character(Response))) %>%
  dplyr::filter(!is.na(Response))

df21$Screen <- ifelse(df21$Trial.Number == 1 & (df21$Display == "Mood " | df21$Display == "Anxiety "), "BL_1",
                      ifelse(df21$Trial.Number == 2 & (df21$Display == "Mood " | df21$Display == "Anxiety "), "BL_2", 
                             df21$Screen))

df21$m_hist <- ifelse(df21$Spreadsheet..Histogram == "h2.png", 29,
                             ifelse(df21$Spreadsheet..Histogram == "h3.png", 37,
                                                  ifelse(df21$Spreadsheet..Histogram == "h6.png", 63,
                                                         ifelse(df21$Spreadsheet..Histogram == "h7.png", 71, NA))))  


# get rid of the rows we don't need: practice runs, continue button presses etc. and only keep Trials, Anxiety and Mood that include all variables we are interested in:
df21 <- df21 %>%
  dplyr::filter(
    (Display == "Trials ") |
      (Display == "Exit") |
      (Display == "Anxiety " & !Trial.Number %in% c(1, 2)) |
      (Display == "Mood " & !Trial.Number %in% c(1, 2)) 
  )

# # setting Mood and Anxiety trial numbers to match the trials starting from 1 (since we removed the baseline ones above)
df21$Trial.Number <- ifelse(df21$Display == 'Mood ' | df21$Display == 'Anxiety ', df21$Trial.Number - 2, df21$Trial.Number)
df21$Display <- ifelse(df21$Display == 'Mood ' | df21$Display == 'Anxiety ', "Trials", df21$Display)

# renaming the feedback column to fdbk
names(df21)[names(df21) == 'Spreadsheet..Feedback'] <- 'fdbk'

# Now let's create columns for PE (fdbk-hist) and Subj_PE (fdbk_Prediction)

df21$SubjPE <- ifelse(df21$Screen == "Prediction ", df21$fdbk - df21$Response, NA)
df21$PE <- ifelse(df21$Screen == "Prediction ", df21$fdbk - df21$m_hist, NA)
# to keep just one repetition of feedback and mean histogram per trial per subject 
# and replace the rest with NA so that when we want to convert to long format we won't have duplicates
df21$fdbk <- ifelse(df21$Screen == "Prediction ", df21$fdbk, NA)
df21$m_hist <- ifelse(df21$Screen == "Prediction ", df21$m_hist, NA)
df21$stress_level <- ifelse(df21$Screen == "Screen 12", df21$Response, NA)

long_df21 <- df21 %>%
  dplyr::select(Random_ID, Trial.Number, fdbk, m_hist, PE, SubjPE, stress_level) %>%
  pivot_longer(cols = c(fdbk, m_hist, PE, SubjPE, stress_level),
               names_to = "Screen",
               values_to = "Response")

# This will keep only the rows where 'Response' is not NA
long_df21 <- long_df21[!is.na(long_df21$Response), ]

# Selecting relevant columns from the original df21
df21 <- df21 %>%
  dplyr::select(-c(fdbk, m_hist, PE, SubjPE, stress_level))

# Binding the rows together
df21 <- bind_rows(df21, long_df21)

df21$Response <- as.numeric(df21$Response)

# looking at the relationship between PE and SubjPE
df21_PE <- subset(df21, Screen == "PE")
names(df21_PE)[names(df21_PE) == "Screen"] <- "Screen_PE"
names(df21_PE)[names(df21_PE) == "Response"] <- "Response_PE"

df21_SubjPE <- subset(df21, Screen == "SubjPE")
names(df21_SubjPE)[names(df21_SubjPE) == "Screen"] <- "Screen_SubjPE"
names(df21_SubjPE)[names(df21_SubjPE) == "Response"] <- "Response_SubjPE"

df21_fdbk <- subset(df21, Screen == "fdbk")
names(df21_fdbk)[names(df21_fdbk) == "Screen"] <- "Screen_fdbk"
names(df21_fdbk)[names(df21_fdbk) == "Response"] <- "Response_fdbk"

df21_hist <- subset(df21, Screen == "m_hist")
names(df21_hist)[names(df21_hist) == "Screen"] <- "Screen_m_hist"
names(df21_hist)[names(df21_hist) == "Response"] <- "Response_m_hist"

df21_stress_level <- subset(df21, Screen == "Screen 12")
names(df21_stress_level)[names(df21_stress_level) == "Screen"] <- "Screen_stress_level"
names(df21_stress_level)[names(df21_stress_level) == "Response"] <- "Response_stress_level"

df21_predic <- subset(df21, Screen == "Prediction ")
names(df21_predic)[names(df21_predic) == "Screen"] <- "Screen_pred"
names(df21_predic)[names(df21_predic) == "Response"] <- "Response_pred"


# df21_cert <- subset(df21, Screen == "Certainty rating ")
# names(df21_cert)[names(df21_cert) == "Screen"] <- "Screen_certainty"
# names(df21_cert)[names(df21_cert) == "Response"] <- "Response_certainty"

list_of_dfs_21 <- list(df21_PE, df21_fdbk, df21_hist, df21_predic, df21_SubjPE)

# Using reduce with inner_join
merged_df21 <- reduce(list_of_dfs_21, inner_join, by = c("Random_ID", "Trial.Number"))

df21_Anxious <- subset(df21, Screen == "Anxious")
names(df21_Anxious)[names(df21_Anxious) == "Screen"] <- "Screen_Ax"
names(df21_Anxious)[names(df21_Anxious) == "Response"] <- "Response_Ax"

df21_Happy <- subset(df21, Screen == "Happy")
# df21_fdbk <- subset(df21, Screen == "Prediction")
names(df21_Happy)[names(df21_Happy) == "Screen"] <- "Screen_H"
names(df21_Happy)[names(df21_Happy) == "Response"] <- "Response_H"

final_df21 <- merged_df21 %>%
  inner_join(df21_Anxious, by = c("Random_ID", "Trial.Number")) %>%
  inner_join(df21_Happy, by = c("Random_ID", "Trial.Number"))


# subset only the columns we are interested in
final_df21 <- final_df21[c("Trial.Number", "Random_ID", "Response_H", "Response_Ax", "Response_fdbk", "Response_SubjPE", "Response_PE", "Response_m_hist", "Response_pred")]

final_df21 <- final_df21 %>%
  left_join(df21_spin %>% dplyr::select(Random_ID, mini_SPIN_total), by = "Random_ID")

final_df21 <- final_df21 %>%
  left_join(df21_stress_level %>% dplyr::select(Random_ID, Response_stress_level), by = "Random_ID")

final_df21 <- final_df21 %>%
  left_join(CESD_data_clean %>% dplyr::select(Random_ID, CESD_score, Depression_Threshold, Depression_status), by = "Random_ID")

final_df21$Social_Anxiety <- ifelse(final_df21$mini_SPIN_total >= 6, "high", "low")


write.csv(final_df21, "pilot_21_variables.csv", row.names = FALSE)


final_df21 %>%
  group_by(Random_ID) %>%
  summarise(Trial.Number = n())

write.csv(final_df21, "final_df21_with_stresslevels.csv", row.names = FALSE)

```



\newpage 
# Relationship between prediction and mean histograms (4x only in the beginning)


```{r echo=FALSE, warning=FALSE, message=FALSE}
correlations <- final_df21 %>%
  group_by(Random_ID) %>%
  summarise(correlation = cor(Response_m_hist, Response_pred, method = "spearman", use = "complete.obs")) %>%
  mutate(label = paste("R = ", round(correlation, digits = 2)))

# # calculate the average correlation across all individuals and print it
average_correlation <- mean(correlations$correlation, na.rm = TRUE)
message_to_print_H <- paste("average correlation between mean_hist and prediction:", average_correlation)

print(message_to_print_H)

ggplot(final_df21, aes(x = Response_m_hist, y = Response_pred, color = Social_Anxiety, group= Social_Anxiety)) +
  geom_point(aes(color=Social_Anxiety, alpha = 0.3)) +
  geom_smooth(method = "lm", color="blue", aes(group=Random_ID)) +
  # labs(color="Legend") +
  theme_minimal() +
  xlab("prediction") +
  ylab("mean_histogram") +
    facet_wrap(~ Random_ID, scales = "free") +
    geom_text(data=correlations, aes(x=Inf, y=Inf, label=label, group=Random_ID), hjust=1.1, vjust=1.1, size=2.7, fontface = "bold", inherit.aes=FALSE) +
    theme(strip.text = element_text(size = 6),
        axis.text.x = element_text(size = 5.5),
        axis.text.y = element_text(size = 5.5),
        strip.text.x = element_text(face = "bold"),
        strip.text.y = element_text(face = "bold"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank())
  
```

\newpage 
# Relationship between Anxiety and SubjPE

```{r echo=FALSE, warning=FALSE, message=FALSE}
correlations_Ax <- final_df21 %>%
  group_by(Random_ID) %>%
  summarise(correlation = cor(Response_Ax, Response_SubjPE, use = "complete.obs")) %>%
  mutate(label = paste("R = ", round(correlation, digits = 2))) 

# calculate the average correlation across all individuals and print it 
average_correlation <- mean(correlations_Ax$correlation, na.rm = TRUE)
message_to_print_Ax <- paste("average correlation between anxiety and SubjPE:", average_correlation)

print(message_to_print_Ax)

ggplot(final_df21, aes(x = Response_SubjPE, y = Response_Ax, color = Social_Anxiety, group= Social_Anxiety)) +
  geom_point(aes(color=Social_Anxiety, alpha = 0.3)) +
  geom_smooth(method = "lm", color="blue", aes(group=Random_ID)) + 
  # labs(color="Legend") +
  theme_minimal() +
  xlab("SubjPE: feedback - prediction") + 
  ylab("Anxiety") +
    facet_wrap(~ Random_ID, scales = "free") +
    geom_text(data=correlations_Ax, aes(x=Inf, y=Inf, label=label, group=Random_ID), hjust=1.1, vjust=1.1, size=2.7, fontface = "bold", inherit.aes=FALSE) +
    theme(strip.text = element_text(size = 6),
        axis.text.x = element_text(size = 5.5),  
        axis.text.y = element_text(size = 5.5),  
        strip.text.x = element_text(face = "bold"),  
        strip.text.y = element_text(face = "bold"),  
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank()) +
ylim(c(0, 100)) +
scale_y_continuous(breaks = seq(0, 100, by = 25), limits = c(0, 100))+
xlim(c(-100, 100)) +
scale_x_continuous(breaks = seq(-80, 80, by = 50), limits = c(-80,80))
```

\newpage 
# Relationship between Mood and SubjPE

```{r echo=FALSE, warning=FALSE, message=FALSE}

correlations_M <- final_df21 %>%
  group_by(Random_ID) %>%
  summarise(correlation = cor(Response_H, Response_SubjPE, use = "complete.obs")) %>%
  mutate(label = paste("R = ", round(correlation, digits = 2))) 

# calculate the average correlation across all individuals and print it 
average_correlation <- mean(correlations_M$correlation, na.rm = TRUE)
message_to_print_H <- paste("average correlation between mood and SubjPE:", average_correlation)

print(message_to_print_H)

ggplot(final_df21, aes(x = Response_SubjPE, y = Response_H, color = Social_Anxiety, group= Social_Anxiety)) +
  geom_point(aes(color=Social_Anxiety, alpha = 0.3)) +
  geom_smooth(method = "lm", color="blue", aes(group=Random_ID)) + 
  # labs(color="Legend") +
  theme_minimal() +
  xlab("SubjPE: feedback - prediction") + 
  ylab("Mood") +
    facet_wrap(~ Random_ID, scales = "free") +
    geom_text(data=correlations_M, aes(x=Inf, y=Inf, label=label, group=Random_ID), hjust=1.1, vjust=1.1, size=2.7, fontface = "bold", inherit.aes=FALSE) +
    theme(strip.text = element_text(size = 6),
        axis.text.x = element_text(size = 5.5),  
        axis.text.y = element_text(size = 5.5),  
        strip.text.x = element_text(face = "bold"),  
        strip.text.y = element_text(face = "bold"),  
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank()) +
  ylim(c(0, 100)) + 
  scale_y_continuous(breaks = seq(0, 100, by = 25), limits = c(0, 100))+
  xlim(c(-100, 100)) + 
  scale_x_continuous(breaks = seq(-80, 80, by = 50), limits = c(-80,80))
  
```
\newpage 
# Relationship between Mood and feedback

```{r echo=FALSE, warning=FALSE, message=FALSE}
correlations_Mfd <- final_df21 %>%
  group_by(Random_ID) %>%
  summarise(correlation = cor(Response_H, Response_fdbk, use = "complete.obs")) %>%
  mutate(label = paste("R = ", round(correlation, digits = 2))) 

# calculate the average correlation across all individuals and print it 
average_correlation <- mean(correlations_Mfd$correlation, na.rm = TRUE)
message_to_print_H <- paste("average correlation between mood and feedback:", average_correlation)

print(message_to_print_H)

ggplot(final_df21, aes(x = Response_fdbk, y = Response_H, color = Social_Anxiety, group= Social_Anxiety)) +
  geom_point(aes(color=Social_Anxiety, alpha = 0.3)) +
  geom_smooth(method = "lm", color="blue", aes(group=Random_ID)) + 
  # labs(color="Legend") +
  theme_minimal() +
  xlab("Feedback") + 
  ylab("Mood") +
    facet_wrap(~ Random_ID, scales = "free") +
    geom_text(data=correlations_Mfd, aes(x=Inf, y=Inf, label=label, group=Random_ID), hjust=1.1, vjust=1.1, size=2.7, fontface = "bold", inherit.aes=FALSE) +
    theme(strip.text = element_text(size = 6),
        axis.text.x = element_text(size = 5.5),  
        axis.text.y = element_text(size = 5.5),  
        strip.text.x = element_text(face = "bold"),  
        strip.text.y = element_text(face = "bold"),  
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank()) +
  ylim(c(0, 100)) + 
  scale_y_continuous(breaks = seq(0, 100, by = 25), limits = c(0, 100))+
  xlim(c(-100, 100)) + 
  scale_x_continuous(breaks = seq(0, 100, by = 25), limits = c(0,100))
  
```

\newpage 
# Relationship between Mood and prediction (pre-performance)

```{r echo=FALSE, warning=FALSE, message=FALSE}
correlations <- final_df21 %>%
  group_by(Random_ID) %>%
  summarise(correlation = cor(Response_H, Response_pred, use = "complete.obs")) %>%
  mutate(label = paste("R = ", round(correlation, digits = 2))) 

# calculate the average correlation across all individuals and print it 
average_correlation <- mean(correlations$correlation, na.rm = TRUE)
message_to_print_H <- paste("average correlation between mood and prediction before performance:", average_correlation)

print(message_to_print_H)

ggplot(final_df21, aes(x = Response_pred, y = Response_H, color = Social_Anxiety, group= Social_Anxiety)) +
  geom_point(aes(color=Social_Anxiety, alpha = 0.3)) +
  geom_smooth(method = "lm", color="blue", aes(group=Random_ID)) + 
  # labs(color="Legend") +
  theme_minimal() +
  xlab("Prediction pre performance") + 
  ylab("Mood") +
    facet_wrap(~ Random_ID, scales = "free") +
    geom_text(data=correlations, aes(x=Inf, y=Inf, label=label, group=Random_ID), hjust=1.1, vjust=1.1, size=2.7, fontface = "bold", inherit.aes=FALSE) +
    theme(strip.text = element_text(size = 6),
        axis.text.x = element_text(size = 5.5),  
        axis.text.y = element_text(size = 5.5),  
        strip.text.x = element_text(face = "bold"),  
        strip.text.y = element_text(face = "bold"),  
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank()) +
  ylim(c(0, 100)) + 
  scale_y_continuous(breaks = seq(0, 100, by = 25), limits = c(0, 100))+
  xlim(c(-100, 100)) + 
  scale_x_continuous(breaks = seq(0, 100, by = 25), limits = c(0,100))
  
```



\newpage 
# Relationship between Anxiety and prediction

```{r echo=FALSE, warning=FALSE, message=FALSE}
correlations <- final_df21 %>%
  group_by(Random_ID) %>%
  summarise(correlation = cor(Response_Ax, Response_pred, use = "complete.obs")) %>%
  mutate(label = paste("R = ", round(correlation, digits = 2))) 

# calculate the average correlation across all individuals and print it 
average_correlation <- mean(correlations$correlation, na.rm = TRUE)
message_to_print_H <- paste("average correlation between anxiety and prediction:", average_correlation)

print(message_to_print_H)

ggplot(final_df21, aes(x = Response_pred, y = Response_Ax, color = Social_Anxiety, group= Social_Anxiety)) +
  geom_point(aes(color=Social_Anxiety, alpha = 0.3)) +
  geom_smooth(method = "lm", color="blue", aes(group=Random_ID)) + 
  # labs(color="Legend") +
  theme_minimal() +
  xlab("Pre performance prediction") + 
  ylab("Anxiety") +
    facet_wrap(~ Random_ID, scales = "free") +
    geom_text(data=correlations, aes(x=Inf, y=Inf, label=label, group=Random_ID), hjust=1.1, vjust=1.1, size=2.7, fontface = "bold", inherit.aes=FALSE) +
    theme(strip.text = element_text(size = 6),
        axis.text.x = element_text(size = 5.5),  
        axis.text.y = element_text(size = 5.5),  
        strip.text.x = element_text(face = "bold"),  
        strip.text.y = element_text(face = "bold"),  
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank()) +
  ylim(c(0, 100)) + 
  scale_y_continuous(breaks = seq(0, 100, by = 25), limits = c(0, 100))+
  xlim(c(-100, 100)) + 
  scale_x_continuous(breaks = seq(0, 100, by = 25), limits = c(0,100))
  
```


\newpage 
# Relationship between Anxiety and feedback

```{r echo=FALSE, warning=FALSE, message=FALSE}
correlations <- final_df21 %>%
  group_by(Random_ID) %>%
  summarise(correlation = cor(Response_Ax, Response_fdbk, use = "complete.obs")) %>%
  mutate(label = paste("R = ", round(correlation, digits = 2))) 

# calculate the average correlation across all individuals and print it 
average_correlation <- mean(correlations$correlation, na.rm = TRUE)
message_to_print_H <- paste("average correlation between anxiety and feedback:", average_correlation)

print(message_to_print_H)

ggplot(final_df21, aes(x = Response_fdbk, y = Response_Ax, color = Social_Anxiety, group= Social_Anxiety)) +
  geom_point(aes(color=Social_Anxiety, alpha = 0.3)) +
  geom_smooth(method = "lm", color="blue", aes(group=Random_ID)) + 
  # labs(color="Legend") +
  theme_minimal() +
  xlab("Feedback") + 
  ylab("Anxiety") +
    facet_wrap(~ Random_ID, scales = "free") +
    geom_text(data=correlations, aes(x=Inf, y=Inf, label=label, group=Random_ID), hjust=1.1, vjust=1.1, size=2.7, fontface = "bold", inherit.aes=FALSE) +
    theme(strip.text = element_text(size = 6),
        axis.text.x = element_text(size = 5.5),  
        axis.text.y = element_text(size = 5.5),  
        strip.text.x = element_text(face = "bold"),  
        strip.text.y = element_text(face = "bold"),  
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank()) +
  ylim(c(0, 100)) + 
  scale_y_continuous(breaks = seq(0, 100, by = 25), limits = c(0, 100))+
  xlim(c(-100, 100)) + 
  scale_x_continuous(breaks = seq(0, 100, by = 25), limits = c(0,100))
  
```



```{r echo=FALSE, warning=FALSE, message=FALSE}
# trying to keep the BL_1 and BL_2 mood and anxiety ratings
df21_with_BL <- df21_raw[, c("Trial.Number", "Display", "Screen", "Response.Type", "Response", 
                     "Reaction.Time", "Spreadsheet..Histogram", "Spreadsheet..Feedback", "Random_ID")]

df21_with_BL <- df21_with_BL %>%
  mutate(Response = as.numeric(as.character(Response))) %>%
  dplyr::filter(!is.na(Response))

df21_with_BL <- df21_with_BL %>% dplyr::filter(Response.Type != "info")

df21_with_BL$Screen <- ifelse(df21_with_BL$Trial.Number == 1 & (df21_with_BL$Display == "Mood " | df21_with_BL$Display == "Anxiety "), "BL_1",
                      ifelse(df21_with_BL$Trial.Number == 2 & (df21_with_BL$Display == "Mood " | df21_with_BL$Display == "Anxiety "), "BL_2", 
                             df21_with_BL$Screen))

df21_with_BL$m_hist <- ifelse(df21_with_BL$Spreadsheet..Histogram == "h1.png", 21,
                      ifelse(df21_with_BL$Spreadsheet..Histogram == "h2.png", 29,
                             ifelse(df21_with_BL$Spreadsheet..Histogram == "h3.png", 37,
                                    ifelse(df21_with_BL$Spreadsheet..Histogram == "h4.png", 46,
                                           ifelse(df21_with_BL$Spreadsheet..Histogram == "h5.png", 54,
                                                  ifelse(df21_with_BL$Spreadsheet..Histogram == "h6.png", 63,
                                                         ifelse(df21_with_BL$Spreadsheet..Histogram == "h7.png", 71,
                                                                ifelse(df21_with_BL$Spreadsheet..Histogram == "h8.png", 80, NA))))))))  


# get rid of the rows we don't need: practice runs, continue button presses etc. and only keep Trials, Anxiety and Mood that include all variables we are interested in:
df21_with_BL <- df21_with_BL %>%
  dplyr::filter(
    (Display == "Trials ") |
      (Display == "Anxiety ") |
      (Display == "Mood ")
  )

# # setting Mood and Anxiety trial numbers to match the trials starting from 1 (since we removed the baseline ones above)
df21_with_BL$Trial.Number <- ifelse(df21_with_BL$Display == 'Mood ' | df21_with_BL$Display == 'Anxiety ', df21_with_BL$Trial.Number - 2, df21_with_BL$Trial.Number)
# df21_with_BL$Display <- ifelse(df21_with_BL$Display == 'Mood ' | df21_with_BL$Display == 'Anxiety ', "Trials", df21_with_BL$Display)

final_df21_with_BL <- df21_with_BL[c("Trial.Number", "Display", "Screen", "Response", "Random_ID")]

final_df21_with_BL <- final_df21_with_BL %>%
  left_join(df21_spin %>% dplyr::select(Random_ID, mini_SPIN_total), by = "Random_ID")

final_df21_with_BL <- final_df21_with_BL %>%
  left_join(CESD_data_clean %>% dplyr::select(Random_ID, CESD_score, Depression_Threshold, Depression_status), by = "Random_ID")

final_df21_with_BL$Social_Anxiety <- ifelse(final_df21_with_BL$mini_SPIN_total >= 6, "high", "low")


```



\newpage 
# Mood over time 

```{r echo=FALSE, warning=FALSE, message=FALSE}
df21_BL_ax <- subset(final_df21_with_BL, Display == "Anxiety ")
df21_BL_H <- subset(final_df21_with_BL,Display == "Mood ")

ggplot(df21_BL_H, aes(x = Trial.Number, y = Response, color = Display, group = Display)) +
  geom_line(color = "blue") +
  geom_vline(xintercept = 1, linetype = "dashed", color = "red") + # Adding a vertical line at Trial.Number == 1
  theme_minimal() +
  labs(title = "Mood across time",
       x = "Trial Number",
       y = "Mood",
       color = "") +
  facet_wrap(~ Random_ID, ncol = 6) + 
  theme(strip.text = element_text(size = 6)) +  
  scale_x_continuous(breaks = seq(-1, 48, by = 10), limits = c(-1, 48)) +
  scale_y_continuous(breaks = seq(0, 100, by = 21), limits = c(0, 100))+
  theme(axis.text.x = element_text(size = 5),axis.text.y = element_text(size = 5))

```

\newpage 
# Anxiety over time 

```{r echo=FALSE, warning=FALSE, message=FALSE}
ggplot(df21_BL_ax, aes(x = Trial.Number, y = Response, color = Display, group = Display)) +
  geom_line(color = "blue") +
  geom_vline(xintercept = 1, linetype = "dashed", color = "red") + # Adding a vertical line at Trial.Number == 1
  theme_minimal() +
  labs(title = "Anxiety across time",
       x = "Trial Number",
       y = "Anxiety",
       color = "") +
  facet_wrap(~ Random_ID, ncol = 6) + 
  theme(strip.text = element_text(size = 6)) +  
  scale_x_continuous(breaks = seq(-1, 48, by = 10), limits = c(-1, 48)) +
  scale_y_continuous(breaks = seq(0, 100, by = 21), limits = c(0, 100))+
  theme(axis.text.x = element_text(size = 5),axis.text.y = element_text(size = 5))

```

\newpage 
# Prediction before performance over time 

Red line presents until what points histograms were presented (4 first trials only).

```{r echo=FALSE, warning=FALSE, message=FALSE}
ggplot(final_df21, aes(x = Trial.Number, y = Response_pred)) +
  geom_line(color = "blue") +
  geom_vline(xintercept = 5, linetype = "dashed", color = "red") + 
  theme_minimal() +
  labs(title = "Prediction before performance across time",
       x = "Trial Number",
       y = "Pre performance prediction",
       color = "") +
  facet_wrap(~ Random_ID, ncol = 6) + 
  theme(strip.text = element_text(size = 6)) +  
  scale_x_continuous(breaks = seq(1, 48, by = 10), limits = c(1, 48)) +
  scale_y_continuous(breaks = seq(0, 100, by = 21), limits = c(0, 100))+
  theme(axis.text.x = element_text(size = 5),axis.text.y = element_text(size = 5))

```


\newpage 
# Stress levels and social anxiety

```{r echo=FALSE, warning=FALSE, message=FALSE}
onetrial_final_df21 <- subset(final_df21, final_df21$Trial.Number == 1)


ggplot(onetrial_final_df21, aes(x = Social_Anxiety, y = Response_stress_level , fill = Social_Anxiety)) +
  geom_boxplot(outlier.colour = "black") +
  stat_boxplot(geom = "errorbar",
               width = 0.15) + 
  geom_point(color = "black", position = position_jitter(width = 0.1), alpha = 0.7) +
  theme_minimal() +
  # labs(x = "Display", y = "Response") +
  # scale_y_continuous(breaks = seq(0, 100, by = 10), limits = c(0, 100)) +
  # ggtitle("Average anxiety ratings in pilots 1 and 2 in socially anxious people") +
  xlab("") + 
  ylab("stress levels (0-10)") +
  # facet_wrap(~pilot_nr, scales = "free") +
  # scale_fill_manual(values = c("black", "purple", "darkgreen", "blue"))+
  # ylim(c(50, 100)) + 
  scale_y_continuous(breaks = seq(0, 10, by = 1), limits = c(1, 10))+
  theme(
    panel.grid.major = element_blank(),  # Removes major grid lines
    panel.grid.minor = element_blank(),  # Removes minor grid lines
    panel.border = element_blank(),      # Removes the border line
    axis.line = element_blank(),          # Removes axis lines
    plot.background = element_rect(fill = "white", colour = NA)   # Ensure plot background is white
  )

```

\newpage
# LME models for Mood and SubjPE

The best model seems to be: Mood ~ SubjPE + mini_SPIN_total + (SubjPE | Random_ID)

```{r echo=FALSE, warning=FALSE, message=FALSE}
model1 <- lme4::lmer(Response_H ~ Response_SubjPE +  (Response_SubjPE | Random_ID), data = final_df21, control=lmerControl(optimizer="bobyqa"))
model2 <- lme4::lmer(Response_H ~ Response_SubjPE +  mini_SPIN_total + (1 | Random_ID), data = final_df21, control=lmerControl(optimizer="bobyqa"))
model3 <- lme4::lmer(Response_H ~ Response_SubjPE + mini_SPIN_total + (Response_SubjPE | Random_ID), data = final_df21, control=lmerControl(optimizer="bobyqa"))

AIC(model1)
AIC(model2)
AIC(model3)
summary(model3)
coef_fixed <- fixef(model3)
intercept_Response_H <- coef_fixed[1]
slope_Response_H <- coef_fixed[2]
standard_beta_Response_SubjPE <- parameters:: standardise_parameters (model3)

# Hypothetical standard errors for intercept and slope
#SE_intercept <- 0.15  # Placeholder value
#SE_slope <- 0.43      # Placeholder value

model3_summary <- summary(model3)

# Extract the standard errors for the intercept and slope
SE_intercept <- model3_summary$coefficients["(Intercept)", "Std. Error"]
SE_slope <- model3_summary$coefficients["Response_SubjPE", "Std. Error"]

CI_multiplier <- 1.96  # 95% CI multiplier for a normal distribution

# Creating a sequence of `SubjPE` values for prediction
Response_SubjPE_range <- seq(min(final_df21$Response_SubjPE), max(final_df21$Response_SubjPE), length.out = 100)

# Calculating predicted Response_H and its CI bounds across the SubjPE range
predicted_Response_H <- intercept_Response_H + slope_Response_H * Response_SubjPE_range
CI_lower <- predicted_Response_H - CI_multiplier * sqrt(SE_intercept^2 + (Response_SubjPE_range^2 * SE_slope^2))
CI_upper <- predicted_Response_H + CI_multiplier * sqrt(SE_intercept^2 + (Response_SubjPE_range^2 * SE_slope^2))

# Preparing a data frame for ggplot
CI_data <- data.frame(Response_SubjPE=Response_SubjPE_range, CI_lower=CI_lower, CI_upper=CI_upper)


ggplot(final_df21, aes(x=Response_SubjPE, y=Response_H)) +
  # Adding points from your dataset
  # geom_point() +
  # Adding a regression line
  geom_abline(intercept=intercept_Response_H, slope=slope_Response_H, color="darkgoldenrod1", linetype="dashed", size=1) +
  # Adding the confidence interval with geom_ribbon
  geom_ribbon(data=CI_data, aes(x=Response_SubjPE, ymin=CI_lower, ymax=CI_upper), fill="gray80", alpha=0.5, inherit.aes = FALSE) +
  # Further customization
  xlab("Social PE") + 
  ylab("Mood") +
  ggtitle("", subtitle=paste("Estimated slopes of the association in n = ", length(unique(final_df21$Random_ID)))) +
  theme(plot.title=element_text(size=12), plot.subtitle=element_text(size=10),
        legend.title=element_text(size=12), legend.text=element_text(size=12),
        axis.title=element_text(size=13),
        axis.text=element_text(size=12),
        panel.background=element_blank(), panel.grid.major=element_blank(), panel.grid.minor=element_blank(),
        panel.border=element_rect(colour="black", fill=NA)) +
  annotate("label", x=12, y=55, label=paste("beta =", round(standard_beta_Response_SubjPE$Std_Coefficient[2],2), ", 95%CI =", 
                                            round(standard_beta_Response_SubjPE$CI_low[2],2), "-", round(standard_beta_Response_SubjPE$CI_high[2],2))) +
  scale_y_continuous(breaks=seq(0, 100, by=20), limits=c(0, 100)) +
  scale_x_continuous(breaks=seq(-80, 80, by=40), limits=c(-80, 80))

```

\newpage
# LME models for Anxiety and SubjPE

The best model seems to be: Anxiety ~ SubjPE + mini_SPIN_total + (SubjPE | Random_ID)

```{r echo=FALSE, warning=FALSE, message=FALSE}
model1 <- lme4::lmer(Response_Ax ~ Response_SubjPE +  (Response_SubjPE | Random_ID), data = final_df21, control=lmerControl(optimizer="bobyqa"))
model2 <- lme4::lmer(Response_Ax ~ Response_SubjPE +  mini_SPIN_total + (1 | Random_ID), data = final_df21, control=lmerControl(optimizer="bobyqa"))
model3 <- lme4::lmer(Response_Ax ~ Response_SubjPE + mini_SPIN_total + (Response_SubjPE | Random_ID), data = final_df21, control=lmerControl(optimizer="bobyqa"))

AIC(model1)
AIC(model2)
AIC(model3)

coef_fixed <- fixef(model3)
intercept_Response_Ax <- coef_fixed[1]
slope_Response_Ax <- coef_fixed[2]
standard_beta_Response_SubjPE <- parameters:: standardise_parameters (model3)

# Hypothetical standard errors for intercept and slope
#SE_intercept <- -0.03  # Placeholder value
#SE_slope <- -0.27      # Placeholder value

model3_summary <- summary(model3)

# Extract the standard errors for the intercept and slope
SE_intercept <- model3_summary$coefficients["(Intercept)", "Std. Error"]
SE_slope <- model3_summary$coefficients["Response_SubjPE", "Std. Error"]
CI_multiplier <- 1.96  # 95% CI multiplier for a normal distribution

# Creating a sequence of `SubjPE` values for prediction
Response_SubjPE_range <- seq(min(final_df21$Response_SubjPE), max(final_df21$Response_SubjPE), length.out = 100)

# Calculating predicted Response_Ax and its CI bounds across the SubjPE range
predicted_Response_Ax <- intercept_Response_Ax + slope_Response_Ax * Response_SubjPE_range
CI_lower <- predicted_Response_Ax - CI_multiplier * sqrt(SE_intercept^2 + (Response_SubjPE_range^2 * SE_slope^2))
CI_upper <- predicted_Response_Ax + CI_multiplier * sqrt(SE_intercept^2 + (Response_SubjPE_range^2 * SE_slope^2))

# Preparing a data frame for ggplot
CI_data <- data.frame(Response_SubjPE=Response_SubjPE_range, CI_lower=CI_lower, CI_upper=CI_upper)


ggplot(final_df21, aes(x=Response_SubjPE, y=Response_Ax)) +
  # Adding points from your dataset
  # geom_point() +
  # Adding a regression line
  geom_abline(intercept=intercept_Response_Ax, slope=slope_Response_Ax, color="darkgoldenrod1", linetype="dashed", size=1) +
  # Adding the confidence interval with geom_ribbon
  geom_ribbon(data=CI_data, aes(x=Response_SubjPE, ymin=CI_lower, ymax=CI_upper), fill="gray80", alpha=0.5, inherit.aes = FALSE) +
  # Further customization
  xlab("Social PE") + 
  ylab("Anxiety") +
  ggtitle("", subtitle=paste("Estimated slopes of the association in n = ", length(unique(final_df21$Random_ID)))) +
  theme(plot.title=element_text(size=12), plot.subtitle=element_text(size=10),
        legend.title=element_text(size=12), legend.text=element_text(size=12),
        axis.title=element_text(size=13),
        axis.text=element_text(size=12),
        panel.background=element_blank(), panel.grid.major=element_blank(), panel.grid.minor=element_blank(),
        panel.border=element_rect(colour="black", fill=NA)) +
  annotate("label", x=12, y=55, label=paste("beta =", round(standard_beta_Response_SubjPE$Std_Coefficient[2],2), ", 95%CI =", 
                                            round(standard_beta_Response_SubjPE$CI_low[2],2), "-", round(standard_beta_Response_SubjPE$CI_high[2],2))) +
  scale_y_continuous(breaks=seq(0, 100, by=20), limits=c(0, 100)) +
  scale_x_continuous(breaks=seq(-80, 80, by=40), limits=c(-80, 80))
```


\newpage 
# ICC for Mood with chocking
```{r echo=FALSE, warning=FALSE, message=FALSE}
test_icc_id <- lmer(Response_H ~  (1| Random_ID), data = 
                      final_df21, 
                    REML = FALSE, 
                    control = lmerControl(optimizer = "bobyqa")) 
icc_results_id <- performance::icc(test_icc_id)

icc_results_id
```

\newpage 
# ICC for Anxiety with chocking
```{r echo=FALSE, warning=FALSE, message=FALSE}
test_icc_id <- lmer(Response_Ax ~  (1| Random_ID), data = 
                      final_df21, 
                    REML = FALSE, 
                    control = lmerControl(optimizer = "bobyqa")) 
icc_results_id <- performance::icc(test_icc_id)

icc_results_id
```
